### 2017-09-19 icde/sec-alg.tex

\section{Ranking Computation}
\label{sec-alg}

In this section, we present our batch algorithm for computing scholarly article ranking based on our  model \ensemblerank.

%\marked{We first introduce the framework of our batch algorithm, and then explain the details.}

\subsection{Algorithm Framework}
\label{subsec-bat-alg}

Our batch algorithm \batensemble  combines the importance scores computed by the citation, venue and author components with Eq.~(\ref{eq-ensemble}). It takes as input academic graph data $D$ and an iteration threshold $\epsilon$ and returns the scholarly article ranking of $D$. It first constructs the citation and venue graphs $G^c(V^c,E^c)$ and $G^v(V^v,E^v)$. Then it computes the prestige and popularity of citation, venue and author components.
Finally, it combines the  prestige and popularity of the three components to produce the final ranking with Eq.~(\ref{eq-ensemble}).

%\stitle{Popularity computation}. It is easy to see that
For popularity computation, it is easy to see that
(a) the popularity of articles can be computed by scanning through all citations once and adding the freshness of citations to their corresponding articles, by Eq.~(\ref{eq-pop}), and (b) the popularity of venues in a specific year or authors is computed by averaging the popularity of the articles published in the venues or by the authors.
That is, the popularity computation can be done by scanning through all citations once.

%\stitle{Prestige computation}. As the prestige of authors is defined as the average prestige of their published articles,
For prestige computation, as the one of authors is defined as the average prestige of their published articles,
it suffices to scan through all author-article  relationships for computing the prestige of authors. The prestige of  articles and venues in a specific year is computed by TWPageRank on citation graphs and venue graphs, which is usually computed in an iterative manner~\cite{Brin98:PageRank} and is the most expensive computation. Hence, the key of the computation of our approach is a good solution for computing TWPageRank.

%While graphs derived from scholarly data is a special class of graphs in the sense that edges strictly follow {\em temporal order}, \eg an article can only cite others that are published earlier. In this section, we exploit this temporal order of scholarly data in ensemble computation, which significantly speeds up the efficiency.

\subsection{TWPageRank Computation}
\label{subsec-TWPageRank-computation}

The main result here is to speed up computing TWPageRank by exploiting the {\em temporal order} of scholarly articles.

\begin{claim}
\label{thm-prestige}
%TWPageRank can be computed in linear time in practice on scholarly data obeying a temporal order.
A block-wise PageRank computation method~\cite{Berkhin05} is a good choice for TWPageRank on scholarly data.
\end{claim}

The main idea of the block-wise PageRank computation is that each strongly connected component (\scc) of the input graph is treated as a block, and blocks are processed one by one following the {\em topological order} of the block-wise graph, \ie each node represents a block of the original graph~\cite{Berkhin05}.
We next show Claim~\ref{thm-prestige} by introducing and analyzing such a block-wise computation method.

%the directed and acyclic structure of the  can improve the efficiency of PageRank computation~\cite{Berkhin05,ObjectRank04}.

\stitle{Block-wise algorithm~\twprscc}.  It takes as input a citation or venue graph $G$ and an iteration threshold $\epsilon$, and returns the TWPageRank vector of $G$.
Moreover, to process an \scc instead of the entire graph, the edges of the citation or venue graph $G(V, E)$ are partitioned into the sets $E_i$ and $E_a$ of edges inside and across \sccs  such that $E_i\cap E_a = \emptyset$ and $E = E_i \cup E_a$.  The update rule in Eq.~(\ref{eq-twpr-update})  is revised accordingly to treat $E_i$ and $E_a$ separately as follows.

\vspace{-1ex}
\begin{scriptsize}
\begin{equation}\label{eq-prscc}
%\begin{split}
PR(v) =  d \sum_{(u,v)\in E_i} M_{u,v} PR(u)
   + d \sum_{(u,v)\in E_a} M_{u,v} PR(u) +  \frac{1-d}{n}.
%\end{split}
\end{equation}
\end{scriptsize}
%
\noindent
It first computes the block-wise graph $G'$ by treating \sccs in $G$ as single nodes, and then derives a topological order $O$ of nodes in $G'$. It then processes each \scc in the topological order  $O$ with Eq.~(\ref{eq-prscc}). Finally, it returns the TWPageRank vector. When processing an \scc, it iteratively updates the TWPageRank scores of the nodes in the \scc, and the iteration continues until the sum of TWPageRank score changes is less than $\epsilon\cdot\frac{|scc|}{|V|}$, where $|scc|$ is the number of nodes in the \scc. Note that there must exist a topological order $O$, as the block-wise graph is a directed acyclic graph~\cite{CormenLRS01}.

\eat{
%%% algorithm details
%%%%%%%%%%%%%%%%%%%%%Algorithm
\begin{figure}[tb!]
%\vspace{2ex}
\begin{center}
{\small
\begin{minipage}{3.36in}
\myhrule \vspace{-1.5ex}
\mat{0ex}{
%%%%%%%%%%%%%%%%%%%
{\sl Input:\/} \= citation graph or venue graph $G(V,E)$, iteration threshold $\epsilon$.\\
{\sl Output:\/} the TWPageRank vector of $G$. \\
\bcc \hspace{1.5ex}\=  $G'$ := the converted graph of $G$; \\
\icc \>  $O$ := topological order of $G'$; \\
\icc\>  \For each node $v'$ following $O$ \Do\\
\icc\>\hspace{2.5ex}\=  $scc$ := the corresponding SCC of $v'$; \\
\icc\>\> \While sum of changes of $PR(v)$ where $v\in scc$ exceeds $\frac{|scc|}{|V|} \epsilon$ \Do \\
\icc\>\>\hspace{3.5ex}\= update $PR(v)$ using Eq.~(\ref{eq-prscc}) where $v\in scc$; \\
\icc\> \Return $PR$.}
\vspace{-2.5ex} \myhrule
\end{minipage}
}
\end{center}
\vspace{-3ex}
\caption{\small Algorithm~\twprscc for computing TWPageRank} \label{alg-TWPageRank-venue}
\vspace{-3ex}
\end{figure}

%%%%%%%%%%%%Algorithm
}

%\stitle{Algorithm~\twprscc}.
%The block-wise algorithm to compute the TWPageRank vector for citation or venue graph $G$ is shown in Fig.~\ref{alg-TWPageRank-venue}.
%
%It first computes the converted graph $G'$  by treating SCCs in $G$ as single nodes (line 1), and then derives a topological order $O$ of $G'$ (line 2). It then iteratively updates the TWPageRank scores of nodes in each SCC in the topological order of $G'$ using  Eq.~(\ref{eq-prscc}) (lines 3--6), and finally returns the TWPageRank vector (line 7). More specifically, the iteration continues until the sum of TWPageRank score changes is less than $|scc|\cdot\epsilon/|V|$ (lines 5--6). Note that there must exist at least one topological order of $G'$ since $G'$ is a DAG.

\begin{cor} \label{prop-prscc}
The vector $PR$ returned by~\twprscc converges such that $||PR-PR^*||_1 < \epsilon$ where vector $PR^*$ is the convergent TWPageRank vector~\cite{Berkhin05}.
\end{cor}

\begin{proofSketch}
We first prove that the sum of changes after another iteration from $PR$, \ie $||d M^T PR + (1-d)e/n-PR||_1$, is smaller than $\epsilon$, and then prove that $||PR^*-PR||_1$ is smaller than the sum of changes. %(see~\cite {ERank-full} for details). % since $\epsilon > ||PR^+-PR||_1 = ||d\cdot M^T \cdot (PR-PR^*)||_1 + ||PR-PR^*||_1$.
\end{proofSketch}

%%% detailed proof sketch
\eat{
(1) We first prove that the sum of changes of TWPageRank vector after another iteration is less than $\epsilon$, \ie $||PR^+-PR||_1 < \epsilon$ where $PR^+=d\cdot M^T\cdot PR + \frac{1-d}{n}\cdot e$.
(2) Let $PR^-$ be the TWPageRank vector in the previous iteration of each SCC, and $PR_k$, $PR_k^-$ and $PR_k^+$ be the TWPageRank vectors of nodes within the $k$-th SCC in $PR$, $PR^-$ and $PR^+$, respectively. Note that SCCs are ordered such that the sequence of the corresponding nodes of SCCs follow the the topological order of $G'$
(3) We then show that the sum of changes $||PR-PR^-||_1$ is no more than $\epsilon$.
(4) We finally build the connection between $PR_k-PR_k^-$ and $PR_k^+-PR_k$ such that  $PR_k^+-PR_k=d\cdot M_{kk}^T\cdot(PR_k-PR_k^-)$, where $M_{kk}$ is the transition submatrix of nodes in the $k$-th SCC.
} %%%% eat

\stitle{Analysis of the block-wise algorithm}. While similar block-wise algorithms were originally proposed for Web graphs~\cite{Berkhin05}, we next show that they are even better for the TWPageRank computation associated with scholarly data.
%
The block-wise graph and its topological order can be done in $O(|V|+|E|)$ time~\cite{CormenLRS01}, and updating TWPageRank scores takes $O(|V|+|E_a|+t|E_i|)$ time as the edges in $E_a$ are only scanned once.
From these, we have the following.

\begin{lemma}
\label{prop-venue-time-complexity}
Given a citation graph or venue graph $G(V, E)$, algorithm \twprscc runs in  $O(|V|+|E_a|+t|E_i|)$ time, where $t$ is  the maximum number of iterations among all \sccs.
\end{lemma}

Recall that $t$ is very likely to be in the scale of tens to hundreds~\cite{Brin98:PageRank}.
%, and (b) $O(|V|+|E_a|+t|E_i|)$ is essentially $O(|V|+|E|+(t-1)|E_i|)$ as $|E_i|$ + $|E_a|$  = $|E|$.
Hence, the efficiency of block-wise algorithm \twprscc is mainly affected by $|E_i|$, \ie the smaller $|E_i|$ is, the faster algorithm \twprscc is.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[tb!]
%\vspace{-2ex}
\begin{center}
\caption{\small Statistics of citation/venue graphs and Web graphs~\cite{LeskovecLDM09}}
\label{tab-batch}
\begin{small}
\vspace{-.5ex}
\begin{tabular}{|c|c|c|c|c|}
\hline
 &   &  & \multicolumn{1}{c|}{\bf Largest }   & \multicolumn{1}{c|}{\bf \scc }    \\
\raisebox{1ex}[0pt]{\bf Graphs}      & \multicolumn{1}{c|}{\raisebox{1ex}[0pt]{\bf Nodes}} & \multicolumn{1}{c|}{\raisebox{1ex}[0pt]{\bf Edges}} &
\multicolumn{1}{c|}{\bf $|\scc|$} &  \multicolumn{1}{c|}{\bf edge ratio}    \\
\hline \hline
\aan  & 18,041/565 & 82.9K/22.5K &  20/18  & 0.9\%/2.8\%      \\  %\hline
\aminer  & 3.14M/56K & 14.3M/7.1M   & 23/1.5 &  1.6\%/2.1\%     \\ %\hline    % 1.5K = 1467
\magdata  & 127M/584K & 526M/162M & 351/10K & 0.1\%/1.8\%    \\ \hline
web-BS  &  685,230 & 7,600,595 & \multicolumn{1}{c|}{334,857} & \multicolumn{1}{c|}{59.51\%}\\  %\hline
web-G  & 875,713 & 5,105,039 & \multicolumn{1}{c|}{434,818} & \multicolumn{1}{c|}{66.98\%} \\  %\hline
\hline
\end{tabular}
\end{small}
\end{center}
\vspace{-5ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

It is well-known that article citations obey a natural temporal order, \ie an article only cites those published earlier, and it is really rare for the mutual citations between two articles published in the same time. That is, $|E_i|$ is essentially small for the citation graphs of scholarly articles.
%
To verify this observation, we also collect the statistics of citation graphs, venue graphs and Web graphs (shown in Table~\ref{tab-batch}), where Web graphs are extracted from berkely.edu and stanford.edu domains in 2002 and from the Google programming contest in 2002, respectively~\cite{LeskovecLDM09}.
Due to the existence of the ``bow tie'' structure and the giant \scc in Web graphs~\cite{BroderKMRRSTW00}, the edge ratios $|E_i|/|E|$ are greater than 59\% for both Web graphs. In contrast, the \sccs in citation and venue graphs are quite small as a result of the temporal order of citation, and $|E_i|/|E|$ is less than 3\% for all tested citation and venue graphs.
%
This specific structure in scholarly data has long been ignored in the literature, which has a large impact on the running time. Taking $t=100$ for example, algorithm \twprscc needs to scan through $3|E|$ and $4|E|$ edges on citation and venue graphs, respectively, while over $59|E|$ edges on Web graphs.

By Corollary \ref{prop-prscc}, Lemma \ref{prop-venue-time-complexity} and the  above analysis of our block-wise algorithm, we have informally established Claim~\ref{thm-prestige}.

\eat{
In the Web graph with the ``bow tie" structure~\cite{BroderKMRRSTW00}, the nodes in the largest SCC amount to 51\% of the entire graph in 2014~\cite{MeuselVLB14}, and $|E_i|$ is already 25\% of $|E|$ even when edges are randomly generated.
%
However, the situation is completely different on scholarly data obeying temporal order in the sense that an article can only cite the ones published earlier. Moreover, it is pretty rare that two articles published in the same time mutually cite each other. Hence, both the citation graph and the venue graph can be treated as almost-DAGs~\cite{ObjectRank04}.
%
Indeed, on (\aan, \aminer, \magdata), the nodes in the largest SCC amount to (0.11\%, 0.00073\%, 0.00028\%) of the entire citation graph, and $|E_i|$ is (0.92\%, 0.14\%, 0.063\%) of $|E|$, respectively. %Here we present statistics of citation graphs since citation graphs are typically much larger than corresponding venue graphs and occupy most computation.
}

%Note that $O(|V|+|E_b|+t |E_w|)$ remains linear to $|E|$ in practice since $|E_w|$ is typically much smaller than $|E|$ (\eg 0.92\%) for scholarly data obeying a temporal order.

%\stitle{Temporal order}. Scholarly data follows temporal order in the sense that an article can only cite the articles published earlier, and, moreover, it is pretty rare that two articles published in the same time mutually cite each other. Hence, both the citation graph and the venue graph can be treated as a almost directed acyclic graph (DAG)~\cite{ObjectRank04}. Indeed, they become DAGs by replacing their strongly connected components (SCCs) with single nodes~\cite{CormenLRS01}.

%More specifically, the citation graph and the venue graph have the following two characteristics:
%a) the size of the largest SCC is much less than the one of the entire graph,
%and, as the result of that, b) the number of edges inside SCCs is much less than the total number of edges.

%\subsubsection{Prestige of authors}
%\label{subsubsec-prs-A}
%\subsubtitle{Prestige of authors}.

%\subsection{Time \& Space Complexity Analyses}

\stitle{Time \& space complexity analyses of the batch algorithm}.
%
By Lemma~\ref{prop-venue-time-complexity} and the analyses in Section~\ref{subsec-bat-alg}, one can verify that algorithm \batensemble takes $O(|V^c|+|V^v|+|E^c_a|+|E^v_a|+t|E^c_i|+t|E^v_i|+|PA|)$ time, where $|PA|$ is the total number of author-article relationships, and takes $O(7|V^c|+2|V^c{'}|+4|V^v|+2|V^v{'}|+|E^c|+|E^c{'}|+|E^v|+|E^v{'}|+2|A|+|D|)$ space, where $|A|$ is the number of authors and $|D|$ is the size of academic graph data $D$.
% TWPageRank on V^c: 3|V^c| + |E^c| + 2|V^c{'}| + |E^c{'}|
% TWPageRank on V^v: 3|V^v| + |E^v| + 2|V^v{'}| + |E^v{'}|
% Prestige of authors: |A|
% popularity: |V^c| + |V^v| + |A|
% Importance scores: 3|V^c|
% D: academic graph data, i.e., |PA|, |PV|, paper years, ect
% total: 7|V^c| + |E^c| + 2|V^c{'}| + |E^c{'}| + 4|V^v| + |E^v| + 2|V^v{'}| + |E^v{'}| + 2|A| + |D|

The key of algorithm \batensemble is to compute TWPageRank with algorithm \twprscc.
Compared with the traditional power method~\cite{Brin98:PageRank}, our block-wise algorithm \twprscc uses $(2|V^c{'}|+|E^c{'}|)$ and $(2|V^v{'}|+|E^v{'}|)$ extra space to store the block-wise graphs $G^c{'}(V^c{'},E^c{'})$ of $G^c$ and $G^v{'}(V^v{'},E^v{'})$ of $G^v$ and their topological orders, while speeds up computation by $O((t-1)(|E^c_a|+|E^v_a|))$.

%. That is, \batensemble speeds up computation with a reasonable extra space.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% original ensemble version
\eat{
\subsection{Citation Ensemble Computation}
\label{subsec-citation}

%%% computation overview
We first present the computation of the citation ensemble.

It is easy to see that the popularity of articles can be computed by scanning all citations once and adding the freshness of citations to their corresponding articles,
by Eq.~(\ref{eq-pop}).
%
The prestige of articles is computed with TWPageRank on citation graphs, which occupies most computation cost of the citation ensemble.
Nevertheless, we speed-up  TWPageRank computation on citation graphs by exploiting the temporal order of scholarly data.

The main result here is stated as follows.

\begin{theorem}
\label{thm-citation}
TWPageRank on a citation graph $G^c(V^c, E^c)$ can be computed in $O(|V^c|+|E^c|)$ time.
\end{theorem}

%%% citation graph with temporal order --> the rare case of loops --> approximately a DAG
\stitle{Topological ordering}. The edges of the citation graph strictly follow temporal order, in the sense that an article can only cite the articles published earlier, and, moreover, it is pretty rare that two articles published in the same time mutually cite each other.
Hence, the citation graph $G^c$ can be treated as a directed acyclic graph with few side effects.
%
Accordingly, there exits a {\em topological order} for the nodes in a citation graph, \ie a sequence of its nodes such that every edge is directed from earlier to later.

We next prove Theorem~\ref{thm-citation} by providing such an algorithm with the desired property, by using the temporal order on a citation graph.

%%%%%%%%%%%%%%%%%%%%%Algorithm
\begin{figure}[tb!]
%\vspace{2ex}
\begin{center}
{\small
\begin{minipage}{3.36in}
\myhrule \vspace{-2ex}
\mat{0ex}{
%%%%%%%%%%%%%%%%%%%
%{\bf Algorithm}~\twprdag($G^c$) \\ %\hspace{6ex}/* $G$ is a DAG */
{\sl Input:\/} \= citation graph $G^c(V^c,E^c)$.\\
{\sl Output:\/} the TWPageRank vector of $G^c$. \\
\bcc \hspace{1.5ex}\=  $O$ := the topological order of $G^c$; \\
\icc\>  \For each node $v$ following $O$ \Do\\
\icc\>\hspace{2.5ex}\=  update $PR(v)$ using Eq.~(\ref{eq-twpr}); \\
\icc\> \Return $PR$.}
\vspace{-3ex} \myhrule
\end{minipage}
}
\end{center}
\vspace{-3ex}
\caption{\small Algorithm for TWPageRank on citation graphs} \label{alg-TWPageRank-citation}
\vspace{-3ex}
\end{figure}
%%%%%%%%%%%%Algorithm

\stitle{Algorithm \twprdag}. The algorithm is presented in Fig.~\ref{alg-TWPageRank-citation}, which takes as input a citation graph $G^c$ and returns its corresponding TWPageRank vector $PR$. It first computes a topological order of $G^c$ since $G^c$ is acyclic (line 1).
By the topological order with nodes in higher oder first, it updates the TWPageRank score of each node with the update rule in Eq.~(\ref{eq-twpr}) (lines 2--3), and finally  it returns the computed TWPageRank vector (line 4).
%such that node $v$ occurs iff every node $u$ that points to $v$, \ie $(u,v)\in E$, has already occurred.

%%% algorithm analysis: correctness & complexity

We now show that \twprdag is indeed the desired algorithm.

\begin{lemma}
\label{prop-nonitercomputing}
The TWPageRank vector $PR$ returned by \twprdag equals to the convergent TWPageRank vector $PR^*$.
\end{lemma}

\begin{proofSketch}
We have $PR^* = d M^T PR^* + \frac{1-d}{n} e$, as $PR^*$ is the convergent TWPageRank vector. Hence, we also have
\begin{small}
\begin{equation}
PR^*(v)=d \sum_{(u,v)\in E^c} M_{u,v} PR^*(u) + \frac{1-d}{n}.
\end{equation}
\end{small}

\vspace{-1ex}
Consider a topological order $v_1/\dots/v_n$ on citation graph $G^c(V^c,$ $E^c)$, we then prove $PR(v_k)=PR^*(v_k)$ ($k\in[1,n]$) by induction, from which we have the conclusion (see~\cite {ERank-full} for details).
\end{proofSketch}

\begin{lemma}
\label{prop-citation-time-complexity}
Given a citation graph $G^c(V^c, E^c)$, algorithm \twprdag runs in $O(|V^c|+|E^c|)$ time.
\end{lemma}

\begin{proof}
The topological order of citation graph $G^c$ can be computed in  $O(|V^c|+|E^c|)$ time~\cite{CormenLRS01} (line 1), and the updating step (lines 2--3) can be done in $O(|V^c|+|E^c|)$ time as well.
\end{proof}

%\ref{prop-converg},
By Lemmas \ref{prop-nonitercomputing} \& \ref{prop-citation-time-complexity}, we have shown Theorem~\ref{thm-citation}.

\stitle{Remark}. Observe that by employing the topological order, the time complexity of TWPageRank on citation graphs is significantly reduced to $O(|V^c|+|E^c|)$, instead of $O(t(|V^c|+|E^c|))$ that is closely related to the number $t$ of iterations.

\eat{
In this case the transition matrix $M$ of $G$ is organized as follows:
\begin{equation}
M=\left(
\begin{array}{ccccc}
\textbf{0} &  & \cdots &  &  \textbf{0} \\
M_{10}     &  \textbf{0} &  &  &  \\
M_{20}     &  M_{21}   &  \ddots &      & \vdots \\
\cdots     &        &       & \textbf{0} &  \\
M_{L0}     &    M_{L1}   &   \cdots   &     M_{L(L-1)}      & \textbf{0}  \\
\end{array}
\right) ,
\end{equation}
where $M_{ij}$ represents the transition between $V_i$ and $V_j$ and $\textbf{0}$ denotes all-zero matrices of proper sizes. Hence $M$ is a strictly lower triangular matrix, and we have:
}

\subsection{Venue Ensemble Computation}
\label{subsec-venue}

%%% computation overview
We next present the computation of the venue ensemble.
The popularity of venues in a specific year, is computed by averaging the popularity of the corresponding articles (given by the citation ensemble) published in the venues.

The prestige of venues in a specific year  is also computed by TWPageRank on a venue graph  $G^v(V^v, E^v)$. However, mutual citations are common on the venue graphs, \eg journal articles in a specific year may be published in different issues and/or numbers, and, hence, two journal venues in the same year can cite each other. That is, the venue graph is cyclic, and the linear algorithm on citation graphs does not work on venue graphs.

Nevertheless, articles typically cite those closely related articles, \eg from the same field of study. That is, there is a possibility of grouping venues.
It is known that a graph becomes acyclic by replacing its strongly connected components (SCCs) with single nodes~\cite{CormenLRS01}.
This motivates us to revise the algorithm by processing an SCC, instead of a single node, at each time, by which we can exploit the temporal order of scholarly data again.
%
More specifically, the edges of venue graph $G^v$ is first partitioned into two disjoint sets $E^v_w$ and $E^v_b$ with $E^v=E^v_w \cup E^v_b$, where $E^v_w$ and $E^v_b$ are sets of edges inside and across SCCs, respectively. Further, the update rule is revised by treating $E^v_b$ and $E^v_w$ differently as follows.
\begin{small}
\begin{equation}\label{eq-prscc}
PR(v) =  d \sum_{(u,v)\in E^v_w} M_{u,v} PR(u)
  + d \sum_{(u,v)\in E^v_b} M_{u,v} PR(u) +  \frac{1-d}{n}.
\end{equation}
\end{small}

\vspace{-2ex}
The main result here is stated as follows.

\begin{theorem}
\label{thm-venue}
TWPageRank on a venue graph $G^v(V^v, E^v)$ can be done in  $O(|V^v|+|E^v_b|+t|E^v_w|)$ time.
\end{theorem}

We next prove Theorem~\ref{thm-venue} by providing such an algorithm with the desired property, which uses the temporal order, and
processes an SCC, instead of a single node, at each time on a venue graph.

%%% algorithm details
%%%%%%%%%%%%%%%%%%%%%Algorithm
\begin{figure}[tb!]
%\vspace{2ex}
\begin{center}
{\small
\begin{minipage}{3.36in}
\myhrule \vspace{-2ex}
\mat{0ex}{
%%%%%%%%%%%%%%%%%%%
%{\bf Algorithm}~\twprscc($G^v$, $\epsilon$) \\
{\sl Input:\/} \= venue graph $G^v(V^v,E^v)$, iteration threshold $\epsilon$.\\
{\sl Output:\/} the TWPageRank vector of $G^v$. \\
\bcc \hspace{1.5ex}\=  $G'$ := the converted graph of $G^v$; \\
\icc \>  $O$ := topological order of $G'$; \\
\icc\>  \For each node $v'$ following $O$ \Do\\
\icc\>\hspace{2.5ex}\=  $scc$ := the corresponding SCC of $v'$; \\
\icc\>\> \While sum of changes of $PR(v)$ where $v\in scc$ exceeds $\frac{|scc|}{|V^v|} \epsilon$ \Do \\
\icc\>\>\hspace{3.5ex}\= update $PR(v)$ using Eq.~(\ref{eq-prscc}) where $v\in scc$; \\
\icc\> \Return $PR$.}
\vspace{-3ex} \myhrule
\end{minipage}
}
\end{center}
\vspace{-3ex}
\caption{\small Algorithm for TWPageRank on venue graphs} \label{alg-TWPageRank-venue}
\vspace{-3ex}
\end{figure}

\eat{%%%%%%%%%%%%%%
{\bf Algorithm}~\batensemble\\
\sttab {\sl Input:\/} \= academic graph data $D$, iteration threshold $\epsilon$.\\
{\sl Output:\/} scholarly article ranking $R$ of $D$. \\
%%% \icc \hspace{1.5ex}\= extract article (venue) citation graph $G_c$ ($G_v$) from D; \\
\icc \hspace{1.5ex}\= compute prestige of citation ensemble with \twprdag($G_c$); \\
\icc\> compute prestige of venue ensemble with \twprscc($G_v$, $\epsilon$);\\
\icc\> compute prestige of author ensemble based on citation ensemble;\\
\icc\> compute popularity of three ensembles;\\
\icc\> \Return ranking $R$ based on three ensembles;}

%%%%%%%%%%%%Algorithm

\stitle{Algorithm~\twprscc}.
The SCC-based algorithm to compute the TWPageRank vector for venue graph $G^v$ is shown in Fig.~\ref{alg-TWPageRank-venue}.

It first computes the converted graph $G'$  by treating SCCs in $G^v$ as single nodes (line 1), and then derives a topological order $O$ of $G'$ (line 2). It then iteratively updates the TWPageRank scores of nodes in each SCC in the topological order of $G'$ using  Eq.~(\ref{eq-prscc}) (lines 3--6), and finally returns the TWPageRank vector (line 7). More specifically, the iteration continues until the sum of TWPageRank score changes is less than $\frac{|scc|}{|V^v|} \epsilon$ (lines 5--6).

\begin{lemma} \label{prop-prscc}
The TWPageRank vector $PR$ returned by~\twprscc converges such that $||PR-PR^*||_1 < \epsilon$, where $PR^*$ is the convergent TWPageRank vector.
\end{lemma}

\begin{proofSketch}
%We first prove that $||PR^+-PR||_1 < \epsilon$ where $PR^+=d\cdot M^T\cdot PR + \frac{1-d}{n}\cdot e$.
%We then prove that $||PR^*-PR||_1 < ||PR^+-PR||_1$.
We first prove that the sum of changes after another iteration from $PR$, \ie $||d M^T PR + \frac{1-d}{n} e-PR||_1$, is smaller than $\epsilon$, and then prove that $||PR^*-PR||_1$ is smaller than the sum of changes (see~\cite {ERank-full} for details). % since $\epsilon > ||PR^+-PR||_1 = ||d\cdot M^T \cdot (PR-PR^*)||_1 + ||PR-PR^*||_1$.
\end{proofSketch}

%%% detailed proof sketch
\eat{
(1) We first prove that the sum of changes of TWPageRank vector after another iteration is less than $\epsilon$, \ie $||PR^+-PR||_1 < \epsilon$ where $PR^+=d\cdot M^T\cdot PR + \frac{1-d}{n}\cdot e$.
(2) Let $PR^-$ be the TWPageRank vector in the previous iteration of each SCC, and $PR_k$, $PR_k^-$ and $PR_k^+$ be the TWPageRank vectors of nodes within the $k$-th SCC in $PR$, $PR^-$ and $PR^+$, respectively. Note that SCCs are ordered such that the sequence of the corresponding nodes of SCCs follow the the topological order of $G'$
(3) We then show that the sum of changes $||PR-PR^-||_1$ is no more than $\epsilon$.
(4) We finally build the connection between $PR_k-PR_k^-$ and $PR_k^+-PR_k$ such that  $PR_k^+-PR_k=d\cdot M_{kk}^T\cdot(PR_k-PR_k^-)$, where $M_{kk}$ is the transition submatrix of nodes in the $k$-th SCC.
} %%%% eat

\begin{lemma}
\label{prop-venue-time-complexity}
Given a venue graph $G^v(V^v, E^v)$, algorithm \twprscc runs in  $O(|V^v|+|E^v_b|+t|E^v_w|)$ time, where $t$ is  the maximum number of iterations among all SCCs.
\end{lemma}

\begin{proof}
Observe the following. (1) The converted graph $G'$ and topological order $O$ can be computed in $O(|V^v|+|E^v|)$~\cite{CormenLRS01} (lines 1,2), and (2) updating the TWPageRank scores takes $O(|V^v|+|E^v_b|+t |E^v_w|)$ where edges in $|E^v_b|$ are only scanned once (lines 3--6). Note that $|E^v_w|$ is typically much smaller than $|E^v|$ for scholarly article data obeying a temporal citation order in practice.
\end{proof}

By Lemmas \ref{prop-prscc} \& \ref{prop-venue-time-complexity}, we have shown Theorem~\ref{thm-venue}.

\subsection{Author Ensemble Computation}

As the prestige (popularity) of authors is defined as the average prestige (popularity) of their published articles, it suffices to scan through all author-article  relationships for computing both the prestige and the popularity of authors.

\subsection{The Complete Batch Algorithm}
\label{subsec-bat-alg}
We finally present the complete batch algorithm \batensemble, which combines the computation of the citation, author and venue ensembles with Eq.~(\ref{eq-ensemble}). It takes as input academic graph data $D$ and an iteration threshold $\epsilon$ and returns the scholarly article ranking of $D$. It first constructs the citation and venue graphs $G^c(V^c,E^c)$ and $G^v(V^v,E^v)$. Then it computes the prestige and popularity of citation, venue and author ensembles.
Finally, it combines the prestige and popularity of three ensembles to produce the final ranking.

\stitle{Time \& space complexity analyses}. By the analyses above and Lemmas~\ref{prop-citation-time-complexity} \& \ref{prop-venue-time-complexity}, it is easy to verify that algorithm \batensemble runs in $O(|V^c|+|E^c|+|V^v|+|E^v_b|+t|E^v_w|+|PA|)$, where $|E^v_w|$ is the number of edges inside SCCs of $G^v$ and $|PA|$
is the total number of author-article relationships.

%Observe the following. (1) Procedures \twprdag and \twprscc run in $O(|V_c|+|E_c|)$ and $O(|V_v|+|E_v|+t\cdot|E_v^w|)$, respectively (lines 12--13). (2) Computing prestige of author ensemble costs $O(|PA|)$ time (line 14). (3) Computing popularity of three ensembles costs $O(|V_c|+|E_c|+|PA|)$ time (line 15). Finally, (4) generating ranking $R$ costs $(|V_c|+|PA|)$ time.

Compared with the traditional power method, algorithm \batensemble uses (a)  $|V^c|$ extra space to store the topological order of $G^c$, (b) $(2|V'|+|E'|)$ extra space to store the converted graph $G'(V',E')$ of $G^v$ and its topological order, and (c) $|V^c|$ space is saved for the TWPageRank vector of $G^c$. To conclude, algorithm \batensemble only uses limited extra space to speed-up computation.

%\subsection{Author Ensemble}
%\label{subsec-author}

%\subsection{Optimization Techniques}
%\label{subsec-opt}

%%%% dangling node manipulation
\eat{
The article citation graph has a strong possibility to contain dangling nodes which do not have any out-links, \ie citations, due to factors such as dataset coverage and data missing.
These dangling nodes are usually handled by adding artificial edges to all nodes in the graph such that its prestige is propagated to all node. For Web pages this can be interpreted as users randomly select a new page to visit when current one does not contain any out-link to follow. However, dangling articles are more likely because of missing citations. It is inappropriate to propagate the prestige of dangling articles to others which will erroneously increase the prestige of most articles. Hence, we do not manipulate the dangling nodes on the article citation graph.
The relationship between the two PageRank vectors with or without manipulating dangling nodes is given by Proposition~\ref{prop-prvector}:
\begin{prop} \label{prop-prvector}
PageRank vectors with or without manipulating dangling nodes can derive the other through scaling.
\end{prop}
}

%%% proof of citation graph is a DAG
\eat{
\begin{proof}
Suppose there exists a circle $v_1/v_2/\dots/v_k/v_1$ in $G$ (where $k>1$). Edges in the circle imply $T_{v_1}<T_{v_2}<\dots <T_{v_k}<T_{v_1}$, where $T_{v_i}<T_{v_j}$ means $T_{v_i}$ is strictly earlier than $T_{v_j}$. However, this cannot be true since there does not exist $T_{v_k}$ which is both strictly earlier and later than $T_{v_1}$ in the same time. Hence, $G$ is acyclic and further a DAG since $G$ is directed.
\end{proof}
} %%%%eat

}

### 2017-09-19 icde/sec-alg.tex

@@
 \label{tab-batch}
-\begin{small}
+%\begin{small}
 \vspace{-.5ex}
@@
 \end{tabular}
-\end{small}
+%\end{small}
 \end{center}
@@
 
-It is well-known that article citations obey a natural temporal order, \ie an article only cites those published earlier, and it is really rare for the mutual citations between two articles published in the same time.
+\stitle{Observation.} It is well-known that article citations obey a natural temporal order, \ie an article only cites those published earlier, and it is really rare for the mutual citations between two articles published in the same time.
 That is, $|E_i|$ is essentially small for the citation graphs of scholarly articles.
-%
+
 To verify this observation, we also collect the statistics of citation graphs, venue graphs and Web graphs (shown in Table~\ref{tab-batch}), where Web graphs are extracted from berkely.edu and stanford.edu domains in 2002 and from the Google programming contest in 2002, respectively~\cite{LeskovecLDM09}.
-Due to the existence of the ``bow tie'' structure and the giant \scc in Web graphs~\cite{BroderKMRRSTW00}, the edge ratios $|E_i|/|E|$ are greater than 59\% for both Web graphs.
+Due to the existence of the ``bow tie'' structure and the giant \scc in Web graphs~\cite{BroderKMRRSTW00}, the edge ratios $|E_i|/|E|$ are greater than 59\% for Web graphs.
 In contrast, the \sccs in citation and venue graphs are quite small as a result of the temporal order of citation, and $|E_i|/|E|$ is less than 3\% for all tested citation and venue graphs.
 %
-This specific structure in scholarly data has long been ignored in the literature, which has a large impact on the running time.
-Taking $t=100$ for example, algorithm \twprscc needs to scan through $3|E|$ and $4|E|$ edges on citation and venue graphs, respectively, while over $59|E|$ edges on Web graphs.
+This specific structure in scholarly data has been ignored in the literature, and has a positive impact on computations.
+Taking $t=100$ for example, algorithm \twprscc needs to scan $3|E|$ and $4|E|$ edges on citation and venue graphs, respectively, but over $59|E|$ edges on Web graphs.
 

### 2017-09-19 icde/sec-incAlg.tex

\section{Dynamic Ranking Computation}
\label{sec-incAlg}

Scholarly articles are dynamic and continuously growing, and it is impractical to recompute ranking from scratch once they get updated. In this section, we present an incremental algorithm for our ranking model \ensemblerank.

\subsection{Incremental Algorithm Framework}
\label{subsec-inc-alg}

Our incremental algorithm \incensemble incrementally computes the popularity and prestige of scholarly articles.
We consider that an update $\Delta$ = $\Delta V\cup\Delta E$ is added to a   (citation or venue) graph $G(V, E)$,
and the resulting graph is $G^+(V\cup\Delta V, E\cup\Delta E)$, where
$\Delta V$ is a set of nodes with $\Delta V\cap V = \emptyset$, and $\Delta E$ is a set of directed edges on $\Delta V$ and from $\Delta V$ to $V$ only, as article citation relationships obey a natural temporal order, \ie an article only cites those published earlier, and it is rare for the mutual citations between two articles published in the same time.

\stitle{Incremental popularity computation}.
The popularity of venues and authors is computed along the same lines as their batch counterparts of algorithm \batensemble,
as almost all venues and authors are affected  by the definitions of the popularity of venues and authors.

As the popularity of articles is defined as the freshness sum of all their citations, it is convenient to maintain in a dynamic scenario. Consider an updated citation graph $G^{c,+}(V^c\cup\Delta V^c, E^c\cup\Delta E^c)$ of $G^c(V^c, E^c)$, and the updated popularity $Pop_{c}^+(v)$ can be computed as:

\vspace{-1ex}
\begin{small}
\begin{equation}\label{eq-inc-pop}
Pop_c^+(v) = Pop_c(v) {e^{\sigma (T^+_0-T_0)}} + \sum_{(u,v)\in \Delta E^c} {e^{\sigma (T^+_0-T_u)}},
\end{equation}
\end{small}
\noindent
where $Pop_c(v)$ (resp. $Pop_c^+(v)$) is the popularity of node $v$ on $G^c$ (resp. $G^{c,+}$), and
 $T_0$ (resp. $T^+_0$) is the current time in $G^c$ (resp. $G^{c,+}$).
%
By Eq.~(\ref{eq-inc-pop}), it is easy to see that it takes $O($ $|V^c|+|\Delta V^c|+|\Delta E^c|)$ time to update the popularity.
%This further shows that Eq.~(\ref{eq-inc-pop}) is a desired solution for popularity maintenance.

\stitle{Incremental prestige computation}.
The prestige of authors is computed along the same lines as the batch algorithm \batensemble,
as almost all authors are affected  by the definition of the prestige of authors.
%
For articles and venues, we propose an incremental algorithm to maintain their prestige.

%We first present the incremental  prestige computation. Again, it differs for the prestige of articles and venues in a specific year and the one of authors. We finally present the complete incremental algorithm \incensemble, which is similar to the batch algorithm \batensemble, except that (1) it uses algorithm \inctwprscc to incrementally compute the prestige of articles and venues, and (2) it incrementally computes the popularity of articles based on Eq.~(\ref{eq-inc-pop}).

\subsection{Incremental TWPageRank Computation}
\label{subsec-incTWPageRank-computation}

%\subsubsection{Prestige of articles and venues in a specific year}
%\label{subsubsec-incprs-CV}
%\subsubtitle{Prestige of articles and venues in a specific year}.
%We expand $M$ and $PR$ to the same sizes as $M^+$ and $PR^+$, respectively, by filling zeros, and let $\Delta M=M^+ - M$ and $\Delta PR = PR^+ - PR$.

Consider a citation or venue graph $G(V, E)$, its TWPageRank vector $PR$ and the topological order $O$ of its block-wise graph. Given an update $\Delta$ = $\Delta V\cup\Delta E$ to $G$, the incremental prestige computation for articles and venues in a specific year is to compute the TWPageRank vector $PR^+$ on the updated graph $G^+(V\cup\Delta V, E\cup\Delta E)$.

\stitle{Auxiliary data structure maintenance}.
Two auxiliary data structures in the batch algorithm~\twprscc need to be maintained : (a) on the block-wise graph,  a mapping that, given a node of graph $G$, returns the index of the \scc to which it belongs, and (b) the topological order of the nodes in the block-wise graph.
%
Observe that these auxiliary data structures can be easily maintained as follows.

%the idea is to divide $G$ into affected and unaffected areas such that TWPageRank scores of nodes in affected and unaffected areas are updated accordingly.

\sstab(1) The block-wise graph of $G^+$ needs to be computed, whose \sccs consist of the \sccs in $G$ and \sccs in the induced subgraph $G^+[\Delta V]$, as  the edges of $\Delta E$ are  on nodes in $\Delta V$ and from $\Delta V$  to $V$ only. Hence, only those new \sccs in $G^+[\Delta V]$ need to be computed.

\sstab(2) The updated topological order $O^+=\Delta O/O$, where $\Delta O$ is the topological order of the block-wise graph of induced subgraph $G^+[\Delta V]$. Hence, only $\Delta O$ needs to be computed. One can easily verify the following.

\begin{prop} \label{lemma-inc-topo}
 $O^+=\Delta O/O$ is indeed a valid topological order of the block-wise graph of $G^+$.
\end{prop}

\begin{proofSketch}
We prove that for each edge $(u,v)$ in the block-wise graph of $G^+$, node $u$ comes before $v$ in $O^+$, and the conclusion follows by the definition of topological order.
\end{proofSketch}

\eat{
\begin{proof}
Let $E'_c$ denote the set of cross edges from $V'_\Delta$ to $V'$.
It suffices to show that for each $(u,v)\in E'\cup E'_\Delta \cup E'_c$, $u$ comes before $v$ in $O^+$,
which obviously holds (1) for  $E'\cup E'_\Delta$ as $O$ and $\Delta O$ are topological orders of $G'$ and $G'_\Delta$, respectively, and (2) for $E_{c}'$ as nodes in $G'_\Delta$ come before nodes in $G'$.
\end{proof}
} %%%%%%%%%% for eat

%%%%%%%%%%%%%%%%%%%%%Algorithm
\begin{figure}[tb!]
%\vspace{2ex}
\begin{center}
{\small
\begin{minipage}{3.36in}
\myhrule \vspace{-1.5ex}
\mat{0ex}{
%%%%%%%%%%%%%%%%%%%
{\sl Input:\/} \= An update $\Delta$ = $\Delta V\cup\Delta E$, TWPageRank vector $PR$ of $G$,\\
\hspace{5ex}   and the  topological order $O$ of the block-wise graph $G'$.\\
{\sl Output:\/} TWPageRank vector $PR^+$ of the updated graph $G^+$. \\
\\
\bcc \hspace{1.5ex}\=  $G_C'$ := the block-wise graph of $G_C$; \\
%\ \  $E_{CB}'$ := edges from $G_C'$ to $G'$\\
\icc\> $\Delta O$ := topological order of $G_C'$; \ \ $O^+$ := $\Delta O/O$; \\
\icc\> label \sccs of $G_C$ as $C$ and \sccs of $G$ with outgoing edges \\ \hspace{2.5ex}  having  weight changes as $B$,  the remaining \sccs of $G$ as $A$\\
\icc\>  \For each node $v'$ following $O^+$ \Do\\
\icc\>\hspace{2.5ex}\= $scc$ := the corresponding \scc of $v'$; \\
%\icc\>\>\If impact weight of $(v,w)$ is changed where $v\in scc$ \Then \\
%\icc\>\>\hspace{3ex}\= label $scc$ as $B$;\\
%\icc\>\>\> label SCC $w'$ as $B$ such that $(v',w')\in E'$; \\
\icc\>\> \If $scc$ is labeled as $C$ \Then \\
\icc\>\>\hspace{3ex}\= update $PR^+(v)$ ($v\in scc$) following algorithm~\twprscc; \\
\icc\>\>\> label \scc $w'$ as $B$ with $w'\in G'$ and $(v', w')\in E^+{'}$;\\
\icc\>\> \Else \If $scc$ is labeled as $B$ \Then \\
\icc\>\>\> update $PR^+(v)$ where $v\in scc$ with Eq.~(\ref{eq-inc-prscc}) until the \\ \hspace{8ex}  sum of TWPageRank score changes is less than $\epsilon\cdot \frac{|scc|}{|V^+|}$; \\
\icc\>\>\> label \scc $w'$ as $B$ with $(v',w')\in E'$;\\
\icc\>\> \Else $PR^+(v)$:=$PR(v)\cdot {n}/{n^+}$ where $v\in scc$; \\
\icc\> \Return $PR^+$.
}
\vspace{-2.5ex} \myhrule
\end{minipage}
}
\end{center}
\vspace{-1ex}
\caption{\small Algorithm~\inctwprscc for incremental TWPageRank} \label{alg-inctwprscc}
\vspace{-3ex}
\end{figure}
%%%%%%%%%%%%Algorithm

%%% affected/unaffected division
\stitle{Analyses of affected and unaffected areas}.
The TWPageRank vector $PR$ of graph $G$ is mainly affected in two ways.

\sstab(1) Let $V_{B,1}\subseteq V$ be the set of nodes reachable from the newly added nodes $\Delta V$, $V_{B,2}\subseteq V$ be the set of nodes with outgoing edges having weight changes, and $V_{B,3}\subseteq V$ be the set of nodes reachable from  $V_{B,2}$.
%
Then $V_B=V_{B,1}\cup V_{B,2}\cup V_{B,3}$ is obviously the set of nodes in $G$ affected by the update $\Delta$.
%
TWPageRank scores on $V_B$ are re-iterated as follows, where notations with superscript `$+$' are defined on  $G^+$.
%using the existing TWPageRank vector scaled with constant ${n}/{n^+}$.

\vspace{-2ex}
\begin{scriptsize}
\begin{equation}\label{eq-inc-prscc}
\begin{split}
PR^+(v) \ = \ &  d \sum_{(u,v)\in E^+_i} M^+_{u,v} PR^+(u) + d \sum_{(u,v)\in E^+_a} M^+_{u,v} PR^+(u)  \\
 + \frac{n}{n^+} \Big( PR(v) &  - d \sum_{(u,v)\in E_i} M_{u,v} PR(u) - d\sum_{(u,v)\in E_a} M_{u,v} PR(u)\Big).
\end{split}
\end{equation}
\vspace{-2ex}
\end{scriptsize}

\sstab(2) Let $V_A = V\setminus V_B$. Since nodes in $V_A$ are not reachable from newly added or affected nodes, $V_A$ is essentially not affected by the update $\Delta$. And TWPageRank scores on $V_A$ only need to scale with constant ${n}/{n^+}$.

Let $G_A=(V_A,E_A)$, $G_B=(V_B,E_B)$ and $G_C=(V_C,E_C)$, respectively, and
let $E_{AB}$ and $E_{CB}$  be the sets of edges from $G_A$ to $G_B$ and from $G_C$ to $G_B$, respectively.
In this way, graph $G^+$ is divided into subgraphs $\{G_A$, $G_B$, $G_C\}$ and edge sets $\{E_{AB}, E_{CB}\}$.
%
We then have $G_C$ = $G^+[\Delta V]$, $\Delta E$ = $E_C\cup E_{CB}$, $V$ = $V_A\cup V_B$ and $E$ = $E_A\cup E_B\cup E_{AB}$.

\stitle{Incremental algorithm \inctwprscc}. We now present our incremental algorithm for TWPageRank, shown in Fig.~\ref{alg-inctwprscc}.

It takes as input an update $\Delta$ and the previous results on the original graph $G(V, E)$, and returns the TWPageRank vector of the updated graph $G^+$. It first incrementally computes the topological order $O^+$
%by concatenating the topological orders of $G_C'$ and $G'$
(lines 1--2). %Note that $G_C'$ is the same to $G'_\Delta$.
%
After that, it labels the newly added \sccs with $C$ and existing \sccs with $A$ or $B$, depending on whether the existing \sccs have weight changes on outgoing edges (line 3).
%
It then processes each \scc in the order $O^+$ such that the TWPageRank scores of nodes in each \scc are updated according to the labels (lines 4--12), and finally returns the TWPageRank vector (line 13).
%
%More specifically, the scores of nodes in SCCs labeled as $C$ and $B$ are updated the same to Algorithm~\twprscc, while the scores of nodes in SCCs labeled as $A$ are simply scaled.
%
%It is also easy to verify that nodes in SCCs labeled as $A$, $B$ and $V$ corresponding to $V_A$, $V_B$ and $V_C$.

When processing $V_B$ with Eq.~(\ref{eq-inc-prscc}), {\em edges in $E_{AB}$ can be skipped}  since $PR^+(u)={n}/{n^+}\cdot PR(u)$ for $u\in V_A$ and $M_{u,v}=M^+_{u,v}$ for $(u,v)\in E_{AB}$. Besides, we use ${n}/{n^+}\cdot PR$ as the initial vector. Both of them can speed up the computation.

\eat{
\begin{figure}[tb!]
\centering
\includegraphics[scale=0.6]{fig/General_framework_peak_ABC.eps}
\vspace{-3ex}
\caption{\small An example of affected and unaffected areas}
\label{fig-inc-division}
\vspace{-3ex}
\end{figure}

\begin{example} \label{eg-layer-dag}
Figure~\ref{fig-inc-division} illustrates an example of affected and unaffected areas, in which subgraphs $G_A$, $G_B$ and $G_C$ are associated with node sets $V_A$, $V_B$ and $\Delta V$, respectively. Here the citation peak time of node $x$ is changed, which leads to the changes of the normalized weights of edges $(w,x)$, $(w,y)$ and $(w,z)$.
\end{example}
}

\begin{figure}[tb!]
\centering
\includegraphics[scale=0.7]{fig/General_framework_peak.eps}
\vspace{-1ex}
\caption{\small An example of incremental TWPageRank computation}
\label{fig-inc-division}
\vspace{-3ex}
\end{figure}

\begin{example} \label{eg-layer-dag}
Figure~\ref{fig-inc-division} illustrates an example of incremental TWPageRank computation. Consider an update $\Delta$ on the original graph $G$.
%
It is obvious that the update $\Delta$ has no impacts on the SCCs of $G$, and $O^+$ defined earlier is a valid topological order of $G^+{'}$.
%
The original graph $G$ is then partitioned into affected and unaffected areas, and subgraphs $G_A$, $G_B$ and $G_C$ are associated with node sets $V_A$, $V_B$ and $\Delta V$, respectively. Here edge weight on $(y, x)$ changes due to the change of the citation peak time of node $x$, and, hence, node $y$ as well as all nodes reachable from $y$ are included in $G_B$.
%
When updating the TWPageRank scores, following $O^+$, scores of nodes in $G_C$, $G_B$ and $G_A$ are computed by iterations from scratch, by iterations with Eq.~(\ref{eq-inc-prscc}) using the existing TWPageRank vector and by scaling, respectively.
\end{example}

\vspace{-1ex}
\begin{theorem}
\label{lemma-subgraphA}
The TWPageRank vector $PR^+$ returned by~\inctwprscc converges such that $||PR^+-PR^{*}||_1 < \epsilon$, where $PR^{*}$ is the convergent TWPageRank vector.
\end{theorem}

\begin{proofSketch}
Assume a topological order $v_1'/\dots/v_{l}'$ of the block-wise graph $G^+{'}$ where $l=|O^+|$. It suffices to prove by induction that the sum of changes of $PR^+(v)$ ($v\in scc_k$) is no more than $\epsilon |scc_k|/|V^+|$ for $scc_k$ of $v_k'$ ($k\in [1,l]$).
%The conclusion follows combining Lemma~\ref{prop-prscc}
%(see \cite{SARank-full} for details).
\end{proofSketch}

Observe that (a) a topological order of $G'_C$ can be computed in $O(|V_C|+|E_C|+|E_{CB}|)$ time,
(b) updating the TWPageRank scores of nodes in subgraphs $G_B$ and $G_C$ costs $O(|V_B\cup V_C|+|E_{B,a}\cup E_{C,a}\cup E_{CB}|)+t^+|E_{B,i}\cup E_{C,i}|)$ time, and , finally, (c) updating the scores of nodes in $G_A$ costs $O(|V_A|)$ time. From these, the following holds.

\begin{prop} \label{lemma-inc-citation-comp}
Given an update $\Delta$ = $\Delta V\cup\Delta E$ of citation or venue graph $G(V,E)$, the TWPageRank vector of $G$ and the topological order of $G'$, algorithm \inctwprscc runs in $O(|V\cup \Delta V| + |E_B\cup E_C\cup E_{CB}| + t^+|E_{B,i}\cup E_{C,i}|)$ time.
\end{prop}

%Note that the incremental algorithm reduces the complexity of updating subgraph $A$ from $O(|E^c_A|)$ to $O(|V^c_A|)$. It is more effective when only a small number of articles are updates, resulting in $|V^c_A|>>|V^c_B|+|V^c_C|$ and updating subgraph $A$ occupies most of the computation.

By Propositions~\ref{prop-converg} \& \ref{lemma-inc-topo} and Theorem \ref{lemma-subgraphA}, one can easily verify the correctness of algorithm \inctwprscc.
%
Note that  a) algorithm \inctwprscc computes \sccs and derives the topological order based  on $\Delta$ only, instead of $G^{+}$,
b) it skips edges in $E_A\cup E_{AB}$ when updating the scores of nodes in $G_A$ and $G_B$, and
c) the number $t^+$ is very likely smaller than the number $t$ of \twprscc when updating scores of nodes in $G_B$.
%
All these make \inctwprscc faster than \twprscc even though they have very similar time complexity.
%, as will also been shown by the experimental study,

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[tb!]
%\vspace{-2ex}
\begin{center}
\caption{\small Statistics of affected/unaffected areas given a yearly update, \ie articles of 2011 on \aan and 2015 on \aminer and \magdata, respectively.}
\label{tab-inc}
%\begin{small}
%\vspace{-.5ex}
\eat{
\begin{tabular}{|c|c|c|}
\hline
{\bf Graphs} & $|V_A|$\hspace{2ex}$|V_B|$\hspace{3ex}$|V_C|$ & $|E_A|$\hspace{2ex}$|E_{AB}|$\hspace{2ex}$|E_B|$\hspace{2ex}$|E_{CB}|$\hspace{2ex}$|E_C|$ \\
\hline \hline
% citation graphs
\aan & $46.9\%$\ $47.3\%$\ $5.8\%$ & \ $2.9\%$\ $25.9\%$\ $60.5\%$\ $10.4\%$ \hspace{1ex} $0.3\%$ \\
\aminer & $81.4\%$ \hspace{1ex} $10.7\%$ \hspace{1ex} $7.8\%$ & $18.0\%$ \hspace{1ex} $53.2\%$ \hspace{1ex} $25.1\%$ \hspace{1ex} \ $2.3\%$ \hspace{1ex} $1.4\%$ \\
\magdata & $69.5\%$ \hspace{1ex} $25.9\%$ \hspace{1ex} $4.5\%$ & \ $1.0\%$ \hspace{1ex} $27.4\%$ \hspace{1ex} $64.5\%$ \hspace{1ex} \ $7.0\%$ \hspace{1ex} $0.1\%$ \\ \hline
% venue graphs
\aan & \ $2.1\%$ \hspace{1ex} $92.0\%$ \hspace{1ex} $5.8\%$ & \ $1.0\%$ \hspace{1ex} \ $1.0\%$ \hspace{1ex} $88.8\%$ \hspace{1ex} $10.0\%$ \hspace{1ex} $0.2\%$ \\
\aminer & $45.8\%$ \hspace{1ex} $47.7\%$ \hspace{1ex} $6.4\%$ & \ $0.0\%$ \hspace{1ex} \ $3.2\%$ \hspace{1ex} $95.4\%$ \hspace{1ex} \ $1.0\%$ \hspace{1ex} $0.1\%$ \\
\magdata & $12.4\%$ \hspace{1ex} $84.6\%$ \hspace{1ex} $3.0\%$ & \ $0.0\%$ \hspace{1ex} \ $0.1\%$ \hspace{1ex} $92.6\%$ \hspace{1ex} \ $7.1\%$ \hspace{1ex} $0.1\%$ \\
 \hline
\end{tabular}
}
\begin{tabular}{|c|c c c|c c c|}
\hline
 & \multicolumn{3}{c|}{\bf Citation graphs on}   & \multicolumn{3}{c|}{\bf Venue graphs on}    \\
\raisebox{1ex}[0pt]{\bf Statis.} & \aan & \aminer & \magdata & \aan & \aminer & \magdata \\
\hline \hline
$|V_A|$ & 47.4\% & 52.3\% & 69.2\% & 2.1\% & 8.7\% & 12.4\% \\
$|V_B|$ & 46.8\% & 40.0\% & 26.3\% & 92.0\% & 84.8\% & 84.6\% \\
$|V_C|$ & \ 5.8\% & \ 7.8\% & \ 4.5\% & \ 5.8\% & \ 6.4\% & \ 3.0\% \\ \hline
% venue graphs
$|E_A|$ & \ 3.0\% & 2.4\% & \ 0.9\% & \ 0.0\% & \ 0.0\% & \ 0.0\% \\
$|E_{AB}|$ & 26.5\% & 30.2\% & 26.6\% & \ 1.2\% & \ 0.2\% & \ 0.1\% \\
$|E_B|$ & 59.8\% & 59.3\% & 65.5\% & 88.6\% & 92.3\% & 92.6\% \\
$|E_{CB}|$ & 10.4\% & \ 7.2\% & \ 7.0\% & 10.0\% & \ 7.3\% & \ 7.1\% \\
$|E_C|$ & \ 0.3\% & \ 0.9\% & \ 0.1\% & \ 0.2\% & \ 0.2\% & \ 0.1\% \\ \hline
\end{tabular}
%\end{small}
\end{center}
\vspace{-5ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

\stitle{Time \& space complexity analyses of the incremental algorithm}.
By the analyses above, the time complexity of \incensemble is the same as \batensemble, except that \incensemble saves $O(|E^c_A\cup E^c_{AB}|)$ and $O(|E^v_A\cup E^v_{AB}|)$ time on the updated citation and venue graphs. And its space complexity is also the same as \batensemble, except that it uses $(|V^c\cup \Delta V^c|+|V^v\cup\Delta V^v|)$ extra space to store the affected/unaffected areas and $(|E^c\cup \Delta E^c|+|E^v\cup \Delta E^v|)$ extra space to store the original edge weights before update.

Despite of its similar time complexity to \batensemble, algorithm \incensemble typically achieves a substantial efficiency improvement over \batensemble, according to our statistics of affected/unaffected areas shown in Table~II.
%
(a) It saves $O(|V^c|+|E^c|)$ and $O(|V^v|+|E^v|)$ time when maintaining \sccs and the topological order based on $\Delta^c$ and $\Delta^v$ only, where ($|V^c|$, $|E^c|$, $|V^v|$, $|E^v|$) are more than (92\%, 89\%, 93\%, 89\%) of ($|V^{c,+}|$, $|E^{c,+}|$, $|V^{v,+}|$, $|E^{v,+}|$) on all tested graphs;
(b) It saves $O(|E^c_A \cup E^c_{AB}|)$ time when updating scores on $V^c$, where edges in $E^c_A\cup E^c_{AB}$ account for more than 28\% of total edges;
(c) It saves $O(|E^c|)$ time when computing popularity of articles, which accounts for more than 89\% of $|E^{c,+}|$;
And, finally, (d) It is likely to compute TWPageRank scores on $V^c_B$ and $V^v_B$ with less iterations.

### 2017-09-19 icde/sec-model.tex

\section{Ranking Model}
\label{sec-model}

In this section, we first present Time-Weighted PageRank for evaluating  the importance of entities, defined as a combination of the prestige and popularity, and then introduce our ranking model \ensemblerank that assembles the importance of articles, venues and authors involved in scholarly articles.

%It further assembles the importance of heterogeneous entities involved to rank scholarly articles.
%The model is based on PageRank~\cite{Brin98:PageRank}, which was initially designed for web pages and widely applied to many other tasks, including article ranking~\cite{Li08TSRanking,Richardson06:BPR,sayyadi09,Zhou07-CoRank}.

\subsection{Time-Weighted PageRank}
\label{subsec-twpr}

We first present Time-Weighted PageRank (TWPageRank) based on citation statistics, as the direct use of PageRank for ranking scholarly articles is problematic as discussed below.

%PageRank~\cite{Brin98:PageRank} has been extensively applied to the ranking of scholarly articles~\cite{Waltman2014,sayyadi09,Zhou07-CoRank,ChenXMR07}, as hyperlinks among Web pages can be easily replaced with citation relationships among articles, and citation analysis plays a key role to evaluate the importance of scholarly articles. However,

\noindent(1) Different articles typically have different impacts in practice, and there is a need to differentiate, while PageRank essentially assumes equal impacts.

%, such that each article can distribute more of its authority to those that are more influential to it.

\noindent(2) The semantics of citation relationships are time-dependent, which means that citations at different periods of time may reveal different information. Note that this has already been exploited for scholarly article ranking~\cite{Li08TSRanking,Wang13AAAI,WalkerXKM07}, while PageRank does not consider this temporal factor at all.
% and each individual article reaches their periods in different time

\stitle{Time-Weighted PageRank (TWPageRank)}. Most previous work simply exploits temporal information in the form of exponential decay~\cite{Li08TSRanking,Wang13AAAI,sayyadi09,WalkerXKM07}. We rethink the usage of time information in terms of the impacts of scholarly articles.
Recall that articles are categorized  into six citation patterns featured by the time when the articles reach their citation peaks~\cite{Chakraborty15}: (a) {\em PeakInit} with the citation-count peak in the first five years (but not the first year) after publication, (b) {\em PeakMul} with distinct multiple peaks, (c) {\em PeakLate} with a single peak in at least five years after publication, (d) {\em MonDec} with monotonically decreasing citations, (e) {\em MonIncr} with monotonically increasing citations, and, (f) {\em Other} for articles whose average numbers of citations per year are less than 1. Though the number of citations is an indicator of the impacts of articles~\cite{WangSB13,Garfield471}, its impact is time-dependent and is not simply in the form of exponential decay.
In general, {\em the impact of an article tends to decay with time after the peak time only}. That is, the impacts of articles directly decay with time only for those in {\em MonDec}, and decay with time after the peak time for those in {\em PeakInit}, {\em PeakLate} and {\em PeakMul}, and do not decay for ones in {\em MonIncr} (which is rare).
%Otherwise, its impact is fixed as a constant number. %, since we argue that the increment of its citations during this period is mainly due to the increase of its popularity.
Also observe that {\em each individual article has its own peak time} as articles may reach their citation peaks in different patterns and time.
%using the peak year in Fig.~\ref{fig-citation} is not appropriate for all articles. On the contrary, we compute a peak year for each article.

\eat{
 the proportion of total citations \wrt the number of years after publication.
%Here we use the number of citations to evaluate the impacts of articles.
\marked{As we can see, the number of citations reaches a peak in the first 1 or 2 years, and gradually decreases after that, which also conforms to our perception of the impacts of articles~\cite{WangSB13}. Note that the peak time differs from one dataset to another.}

According to Fig.~\ref{fig-citation}, the impact of an article does depend on time, but not simply in the form of exponential decay. Specifically, if an article is cited after the citation peak, its impact should decay with time. Otherwise, its impact is fixed as a constant number. %, since we argue that the increment of its citations during this period is mainly due to the increase of its popularity.
Moreover, considering that articles might reach their citation peaks in different time, we compute {\em the peak time for each individual article}, rather than using the same citation peak for all articles.
%using the peak year in Fig.~\ref{fig-citation} is not appropriate for all articles. On the contrary, we compute a peak year for each article.
}

\begin{figure}
\centering
\includegraphics[scale=0.48]{fig/yearly-references.eps}
\vspace{-1ex}
\caption{\small Citation statistics of scholarly articles that reports the (logscale) percentage of the number of citations of each year \wrt\ the total number of citations  in  \aan, \aminer and \magdata, respectively.}
\label{fig-reference}
\vspace{-4ex}
\end{figure}

Based on the above discussion, we propose TWPageRank that evaluates the prestige of nodes (\eg scholarly articles) in a directed graph, such that each node is attached with time information. It differs from PageRank by weighting the influence propagation using the {\em impact weights on edges}, which represent the relative amounts of time-dependent prestige that should be propagated from the edge sources to targets.
%
Formally, the impact weight on a directed edge $(u,v)$, \ie an edge from $u$ to $v$, is defined as:

\vspace{-1ex}
\begin{small}
\begin{equation} \label{eq-infl-weights}
w(u,v)  =  \begin{cases}  \hspace{7ex} 1 & T_u <  Peak_v \\
  e^{\sigma(T_u-Peak_v)} & T_u \geq Peak_v,
\end{cases}
\end{equation}
\end{small}
%
\noindent where $T_u$ is the time of node $u$, $Peak_v$ is the peak time of node $v$ after which the impact weights of edges to $v$ decay with time, and $\sigma$ is a negative number controlling the decaying speed of the impacts.
By default, Eq.~(\ref{eq-infl-weights}) uses years as its time granularity. Note that the time decaying factor $\sigma$ is introduced to provide flexibility for TWPageRank in various applications, and its value is typically within a small interval, \eg $[-2,0]$, such that $w(u,v)$ does not decay when $\sigma=0$ and already decays more than a half per year when $\sigma=-1$.
For the sake of completeness, we further set $w(u,v)$ to $0$ if there does not exist an edge from $u$ to $v$ in the graph.

For scholarly article ranking, $T_u$ is the publication time of article $u$ and $Peak_v$ should be ideally set to the time when article $v$ has the highest impacts. Basically, it could simply be the year when article $v$ obtains the largest number of citations. However, recent work reveals that the volume of scientific publications as well as the number of citations grow exponentially with time~\cite{Dong2017KDD,BornmannM15}. We also collect and report the citations statistics on three scholarly datasets in Fig.~\ref{fig-reference}, which verifies the exponential distribution. Hence, we adopt the {\em scaled} number of citations $\Psi_v^{(t)}=\Phi_v^{(t)} / \log Z^{(t)}$ such that $\Phi_v^{(t)}$ and $Z^{(t)}$ are the number of citations of article $v$ at year $t$ and the total number of references at year $t$, respectively. The peak time $Peak_v$ is the time that maximizes $\Psi_v^{(t)}$.
%(\aan, \aminer and \magdata)
% since scholarly data is dynamic and continuously growing
%, and the increased number of references of each article over time
%Recent work observes that the volume of scientific publications doubled every 12 years between 1900 and 2015~\cite{Dong2017KDD}. It is not surprising that the number of references also grows exponentially~\cite{BornmannM15}.

The update rule of TWPageRank is:

\vspace{-1ex}
\begin{small}
\begin{equation}\label{eq-twpr}
PR(v)=d\sum_{(u,v)\in E} \frac{w(u,v)PR(u)}{W(u)}+\frac{1-d}{n},
\end{equation}
\end{small}
%
\noindent where $PR(u)$ and $PR(v)$ are the TWPageRank scores of $u$ and $v$, respectively, $E$ is the set of edges, $W(u)=\Sigma_{v} w(u,v)$ is the sum of the impact weights on all edges from $u$, $n$ is the number of nodes and $d$ is a damping parameter in $(0, 1)$. By Eq.~(\ref{eq-twpr}), we can see that prestige is based on the impact weights, not equally distributed.

% in Eq.~(\ref{eq-twpr}) into
Correspondingly, the matrix form of the update rule is:

\vspace{-1ex}
\begin{small}
\begin{equation}
\label{eq-twpr-update}
PR^{(t)}=d M^T  PR^{(t-1)} + (1-d) e/n.
\end{equation}
\end{small}
%
\noindent
Here $PR^{(k)}$ is the TWPageRank vectors after $k$ iterations,  $M$ is the transition matrix such that $M_{u,v}=w(u,v)/W(u)$ and  $e$ is an $n$-dimensional all-one vector $[1]_{n\times1}$.

%We next present the convergence  of TWPageRank as follows.
The linear system in Eq.~(\ref{eq-twpr-update}) is equivalent to {\em irreducible} and {\em aperiodic} Markov chains~\cite{CorsoGR05}, which guarantees the following.

\begin{prop}
\label{prop-converg}
TWPageRank converges to a unique  vector on any graph, regardless of the initial vector.
\end{prop}

\eat{
\begin{proof}
It is known that a sequence of vectors $x^{(k)}$ such that $x^{(k+1)}=A\cdot x^{(k)}+b$ (where $k=0,1,\dots$) converges to a unique vector $x^*$,  regardless of the initial vector $x^0$, if and only if $\rho(A)<1$~\cite{kelley1999iterative}, where $\rho(A)$ is the spectral radius of matrix $A$. Hence, it suffices to show $\rho(d\cdot M^T) < 1$ by Eq.~(\ref{eq-twpr-update}).

As the column sums of $d\cdot M^T$ are all less than or equal to $d$, $||d\cdot M^T||_1 \le d$ where $||d\cdot M^T||_1$ is the 1-norm of matrix $d\cdot M^T$ and is defined as the maximum absolute column sum of $d\cdot M^T$.
We then have $\rho(d\cdot M^T) \le ||d\cdot M^T||_1 \le d < 1$, as the spectral radius of a matrix is always no more than its consistent matrix norms~\cite{spe-radius}, \eg $||\cdot||_1$, which gives the conclusion.
\end{proof}
}

%\stitle{Remarks}. Note that Eq.~(\ref{eq-twpr}) is indeed a general update rule of Weighted PageRank~\cite{Xing04:WPR,Ding11}, and the name of Time-Weighted PageRank comes from the use of time information of citations in the initial impact weight  $w(u,v)$ of Eq.~(\ref{eq-infl-weights}).

\vspace{-1ex}
\subsection{Ranking with Importance Assembling}
\label{subsec-ensemble}

%In our model, the importance of scholarly articles is defined as a combination of the prestige and popularity of its associated articles, venues and authors. Intuitively, prestige favors those with many citations soon after the publication of articles for citation component or associated articles for venue and author components, and popularity favors those with recent citations. Both prestige and popularity capture the temporal nature of entities in scholarly data.
In our model, the importance is defined as a combination of the prestige and popularity. Intuitively, prestige favors those with many citations soon after the publication of articles or associated articles of venues and authors, and popularity favors those with recent citations. Both prestige and popularity capture the temporal nature of entities. %in scholarly data.

Our ranking model \ensemblerank,  illustrated in Fig.~\ref{fig-rankmodel}, assembles the importance of article, venue and author entities for scholarly article ranking, which is computed by the citation, venue and author components, respectively.
%
We next introduce the details of the three components.

\stitle{Citation component}.
The first component computes the importance of articles using the citation information.

A {\em citation graph} $G^c(V^c, E^c)$ is firstly constructed using the citation information such that (a) a node in $V^c$ denotes an article, (b) a directed edge $(u,v)$ in $E^c$ denotes that $u$ cites $v$, and (c) each node is associated with two types of time information: the publication year and the latest year having the largest number of citations.

\sstab(1) The prestige of articles is derived by applying TWPageRank on the citation graph $G^c$, and each article $v$ is assigned the corresponding TWPageRank score as its prestige $Prs_c(v)$.

\sstab(2)  The popularity of an article is the sum of all its citations' freshness, \ie the closeness to the current year:

\vspace{-1ex}
\begin{small}
\begin{equation}\label{eq-pop}
Pop_c(v) = \sum_{{(u,v)\in E^c}} {e^{\sigma (T_0-T_u)}}.
\end{equation}
\end{small}
\noindent
Here $T_0$ is the current year, \ie the latest $T_u$ among all articles in $V^c$, $\sigma$ is the negative decaying factor used in Eq.~(\ref{eq-infl-weights}), and $e^{\sigma (T_0-T_u)}$ represents the freshness of citation $(u,v)$.

%Alternatively, one may want to define $Pop_c(v) = e^{\sigma \cdot (T_0-T_v)}$, \ie decaying with the publication year $T_v$ of article $v$ directly~\cite{sayyadi09,WalkerXKM07}. We propose to use the publication years $T_u$ of citations, instead of $T_v$, since $T_u$ reflects the ages of articles to some extent, \eg articles are probably cited in the next few years after publication(Fig.~\ref{fig-citation}).

Intuitively, the more recent citations an article has, the higher its popularity is, no matter how long it has been published.
Here popularity is introduced to capture the recent importance of articles, and articles with more recent citations have higher popularity scores. %, which is somehow biased to recent articles. Hence, we do not explicitly handle the bias for popularity computation.
%
%\marked{Different from $Peak_v$ in Eq.~(\ref{eq-infl-weights}), the bias of references has little impacts on the popularity. Moreover, the motivation of popularity is to assign higher ranks to articles of recent attention, which is somehow biased to recent articles. Hence, we do not explicitly handle the bias for popularity computation.}
%
Note that the popularity is also normalized such that the sum of  all articles is equal to $1$, similar to the prestige produced by TWPageRank.

\sstab(3) The prestige and popularity are finally combined to produce the importance of articles. Intuitively, an important article is both prestigious and popular. Hence, the {\em citation importance score} $Imp_c(v)$ of an article is defined as a weighted combination of its prestige and popularity:

\vspace{-1ex}
\begin{small}
\begin{equation}\label{eq-imp}
%Imp_c(v) = \sqrt{Prs_c(v) \cdot Pop_c(v)}.
Imp_c(v) = Prs_c(v)^\lambda Pop_c(v)^{1-\lambda},
\end{equation}
\end{small}
\noindent where $\lambda \in [0,1]$ is the importance weighting factor.
The rationales behind Eq.~(\ref{eq-imp}) are as follows. (a) Prestigious articles with many recent citations are ranked at the top, as researchers are very willing to find them; (b) Prestigious articles with rare current citations are ranked lower, as researchers may lose interests in these old articles; And (c) articles with many recent citations are ranked higher, as researchers have potential interests in those of recent attention.

%Here the prestige and popularity are equally weighted to produce the importance of an article, as we focus on query independent ranking. They may be properly weighted when the query information is available, which is beyond the scope of this work.

\begin{figure}[tb!]
\centering
%\includegraphics[scale=0.15]{fig/framework.eps}
\includegraphics[scale=0.16]{fig/framework-lite-2.eps}
\vspace{-1ex}
\caption{\small Ranking model \ensemblerank} \label{fig-rankmodel}
\vspace{-3ex}
\end{figure}

\stitle{Venue component}.
The second component computes the importance of venues with their associated articles. As the importance of a venue  evolves with time, we treat the venue in each year individually, and its importance is the sum of importance in all individual years.

A {\em venue graph} $G^v(V^v, E^v)$ is firstly constructed using the citation information among venues such that (a) a node in $V^v$ represents a venue in a specific year, (b) a direct edge $(s,t)$ in $E^v$ denotes that there exist articles published in venue (in a specific year) $s$ citing articles published in venue (in a specific year) $t$, and (c) we use the {\em impact weight} to denote the weight $w_v(s,t)$ from venues $s$ to $t$, which is the sum of the impact weights from articles published in $s$ to $t$, \ie

\vspace{-1ex}
\begin{small}
\begin{equation} \label{eq-infl-weights-v}
w_v(s,t)  = \sum_{u\in C(s), v\in C(t)} w(u,v).
\end{equation}
\end{small}
\noindent
Here, $C(s)$ and $C(t)$ are the sets of articles published in $s$ and $t$, respectively, and $w(u,v)$ is the impact weight of edge $(u, v)$ produced in the citation component.

The prestige of a venue in a specific year is computed using the impact weights and the update rule in Eq.~(\ref{eq-twpr}), and the popularity of a venue in a specific year is defined as the average popularity of its articles. The prestige and popularity are combined to derive the importance of a venue in a specific year in the same way as the citation component. Finally, the importance of a venue is treated as the {\em venue importance score} for all articles published in this venue.

\stitle{Author component}.
The author component computes the importance of authors with their published articles.
%
Similar to the venue component, we evaluate the importance of each author, and compute the average importance of the authors of an article as its {\em author importance score}.

However, the resulting author citation graph to compute the prestige is typically too large to handle. Hence, we evaluate the prestige of an author, by using the average prestige of all articles published by the author. Similar to the venue component, the popularity of an author is also defined as the average popularity of her/his published articles. Finally, the prestige and popularity are combined to derive the importance in the same way as the citation component.

%, which can be directly obtained from the citation component,
%to evaluate the authority of that author.

\eat{
\stitle{Affiliation ensemble}.
Recall that articles in our data are also associated with affiliation information. Following the way of the venue or author ensemble, we can derive another ensemble, \ie affiliation ensemble. However, we argue that the use of affiliation ensemble may have negative effects since the correlation between the importance of an article and the average authority of its affiliation(s) is not as strong as others such like authors and venues. As shown by the experimental study in Section~\ref{sec-exp},  the incorporation of the affiliation ensemble impairs the ranking accuracy. Hence, we choose not to use the affiliation ensemble in our model.
}

%\subsection{Ranking with Importance}
%{\label{subsec-eerank}}

\stitle{Ranking with importance assembling}. The aforementioned importance is finally assembled to produce the final ranking, as illustrated in Fig.~\ref{fig-rankmodel}. Before assembling, each component is properly scaled such that the average citation importance score, venue importance score and author importance score
are the same.  Let the scaled importance scores of article $v$ be $R_c(v)$, $R_v(v)$, and $R_a(v)$ from the citation, venue and author components, respectively. The final ranking score $R(v)$ of an article $v$ is aggregated as follows:

\vspace{-1ex}
\begin{small}
\begin{equation} \label{eq-ensemble}
R(v) =  \alpha R_c(v) + \beta R_v(v) + (1 - \alpha - \beta) R_a(v).
\end{equation}
\end{small}
\noindent Here aggregating parameters $\alpha$ and $\beta$ and value $(1 - \alpha - \beta)$ regularize the contributions of the citation, venue and author information. Intuitively, these parameters indicate the intensity of the correlation between the importance of scholarly articles and the specific information.

\stitle{Remark}. This work follows the graph-based formalization, and further develops efficient batch and incremental algorithms based on graphs for scholarly article ranking (Sections~\ref{sec-alg} \& \ref{sec-incAlg}). However, it is also possible to learn a discriminative model that directly optimizes certain loss functions for ranking, similar to \cite{Richardson06:BPR} for ranking Web pages.

%\subsection{Framework}
%\label{subsec-framework}

%Our ensemble enabled ranking model~\ensemblerank is illustrated in Fig.~\ref{fig-rankmodel}, which contains three distinct ensembles derived from academic graph data, \ie the citation ensemble, venue ensemble and author ensemble. The citation ensemble directly uses TWPageRank, while the other two are partially based on TWPageRank. Moreover, the citation ensemble also helps to derive the venue ensemble and author ensemble. These ensembles are further assembled to produce the final ranking.

%As illustrated in Fig.~\ref{fig-rankmodel}, external data is also exploited in \ewpr. How to collect and use external data will be introduced in the coming section.

\eat{
\stitle{Remarks}.
Traditional PageRank equally distributes the prestige of nodes, and PageRank based models suffer from the problem that older articles are preferred since they have accumulated a large number of citations~\cite{Li08TSRanking}, and TWPageRank based models alleviate the problem to a certain degree by lowering the impact weights of articles when they are cited after their peak time, \ie $T_u\geq Peak_v$. We further propose the venue and author ensembles to improve the ranking accuracy.
}

%\stitle{Remarks}.
%Recall that articles in our data are also associated with affiliation information. Following the way of the venue or author ensemble, we can derive another ensemble, \ie affiliation ensemble. However, we argue that the use of affiliation ensemble may have negative effects since the correlation between the importance of an article and the average authority of its affiliation(s) is not as strong as others such like authors and venues. As shown by the experimental study in Section~\ref{sec-exp},  the incorporation of the affiliation ensemble impairs the ranking accuracy. Hence, we choose not to use the affiliation ensemble in our model.

%our method used for author ensemble is both lightweight and effective, as will be shown in the experimental study.

%Two methods are used to evaluate the authority of venues and authors, respectively. We point out that the ensembles are quite flexible to the selection of these methods, and others may also be incorporated in the ensembles if appropriate.

\eat{
\subsection{Dealing with Missing Data}
\label{subsec-impl}

Data quality is one of the most challenging issues in large scale data management, especially for data from open domains and multiple sources, \eg the Microsoft Academic Graph (MAG)~\cite{Sinha15:MAG}.
The early version of MAG has $120$ million scholarly articles, among which we find that there are about $73$ million articles without references and about $77$ million ones without venues. The ranks of those articles with missing information are underestimated by our model \ewpr, since ensembles assign the minimum scores to articles. As a result, data missing seriously impairs the ranking accuracy.

As for references and venues, the later are easier to obtain, and each filled venue can have a direct and substantial impact on the article ranking, \ie $R_v(u)$ of Eq.~(\ref{eq-ensemble}). In contrast, a filled reference only has an indirect and slight impact. Hence, we decide to use external data to fill in missing venues.

%\subsection{Data Collecting}
%\label{subsec-datacraw}
\stitle{Data collecting}.
The raw external data is collected from publicly available Digital Libraries, such as IEEE Xplore ({\footnotesize http://ieeexplo-re.ieee.org/gateway/}),  PubMed ({\footnotesize http://www.ncbi.nlm.nih.gov/pub-med/}) and DBLP ({\footnotesize http://dblp.uni-trier.de/db/}). In total, we collect $2.8$ million articles with venue information as our external data, in which there are $57,000$ different venues.

%\subsection{Data Preprocessing}
%\label{subsec-dataprep}
\stitle{Data preprocessing}.
The venues in MAG are well processed, and are replaced by their series names. For example, {\em ``9th International Conference on Web Search and Data Mining, 2016''} is replaced with {\em ``Web Search and Data Mining''}. This makes it hard to directly link with the collected raw venue names. Hence, we preprocess raw venue names for the simplification of subsequent venue linking.
%
We first remove stop words such as {``on''} and common words like {``Conference''}, as well as years and some special characters from collected raw venue names. Then the same venues are merged, and the number of different venue names is reduced to $42,000$.

%\subsection{Data Linking}
%\label{subsec-datamap}
\stitle{Data linking}.
The final and also the most important step of filling missing venue information is to link each collected venue name to an existing one in MAG. Intuitively, linking based on name similarity is the most effective way such that two venues are linked if their names bear high similarity. We exploit the Jaro metric to evaluate the name similarity, which is based on the number and order of the common characters between two strings, and obtains good results in tasks such as record linkage and name matching~\cite{Cohen03strcompa}. Formally, a collected venue name is linked to an existing one in MAG if their Jaro similarity exceeds a pre-define threshold.

However, such a threshold is nontrivial to determine in practice. A high threshold can guarantee the accuracy of linked pairs, while only a tiny proportion of collected venue names are linked. On the other hand, a low threshold increases the number of linked pairs, which, in the same time, also introduces many errors. In order to reach a good balance between the number of linked pairs and the accuracy, we propose to combine another constraint on topic similarity of venues for linking, and only weaker filter conditions need be used in both constraints.

In MAG, fields of study (FOS) represent research topics of articles, such as {\em Web pages}, and {\em language technology}. Hence, we use FOS to evaluate the topic similarity of two venues. There are about $54,000$ FOS in MAG and most articles are assigned with two or three FOS. Let the set of FOS of each venue be the union of the sets of FOS of articles published in that venue. And the topic similarity of two venues based on FOS is defined as:
\begin{small}
\begin{equation} \label{eq-fos}
TS(s,t)=({|F_s\bigcap F_t|})/{\sqrt{|F_s|\cdot|F_t|}},
\end{equation}
\end{small}
\noindent in which $s$ and $t$ are two venues, and $F_s$ and $F_t$ are the sets of FOS of $s$ and $t$, respectively.

When we link a collected venue name, it is directly linked to the most similar one in terms of name similarity, if their Jaro similarity exceeds a high threshold $\lambda$. Otherwise, we first use the topic similarity constraint to select several candidates in MAG, \ie venues whose topic similarities with the collected venue exceed a threshold $\theta$. Intuitively, these candidates are in the similar fields of the collected one. We then select the most similar candidate in terms of name similarity as its linked venue, if their Jaro similarity exceeds another threshold $\phi$. Hence, the collected venue is linked to the one to which it is similar in terms of both topics and names.

In our model \ewpr, threshold $\lambda$ is set to $0.95$, while thresholds $\theta$ and $\phi$ need not be very high, which are $0.5$ and $0.7$, respectively. Finally, $6,000$ among the $42,000$ collected venues are linked, resulting in $340,000$ (about $12\%$) articles with enriched venue information. Note that a majority of the collected venue names are not valid venues, such as booktitles and names of workshops, and cannot be linked to any one in MAG.
}

### 2017-09-19 icde/sec-exp.tex

\section{Experimental Study}
\label{sec-exp}

In this section, we present an extensive experimental study of our approach \ensemblerank, compared with competitive methods.
Using three real-life scholarly datasets (\aan, \aminer and \magdata) and two sets of ground-truth (\recom and \fcita), we conducted four sets of experiments to evaluate: (1) the effectiveness of \ensemblerank,
%two sets of benchmark article pairs (\recom and \fcita) ranked by numbers of recommendations and future citations,
(2) the efficiency of our batch algorithm \batensemble and incremental algorithm \incensemble, and (3) the impacts of parameters. %\ie time decaying factor $\sigma$, importance weighting factor $\lambda$ and aggregating parameters $\alpha$ and $\beta$.

\subsection{Experimental Settings}

We first present the settings of our experimental study.

\eat{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t!]
%\vspace{-2ex}
\label{tab-statistics}
\begin{center}
\begin{scriptsize}
\vspace{1ex}
\begin{tabular}{|c|c|c|}
\hline
{\bf Entity / Relation}       &  {\bf Quantity in Phase~1}     & {\bf Quantity in Phase~2} \\
\hline\hline
Paper      &  $122,675,085$       &  $120,887,833$ \\ \hline
Author      &  $123,017,488$       &  $119,892,201$ \\ \hline
Venue      &  $24,841$       &  $24,843$ \\ \hline
Affiliation      &  $2,716,493$       &  $19,849$ \\ \hline
Fields of study     &  $53,834$       &  $53,830$ \\ \hline
Reference      &  $757,462,733$       &  $952,364,264$ \\ \hline
P-A      &  $324,948,062$       &  $312,034,259$ \\ \hline
P-V      &  $45,783,880$       &  $45,290,168$ \\ \hline
\end{tabular}
\vspace{-5ex}
\end{scriptsize}
\end{center}
\caption{Statistics of MAG}
\vspace{-3ex}
\end{table}
%%%%%%%%%%%%%%%%%%%
}

\stitle{Datasets}. We chose three datasets to test our approach.

\noindent
(1) \aan records the collection of computational linguistics articles published at ACL conferences from the year of 1965 to 2011~\cite{Liang16AAAI}.
It contains 18,041 articles, 14,386 authors, 273 venues and 82,944 citations.

\noindent
(2) \aminer records articles in the computer science domain from 1936 to 2016~\cite{Tang:08KDD}.
It contains 3.14 million articles, 1.74 million authors, 11,619 venues and 6.38 million citations.

\noindent
(3) \magdata records articles of various disciplines from 1800 to 2016~\cite{Sinha15:MAG}.
It contains around 127 million articles, 115 million authors, 24,024 venues and 529 million citations.
%Please refer to~\cite{Sinha15:MAG} for more details about \magdata.

To alleviate the issue of citation missing of \aminer, we added citations by title matching  based on \magdata, and the finally total number of citations is is 14.26 million. These datasets were further cleaned by deleting self-citations and citations from old articles to new ones, which accounted for (0.1\%, 0.8\%, 0.4\%) of the total citations on (\aan, \aminer, \magdata), respectively.
%from old articles to more recent ones
%These datasets were further cleaned by detecting citation cycles and removing those edges violating the temporal order if any.

%The original datasets does not strictly follow the temporal order due to the data quality problem. We hence dealt with the issuef by repeatedly detecting cycles in citation graphs and removing edges that break temporal order, if existing, or all edges in cycles.

%Actually, the citation networks of scholarly article in the three datasets are not DAG, since there are some mistaken citaions which can't be found in the references of articles. In order to delete these edges to make sure the citation network is a DAG, we do the followings:
%(1) Detect possible loops in the network by depth-first-search
%(2) Delete the edges with time error in loops found in (1) which are edges from earlier articles to later, only if all the edges in the loop haven't be deleted
%(3) Delete all the edges in loops found in (1) only if all the edges in the loop haven't be deleted
%(4) Repeat (1)-(3) until there is no loop in the network.

\stitle{Accuracy metric and ground-truth}.
We adopted the {\em pairwise accuracy} introduced by Microsoft~\cite{Richardson06:BPR,wsdmcup} to evaluate the ranking quality, \ie the fraction of times that a ranking agrees with the correct ranking orders of scholarly article pairs.
We constructed two sets of ground-truth importance orders of article pairs with \recom and \fcita.

\eat{
\vspace{-1ex}
\begin{small}
\begin{equation}
\label{eq-metric}
\PairAcc=\frac{\#\mbox{ of agreed pairs}}{\# \mbox{ of all pairs}}.
%\PairAcc=(\#\mbox{ of agreed pairs}) / (\# \mbox{ of all pairs}).
\end{equation}
\end{small}
\vspace{-3ex}
}

\noindent
(1) \recom assumes that scholarly articles with more recommendations are of higher importance.
%
%evaluates the importance of scholarly articles by the numbers of recommendations (from textbooks and/or university course reading lists).
We used the numbers of recommendations of 93 articles on \aan~\cite{Liang16AAAI}, %which are recommended by 2 to 10 times,
and, by exact title matching, %then matched articles in \aminer and \magdata with titles.  Finally, we
generated (2133, 966, 1972) scholarly article pairs on (\aan, \aminer, \magdata), respectively.
%These articles were further matched into \aminer and \magdata through titles, which generated 966 and 1,972 article pairs for \aminer and \magdata, respectively.

\noindent 
(2) \fcita assumes that scholarly articles with more citations are of higher importance.
%
However, the number of all citations is obviously biased to old articles. Some work adopts the number of future citations~\cite{Wang13AAAI,Wang16TIST,Li08TSRanking}, which is also not appropriate since this gives an estimation of impacts of articles in the near future, not at the concerned time. Differently, we propose to use the number of past and future citations, where past and future periods span the same length of time such that the number of citations within the two periods reveals the importance of articles at the conerned time.
%
We hence divided each dataset into two parts by a splitting year where the data before the splitting year (exclusive) were used for ranking and the remaining data as well as the most recent part of ranking data which spans the same time as the remaining data were used to count the numbers of past and future citations.
%
Moreover, articles in the same pair were required to be in similar research fields, by utilizing the Fields-Of-Study information on \magdata~\cite{Sinha15:MAG}, and published in the same year, similar to~\cite{Wang16TIST}.
We used all pairs (around 50,000) for \aan, and randomly chose 300,000 pairs for both \aminer and \magdata.

\eat{
\noindent
(2) \fcita assumes that scholarly articles with more future citations are of higher importance~\cite{Wang13AAAI,Wang16TIST,Li08TSRanking}.
We first divided each dataset into ranking part and evaluation part by a splitting year such that data before the splitting year were used for ranking and the remaining data were used to count the numbers of future citations for articles in the ranking part.
%
Moreover, articles in the same pair were required to be in similar research fields, by utilizing the Fields-Of-Study information on \magdata~\cite{Sinha15:MAG}, and published in the same year, similar to~\cite{Wang16TIST}.
We used all pairs (around 25,000) for \aan, and randomly chose 300,000 pairs for both \aminer and \magdata.
%
\marked{Due to the sparse citations on \aminer, the two articles in 50\% pairs have 0 and 1 future citation, which is a very weak evidence for importance order. Hence, we further required articles in pairs must have at least 1 future citation on \aminer.}
%Finally, we generated  26,987 article pairs for \aan, and randomly selected 300,000 article pairs for both \aminer and \magdata.
}%% eat

\stitle{Algorithms}.
We compared our approach with three competitive methods: \pagerank~\cite{Brin98:PageRank}, \futurerank~\cite{sayyadi09} and \hhgrank~\cite{Liang16AAAI}.

\noindent
(1) \pagerank (PageRank) is a classic method that uses only citation information to rank scholarly articles.
%and articles are ranked according to PageRank scores computed on the citation graph.

\noindent
(2) \futurerank (FutureRank) combines citation, temporal and other heterogeneous information to rank scholarly articles.
%by predicting their future PageRank.
%is a \pagerank based ranking methods which is able to evaluate the importance of articles by predicting their future ranking. In order to do that, it uses both citation network and other available information such as the authorship network and the publication time of the articles.

\noindent
(3) \hhgrank (HHGBiRank) is a very recent method using both citation and heterogeneous information, such that heterogeneous entities are mutually reinforced based on hypernetworks.
%It uses hypernetworks to propagate importance/authority between entities.
%a scientific literature ranking algorithm based on the heterogeneous academic hypernetwork. An ingredient of \hhgrank is based on the fact that, the importance of scholarly articles not only depends on the frequency it has been cited and the quality of citation but also depends on the importance of authors and researchers of the paper.

\stitle{Implementation}.
All algorithms were implemented with Microsoft Visual C++.
%Parameters.
For all algorithms, (a) the damping parameter $d$ and the iteration threshold $\epsilon$ were fixed to 0.85 and $10^{-8}$, respectively,
(b) \marked{the default splitting years were selected such that the ranking data accounted for around 75\% of all, which were 2008 on \aan and 2012 on both \aminer and \magdata,} and,
(c) for the sake of fairness, aggregating parameters of \futurerank, \hhgrank and \ensemblerank were tuned at the granularity of 0.1 and the best results were reported.
%
Moreover, $\rho$ was set to -0.2 for \futurerank following~\cite{sayyadi09}, and the time decaying factor $\sigma$ and the importance weighting factor $\lambda$ were set to -1 and 0.5  by default for \ensemblerank.

All experiments were conducted on a PC with 2 Intel Xeon E5--2630 2.4GHz CPUs and 64 GB of memory, running 64 bit Windows 7 professional system. The usage of virtual memory was forbidden. %in all of our tests.
When quantity measures are evaluated, the test was repeated over 5 times and the average results are reported.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t!]
%\vspace{-2ex}
\label{tab-result}
\begin{center}
\caption{\small Accuracy tests with \recom}
\begin{small}
\vspace{-.5ex}
\begin{tabular}{|c|c|c|c|c|}
\hline
{\bf Datasets}   &  \hspace{1ex}\pagerank\hspace{1ex}     & \hspace{1ex}\futurerank\hspace{1ex}  &  \hspace{1ex}\hhgrank\hspace{1ex}  &   \hspace{1ex}\ensemblerank\hspace{1ex}    \\
\hline \hline
\aan  & $0.671$   & $0.738$   & $0.758$     & {\bf 0.805}      \\  %\hline
\aminer  & $0.651$   & $0.729$   & $0.730$     & {\bf 0.778}      \\ %\hline
\magdata  & $0.615$   & $0.655$   & $0.658$     & {\bf 0.680}      \\ \hline
\end{tabular}
\vspace{-.5ex}
\end{small}
\end{center}
\vspace{-5ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

\newcommand{\graphscale}{0.36} %0.38
\newcommand{\graphmargin}{-4ex}
\newcommand{\exppath}{./exp/}
%\newcommand{\exppath}{./exp/wpr/}
%%% all in 1 Figure
\begin{figure*}[tb!]
%\vspace{-2ex}
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
%\hspace{10ex}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-futureyear}
\includegraphics[scale=\graphscale]{\exppath AAN_PairAcc1.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-t}
\includegraphics[scale=\graphscale]{\exppath AAN_PairAcc2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-fcdiff}
\includegraphics[scale=\graphscale]{\exppath AAN_PairAcc3.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-sigma}
\includegraphics[scale=\graphscale]{./exp/AAN_sigma2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aan}]{\label{exp-aan-lambda}
\includegraphics[scale=\graphscale]{./exp/AAN_lambda.eps}}
\\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1.5ex}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-futureyear}
\includegraphics[scale=\graphscale]{\exppath AMiner_PairAcc1.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-t}
\includegraphics[scale=\graphscale]{\exppath AMiner_PairAcc2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-fcdiff}
\includegraphics[scale=\graphscale]{\exppath AMiner_PairAcc3.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-sigma}
\includegraphics[scale=\graphscale]{./exp/AMiner_sigma2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \aminer}]{\label{exp-aminer-lambda}
\includegraphics[scale=\graphscale]{./exp/AMiner_lambda.eps}}
\\%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1.5ex}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-futureyear}
\includegraphics[scale=\graphscale]{\exppath MAG_PairAcc1.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-t}
\includegraphics[scale=\graphscale]{\exppath MAG_PairAcc2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-fcdiff}
\includegraphics[scale=\graphscale]{\exppath MAG_PairAcc3.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-sigma}
\includegraphics[scale=\graphscale]{./exp/MAG_sigma2.eps}}
%\quad\quad
\hspace{\graphmargin}
\subfigure[{\scriptsize \magdata}]{\label{exp-mag-lambda}
\includegraphics[scale=\graphscale]{./exp/MAG_lambda.eps}}
\end{center}
\vspace{-2.5ex}
\caption{\small Accuracy tests with \fcita (all) and \recom ((d)--(e), (i)--(j) and (n)--(o))}
\label{exp-pairacc}
\vspace{-2ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tb!]
%\vspace{1ex}
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
%\hspace{10ex}
\subfigure[{\scriptsize TWPageRank (batch vs. inc.)}]{\label{exp-aminer-time1}
\includegraphics[scale=\graphscale]{./exp/AMiner_time_twpr.eps}}
\hspace{0ex}
%\hfill
\subfigure[{\scriptsize Comparison of ranking algorithms}]{\label{exp-aminer-time2}
\includegraphics[scale=\graphscale]{./exp/AMiner_time.eps}}
\hspace{0ex}
%\hfill
\subfigure[{\scriptsize TWPageRank (batch vs. inc.)}]{\label{exp-mag-time1}
\includegraphics[scale=\graphscale]{./exp/MAG_time_twpr.eps}}
\hspace{0ex}
%\hfill
\subfigure[{\scriptsize Comparison of ranking algorithms}]{\label{exp-mag-time2}
\includegraphics[scale=\graphscale]{./exp/MAG_time.eps}}
\end{center}
\vspace{-2.5ex}
\caption{\small Efficiency tests on \aminer ((a)--(b)) and  \magdata ((c)--(d))}
\label{exp-time}
\vspace{-3ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Experimental Results}
\label{subsec-expres}

We next present our findings.

\stitle{Exp-1: Effectiveness with \recom}.
%\subsubsection{Exp-1: Effectiveness with \recom}
In the first set of our tests, we used ground-truth \recom to evaluate the effectiveness of our approach.
All algorithms used articles published before 2012, since article pairs of \recom were from this portion of articles.
Aggregating parameters were selected as follows: $(\alpha,\beta,\gamma)$ = $(0.1, 0.2, 0.2)$ for \futurerank, $(a_{i1},a_{i2},a_{i3})$ = $(0.6, 0.2, 0.2)$ for \hhgrank ($i\in[1,3]$), and $(\alpha,\beta)$ = $(0.1, 0.8)$ for \ensemblerank.
%The venue ensemble contributed most in \ensemblerank, indicating that venue information plays a key role when people recommend scholarly articles.
The results of \PairAcc are reported in Table~III.

The \PairAcc of \pagerank is much lower than the one of other algorithms, indicating that citation information alone is insufficient for scholarly article ranking, and other information helps to refine the results. Moreover, \ensemblerank consistently ranks better than all competitors. Indeed, \ensemblerank improves the \PairAcc over (\pagerank, \futurerank, \hhgrank) by (13.5\%, 6.8\%, 4.8\%) on \aan, (12.7\%, 5.0\%, 4.9\%) on \aminer, and (6.5\%, 2.5\%, 2.2\%) on \magdata, respectively.

\stitle{Exp-2: Effectiveness with \fcita}.
%\subsubsection{Exp-2: Effectiveness with \fcita}
In the second set of tests, we used ground-truth \fcita to evaluate the effectiveness.
%All algorithms produced results based on articles in ranking data.
Aggregating parameters were selected as follows: $(\alpha, \beta, \gamma)$ = $(0.7, 0.1,$ $0.2)$ for \futurerank, $(a_{i1}, a_{i2}, a_{i3})$ = $(0.3, 0.6, 0.1)$ for \hhgrank ($i\in[1, 3]$), and $(\alpha, \beta)$ = $(0.8, 0.1)$ for \ensemblerank.
%Here the citation component contributed most in \ensemblerank, since \fcita is based on citation information.
To evaluate the effectiveness of ranking in different scenarios, we varied three factors in our tests: the splitting year $Y_s$, the number $T_p$ of published years of articles, and the difference $dif$ of future citation counts.
%
Given $Y_s$, $T_p$ and $dif$, we only used article pairs whose articles were published within $[Y_s - T_p, Y_s)$ and the difference of future citation counts was equal to or larger than $dif$ to test the \PairAcc.
% no earlier than $T_p$ years before $Y_s$

%varying number of years as future period
\etitle{Exp-2.1}.
%\stitle{Exp-2.1}.
To evaluate the effectiveness of ranking \wrt\ {\em short-term and long-term importance},
we varied the splitting year $Y_s$ from 2006 to 2011 on \aan and from 2010 to 2015 on both \aminer and \magdata, while fixed $T_p$ = $+\infty$ and $dif$ = $1$, \ie using all scholarly article pairs.
%
Intuitively, large and small $Y_s$ correspond to short-term and long-term importance, respectively.
The results of \PairAcc are reported in Figs.~\ref{exp-aan-futureyear}, \ref{exp-aminer-futureyear} and \ref{exp-mag-futureyear}, in which the red markers $\Box$ in dashed lines mean that \hhgrank ran out of memory.

%For each $Y_s$ we generated benchmark pairs as described earlier, and tested \PairAcc using all pairs, \ie $b$ = $+\infty$, $dif$ = $1$.
%We did not use the latest year since the complete articles have not been included yet.

When varying $Y_s$, the \PairAcc of all algorithms increases with the increment of $Y_s$ on both \aminer and \magdata, indicating that it is easier to assess short-term (large $Y_s$) than long-term (small $Y_s$) importance. While the results on \aan do not follow this trend, possibly because \aan does not record the complete articles of 2007 and 2009.
Moreover, \ensemblerank consistently ranks better than all competitors, regardless of assessing short-term or long-term importance.
Indeed, \ensemblerank improves the \PairAcc over (\pagerank, \futurerank, \hhgrank) by (17.9\%, 5.4\%, 5.5\%) on \aan, (18.6\%, 7.7\%, 5.8\%) on \aminer, and  (16.7\%, 7.2\%, 2.9\%) on \magdata, respectively.

%varying number of years as evaluate period.
\etitle{Exp-2.2}.
%\stitle{Exp-2.2}.
To evaluate the effectiveness of ranking \wrt\ {\em the published time of articles},
we varied the number $T_p$ of published years from 1 to $+\infty$, while fixed $Y_s$ to default values of three datasets and $dif=1$, respectively. The results of \PairAcc are reported in Figs.~\ref{exp-aan-t}, \ref{exp-aminer-t} and \ref{exp-mag-t}.

When varying $T_p$, the \PairAcc of all algorithms increases with the increment of $T_p$, since old articles (large $T_p$) are easier to rank based on adequate information, while new articles (small $T_p$) are hard to rank with little information available. Moreover, \ensemblerank consistently ranks better than all competitors, especially when $T_p\le3$, \ie ranking recently published articles. Indeed, \ensemblerank improves the \PairAcc over (\pagerank, \futurerank, \hhgrank) by (19.0\%, 3.1\%, 3.9\%) on \aan, (25.0\%, 8.2\%, 6.3\%) on \aminer, and (23.6\%, 8.3\%, 3.2\%) on \magdata, on average, respectively.

%varying difference of future citation count in benchmark
\etitle{Exp-2.3}.
%\stitle{Exp-2.3}.
To evaluate the effectiveness of ranking \wrt\ {\em the difference of future citations},
we varied the difference $dif$ of future citation counts from 1 to 7, while fixed $Y_s$ to default values of three datasets and $T_i=+\infty$. The results of \PairAcc are reported in Figs.~\ref{exp-aan-fcdiff}, \ref{exp-aminer-fcdiff} and \ref{exp-mag-fcdiff}.

When varying $dif$, the \PairAcc of all algorithms increases with the increment of $dif$, since scholarly article pairs with larger $dif$ are easier to rank. Moreover, \ensemblerank consistently ranks better than all competitors, regardless of easy or difficult article pairs. Indeed, \ensemblerank improves the \PairAcc over (\pagerank, \futurerank, \hhgrank) by (12.0\%, 3.0\%, 3.2\%) on \aan, (14.0\%, 6.5\%, 4.6\%) on \aminer, and (13.4\%, 6.0\%, 2.4\%) on \magdata, on average, respectively.

%The pair accuracy results tell us that (a) \ensemblerank outperforms other methods on all datasets with all difference of future citation count and obtains the highest accuracy when the difference is greater than 6, and (b) the accuracy of all method increases with the addition of difference of future citation count which means it is easier for all methods to evaluate the importance of two scholarly articles in one pair when there is a obvious different between them. Our algorithm \ensemblerank improves the pair accuracy over \pagerank, \futurerank and \hhgrank by $(15.7\%, 2.8\%, 3.9\%)$ on \aan, $(17.3\%, 7.6\%, 5.8\%)$ on \aminer, and $(10.3\%, 4.4\%, 1.6\%)$ on \magdata, when evaluate all the pairs which have difference of future citation count greater than 0, which means \ensemblerank can evaluate and distinguish the articles only have small difference better.

\stitle{Exp-3: Efficiency}.
%\subsubsection{Exp-3: Efficiency}
In the third set of tests, we evaluated the efficiency of our algorithms.
%
We compared our algorithms with \powtwprscc and \powensemble, which were the same to \twprscc and \batensemble except using power method for TWPageRank computation, and with algorithms \futurerank and \hhgrank.
Here \pagerank was omitted due to its effectiveness.
%
We varied the splitting year $Y_s$ from 2009 to 2016 and tested the running time on both \aminer and \magdata.
%
For incremental algorithms, base and update parts consisted of data before 2008 and within $[2008, Y_s)$, respectively.
%And the incremental ratio evaluated by the size of data was 0.11, 0.25, 0.39, 0.55, 0.73, 0.93, 1.14 and 1.30 for $Y_s\in[2009,2016]$.
%
The results of running time are reported in Fig.~\ref{exp-time}, where the red markers $\Box$ in dashed lines mean that \hhgrank ran out of memory.
%The results on the large data \magdata are reported in Fig.~\ref{exp-time}, where red markers \marked{$\Box$} in dashed line mean \hhgrank ran out of memory, and the results on \aminer are left in~\cite{SARank-full}.

When varying $Y_s$, the running time of all algorithms increases with the increment of $Y_s$, and our incremental algorithms
consistently run faster than all competitors, especially with less update data.
%
For TWPageRank computation, algorithm \inctwprscc is on average (1.9, 3.8) and (2.5, 4.1) times faster than (\twprscc, \powtwprscc) on \aminer and \magdata, respectively.
%
For scholarly article ranking, algorithm \incensemble is on average (1.7, 3.1, 2.8, 117) and (2.0, 3.0, 4.4, 245) times faster than (\batensemble, \powensemble, \futurerank, \hhgrank) on \aminer and \magdata, respectively.

%\etitle{Remarks}.
In our tests we adopted a yearly update policy due the limitation of  available time information. In practice our algorithms may bring more efficiency benefits since the ranking is usually more frequent, such that the data updates are smaller and the unaffected area is very likely much larger.

%algorithm \batensemble is on average (1.3, 2.5, 348) times faster than (\powensemble, \futurerank, \hhgrank), respectively. And algorithm \incensemble further improves the efficiency by 22\% on average, compared with \batensemble.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\graphscaleexpapp}{0.25}
\newcommand{\graphmarginexpapp}{-2ex}
%%% all in 1 Figure
\begin{figure*}[tb!]
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
\subfigure[{\scriptsize \aan with \recom}]{\label{exp-aan-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/AAN-para-recm.eps}}
%\quad\quad
%\hspace{\graphmarginexpapp}
\hfill
\subfigure[{\scriptsize \aminer with \recom}]{\label{exp-aminer-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/AMiner-para-recm.eps}}
%\quad\quad
%\hspace{\graphmarginexpapp}
\hfill
\subfigure[{\scriptsize \magdata with \recom}]{\label{exp-mag-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/MAG-para-recm.eps}}
\\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-2ex}
%\hspace{-10ex}
\subfigure[{\scriptsize \aan  with \fcita}]{\label{exp-aan-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/AAN-para-fcita.eps}}
%\quad\quad
%\hspace{\graphmarginexpapp}
\hfill
\subfigure[{\scriptsize \aminer with \fcita}]{\label{exp-aminer-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/AMiner-para-fcita.eps}}
%\quad\quad
%\hspace{\graphmarginexpapp}
\hfill
\subfigure[{\scriptsize \magdata with \fcita}]{\label{exp-mag-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/MAG-para-fcita.eps}}
\end{center}
\vspace{-2.5ex}
\caption{\small Accuracy tests: varying aggregating parameters $\alpha$ and $\beta$}
\label{exp-ab}
\vspace{-3ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\stitle{Exp-4: Impacts of parameters}.
%\subsubsection{Exp-4: Impacts of parameters}.
In the last set of tests, we evaluated the impacts of time decaying factor $\sigma$, importance weighting factor $\lambda$, aggregating parameters $\alpha$ and $\beta$, and the TWPageRank. We fixed these parameters as well as $Y_s$ to their default values, used the TWPageRank proposed in this work by default, and tested the \PairAcc with the entire \recom and \fcita (\ie $T_i=+\infty$, $dif=1$).

%We present main results only and more details are available in~\cite{SARank-full}.

\etitle{Exp-4.1}.
%\stitle{Exp-4.1}.
To evaluate the impacts of the time decaying factor $\sigma$, we varied $\sigma$ from -1.6 to -0.4.
%, while fixed $Y_s$ to default values, $T_i=+\infty$, $dif=1$ and $\lambda=0.5$.
The results of \PairAcc are reported in Figs.~\ref{exp-aan-sigma}, \ref{exp-aminer-sigma} and \ref{exp-mag-sigma}.
%with both sets of ground-truth

When varying $\sigma$, the \PairAcc of \ensemblerank is very stable on all datasets using both \recom and \fcita. Indeed, with \recom and \fcita, the \PairAcc only varies (0.42\%, 1.55\%, 0.81\%) and (1.26\%, 0.96\%, 1.16\%) on (\aan, \aminer, \magdata), respectively.
%
%We omitted the detailed results of running time due to space constraint.
The running time varies (11.3\%, 8.6\%) on average only on (\aminer, \magdata), respectively.
%(0.18, 33.6) seconds, \ie

%Both of these show the robustness of \ensemblerank to the time decaying factor $\sigma$.

%As we can see from the figure, our method \ensemblerank is almost stable with the reduction of $\sigma$, since there is only a small fluctuation and the accuracy of our methods is always higher than the best baseline result in all datasets regardless of the change of $\sigma$. This means \ensemblerank is insensitive with $\sigma$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[tb!]
%\vspace{-2ex}
\begin{center}
\caption{\small Accuracy tests using different components with \recom (rows 2--4) and \fcita (rows 5--7).}
\label{tab-recom}
\begin{small}
\vspace{-.5ex}
\begin{tabular}{|c| c |c | c|}
\hline
{\bf Datasets} & {\bf C}\hspace{5ex}{\bf V}\hspace{5ex}{\bf A} & {\bf CV}\hspace{3ex}{\bf CA}\hspace{3ex}{\bf VA} & {\bf CVA} \\
\hline \hline
% \recom
\aan & 0.752 \ 0.616 \ 0.649 & 0.809 \ 0.764 \ 0.747 & {\bf 0.810} \\
\aminer & 0.735 \  0.581 \  0.640 & 0.784 \ 0.749 \ 0.729 & {\bf 0.785} \\
\magdata & 0.635 \ 0.534 \ 0.553 & 0.697 \ 0.673 \  0.648 & {\bf 0.698} \\ \hline
% \ficta
\aan & 0.785 \ 0.557 \ 0.761 & 0.849 \ 0.866 \ 0.771 & {\bf 0.870} \\
\aminer & 0.713 \  0.603 \  0.725 & 0.843 \ 0.847 \ 0.740 & {\bf 0.856} \\
\magdata & 0.736 \ 0.628 \ 0.718 & 0.848 \ 0.857 \ 0.751 & {\bf 0.874} \\
\hline
\end{tabular}
\end{small}
\end{center}
\vspace{-6ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

\etitle{Exp-4.2}.
%\stitle{Exp-4.2}.
To evaluate the impacts of importance weighting factor $\lambda$, we varied $\lambda$ from 0 to 1.
%while fixed $Y_s$ to default values, $T_i=+\infty$, $dif=1$ and $\sigma=-1.0$.
The results of \PairAcc are reported in Figs.~\ref{exp-aan-lambda}, \ref{exp-aminer-lambda} and \ref{exp-mag-lambda}. Note that parameter $\lambda$ has no impacts on efficiency.
%with both sets of ground-truth

When varying $\lambda$, the \PairAcc of \ensemblerank first increases and then decreases on all datasets with both \fcita and \recom, except on \aminer with \recom.
%\marked{The value of $\lambda$ for \ensemblerank to achieve the best effectiveness is (0.6, 0, 0.2) and (0.6, 0.4, 0.1) on (\aan, \aminer, \magdata) with \recom and \fcita, respectively.}
This result indicates that combining prestige and popularity generally produces more robust results than using either of prestige and popularity.
Indeed, with \recom and \fcita, the \PairAcc of combining prestige and popularity is (10.2\%, 10.7\%, 5.5\%) and (8.0\%, 8.7\%, 9.0\%) higher than using prestige alone, and is (1.2\%, -0.1\%, 1.0\%) and (1.0\%, 1.0\%, 0.3\%) higher than using popularity alone on (\aan, \aminer, \magdata), respectively.

%The selection of $\lambda$ is influenced by ground-truth, such that the best $\lambda$ falls into $[xx,xx]$ and $[yy,yy]$ on \fcita and \recom, respectively. Moreover, equally weighting, \ie $\lambda=0.5$, is a good default setting when no query information is available in advance.
%Indeed, the best obtained \PairAcc using (\fcita, \recom) is only (0.10\%, 0.38\%), (0.04\%, 2.59\%) and (0.06\%, 0.91\%)  higher than the \PairAcc of equally weighting on \aan, \aminer and \magdata, respectively.

\etitle{Exp-4.3}.
To evaluate the impacts of aggregating parameters $\alpha$ and $\beta$, we varied $\alpha$ and $\beta$ at the granularity of 0.01. Again, parameters $\alpha$ and $\beta$ have few impacts on efficiency. The results are reported in Fig.~\ref{exp-ab}, where the parameters selected earlier and their corresponding \PairAcc are marked with $*$.

When varying $\alpha$ and $\beta$, the \PairAcc of \ensemblerank changes gently, as shown in Fig.~\ref{exp-ab}.
The optimal \PairAcc is obtained within a single region, rather than a complex collection of optimal regions.
%
Moreover, the \PairAcc keeps at a high level within a certain ($\alpha$, $\beta$) combination space around the optimal region, as shown in Fig.~\ref{exp-ab}.
%For instance, consider a square of length 0.3, which covers 8.5\% of the parameter combination space. The fraction of parameters such that the \PairAcc is no worse than 1\% of the corresponding \PairAcc with marker $*$ is (73\%, 94\%) on \aan, (96\%, 87\%) on \aminer and (83\%, 95\%) on \magdata, using (\recom, \fcita), respectively.
%
Further, the optimal parameters on the same sets of ground-truth are very similar for (\aan, \aminer and \magdata), indicating that the setting of $\alpha$ and $\beta$ can be easily transferred across different datasets.
To conclude, \ensemblerank is very robust to parameters $\alpha$ and $\beta$, and it is quite flexible for choosing proper values of parameters $\alpha$ and $\beta$.

Moreover, this enables to verify the effectiveness of importance assembling from different components, whose results are reported in Table~IV, in which letters C, V and A stand for citation, venue and author components, respectively.
The ranking based on all components consistently performs the best, using both \recom and \fcita, which justifies the use of importance assembling for ranking scholarly articles.
%which, using \recom and \fcita, improves the \PairAcc over using components (C, V, A, CV, CA, VA) by (5.77\%, 19.4\%, 16.1\%, 0.09\%, 4.59\%, 6.28\%) and (9.54\%, 23.7\%, 5.90\%, 2.50\%, 0.71\%, 4.79\%) on \aan, (6.94\%, 23.7\%, 14.4\%, 0.21\%, 1.56\%, 7.67\%) and (17.68\%, 12.4\%, 9.61\%, 0.33\%, 1.88\%, 6.34\%) on \aminer, and (6.29\%, 16.38\%, 14.45\%, 0.05\%, 2.43\%, 5.02\%) and (11.43\%, 19.2\%, 11.2\%, 1.44\%, 0.77\%, 9.62\%) on \magdata, respectively.

\eat{
\etitle{Exp-4.3}.
%\stitle{Exp-4.3}.
To evaluate the impacts of aggregating parameters $\alpha$ and $\beta$, we varied $\alpha$ and $\beta$ at the granularity of 0.01.
%while fixed $Y_s$ to default values, $T_i=+\infty$, $dif=1$, $\sigma=-1.0$ and $\lambda=0.5$.
Again, parameters $\alpha$ and $\beta$ have few impacts on efficiency. Due to space limitations, we only present the main results and more details are available at~\cite{SARank-full}.

Indeed, \ensemblerank is very robust to parameters $\alpha$ and $\beta$.
(a) When varying $\alpha$ and $\beta$, the \PairAcc of \ensemblerank changes gently. (b) \PairAcc also keeps at a high level within a certain ($\alpha$, $\beta$)  combination space. Finally, (c) the optimal parameters on the same set of ground-truth are very similar for \aan, \aminer and \magdata. That is, it is quite flexible for choosing proper values
of  parameters $\alpha$ and $\beta$.
} %%%%%%%% brief version of Exp-4.3

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tb!]
%\vspace{1ex}
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
\subfigure[{\scriptsize \aan with \recom}]{\label{exp-aan-recom-drank}
\includegraphics[scale=0.35]{./exp/AAN_TWPageRank_recom.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \aminer with \recom}]{\label{exp-aminer-recom-drank}
\includegraphics[scale=0.35]{./exp/AMiner_TWPageRank_recom.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \magdata with \recom}]{\label{exp-mag-recom-drank}
\includegraphics[scale=0.35]{./exp/MAG_TWPageRank_recom.eps}}
\\%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1.5ex}
\subfigure[{\scriptsize \aan with \fcita}]{\label{exp-aan-fcita-drank}
\includegraphics[scale=0.35]{./exp/AAN_TWPageRank_fcita.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \aminer with \fcita}]{\label{exp-aminer-fcita-drank}
\includegraphics[scale=0.35]{./exp/AMiner_TWPageRank_fcita.eps}}
\hfill
%\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \magdata with \fcita}]{\label{exp-mag-fcita-drank}
\includegraphics[scale=0.35]{./exp/MAG_TWPageRank_fcita.eps}}
\end{center}
\vspace{-2.5ex}
\caption{\small Impacts of the TWPageRank on accuracy: varying importance weighting
factor $\lambda$}
\label{exp-drank}
\vspace{-3ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\drank}{\kw{DRank}}

\etitle{Exp-4.4}.
\marked{To evaluate the impacts of the proposed TWPageRank, we compared our approach \ensemblerank with an algorithm alternative (referred to as \drank) the same to \ensemblerank except exploiting exponentially decayed impact weights, \ie $w(u,v)=e^{\sigma(T_u-T_v)}$ in Eq.~(\ref{eq-infl-weights}).
%The two algorithms produce the same popularity while different prestige.
To better understand the impacts, we varied the importance weighting factor $\lambda$ from 0.1 to 1. Note that the ranking results are the same when $\lambda=0$ due to the same popularity computation. The results are reported in Fig.~\ref{exp-drank}, where the numbers represent the improvement of \PairAcc by \ensemblerank over the one by \drank.}

\marked{
When varying $\lambda$, the \PairAcc of \ensemblerank is better than the one of \drank in most cases, which shows the superiority of the TWPageRank than exploiting exponentially decayed weights.
The difference of \PairAcc by the two algorithms is higher with \recom than with \fcita, since the two algorithms are using citation information to predict past and future citations with \fcita.
Moreover, algorithm \ensemblerank is consistently better than \drank when $0.5 \le \lambda \le 0.9$.
%, which, with \recom and \fcita, improves the \PairAcc by (2.88\%, 3.91\%, 3.90\%) and (0.55\%, 0.50\%, 0.22\%) on (\aan, \aminer, \magdata) on average, respectively.
The improvement decreases with the decrease of $\lambda$ as the popularity dominates the ranking with small $\lambda$, and in some cases, \drank outperforms \ensemblerank. %as the prestige and popularity orders of article pairs are more diverse for \drank than \ensemblerank.
Overall, with \recom and \fcita, \ensemblerank improves the \PairAcc over \drank by (1.78\%, 3.07\%, 3.20\%) and (0.29\%, 0.48\%, 0.11\%) on (\aan, \aminer, \magdata) on average, respectively.
}

\marked{
The TWPageRank has little impacts on efficiency, and the running time of the two algorithms only varies (6.34\%, 4.83\%) on (\aminer, \magdata) on average, respectively.}

\eat{
With the increment of $\lambda$, \ensemblerank has more promotion than DRank and the \PairAcc of DRank is better than \ensemblerank with small $\lambda$, possibly due to the addition of popularity will correct the mistaken pairs better on DRank, although \ensemblerank rank more pairs correctly.
In addition, the change of \PairAcc with \recom is higher than the one with \fcita, possibly due to the article pairs in \fcita are of the same years.
Moreover, the \PairAcc of \ensemblerank is better than its counterparts from $\lambda=0.5$ to $\lambda=1$, except on \aminer with \fcita. Recall that in Fig.~\ref{exp-aminer-lambda} using popularity alone gives the best results on \aminer, indicating that the prestige computed by TWPageRank is less accurate on \aminer than on the other two datasets.
%
Indeed, with \recom and \fcita, the \PairAcc of \ensemblerank is (2.20\%, 6.63\%, 5.68\%) and (0.25\%, 0.05\%, 0.05\%) higher than DRank on (\aan, \aminer, \magdata), respectively, when using prestige alone, and is (1.73\%, 2.97\%, 2.92\%) and (0.22\%, -0.08\%, 0.17\%) higher when combining prestige and popularity, respectively, on average.
%
Finally, the TWPageRank has little impacts on efficiency, and the running time of \ensemblerank and its counterparts only changes (6.34\%, 4.83\%) on (\aminer, \magdata) on average, respectively.
}

\stitle{Summary}.
From these tests we find the followings.

\sstab(1) Our model \ensemblerank is effective for ranking scholarly articles, which is consistently better than competitive methods in all tests. With \recom and \fcita, \ensemblerank improves \PairAcc over (\pagerank, \futurerank, \hhgrank) by
(13.5\%, 6.8\%, 4.8\%) and (12.0\%, 3.0\%, 3.2\%) on \aan,
(12.7\%, 5.0\%, 4.9\%) and (14.0\%, 6.5\%, 4.6\%) on \aminer, and
(6.5\%, 2.5\%, 2.2\%) and (13.4\%, 6.0\%, 2.4\%) on \magdata, on average, respectively.
%, and it has a great advantage in evaluating the importance in a long term. Furthermore, it is more accurate evaluating articles which have just published and is in lack of citations, since it uses both venue network and author information besides of citation network. Indeed, it improves the accuracy by $(7.9\%, 3.2\%, 2.3\%)$ and $(14.4\%, 5.0\%, 3.8\%)$ over \pagerank, \futurerank and \hhgrank on average of three datasets with recommendation based ground truth and future citation ground truth, respectively.

\sstab(2) Our batch algorithm \batensemble and incremental algorithm \incensemble are also efficient.
%
Our incremental algorithm \incensemble is on average (1.7, 3.1, 2.8, 117) and (2.0, 3.0, 4.4, 245) times faster than (\batensemble, \powensemble, \futurerank, \hhgrank)  on the large \aminer and \magdata, respectively.

%The batch algorithm \batensemble is on average (1.3, 2.5, 348) times faster than (\powensemble, \futurerank, \hhgrank)  on the largest \magdata, respectively.

%\noindent (3) Our incremental algorithms are much faster than their batch counterparts in practice, even their time complexity is very close. Indeed, algorithms \inctwprdag, \inctwprscc and \incensemble further improve the efficiency of (\twprdag, \twprscc, \batensemble) by (23\%, 38\%, 22\%) on average, respectively.

\sstab(3) Our ranking model \ensemblerank introduces the time decaying factor $\sigma$, importance weighting factor $\lambda$ and aggregating parameters $\alpha$ and $\beta$ for the sake of practicability and flexibility in real-life applications, and, from our tests, \ensemblerank is very robust to these parameters. Moreover, the proposed TWPageRank is generally more effective than directly using exponentially decayed impact weights.

### 2017-09-19 icde/sec-exp.tex

@@
 \stitle{Accuracy metric and ground-truth}.
-We adopted the {\em pairwise accuracy} introduced by Microsoft~\cite{Richardson06:BPR,wsdmcup} to evaluate the ranking quality, \ie the fraction of times that a ranking agrees with the correct ranking orders of scholarly article pairs.
-We constructed two sets of ground-truth importance orders of article pairs with \recom and \fcita.
+We adopted the {\em pairwise accuracy} introduced by Microsoft~\cite{Richardson06:BPR,wsdmcup} to evaluate the ranking quality, \ie the fraction of times that a ranking agrees with the correct ranking orders of scholarly article pairs:
 
-\eat{
 \vspace{-1ex}
@@
 \end{small}
-\vspace{-3ex}
-}
+\vspace{-2ex}
+
+We constructed two sets of ground-truth importance orders of article pairs with \recom and \fcita.
 
@@
 %
-However, the number of all citations is obviously biased to old articles.
-Some work adopts the number of future citations~\cite{Wang13AAAI,Wang16TIST,Li08TSRanking}, which is also not appropriate since this gives an estimation of impacts of articles in the near future, not at the concerned time.
-Differently, we propose to use the number of past and future citations, where past and future periods span the same length of time such that the number of citations within the two periods reveals the importance of articles at the conerned time.
+However, the number of entire citations is obviously biased to old articles.
+Some work adopts the number of future citations~\cite{Wang13AAAI,Wang16TIST,Li08TSRanking}, which is also not appropriate since this only estimates of future impacts of articles, not at the concerned time.
+For a fair ranking benchmark, we propose to use both past and future citations with the same period of time \wrt\ the concerned time, such that the number of citations within these two periods reveals the importance of articles at the concerned time.
 %
-We hence divided each dataset into two parts by a splitting year where the data before the splitting year (exclusive) were used for ranking and the remaining data as well as the most recent part of ranking data which spans the same time as the remaining data were used to count the numbers of past and future citations.
+We hence divided each dataset into two parts with a splitting (concerned) time such that (a) the data before the splitting time is used for ranking model, (b) the remain part of data is used to collect future citations, and (c) the most recent part of the data for ranking model with the same time span as the future citations is used to collect past citations.
+%
 %
@@
 For all algorithms, (a) the damping parameter $d$ and the iteration threshold $\epsilon$ were fixed to 0.85 and $10^{-8}$, respectively,
-(b) \marked{the default splitting years were selected such that the ranking data accounted for around 75\% of all, which were 2008 on \aan and 2012 on both \aminer and \magdata,} and,
+(b) the default splitting years were selected such that the part of data for ranking model accounted for around 75\% of the entire data, which were 2008 on \aan and 2012 on both \aminer and \magdata, and,
 (c) for the sake of fairness, aggregating parameters of \futurerank, \hhgrank and \ensemblerank were tuned at the granularity of 0.1 and the best results were reported.
@@
 \caption{\small Accuracy tests with \recom}
-\begin{small}
-\vspace{-.5ex}
+%\begin{small}
+%\vspace{-.5ex}
 \begin{tabular}{|c|c|c|c|c|}
@@
 \end{tabular}
-\vspace{-.5ex}
-\end{small}
+%\vspace{-.5ex}
+%\end{small}
 \end{center}
-\vspace{-5ex}
+\vspace{-4ex}
 \end{table}

### 2017-09-19 icde/sec-exp.tex

@@
 \end{center}
-\vspace{-2.5ex}
+\vspace{-2ex}
 \caption{\small Efficiency tests on \aminer ((a)--(b)) and  \magdata ((c)--(d))}
@@
 \end{center}
-\vspace{-2.5ex}
+\vspace{-2ex}
 \caption{\small Accuracy tests: varying aggregating parameters $\alpha$ and $\beta$}
@@
 \label{tab-recom}
-\begin{small}
-\vspace{-.5ex}
+%\begin{small}
+%\vspace{-.5ex}
 \begin{tabular}{|c| c |c | c|}
@@
 \end{tabular}
-\end{small}
+%\end{small}
 \end{center}
-\vspace{-6ex}
+\vspace{-4ex}
 \end{table}
@@
 \end{center}
-\vspace{-2.5ex}
+\vspace{-2ex}
 \caption{\small Impacts of the TWPageRank on accuracy: varying importance weighting
@@
 \etitle{Exp-4.4}.
-\marked{To evaluate the impacts of the proposed TWPageRank, we compared our approach \ensemblerank with an algorithm alternative (referred to as \drank) the same to \ensemblerank except exploiting exponentially decayed impact weights, \ie $w(u,v)=e^{\sigma(T_u-T_v)}$ in Eq.~(\ref{eq-infl-weights}).
+\marked{To evaluate the impacts of our TWPageRank, we compared our \ensemblerank with \drank, an alternative of \ensemblerank by removing the peak time in  Eq.~(\ref{eq-infl-weights}) of  TWPageRank, \ie $w(u,v)=e^{\sigma(T_u-T_v)}$.
+% with a directly exponentially decayed impact weights without peak times, \ie , .
 %The two algorithms produce the same popularity while different prestige.
@@
 
-\marked{
-When varying $\lambda$, the \PairAcc of \ensemblerank is better than the one of \drank in most cases, which shows the superiority of the TWPageRank than exploiting exponentially decayed weights.
-The difference of \PairAcc by the two algorithms is higher with \recom than with \fcita, since the two algorithms are using citation information to predict past and future citations with \fcita.
+When varying $\lambda$, the \PairAcc of \ensemblerank is better than the one of \drank in most cases, which shows the superiority of the TWPageRank than exploiting exponentially decayed weights directly without introducing the peak time.
+The \PairAcc difference of these two algorithms is higher on \recom than on \fcita, since the two algorithms are just using citation information to predict past and future citations with \fcita.
 Moreover, algorithm \ensemblerank is consistently better than \drank when $0.5 \le \lambda \le 0.9$.
@@
 Overall, with \recom and \fcita, \ensemblerank improves the \PairAcc over \drank by (1.78\%, 3.07\%, 3.20\%) and (0.29\%, 0.48\%, 0.11\%) on (\aan, \aminer, \magdata) on average, respectively.
-}
 
-\marked{
-The TWPageRank has little impacts on efficiency, and the running time of the two algorithms only varies (6.34\%, 4.83\%) on (\aminer, \magdata) on average, respectively.}
+The TWPageRank has small impacts on efficiency, and the running time of the two algorithms only varies (6.34\%, 4.83\%) on (\aminer, \magdata) on average, respectively.
 

### 2017-09-19 icde/sec-related.tex

%\stitle{Related work}.

\section{Related work} \label{sec-related}

%We summarize related work as follows.

Scholarly article ranking has shifted from citation count analysis~\cite{Garfield471,Hirsch15112005} to graph analysis~\cite{ChenXMR07,Zhou07-CoRank,Jiang12-MRank,Liang16AAAI,Li08TSRanking,Wang13AAAI,WalkerXKM07,sayyadi09,
Wang16TIST,Ng11KDD}.
Based on the information used, these methods are divided into four categories: (a) using the citation information only~\cite{Garfield471,Hirsch15112005,ChenXMR07,Ng11KDD}, (b) using the citation and temporal information~\cite{Li08TSRanking,WalkerXKM07}, (c) using the citation information and other heterogeneous information, \eg authors and venues of articles~\cite{Zhou07-CoRank,Jiang12-MRank,Liang16AAAI}, and (d) combining the citation, temporal and other heterogeneous information~\cite{sayyadi09,Wang16TIST,Wang13AAAI}.
Our work belongs to the last category aiming at fully employing information available for scholarly article ranking.
%
%Moreover, recent work has also leveraged external data to improve the ranking quality, \eg using Knowledge Graph Embedding to better understand the meaning of research concepts~\cite{XiongPCWWW17}, and has explored scientific journal ranking \cite{PackalenB17} and scholar ranking \cite{ZhangNBKZX17}. Different from these, our work ranks articles based on scholarly data only.

%\stitle{PageRank\&weighted PageRank algorithms}.

%PageRank \cite{Brin98:PageRank} and its extensions have been extensively used for citation analyses \cite{Waltman2014}. While PageRank equally propagates scores along outlinks, Weighted PageRank \cite{Xing04:WPR} extends PageRank by distributing scores based on the popularity of pages. Different from previous work, the Time-Weighted PageRank proposed in this work discriminately propagates scores in terms of citation statistics.

PageRank \cite{Brin98:PageRank} and its extensions have been extensively used for citation analyses \cite{Waltman2014}. While PageRank equally propagates scores along outlinks, Weighted PageRank extends PageRank by distributing scores based on certain criteria such as popularity of pages~\cite{Xing04:WPR} or authority of authors~\cite{Ding11}. Both these approaches fail to capture the time-dependent characteristics, a key factor for scholarly article ranking. There has been work extending temporal information into PageRank, \eg exponential decayed weights~\cite{Li08TSRanking}, exponential decayed initial vector~\cite{WalkerXKM07} and time-dependent weights based on co-authorship~\cite{FIALA2012370}. Different from previous work, the Time-Weighted PageRank of this work discriminately propagates scores in terms of citation statistics.

%\stitle{Dynamic algorithms}.

Dynamic algorithms have proven useful for various tasks by avoiding computing from scratch~\cite{RamalingamR93}.
% and only recomputing those affected by updates
%Dynamic algorithms have proven useful for graph analysis tasks, \eg incremental graph pattern matching~\cite{FanWW13} and  incremental simrank computation~\cite{YuLZ14}.
To our knowledge, little concern has been paid to dynamic scholarly article ranking except that~\cite{GhoshKHLL11} uses PageRank in dynamic citation networks. However, its solution is based on a strong and impractical assumption that there are no citations between articles in the same years.
Further, although there exist several studies on incremental PageRank computation~\cite{DesikanPSK05,AbiteboulPC03,WuR09} and on incremental PageRank approximation \cite{BahmaniCG10,BahmaniKMU12}, they are not designed for scholarly article ranking.
%
Different from previous work, we study scholarly article ranking in a dynamic environment in terms of
the citation characteristics of scholarly articles, which has never been exploited before.

%Our approach only makes the assumption that there are no mutual references within the citation network, which, we admit, violates xx\% of total citations on \magdata, and is significantly different (yy\% on \magdata) from~\cite{GhoshKHLL11}.  - move to Section 3

Ensemble methods use multiple learners to obtain better performance than could be obtained from a constituent learner alone~\cite{zhihua-book}.
%In this work, we leverage ensembles to produce better and robust results for scholarly article ranking~\cite{zhihua-book,wsdmcup,DuanAMHH16}.
In this work, we leverage  importance assembling  to produce better and more robust results for scholarly article ranking~\cite{zhihua-book,wsdmcup,DuanAMHH16}.

### 2017-09-19 icde/sec-exp.tex

@@
 \label{exp-time}
-\vspace{-3ex}
+\vspace{-2ex}
 \end{figure*}
@@
 \label{exp-ab}
-\vspace{-3ex}
+\vspace{-2ex}
 \end{figure*}
@@
 \label{exp-drank}
-\vspace{-3ex}
+\vspace{-2ex}
 \end{figure*}
@@
 \etitle{Exp-4.4}.
-\marked{To evaluate the impacts of our TWPageRank, we compared our \ensemblerank with \drank, an alternative of \ensemblerank by removing the peak time in  Eq.~(\ref{eq-infl-weights}) of  TWPageRank, \ie $w(u,v)=e^{\sigma(T_u-T_v)}$.
+To evaluate the impacts of our TWPageRank, we compared our \ensemblerank with \drank, an alternative of \ensemblerank by removing the peak time in  Eq.~(\ref{eq-infl-weights}) of  TWPageRank, \ie $w(u,v)=e^{\sigma(T_u-T_v)}$.
 % with a directly exponentially decayed impact weights without peak times, \ie , .
@@
 Note that the ranking results are the same when $\lambda=0$ due to the same popularity computation.
-The results are reported in Fig.~\ref{exp-drank}, where the numbers represent the improvement of \PairAcc by \ensemblerank over the one by \drank.}
+The results are reported in Fig.~\ref{exp-drank}, where the numbers represent the improvement of \PairAcc by \ensemblerank over the one by \drank.
 

### 2017-09-19 icde/sec-exp.tex

@@
 \subfigure[{\scriptsize \aan with \recom}]{\label{exp-aan-recom-drank}
-\includegraphics[scale=0.35]{./exp/AAN_TWPageRank_recom.eps}}
+\includegraphics[scale=0.36]{./exp/AAN_TWPageRank_recom.eps}}
 \hfill
@@
 \subfigure[{\scriptsize \aminer with \recom}]{\label{exp-aminer-recom-drank}
-\includegraphics[scale=0.35]{./exp/AMiner_TWPageRank_recom.eps}}
+\includegraphics[scale=0.36]{./exp/AMiner_TWPageRank_recom.eps}}
 \hfill
@@
 \subfigure[{\scriptsize \magdata with \recom}]{\label{exp-mag-recom-drank}
-\includegraphics[scale=0.35]{./exp/MAG_TWPageRank_recom.eps}}
+\includegraphics[scale=0.36]{./exp/MAG_TWPageRank_recom.eps}}
 \\%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subfigure[{\scriptsize \aan with \fcita}]{\label{exp-aan-fcita-drank}
-\includegraphics[scale=0.35]{./exp/AAN_TWPageRank_fcita.eps}}
+\includegraphics[scale=0.36]{./exp/AAN_TWPageRank_fcita.eps}}
 \hfill
@@
 \subfigure[{\scriptsize \aminer with \fcita}]{\label{exp-aminer-fcita-drank}
-\includegraphics[scale=0.35]{./exp/AMiner_TWPageRank_fcita.eps}}
+\includegraphics[scale=0.36]{./exp/AMiner_TWPageRank_fcita.eps}}
 \hfill
@@
 \subfigure[{\scriptsize \magdata with \fcita}]{\label{exp-mag-fcita-drank}
-\includegraphics[scale=0.35]{./exp/MAG_TWPageRank_fcita.eps}}
+\includegraphics[scale=0.36]{./exp/MAG_TWPageRank_fcita.eps}}
 \end{center}

### 2017-09-19 icde/sec-exp.tex

@@
 
-To alleviate the issue of citation missing of \aminer, we added citations by title matching  based on \magdata, and the finally total number of citations is is 14.26 million.
+To alleviate the issue of citation missing in \aminer, we added citations by title matching  based on \magdata, and the finally total number of citations is is 14.26 million.
 These datasets were further cleaned by deleting self-citations and citations from old articles to new ones, which accounted for (0.1\%, 0.8\%, 0.4\%) of the total citations on (\aan, \aminer, \magdata), respectively.
@@
 \end{center}
-\vspace{-2ex}
+\vspace{-1.5ex}
 \caption{\small Efficiency tests on \aminer ((a)--(b)) and  \magdata ((c)--(d))}
@@
 \end{center}
-\vspace{-2ex}
+\vspace{-1.5ex}
 \caption{\small Accuracy tests: varying aggregating parameters $\alpha$ and $\beta$}
@@
 \end{center}
-\vspace{-2ex}
+\vspace{-1.5ex}
 \caption{\small Impacts of the TWPageRank on accuracy: varying importance weighting

### 2017-09-19 icde/sec-exp.tex

@@
 \end{center}
-\vspace{-2.5ex}
-\caption{\small Accuracy tests with \fcita (all) and \recom ((d)--(e), (i)--(j) and (n)--(o))}
+\vspace{-1.5ex}
+\caption{\small Accuracy evaluation with \fcita (all) and \recom ((d)--(e), (i)--(j) and (n)--(o))}
 \label{exp-pairacc}
-\vspace{-2ex}
+\vspace{-1ex}
 \end{figure*}
@@
 \vspace{-1.5ex}
-\caption{\small Efficiency tests on \aminer ((a)--(b)) and  \magdata ((c)--(d))}
+\caption{\small Efficiency evaluation on \aminer ((a)--(b)) and  \magdata ((c)--(d))}
 \label{exp-time}
@@
 \vspace{-1.5ex}
-\caption{\small Accuracy tests: varying aggregating parameters $\alpha$ and $\beta$}
+\caption{\small Accuracy evaluation: varying aggregating parameters $\alpha$ and $\beta$}
 \label{exp-ab}
@@
 \\%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace{-1.5ex}
+\vspace{-.5ex}
 \subfigure[{\scriptsize \aan with \fcita}]{\label{exp-aan-fcita-drank}

### 2017-09-19 icde/sec-exp.tex

@@
 Again, parameters $\alpha$ and $\beta$ have few impacts on efficiency.
-The results are reported in Fig.~\ref{exp-ab}, where the parameters selected earlier and their corresponding \PairAcc are marked with $*$.
+The results are reported in Fig.~\ref{exp-ab}, where the parameters $\alpha$ and $\beta$ are set by default (used earlier) the corresponding values of $\alpha$-axis and $\beta$-axis, respectively, of the \PairAcc marked with $\star$.
 

### 2017-09-19 icde/sec-exp.tex

--- 2017-09-19 icde/sec-exp.tex
@@
 Again, parameters $\alpha$ and $\beta$ have few impacts on efficiency.
-The results are reported in Fig.~\ref{exp-ab}, where the parameters selected earlier and their corresponding \PairAcc are marked with $*$.
+The results are reported in Fig.~\ref{exp-ab}, where the parameters $\alpha$ and $\beta$ are set by default (used earlier) to the corresponding values of $\alpha$-axis and $\beta$-axis of the \PairAcc marked with $\star$, respectively.
 

### 2017-09-19 icde/sec-intro.tex

\section{Introduction}
\label{sec-intro}

Query independent ranking of scholarly articles has drawn significant attentions from both academia~\cite{Garfield471,ChenXMR07,Zhou07-CoRank,ShenAAAI16,Liang16AAAI,Jiang12-MRank,Waltman2014,TanLMGSW16} and industry~\cite{sem-scholar,g-scholar,Sinha15:MAG}.
Generally speaking, a ranking is {\em a function that assigns each item a numerical score}. Query independent ranking aims to give a static ranking based on the scholarly  data only, and is independent of how well articles match a specific query. Such a ranking plays a key role in literature recommendation systems, especially in the {\em cold start} scenario.

In the academia, the most popular approaches have witnessed a shift from citation-count analysis~\cite{Garfield471,Hirsch15112005} to graph analysis~\cite{ChenXMR07,Zhou07-CoRank,Jiang12-MRank,Waltman2014}, as graph-based methods further leverage the global or local structure of bibliographic networks and  the interactions among heterogeneous entities, and, hence, are typically more appropriate.
%
Efforts have also been made from the industry. Google Scholar~\cite{g-scholar} aims to rank articles in the way researchers do, weighing the full text, where they were published, who they were written by, as well as how often and how recently they have been cited; Microsoft Academic~\cite{ms-academic} considers how often and to which a publication is cited to determine the ranking; And
Semantic Scholar~\cite{sem-scholar} proposes to use the citation velocity, which is a weighted average number of article citations in the last three years.

%, \eg Google Scholar~\cite{g-scholar}, Semantic Scholar~\cite{sem-scholar} and Microsoft Academic~\cite{Sinha15:MAG}
% https://scholar.google.com/intl/zh-CN/scholar/about.html
% http://academic.research.microsoft.com/About/Help.htm
% https://www.semanticscholar.org/faq#citation-velocity

Scholarly articles are involved with multiple entities such as authors, venues, dates and references. That is, scholarly article ranking is essentially a problem of assessing the importance of nodes in a heterogeneous network.
However, effective and efficient ranking of nodes in such a large complex network is a challenging task due to the heterogeneous, evolving and dynamic natures of involved entities~\cite{AggarwalS14-survey,fcs-biggraph}.

First, even if we are only to rank one type of entities (\ie scholarly articles), the other types of entities (\eg venues and authors) are closely involved, and, moreover, different types of entities may have different impacts on the ranking of scholarly articles.
%
Second, the importance of articles evolve with time in a complex manner~\cite{WangSB13,Chakraborty15}.
%Newly published articles are very likely to have increasing impacts in the next few years, and those published many years ago tend to have decreasing impacts, as researchers potentially have more interests in recently reported results. Indeed, as shown by the statistics of three scholarly datasets (\aan, \aminer and \magdata) in Fig.~\ref{fig-citation}, the citation numbers of articles in general reach the peak in the first 1 or 2 years after their publication, and then decrease accordingly. % Note that we do not plot the proportion of citations at $x=0$ on \aminer, which is an impractical value of 23.6\%. The above citation pattern is described as a complex log-normal probability in~\cite{WangSB13}.
Newly published articles are very likely to have increasing impacts in the next few years, and those published many years ago tend to have decreasing impacts, which conforms to the universal citation pattern of articles such that the number of citations generally grows in the first two to three years, and then declines in the following years~\cite{Chakraborty15}. In addition to the universal one, individual articles indeed follow a diverse set of patterns featured by the peak time of the number of citations~\cite{Chakraborty15}.
Finally, academic data is dynamic and continuously growing. Indeed, the number of articles in \magdata has exceeded 126 million, and keeps increasing at around 5.7 million per year~\cite{Sinha15:MAG}. This may cause certain long-term biases into data, \eg the number of citations increases significantly over time~\cite{BornmannM15}, which should be properly considered for scholarly article ranking.

Query independent ranking of scholarly articles remains challenging~\cite{wsdmcup}, although there exists quite a bit of work on scholarly article ranking, \eg~\cite{Garfield471,ChenXMR07,Zhou07-CoRank,ShenAAAI16,Liang16AAAI,Jiang12-MRank,Waltman2014}.
Most previous work exploits the time-dependent information of scholarly data in the form of exponential decay~\cite{Li08TSRanking,Wang13AAAI,sayyadi09,WalkerXKM07}, which fails to capture the diverse citation patterns of individual articles~\cite{Chakraborty15}.
Further, to our knowledge, little concern has been paid to dynamic scholarly article ranking except \cite{GhoshKHLL11} with a strong and impractical assumption that there are no citations between papers published in the same years.
%\marked{Finally, the bias caused by the dynamic nature of data has never been exploited in scholarly article ranking}.

\stitle{Contributions \& Roadmap}.
To this end, we propose an effective and efficient approach for query independent scholarly article ranking in a dynamic environment.

\sstab(1) We first  propose a \underline{S}cholarly \underline{A}rticle \underline{Rank}ing model, referred to as \ensemblerank, by assembling the importance of three classes of entities (articles, venues and authors) for scholarly article ranking (Section \ref{sec-model}).
%
The importance is a combination of {\em prestige} and {\em popularity} to capture the evolving nature of entities.
%
To compute the prestige of articles and venues, we propose a novel {\em Time-Weighted PageRank} with a time decaying factor based on the citation statistics (instead of simple exponential decay), and the prestige of authors is the average prestige of all their published articles.
%
The popularity of an article is the sum of all its citation freshness (how close to the current year), while the one of venues and authors is the average popularity of their associated articles.
%
%Observe that (a), intuitively, prestige favors articles with many citations soon after their publication, and popularity favors those with recent citations, and (b) both prestige and popularity capture the evolving nature of entities.
%
To our knowledge, the Time-Weighted PageRank is among the first to incorporate the diverse citation patterns of individual articles for scholarly article ranking.
%and the long-term bias caused by the dynamic nature of data

\sstab(2)  We then develop  a batch algorithm for scholarly article ranking (Section \ref{sec-alg}), in which we propose a block-wise method for Time-Weighted PageRank in terms of an analysis of the citation characteristics of scholarly articles.

\sstab(3)
We further develop an incremental algorithm for dynamic scholarly article ranking (Section~\ref{sec-incAlg}), which partitions graphs into  {\em affected and unaffected areas}, and employs different updating strategies for nodes in affected and unaffected areas.

\sstab(4) Using three real-life scholarly datasets (\aan, \aminer and \magdata) and two sets of ground-truth (\recom and \fcita), we finally conduct an extensive experimental study (Section~\ref{sec-exp}).
(a) We find that our model \ensemblerank improves the pairwise accuracy \cite{Richardson06:BPR} over (\pagerank \cite{Brin98:PageRank}, \futurerank \cite{sayyadi09}, \hhgrank \cite{Liang16AAAI}) by
(13.5\%, 6.8\%, 4.8\%) and (12.0\%, 3.0\%, 3.2\%) \wrt\ \recom and \fcita  on \aan,
(12.7\%, 5.0\%, 4.9\%) and (14.0\%, 6.5\%, 4.6\%) \wrt\ \recom and \fcita on \aminer, and
(6.5\%, 2.5\%, 2.2\%) and (13.4\%, 6.0\%, 2.4\%) \wrt\ \recom and \fcita on \magdata, on average, respectively.
%
(b) Our batch algorithm \batensemble and incremental algorithm \incensemble are also efficient. Indeed, \incensemble is on average (1.7, 2.8, 116) and (2.0, 4.4, 245) times faster than (\batensemble, \futurerank, \hhgrank)  on the large \aminer and \magdata, respectively.
%%%%%%%%%%%%%%%%%%%%%%%%%

All the detailed proofs can be found in \cite{SARank-full}.

\eat{
\stitle{Organization}. The rest of our paper is organized as follows. The latter part of Section~\ref{sec-intro} summarizes related work. Section~\ref{sec-model} introduces the ranking model. Section~\ref{sec-alg} .... Section~\ref{sec-incAlg} .... Experimental results are reported in Section~\ref{sec-exp}, followed by conclusions in Section~\ref{sec-conc}.
}

### 2017-09-21 icde/sec-exp.tex

@@
 
-To alleviate the issue of citation missing in \aminer, we added citations by title matching  based on \magdata, and the finally total number of citations is is 14.26 million.
+To alleviate the issue of citation missing in \aminer, we added citations by title matching  based on \magdata, and the finally total number of citations is 14.26 million.
 These datasets were further cleaned by deleting self-citations and citations from old articles to new ones, which accounted for (0.1\%, 0.8\%, 0.4\%) of the total citations on (\aan, \aminer, \magdata), respectively.
@@
 However, the number of entire citations is obviously biased to old articles.
-Some work adopts the number of future citations~\cite{Wang13AAAI,Wang16TIST,Li08TSRanking}, which is also not appropriate since this only estimates of future impacts of articles, not at the concerned time.
+Some work adopts the number of future citations~\cite{Wang13AAAI,Wang16TIST,Li08TSRanking}, which is also not appropriate since this only estimates future impacts of articles, not at the concerned time.
 For a fair ranking benchmark, we propose to use both past and future citations with the same period of time \wrt\ the concerned time, such that the number of citations within these two periods reveals the importance of articles at the concerned time.
 %
-We hence divided each dataset into two parts with a splitting (concerned) time such that (a) the data before the splitting time is used for ranking model, (b) the remain part of data is used to collect future citations, and (c) the most recent part of the data for ranking model with the same time span as the future citations is used to collect past citations.
+We hence divided each dataset into two parts with a splitting (concerned) time such that (a) the data before the splitting time is used for ranking model, (b) the remaining part of data is used to collect future citations, and (c) the most recent part of the data for ranking model with the same time span as the future citations is used to collect past citations.
 %
@@
 %All algorithms produced results based on articles in ranking data.
-Aggregating parameters were selected as follows: $(\alpha, \beta, \gamma)$ = $(0.7, 0.1,$ $0.2)$ for \futurerank, $(a_{i1}, a_{i2}, a_{i3})$ = $(0.3, 0.6, 0.1)$ for \hhgrank ($i\in[1, 3]$), and $(\alpha, \beta)$ = $(0.8, 0.1)$ for \ensemblerank.
+Aggregating parameters were selected as follows: $(\alpha, \beta, \gamma)$ = $(0.7, 0.1, 0.2)$ for \futurerank, $(a_{i1}, a_{i2}, a_{i3})$ = $(0.3, 0.6, 0.1)$ for \hhgrank ($i\in[1, 3]$), and $(\alpha, \beta)$ = $(0.8, 0.1)$ for \ensemblerank.
 %Here the citation component contributed most in \ensemblerank, since \fcita is based on citation information.
-To evaluate the effectiveness of ranking in different scenarios, we varied three factors in our tests: the splitting year $Y_s$, the number $T_p$ of published years of articles, and the difference $dif$ of future citation counts.
+To evaluate the effectiveness of ranking in different scenarios, we varied three factors in our tests: the splitting year $Y_s$, the number $T_p$ of published years of articles, and the difference $dif$ of past and future citation counts.
 %
-Given $Y_s$, $T_p$ and $dif$, we only used article pairs whose articles were published within $[Y_s - T_p, Y_s)$ and the difference of future citation counts was equal to or larger than $dif$ to test the \PairAcc.
+Given $Y_s$, $T_p$ and $dif$, we only used article pairs whose articles were published within $[Y_s - T_p, Y_s)$ and the difference of past and future citation counts was equal to or larger than $dif$ to test the \PairAcc.
 % no earlier than $T_p$ years before $Y_s$
@@
 %\stitle{Exp-2.3}.
-To evaluate the effectiveness of ranking \wrt\ {\em the difference of future citations},
-we varied the difference $dif$ of future citation counts from 1 to 7, while fixed $Y_s$ to default values of three datasets and $T_i=+\infty$.
+To evaluate the effectiveness of ranking \wrt\ {\em the difference of past and future citations},
+we varied the difference $dif$ of past and future citation counts from 1 to 7, while fixed $Y_s$ to default values of three datasets and $T_i=+\infty$.
 The results of \PairAcc are reported in Figs.~\ref{exp-aan-fcdiff}, \ref{exp-aminer-fcdiff} and \ref{exp-mag-fcdiff}.
@@
 %
-We varied the splitting year $Y_s$ from 2009 to 2016 and tested the running time on both \aminer and \magdata.
+We varied the splitting year $Y_s$ from 2009 to 2015 and tested the running time on both \aminer and \magdata.
 %
@@
 \vspace{-1.5ex}
-\caption{\small Impacts of the TWPageRank on accuracy: varying importance weighting
+\caption{\small Impacts of TWPageRank on accuracy: varying importance weighting
 factor $\lambda$}

### 2017-09-21 icde/sec-alg.tex

@@
 \stitle{Block-wise algorithm~\twprscc}.  It takes as input a citation or venue graph $G$ and an iteration threshold $\epsilon$, and returns the TWPageRank vector of $G$.
-Moreover, to process an \scc instead of the entire graph, the edges of the citation or venue graph $G(V, E)$ are partitioned into the sets $E_i$ and $E_a$ of edges inside and across \sccs  such that $E_i\cap E_a = \emptyset$ and $E = E_i \cup E_a$.
+To process an \scc instead of the entire graph, the edges of the citation or venue graph $G(V, E)$ are partitioned into the sets $E_i$ and $E_a$ of edges inside and across \sccs  such that $E_i\cap E_a = \emptyset$ and $E = E_i \cup E_a$.
 The update rule in Eq.~(\ref{eq-twpr-update})  is revised accordingly to treat $E_i$ and $E_a$ separately as follows.
@@
 \begin{proofSketch}
-We first prove that the sum of changes after another iteration from $PR$, \ie $||d M^T PR + (1-d)e/n-PR||_1$, is smaller than $\epsilon$, and then prove that $||PR^*-PR||_1$ is smaller than the sum of changes.
+We first prove that the sum of changes after another iteration from $PR$, \ie $||d M^T PR + (1-d)e/n-PR||_1$, is smaller than $\epsilon$, and then prove that $||PR^*-PR||_1$ is smaller than the sum of changes computed earlier.
 %(see~\cite {ERank-full} for details).
@@
 %\begin{small}
-\vspace{-.5ex}
+%\vspace{-.5ex}
 \begin{tabular}{|c|c|c|c|c|}
@@
 
-To verify this observation, we also collect the statistics of citation graphs, venue graphs and Web graphs (shown in Table~\ref{tab-batch}), where Web graphs are extracted from berkely.edu and stanford.edu domains in 2002 and from the Google programming contest in 2002, respectively~\cite{LeskovecLDM09}.
+To verify this observation, we also collect the statistics of citation graphs, venue graphs and Web graphs (illustrated in Table~\ref{tab-batch}), where Web graphs are extracted from berkely.edu and stanford.edu domains in 2002 and from the Google programming contest in 2002, respectively~\cite{LeskovecLDM09}.
 Due to the existence of the ``bow tie'' structure and the giant \scc in Web graphs~\cite{BroderKMRRSTW00}, the edge ratios $|E_i|/|E|$ are greater than 59\% for Web graphs.
-In contrast, the \sccs in citation and venue graphs are quite small as a result of the temporal order of citation, and $|E_i|/|E|$ is less than 3\% for all tested citation and venue graphs.
+In contrast, the \sccs in citation and venue graphs are quite small as a result of the temporal order of citations, and $|E_i|/|E|$ is less than 3\% for all tested citation and venue graphs.
 %
-This specific structure in scholarly data has been ignored in the literature, and has a positive impact on computations.
+This specific structure in scholarly data has been long ignored in the past literature, which indeed has a positive impact on computations.
 Taking $t=100$ for example, algorithm \twprscc needs to scan $3|E|$ and $4|E|$ edges on citation and venue graphs, respectively, but over $59|E|$ edges on Web graphs.

### 2017-09-21 icde/sec-exp.tex

@@
 
-To alleviate the issue of citation missing in \aminer, we added citations by title matching  based on \magdata, and the finally total number of citations is 14.26 million.
+To alleviate the issue of citation missing in \aminer, we added citations by title matching  based on \magdata, and finally the  total number of citations is 14.26 million.
 These datasets were further cleaned by deleting self-citations and citations from old articles to new ones, which accounted for (0.1\%, 0.8\%, 0.4\%) of the total citations on (\aan, \aminer, \magdata), respectively.
@@
 %
-Moreover, articles in the same pair were required to be in similar research fields, by utilizing the Fields-Of-Study information on \magdata~\cite{Sinha15:MAG}, and published in the same year, similar to~\cite{Wang16TIST}.
+Moreover, articles in the same pairs were required to be in similar research fields, by utilizing the Fields-Of-Study information on \magdata~\cite{Sinha15:MAG}, and published in the same years, similar to~\cite{Wang16TIST}.
 We used all pairs (around 50,000) for \aan, and randomly chose 300,000 pairs for both \aminer and \magdata.

### 2017-09-21 icde/sec-incAlg.tex

@@
 \stitle{Auxiliary data structure maintenance}.
-Two auxiliary data structures in the batch algorithm~\twprscc need to be maintained : (a) on the block-wise graph,  a mapping that, given a node of graph $G$, returns the index of the \scc to which it belongs, and (b) the topological order of the nodes in the block-wise graph.
+Two auxiliary data structures in the batch algorithm~\twprscc need to be maintained: (a) the block-wise graph and  a mapping that, given a node of graph $G$, returns the index of the \scc to which it belongs, and (b) the topological order of the nodes in the block-wise graph.
 %
@@
 \icc\> $\Delta O$ := topological order of $G_C'$; \ \ $O^+$ := $\Delta O/O$; \\
-\icc\> label \sccs of $G_C$ as $C$ and \sccs of $G$ with outgoing edges \\ \hspace{2.5ex}  having  weight changes as $B$,  the remaining \sccs of $G$ as $A$\\
+\icc\> label \sccs of $G_C$ as $C$, \sccs of $G$ with outgoing edges having \\ \hspace{2.5ex}    weight changes as $B$, and the remaining \sccs of $G$ as $A$;\\
 \icc\>  \For each node $v'$ following $O^+$ \Do\\
@@
 The original graph $G$ is then partitioned into affected and unaffected areas, and subgraphs $G_A$, $G_B$ and $G_C$ are associated with node sets $V_A$, $V_B$ and $\Delta V$, respectively.
-Here edge weight on $(y, x)$ changes due to the change of the citation peak time of node $x$, and, hence, node $y$ as well as all nodes reachable from $y$ are included in $G_B$.
+Here edge weight on $(y, x)$ changes due to the change of the peak time of node $x$, and, hence, node $y$ as well as all nodes reachable from $y$ are included in $G_B$.
 %
@@
 Observe that (a) a topological order of $G'_C$ can be computed in $O(|V_C|+|E_C|+|E_{CB}|)$ time,
-(b) updating the TWPageRank scores of nodes in subgraphs $G_B$ and $G_C$ costs $O(|V_B\cup V_C|+|E_{B,a}\cup E_{C,a}\cup E_{CB}|)+t^+|E_{B,i}\cup E_{C,i}|)$ time, and , finally, (c) updating the scores of nodes in $G_A$ costs $O(|V_A|)$ time.
+(b) updating the TWPageRank scores of nodes in subgraphs $G_B$ and $G_C$ costs $O(|V_B\cup V_C|+|E_{B,a}\cup E_{C,a}\cup E_{CB}|)+t^+|E_{B,i}\cup E_{C,i}|)$ time, and, finally, (c) updating the scores of nodes in $G_A$ costs $O(|V_A|)$ time.
 From these, the following holds.
@@
 %
-Note that  a) algorithm \inctwprscc computes \sccs and derives the topological order based  on $\Delta$ only, instead of $G^{+}$,
-b) it skips edges in $E_A\cup E_{AB}$ when updating the scores of nodes in $G_A$ and $G_B$, and
-c) the number $t^+$ is very likely smaller than the number $t$ of \twprscc when updating scores of nodes in $G_B$.
+Note that  (a) algorithm \inctwprscc computes \sccs and derives the topological order based  on $\Delta$ only, instead of $G^{+}$,
+(b) it skips edges in $E_A\cup E_{AB}$ when updating the scores of nodes in $G_A$ and $G_B$, and
+(c) the number $t^+$ is very likely smaller than the number $t$ of \twprscc when updating scores of nodes in $G_B$.
 %

### 2017-09-21 icde/sec-model.tex

@@
 Recall that articles are categorized  into six citation patterns featured by the time when the articles reach their citation peaks~\cite{Chakraborty15}: (a) {\em PeakInit} with the citation-count peak in the first five years (but not the first year) after publication, (b) {\em PeakMul} with distinct multiple peaks, (c) {\em PeakLate} with a single peak in at least five years after publication, (d) {\em MonDec} with monotonically decreasing citations, (e) {\em MonIncr} with monotonically increasing citations, and, (f) {\em Other} for articles whose average numbers of citations per year are less than 1.
-Though the number of citations is an indicator of the impacts of articles~\cite{WangSB13,Garfield471}, its impact is time-dependent and is not simply in the form of exponential decay.
+Though the number of citations is an indicator of the impact of articles~\cite{WangSB13,Garfield471}, its impact is time-dependent and is not simply in the form of exponential decay.
 In general, {\em the impact of an article tends to decay with time after the peak time only}.
@@
 \label{fig-reference}
-\vspace{-4ex}
+\vspace{-3ex}
 \end{figure}
@@
 We also collect and report the citations statistics on three scholarly datasets in Fig.~\ref{fig-reference}, which verifies the exponential distribution.
-Hence, we adopt the {\em scaled} number of citations $\Psi_v^{(t)}=\Phi_v^{(t)} / \log Z^{(t)}$ such that $\Phi_v^{(t)}$ and $Z^{(t)}$ are the number of citations of article $v$ at year $t$ and the total number of references at year $t$, respectively.
+Hence, we adopt the {\em scaled} number of citations $\Psi_v^{(t)}=\Phi_v^{(t)} / \log Z^{(t)}$ such that $\Phi_v^{(t)}$ and $Z^{(t)}$ are the number of citations of article $v$ at year $t$ and the total number of citations at year $t$, respectively.
 The peak time $Peak_v$ is the time that maximizes $\Psi_v^{(t)}$.
@@
 
-A {\em citation graph} $G^c(V^c, E^c)$ is firstly constructed using the citation information such that (a) a node in $V^c$ denotes an article, (b) a directed edge $(u,v)$ in $E^c$ denotes that $u$ cites $v$, and (c) each node is associated with two types of time information: the publication year and the latest year having the largest number of citations.
+A {\em citation graph} $G^c(V^c, E^c)$ is firstly constructed using the citation information such that (a) a node in $V^c$ denotes an article, (b) a directed edge $(u,v)$ in $E^c$ denotes that $u$ cites $v$, and (c) each node is associated with two types of time information: the publication year and the latest year having the largest (logscale) number of citations.
 
@@
 %\includegraphics[scale=0.15]{fig/framework.eps}
-\includegraphics[scale=0.16]{fig/framework-lite-2.eps}
+\includegraphics[scale=0.175]{fig/framework-lite-2.eps}
 \vspace{-1ex}
@@
 
-A {\em venue graph} $G^v(V^v, E^v)$ is firstly constructed using the citation information among venues such that (a) a node in $V^v$ represents a venue in a specific year, (b) a direct edge $(s,t)$ in $E^v$ denotes that there exist articles published in venue (in a specific year) $s$ citing articles published in venue (in a specific year) $t$, and (c) we use the {\em impact weight} to denote the weight $w_v(s,t)$ from venues $s$ to $t$, which is the sum of the impact weights from articles published in $s$ to $t$, \ie
+A {\em venue graph} $G^v(V^v, E^v)$ is firstly constructed using the citation information among venues such that (a) a node in $V^v$ represents a venue in a specific year, (b) a direct edge $(s,t)$ in $E^v$ denotes that there exist articles published in venue (in a specific year) $s$ citing articles published in venue (in a specific year) $t$, and (c) we use the {\em impact weight} $w_v(s,t)$ to denote the weight  from venues $s$ to $t$, which is the sum of the impact weights from articles published in $s$ to $t$, \ie
 

### 2017-09-21 icde/sec-intro.tex

@@
 
-Query independent ranking of scholarly articles has drawn significant attentions from both academia~\cite{Garfield471,ChenXMR07,Zhou07-CoRank,ShenAAAI16,Liang16AAAI,Jiang12-MRank,Waltman2014,TanLMGSW16} and industry~\cite{sem-scholar,g-scholar,Sinha15:MAG}.
+Query independent ranking of scholarly articles has drawn significant attentions from both academia~\cite{Garfield471,Hirsch15112005,Liang16AAAI,Jiang12-MRank,Waltman2014,Wang16TIST,Ng11KDD,Li08TSRanking,
+Wang13AAAI,sayyadi09,WalkerXKM07,TanLMGSW16} and industry~\cite{g-scholar,Sinha15:MAG,sem-scholar}.
 Generally speaking, a ranking is {\em a function that assigns each item a numerical score}.
@@
 
-In the academia, the most popular approaches have witnessed a shift from citation-count analysis~\cite{Garfield471,Hirsch15112005} to graph analysis~\cite{ChenXMR07,Zhou07-CoRank,Jiang12-MRank,Waltman2014}, as graph-based methods further leverage the global or local structure of bibliographic networks and  the interactions among heterogeneous entities, and, hence, are typically more appropriate.
+In the academia, the most popular approaches have witnessed a shift from citation-count analysis~\cite{Garfield471,Hirsch15112005} to graph analysis~\cite{Liang16AAAI,Jiang12-MRank,Waltman2014,Wang16TIST,Ng11KDD,Li08TSRanking,Wang13AAAI,sayyadi09,WalkerXKM07}, as graph-based methods further leverage the global or local structure of bibliographic networks and  the interactions among heterogeneous entities, and, hence, are typically more appropriate.
 %
 Efforts have also been made from the industry.
-Google Scholar~\cite{g-scholar} aims to rank articles in the way researchers do, weighing the full text, where they were published, who they were written by, as well as how often and how recently they have been cited; Microsoft Academic~\cite{ms-academic} considers how often and to which a publication is cited to determine the ranking; And
+Google Scholar~\cite{g-scholar} aims to rank articles in the way researchers do, weighing the full text, where they were published, who they were written by, as well as how often and how recently they have been cited; Microsoft Academic~\cite{Sinha15:MAG} considers how often and to which a publication is cited to determine the ranking; And
 Semantic Scholar~\cite{sem-scholar} proposes to use the citation velocity, which is a weighted average number of article citations in the last three years.
 
-%, \eg Google Scholar~\cite{g-scholar}, Semantic Scholar~\cite{sem-scholar} and Microsoft Academic~\cite{Sinha15:MAG}
+% Zhou07-CoRank,
+% from citation-count analysis~\cite{Garfield471,Hirsch15112005}
 % https://scholar.google.com/intl/zh-CN/scholar/about.html
@@
 %
-Second, the importance of articles evolve with time in a complex manner~\cite{WangSB13,Chakraborty15}.
+Second, the importance of articles evolves with time in a complex manner~\cite{WangSB13,Chakraborty15}.
 %Newly published articles are very likely to have increasing impacts in the next few years, and those published many years ago tend to have decreasing impacts, as researchers potentially have more interests in recently reported results.
@@
 
-Query independent ranking of scholarly articles remains challenging~\cite{wsdmcup}, although there exists quite a bit of work on scholarly article ranking, \eg~\cite{Garfield471,ChenXMR07,Zhou07-CoRank,ShenAAAI16,Liang16AAAI,Jiang12-MRank,Waltman2014}.
+Query independent ranking of scholarly articles remains challenging~\cite{wsdmcup}, although there exists quite a bit of work on scholarly article ranking, \eg~\cite{Garfield471,Liang16AAAI,Jiang12-MRank,Waltman2014}.
 Most previous work exploits the time-dependent information of scholarly data in the form of exponential decay~\cite{Li08TSRanking,Wang13AAAI,sayyadi09,WalkerXKM07}, which fails to capture the diverse citation patterns of individual articles~\cite{Chakraborty15}.

### 2017-09-21 icde/sec-related.tex

@@
 
-Scholarly article ranking has shifted from citation count analysis~\cite{Garfield471,Hirsch15112005} to graph analysis~\cite{ChenXMR07,Zhou07-CoRank,Jiang12-MRank,Liang16AAAI,Li08TSRanking,Wang13AAAI,WalkerXKM07,sayyadi09,
+Scholarly article ranking has shifted from citation count analysis~\cite{Garfield471,Hirsch15112005} to graph analysis~\cite{Waltman2014,Jiang12-MRank,Liang16AAAI,Li08TSRanking,Wang13AAAI,WalkerXKM07,sayyadi09,
 Wang16TIST,Ng11KDD}.
-Based on the information used, these methods are divided into four categories: (a) using the citation information only~\cite{Garfield471,Hirsch15112005,ChenXMR07,Ng11KDD}, (b) using the citation and temporal information~\cite{Li08TSRanking,WalkerXKM07}, (c) using the citation information and other heterogeneous information, \eg authors and venues of articles~\cite{Zhou07-CoRank,Jiang12-MRank,Liang16AAAI}, and (d) combining the citation, temporal and other heterogeneous information~\cite{sayyadi09,Wang16TIST,Wang13AAAI}.
+Based on the information used, these methods are divided into four categories: (a) using the citation information only~\cite{Garfield471,Hirsch15112005,Ng11KDD}, (b) using the citation and temporal information~\cite{Li08TSRanking,WalkerXKM07}, (c) using the citation information and other heterogeneous information, \eg authors and venues of articles~\cite{Jiang12-MRank,Liang16AAAI}, and (d) combining the citation, temporal and other heterogeneous information~\cite{sayyadi09,Wang16TIST,Wang13AAAI}.
 Our work belongs to the last category aiming at fully employing information available for scholarly article ranking.

### 2017-09-21 icde/sec-intro.tex

@@
 
-In the academia, the most popular approaches have witnessed a shift from citation-count analysis~\cite{Garfield471,Hirsch15112005} to graph analysis~\cite{Liang16AAAI,Jiang12-MRank,Waltman2014,Wang16TIST,Ng11KDD,Li08TSRanking,Wang13AAAI,sayyadi09,WalkerXKM07}, as graph-based methods further leverage the global or local structure of bibliographic networks and  the interactions among heterogeneous entities, and, hence, are typically more appropriate.
+In the academia, popular approaches have witnessed a shift from citation-count analysis~\cite{Garfield471,Hirsch15112005} to graph analysis~\cite{Liang16AAAI,Jiang12-MRank,Waltman2014,Wang16TIST,Ng11KDD,Li08TSRanking,Wang13AAAI,sayyadi09,WalkerXKM07}, as graph-based methods further leverage the global or local structure of bibliographic networks and  the interactions among heterogeneous entities, and, hence, are typically more appropriate.
 %

### 2017-09-24 GruBa/02-overview.tex

\section{\sys{} Overview}
\label{sec:overv}

\subsection{Problem Formulation}
% {user, blog, user-blog} => model
% query (a user u, a blog b that is created or forwarded by u's friend)
% returns: Y/N u shall forward b

We consider people's \retg{} behavior in social media.
For simplicity, with a given user, we assume that blogs created or \retd{} by his/her followees cover the overall candidates, from which the said user may \ret{}.
All our results could straightforwardly generalize to alternative candidate scopes.
%e.g., the like/unlike behavior against the candidate of remarking [double check the network language; register a Facebook]
%e.g., positive comments in the overall comments

\begin{definition}
\label{def:blog}
A blog $B = (O, T, M, R)$ consists of the owner $O$ (a.k.a. user in this paper) to whom $B$ belongs (either created or \retd{}), the timestamp $T$ showing when $B$ is generated, the blog message $M$ and a bit $R$ denoting $B$ is \retd{} (1) or originally created (0) by the owner $O$.
\end{definition}

\begin{comment}
\begin{definition}
A blog $B = (O, T, M, C)$ consists of the owner $O$ to whom $B$ belongs (either created or \retd{}), the timestamp $T$ showing when $B$ is generated, the blog message $M$ and a set of counters $C_s(B) = \{\#comment,\ \#like,\ \#\ret{}\}$ regarding the number of being commented, liked, and \retd{}.
\end{definition}
\end{comment}

\begin{definition}
\label{def:user}
A user $U = (B_s, R_s, E_s)$ consists of three sets regarding the user's blogs $B_s$, followers $R_s$ and followees $E_s$ separately.
Each follower/followee per se refers to a user.
\end{definition}

The mapping between blog $B$ and user $U$ is a bilateral operation, i.e., $U = O(B)$ and $B \in B_s(U)$, through ID(s) of user and blog respectively.

Informally, providing a set of users $\{U\}$ and the associated blogs $\{B\}$, as well as a blog query $b$ and a follower of $O(b)$ written as $f$, i.e., $f \in R_s(O(b))$, \sys{} shall build a \retg{} model for $(\{U\},\ \{B\})$, upon which Y/N is returned regarding whether $f$ shall \ret{} $b$.

\subsection{\sys{} Framework}
\sys{} is designed from the ground up as a system for modeling users' \retg{} behavior in social media.
Figure \ref{fig:framework} shows the architectural components of \sys{}, comprising three subsystems: Data Storage, Processing Runtime and Profile Demonstrator.

\begin{figure}[!htb]
\centering
\includegraphics[width=.96\linewidth]{figures/architecture}
\caption{\sys{} Architecture}
\label{fig:framework}
\end{figure}

% #like and #comment are saved; could generalize \sys{} to model the liking behavior (among commented blogs)
\begin{comment}
\begin{figure}[!htb]
\centering
\includegraphics[width=.99\linewidth]{figures/microblog}
\caption{Blog Data in \sys{}}
\label{fig:blog}
\end{figure}
\end{comment}

\begin{comment}
\begin{figure}[!htb]
\centering
\includegraphics[width=.99\linewidth]{figures/user}
\caption{User Data in \sys{}}
\label{fig:user}
\end{figure}
\end{comment}

\textbf{Data Storage.} The underlying Data Storage subsystem stores data to be processed by \sys{}, i.e., data of blogs and users, as shown in \textit{Definition} \textit{\ref{def:blog}} and \textit{\ref{def:user}}.

\textbf{Processing Runtime.}
In the heart of \sys{} lies the Processing Runtime subsystem, which consists of three major components as follows.
\begin{enumerate}
	\item Feature Extractor: By coalescing the blog data, each user is depicted by a bunch of features, which are grouped into three categories. They are features of \textit{Info} (e.g., the number of followers and followees), \textit{Behavior} (e.g., the frequency and the popular slots of \retg{}) and \textit{Interest} (e.g., the long-term/recent interests, as well as the explicit/implicit interests). These features are extracted from the stored data by Feature Extractor and serve as the input of User Clusterer.
	\item User Clusterer: Providing the user-based features, User Clusterer takes charge of the clustering task such that each user falls into a proper group. 
	\item Group Modeler: For each group obtained by User Clusterer, Group Modeler employs both positive and negative samples to train a model, over which the testing of users' \retg{} behavior is performed.
\end{enumerate}

\textbf{Profile Demonstrator.} At the top layer of \sys{}, it is the Profile Demonstrator subsystem for visualization. 
For the time being, Profile Demonstrator presents \tbc{}.

### 2017-09-24 GruBa/abstr.tex

\begin{abstract} 
Social media applications are emerging, with rapidly growing users and large numbers of \retd{} blogs every minute. 
The variety among users makes it difficult to model their \retg{} activities.
Obviously, it is not suitable to cover the overall users by a single model.
Meanwhile, building one model per user is not practical. 
To this end, this paper presents a novel solution, of which the principle is to model the \retg{} behavior over user groups.
Our approach, \sys{}, consists of three key components for extracting user based features, clustering users into groups, and modeling upon each group.
Particularly, we look into the user interest from different perspectives including long-term/recent interests and explicit/implicit interests, which results deep analyses towards the \retg{} behavior and proper models in the end.
We have evaluated the performance of \sys{} by datasets of real-world social networking applications and a number of query workloads, showcasing its benefits.     
\end{abstract}
% behavior and activity in this paper are interchangeable

### 2017-09-28 icde/sec-exp.tex

@@
 
-We constructed two sets of ground-truth importance orders of article pairs with \recom and \fcita.
+We constructed two sets of ground-truth importance orders of article pairs, referred to as  \recom and \fcita.
 
@@
 %evaluates the importance of scholarly articles by the numbers of recommendations (from textbooks and/or university course reading lists).
-We used the numbers of recommendations of 93 articles on \aan~\cite{Liang16AAAI}, %which are recommended by 2 to 10 times,
+We used the number of recommendations of 93 articles on \aan~\cite{Liang16AAAI}, %which are recommended by 2 to 10 times,
 and, by exact title matching, %then matched articles in \aminer and \magdata with titles.  Finally, we
@@
 \begin{center}
-\caption{\small Accuracy tests with \recom}
+\caption{\small Accuracy evaluation with \recom}
 %\begin{small}
@@
 To evaluate the effectiveness of ranking \wrt\ {\em the difference of past and future citations},
-we varied the difference $dif$ of past and future citation counts from 1 to 7, while fixed $Y_s$ to default values of three datasets and $T_i=+\infty$.
+we varied the difference $dif$ of past and future citation counts from 1 to 7, while fixed $Y_s$ to default values of three datasets and $T_p=+\infty$.
 The results of \PairAcc are reported in Figs.~\ref{exp-aan-fcdiff}, \ref{exp-aminer-fcdiff} and \ref{exp-mag-fcdiff}.
@@
 In the last set of tests, we evaluated the impacts of time decaying factor $\sigma$, importance weighting factor $\lambda$, aggregating parameters $\alpha$ and $\beta$, and the TWPageRank.
-We fixed these parameters as well as $Y_s$ to their default values, used the TWPageRank proposed in this work by default, and tested the \PairAcc with the entire \recom and \fcita (\ie $T_i=+\infty$, $dif=1$).
+We fixed these parameters as well as $Y_s$ to their default values, used the TWPageRank proposed in this work by default, and tested the \PairAcc with the entire \recom and \fcita (\ie $T_p=+\infty$, $dif=1$).
 
@@
 \begin{center}
-\caption{\small Accuracy tests using different components with \recom (rows 2--4) and \fcita (rows 5--7).}
+\caption{\small Accuracy evaluation using different components with \recom (rows 2--4) and \fcita (rows 5--7).}
 \label{tab-recom}
@@
 %%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[tb!]
+%\vspace{1ex}
+\addtolength{\subfigcapskip}{-1ex}
+\begin{center}
+\subfigure[{\scriptsize \aan with \recom}]{\label{exp-aan-recom-drank}
+\includegraphics[scale=0.36]{./exp/AAN_TWPageRank_recom.eps}}
+\hfill
+%\hspace{\graphmarginexpapp}
+\subfigure[{\scriptsize \aminer with \recom}]{\label{exp-aminer-recom-drank}
+\includegraphics[scale=0.36]{./exp/AMiner_TWPageRank_recom.eps}}
+\hfill
+%\hspace{\graphmarginexpapp}
+\subfigure[{\scriptsize \magdata with \recom}]{\label{exp-mag-recom-drank}
+\includegraphics[scale=0.36]{./exp/MAG_TWPageRank_recom.eps}}
+\\%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\vspace{-.5ex}
+\subfigure[{\scriptsize \aan with \fcita}]{\label{exp-aan-fcita-drank}
+\includegraphics[scale=0.36]{./exp/AAN_TWPageRank_fcita.eps}}
+\hfill
+%\hspace{\graphmarginexpapp}
+\subfigure[{\scriptsize \aminer with \fcita}]{\label{exp-aminer-fcita-drank}
+\includegraphics[scale=0.36]{./exp/AMiner_TWPageRank_fcita.eps}}
+\hfill
+%\hspace{\graphmarginexpapp}
+\subfigure[{\scriptsize \magdata with \fcita}]{\label{exp-mag-fcita-drank}
+\includegraphics[scale=0.36]{./exp/MAG_TWPageRank_fcita.eps}}
+\end{center}
+\vspace{-1.5ex}
+\caption{\small Impacts of TWPageRank on accuracy: varying importance weighting
+factor $\lambda$}
+\label{exp-drank}
+\vspace{-2ex}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 } %%%%%%%% brief version of Exp-4.3
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[tb!]
-%\vspace{1ex}
-\addtolength{\subfigcapskip}{-1ex}
-\begin{center}
-\subfigure[{\scriptsize \aan with \recom}]{\label{exp-aan-recom-drank}
-\includegraphics[scale=0.36]{./exp/AAN_TWPageRank_recom.eps}}
-\hfill
-%\hspace{\graphmarginexpapp}
-\subfigure[{\scriptsize \aminer with \recom}]{\label{exp-aminer-recom-drank}
-\includegraphics[scale=0.36]{./exp/AMiner_TWPageRank_recom.eps}}
-\hfill
-%\hspace{\graphmarginexpapp}
-\subfigure[{\scriptsize \magdata with \recom}]{\label{exp-mag-recom-drank}
-\includegraphics[scale=0.36]{./exp/MAG_TWPageRank_recom.eps}}
-\\%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace{-.5ex}
-\subfigure[{\scriptsize \aan with \fcita}]{\label{exp-aan-fcita-drank}
-\includegraphics[scale=0.36]{./exp/AAN_TWPageRank_fcita.eps}}
-\hfill
-%\hspace{\graphmarginexpapp}
-\subfigure[{\scriptsize \aminer with \fcita}]{\label{exp-aminer-fcita-drank}
-\includegraphics[scale=0.36]{./exp/AMiner_TWPageRank_fcita.eps}}
-\hfill
-%\hspace{\graphmarginexpapp}
-\subfigure[{\scriptsize \magdata with \fcita}]{\label{exp-mag-fcita-drank}
-\includegraphics[scale=0.36]{./exp/MAG_TWPageRank_fcita.eps}}
-\end{center}
-\vspace{-1.5ex}
-\caption{\small Impacts of TWPageRank on accuracy: varying importance weighting
-factor $\lambda$}
-\label{exp-drank}
-\vspace{-2ex}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2017-09-28 icde/sec-model.tex

@@
 We rethink the usage of time information in terms of the impacts of scholarly articles.
-Recall that articles are categorized  into six citation patterns featured by the time when the articles reach their citation peaks~\cite{Chakraborty15}: (a) {\em PeakInit} with the citation-count peak in the first five years (but not the first year) after publication, (b) {\em PeakMul} with distinct multiple peaks, (c) {\em PeakLate} with a single peak in at least five years after publication, (d) {\em MonDec} with monotonically decreasing citations, (e) {\em MonIncr} with monotonically increasing citations, and, (f) {\em Other} for articles whose average numbers of citations per year are less than 1.
-Though the number of citations is an indicator of the impact of articles~\cite{WangSB13,Garfield471}, its impact is time-dependent and is not simply in the form of exponential decay.
+Recall that articles are categorized  into six citation patterns featured by the time when the articles reach their citation peaks~\cite{Chakraborty15}: (a) {\em PeakInit} with a single citation-count peak in the first five years (but not the first year) after publication, (b) {\em PeakMul} with distinct multiple peaks, (c) {\em PeakLate} with a single peak in at least five years after publication, (d) {\em MonDec} with monotonically decreasing citations, (e) {\em MonIncr} with monotonically increasing citations, and, (f) {\em Other} for articles whose average numbers of citations per year are less than 1.
+Though the number of citations is an indicator of the impact of an article~\cite{WangSB13,Garfield471}, its impact is time-dependent and is not simply in the form of exponential decay.
 In general, {\em the impact of an article tends to decay with time after the peak time only}.
@@
 \vspace{-1ex}
-\caption{\small Citation statistics of scholarly articles that reports the (logscale) percentage of the number of citations of each year \wrt\ the total number of citations  in  \aan, \aminer and \magdata, respectively.}
+\caption{\small Citation statistics of scholarly articles that reports the (logscale) percentage of the number of citations of each year \wrt\ the total number of citations on \aan, \aminer and \magdata, respectively.}
 \label{fig-reference}
@@
 However, recent work reveals that the volume of scientific publications as well as the number of citations grow exponentially with time~\cite{Dong2017KDD,BornmannM15}.
-We also collect and report the citations statistics on three scholarly datasets in Fig.~\ref{fig-reference}, which verifies the exponential distribution.
+We also collect and report the citation statistics on three scholarly datasets in Fig.~\ref{fig-reference}, which verifies the exponential distribution.
 Hence, we adopt the {\em scaled} number of citations $\Psi_v^{(t)}=\Phi_v^{(t)} / \log Z^{(t)}$ such that $\Phi_v^{(t)}$ and $Z^{(t)}$ are the number of citations of article $v$ at year $t$ and the total number of citations at year $t$, respectively.
@@
 \noindent
-Here $PR^{(k)}$ is the TWPageRank vectors after $k$ iterations,  $M$ is the transition matrix such that $M_{u,v}=w(u,v)/W(u)$ and  $e$ is an $n$-dimensional all-one vector $[1]_{n\times1}$.
+Here $PR^{(k)}$ is the TWPageRank vector after $k$ iterations,  $M$ is the transition matrix such that $M_{u,v}=w(u,v)/W(u)$ and  $e$ is an $n$-dimensional all-one vector $[1]_{n\times1}$.
 
@@
 
-\sstab(2)  The popularity of an article is the sum of all its citations' freshness, \ie the closeness to the current year:
+\sstab(2)  The popularity of an article is the sum of all its citation freshness, \ie the closeness to the current year:
 
@@
 \noindent
-Here $T_0$ is the current year, \ie the latest $T_u$ among all articles in $V^c$, $\sigma$ is the negative decaying factor used in Eq.~(\ref{eq-infl-weights}), and $e^{\sigma (T_0-T_u)}$ represents the freshness of citation $(u,v)$.
+Here $T_0$ is the current year, \ie the largest $T_u$ among all articles in $V^c$, $\sigma$ is the negative decaying factor used in Eq.~(\ref{eq-infl-weights}), and $e^{\sigma (T_0-T_u)}$ represents the freshness of citation $(u,v)$.
 
@@
 
-\stitle{Remark}.
+\stitle{Remarks}.
 This work follows the graph-based formalization, and further develops efficient batch and incremental algorithms based on graphs for scholarly article ranking (Sections~\ref{sec-alg} \& \ref{sec-incAlg}).

### 2017-09-28 icde/sec-related.tex

@@
 Both these approaches fail to capture the time-dependent characteristics, a key factor for scholarly article ranking.
-There has been work extending temporal information into PageRank, \eg exponential decayed weights~\cite{Li08TSRanking}, exponential decayed initial vector~\cite{WalkerXKM07} and time-dependent weights based on co-authorship~\cite{FIALA2012370}.
+There has been work extending temporal information into PageRank, \eg exponentially decayed weights~\cite{Li08TSRanking}, exponentially decayed initial vectors~\cite{WalkerXKM07} and time-dependent weights based on co-authorship~\cite{FIALA2012370}.
 Different from previous work, the Time-Weighted PageRank of this work discriminately propagates scores in terms of citation statistics.

### 2017-09-30 icde/sec-exp.tex

@@
 
-In this section, we present an extensive experimental study of our approach \ensemblerank, compared with competitive methods.
+In this section, we present an extensive experimental study of our approach \ensemblerank, compared with three competitive methods.
 Using three real-life scholarly datasets (\aan, \aminer and \magdata) and two sets of ground-truth (\recom and \fcita), we conducted four sets of experiments to evaluate: (1) the effectiveness of \ensemblerank,
@@
 
-We constructed two sets of ground-truth importance orders of article pairs, referred to as  \recom and \fcita.
+We constructed two sets of ground-truth importance ranking orders of article pairs, referred to as  \recom and \fcita.
 
@@
 %
-We hence divided each dataset into two parts with a splitting (concerned) time such that (a) the data before the splitting time is used for ranking model, (b) the remaining part of data is used to collect future citations, and (c) the most recent part of the data for ranking model with the same time span as the future citations is used to collect past citations.
+We hence divide each dataset into two parts with a splitting (concerned) time such that (a) the data before the splitting time is used for ranking model, (b) the remaining part of data is used to collect future citations, and (c) the most recent part of the data for ranking model with the same time span as the future citations is used to collect past citations.
 %
@@
 For all algorithms, (a) the damping parameter $d$ and the iteration threshold $\epsilon$ were fixed to 0.85 and $10^{-8}$, respectively,
-(b) the default splitting years were selected such that the part of data for ranking model accounted for around 75\% of the entire data, which were 2008 on \aan and 2012 on both \aminer and \magdata, and,
+(b) the default splitting years (time) were selected such that the part of data for ranking model accounted for around 75\% of the entire data, which were 2008 on \aan and 2012 on both \aminer and \magdata, and,
 (c) for the sake of fairness, aggregating parameters of \futurerank, \hhgrank and \ensemblerank were tuned at the granularity of 0.1 and the best results were reported.
@@
 %in all of our tests.
-When quantity measures are evaluated, the test was repeated over 5 times and the average results are reported.
+When quantity measures were evaluated, the test was repeated over 5 times and the average is reported.
 
@@
 In our tests we adopted a yearly update policy due the limitation of  available time information.
-In practice our algorithms may bring more efficiency benefits since the ranking is usually more frequent, such that the data updates are smaller and the unaffected area is very likely much larger.
+In practice our algorithms may bring more efficiency benefits since the update is usually more frequent, such that the data updates are smaller and the unaffected area is very likely much larger.
 
@@
 %
-Further, the optimal parameters on the same sets of ground-truth are very similar for (\aan, \aminer and \magdata), indicating that the setting of $\alpha$ and $\beta$ can be easily transferred across different datasets.
+Further, the optimal parameters on the same set of ground-truth are very similar for (\aan, \aminer and \magdata), indicating that the setting of $\alpha$ and $\beta$ can be easily transferred across different datasets.
 To conclude, \ensemblerank is very robust to parameters $\alpha$ and $\beta$, and it is quite flexible for choosing proper values of parameters $\alpha$ and $\beta$.
@@
 When varying $\lambda$, the \PairAcc of \ensemblerank is better than the one of \drank in most cases, which shows the superiority of the TWPageRank than exploiting exponentially decayed weights directly without introducing the peak time.
-The \PairAcc difference of these two algorithms is higher on \recom than on \fcita, since the two algorithms are just using citation information to predict past and future citations with \fcita.
+The \PairAcc difference of these two algorithms is higher with \recom than with \fcita, since the two algorithms are just using citation information to predict past and future citations with \fcita.
 Moreover, algorithm \ensemblerank is consistently better than \drank when $0.5 \le \lambda \le 0.9$.

### 2017-09-30 icde/sec-incAlg.tex

@@
 
-As the popularity of articles is defined as the freshness sum of all their citations, it is convenient to maintain in a dynamic scenario.
+As the popularity of articles is defined as the sum of the freshness of all their citations, it is convenient to maintain in a dynamic scenario.
 Consider an updated citation graph $G^{c,+}(V^c\cup\Delta V^c, E^c\cup\Delta E^c)$ of $G^c(V^c, E^c)$, and the updated popularity $Pop_{c}^+(v)$ can be computed as:
@@
 where $Pop_c(v)$ (resp. $Pop_c^+(v)$) is the popularity of node $v$ on $G^c$ (resp. $G^{c,+}$), and
- $T_0$ (resp. $T^+_0$) is the current time in $G^c$ (resp. $G^{c,+}$).
+ $T_0$ (resp. $T^+_0$) is the current time on $G^c$ (resp. $G^{c,+}$).
 %

### 2017-09-30 icde/sec-model.tex

@@
 We rethink the usage of time information in terms of the impacts of scholarly articles.
-Recall that articles are categorized  into six citation patterns featured by the time when the articles reach their citation peaks~\cite{Chakraborty15}: (a) {\em PeakInit} with a single citation-count peak in the first five years (but not the first year) after publication, (b) {\em PeakMul} with distinct multiple peaks, (c) {\em PeakLate} with a single peak in at least five years after publication, (d) {\em MonDec} with monotonically decreasing citations, (e) {\em MonIncr} with monotonically increasing citations, and, (f) {\em Other} for articles whose average numbers of citations per year are less than 1.
+Recall that articles are categorized  into six citation patterns featured by the time when the articles reach their citation peaks~\cite{Chakraborty15}: (a) {\em PeakInit} with a single citation-count peak in the first five years (but not the first year) after publication, (b) {\em PeakMul} with distinct multiple peaks, (c) {\em PeakLate} with a single peak in at least five years   (but not the last year) after publication, (d) {\em MonDec} with monotonically decreasing citations, (e) {\em MonIncr} with monotonically increasing citations, and, (f) {\em Other} for articles whose average numbers of citations per year are less than 1.
 Though the number of citations is an indicator of the impact of an article~\cite{WangSB13,Garfield471}, its impact is time-dependent and is not simply in the form of exponential decay.
@@
 Based on the above discussion, we propose TWPageRank that evaluates the prestige of nodes (\eg scholarly articles) in a directed graph, such that each node is attached with time information.
-It differs from PageRank by weighting the influence propagation using the {\em impact weights on edges}, which represent the relative amounts of time-dependent prestige that should be propagated from the edge sources to targets.
+It differs from PageRank by weighing the influence propagation using the {\em impact weights on edges}, which represent the relative amounts of time-dependent prestige that should be propagated from the edge sources to targets.
 %
@@
 
-For scholarly article ranking, $T_u$ is the publication time of article $u$ and $Peak_v$ should be ideally set to the time when article $v$ has the highest impacts.
+For scholarly article ranking, $T_u$ is the publication time of article $u$ and $Peak_v$ should be ideally set to the time when article $v$ has the highest impact.
 Basically, it could simply be the year when article $v$ obtains the largest number of citations.
@@
 \noindent where $PR(u)$ and $PR(v)$ are the TWPageRank scores of $u$ and $v$, respectively, $E$ is the set of edges, $W(u)=\Sigma_{v} w(u,v)$ is the sum of the impact weights on all edges from $u$, $n$ is the number of nodes and $d$ is a damping parameter in $(0, 1)$.
-By Eq.~(\ref{eq-twpr}), we can see that prestige is based on the impact weights, not equally distributed.
+By Eq.~(\ref{eq-twpr}), we can see that prestige is updated based on the impact weights, not equally distributed.
 
@@
 The aforementioned importance is finally assembled to produce the final ranking, as illustrated in Fig.~\ref{fig-rankmodel}.
-Before assembling, each component is properly scaled such that the average citation importance score, venue importance score and author importance score
-are the same.
+Before assembling, each component is properly scaled such that the average importance scores of citations, venues and authors are the same.
 Let the scaled importance scores of article $v$ be $R_c(v)$, $R_v(v)$, and $R_a(v)$ from the citation, venue and author components, respectively.
+
 The final ranking score $R(v)$ of an article $v$ is aggregated as follows:

### 2017-09-30 icde/sec-related.tex

@@
 
-Scholarly article ranking has shifted from citation count analysis~\cite{Garfield471,Hirsch15112005} to graph analysis~\cite{Waltman2014,Jiang12-MRank,Liang16AAAI,Li08TSRanking,Wang13AAAI,WalkerXKM07,sayyadi09,
+Scholarly article ranking has shifted from citation-count analysis~\cite{Garfield471,Hirsch15112005} to graph analysis~\cite{Waltman2014,Jiang12-MRank,Liang16AAAI,Li08TSRanking,Wang13AAAI,WalkerXKM07,sayyadi09,
 Wang16TIST,Ng11KDD}.

### 2017-12-24 icde/revision/sec-intro.tex

--- 2017-09-21 icde/sec-intro.tex
@@
 Most previous work exploits the time-dependent information of scholarly data in the form of exponential decay~\cite{Li08TSRanking,Wang13AAAI,sayyadi09,WalkerXKM07}, which fails to capture the diverse citation patterns of individual articles~\cite{Chakraborty15}.
-Further, to our knowledge, little concern has been paid to dynamic scholarly article ranking except \cite{GhoshKHLL11} with a strong and impractical assumption that there are no citations between papers published in the same years.
+Further, to our knowledge, little concern has been paid to dynamic scholarly article ranking except \cite{GhoshKHLL11} with a strong and impractical assumption that there are no citations between articles published in the same years.
 %\marked{Finally, the bias caused by the dynamic nature of data has never been exploited in scholarly article ranking}.

### 2017-12-24 icde/revision/Response.tex

\documentclass{letter}
\usepackage{geometry}

% duan
\usepackage{xspace}

\geometry{left=2.0cm, right=2.0cm, top=2.5cm, bottom=2.5cm}
\newcommand{\ie}{\emph{i.e.,}\xspace}
\newcommand{\eg}{\emph{e.g.,}\xspace}
\newcommand{\wrt}{\emph{w.r.t.}\xspace}
\newcommand{\aka}{\emph{a.k.a.}\xspace}
\newcommand{\kwlog}{\emph{w.l.o.g.}\xspace}
\newcommand{\etal}{\emph{et al.}\xspace}
\newcommand{\sstab}{\rule{0pt}{8pt}\\[-2.4ex]}

\begin{document}

Prof. xxx,\\
Editor-in-Chief,\\
%IEEE Transactions on Knowledge and Data Engineering\\

Dear Prof. xxx,

%Attached please find a revised version of our submission to IEEE Transactions on Knowledge and Data Engineering, \emph{An Ensemble Approach to Link Prediction}.

%The paper has been substantially revised according to the referees＊ comments. In particular, (1) we have added an example to explain the procedure of the top-$(\epsilon, k)$ prediction, (2) we have compared the suggested Resource Allocation (RA) algorithm in the experimental study, (3) we have added an accuracy comparison with varied hop distances of our methods and BIGCLAM in the experimental study, (4) we have compared our methods with the state-of-the-art methods when $k$ is fixed to the number of links in the ground truth data and reported the accuracy results together with the 95\% confidence intervals in Appendixes A\&B of the supplementary material for the lack of space, (5) we have implemented and evaluated the ensemble-enabled approach with Adamic/Adar (AA) and RA in Appendix C of the supplementary material, and (6) we have also taken this opportunity to rewrite several parts of the paper to improve the presentation.

We would like to thank all the referees for their thorough reading of our paper and for their valuable comments.

Below please find our responses to the comments by the referees.

%******************* reviewer 1 ***********************************************
\line(1,0){500}

\textbf{Response to the comments of Referee 1.}

\textbf{[R1W1]} \emph{Formula 7 in SARank still needs parameters, which are not easy to set.}

We have added this survey in the related work (Section 5). Thanks!

\textbf{[R1W2]} \emph{The extension of this method to query dependent ranking or other heterogeneous information network should be discussed.}

Yes, we have discussed the complexities of AA and RA when we introduce them in Section 4.1. Moreover, $O(n^2)$ typically refers to the number of possible links in our paper.

\textbf{[R1D1]} \emph{In the time-weighted pagerank algorithm, the impacts are encoded into the edge weight. How about changing the values on nodes?}

We have added Example 1 (Section 2.1) to illustrate the procedure for
top-$(\epsilon, k)$ prediction searching. Thanks for the suggestion!

\textbf{[R1D2]} \emph{This paper has an important observation that ※the impact of an article tends to decay with time after the peak time only.§ However, I cannot see that from Figure 1. It is better to add some references to support the claim.}

We have explained the setting of the parameter $\theta$ in the second last paragraph of Section 3.6, and removed Proposition 2. Thanks for the suggestion!

\textbf{[R1D3]} \emph{How to determine the peak time for the PeakMul pattern?}

The snowball sampling has been introduced in the graph sampling
survey [4] in our references. Indeed, the edge bagging method
is different from the snowball sampling because the edge bagging only
selects a random adjacent node when the sampled node set is growing.
Hence, we did not cite the recommended paper directly due to space limitations (as you may notice, we already provide a supplementary material).  Thanks!

[4] N. K. Ahmed, J. Neville, and R. Kompella. Network sampling: From
static to streaming graphs. Transactions on Knowledge Discovery from
Data (TKDD), 8(2):7:1每7:56, 2014.

\textbf{[R1D4]} \emph{For large scholar graph, such as MAG, it is better to use the distributed graph processing framework to improve the scalability of the method}

We focus on predicting future links that split by timestamps (the datasets that we used have timestamps of edge arrivals) rather than missing links
that selected randomly from the network as the testing set [17][24]. Hence, we believe these methods are not comparable.

\textbf{[R1D5]} \emph{TWPageRank works better on the scholar graphs than the general web graph. is it due to that the citation graph is an directed acyclic graph?}

We have added
the link predictability work [30] in the related work (Section 5), and the survey papers [17]\&[31].

[17] M. A. Hasan and M. J. Zaki. A survey of link prediction in social
networks. In Social Network Data Analytics, 2011.

[30] L. L\"{u}, L. Pan, T. Zhou, Y. Zhang, and H. Stanley. Toward link
predictablility of complex networks. PNAS, 118(8):2325每2330, 2015.

[31] L. L\"{u} and T. Zhou. Link prediction in complex networks: A survey.
Physica A, pages 1150每1170, 2011.

\textbf{[R1D6]} \emph{MAG is used before description in Page 1.
Some cells in Table 1 have two values, while others have one value. The meaning should be given explicitly}

Yes, we have added RA as a comparison algorithm in the experimental study. However,
we did not adopt the other algorithms for comparison since the complexities of these
algorithms are at least $O(n^2)$ and they cannot work on large
networks with millions of nodes. Thanks for the suggestion!

%******************* reviewer 2 ***********************************************
\line(1,0){500}

\textbf{Response to the comments of Referee 2.}

\textbf{[R2W1]} \emph{While practically the paper makes a good case about the particular application domain and its contributions there, the paper lacks technical depth.}

We have added the accuracy test with the 95\% confidence intervals when $k$ is fixed
to its default value and the number of links in the ground truth data (R2C2).
Due to space limitations, we choose to report these experimental results in the Appendix B
of the supplementary material, in which the results justify the effectiveness of our methods compared with the state-of-the-art methods.
Thanks for the suggestion!

\textbf{[R2W2]} \emph{Presentation could improve a bit since the paper has too much notation making it hard to read/follow.}

We agree that small changes of the value $k$ may lead to different conclusions.
This is why we tested the impact of varying $k$ in the experimental study.

Similar to [35][39] that do not use the number of links in the
ground truth data for testing accuracy, we keep the results using default values for $k$ in the experimental study.
However, we further tested the ensemble-enabled approach with $k$ fixed to the number of links in
the ground truth data. Due to space limitations, we choose to report these experimental results in the Appendix A
of the supplementary material, in which the results justify the effectiveness and efficiency of our methods compared with the state-of-the-art methods.
Thanks for the suggestion!

It is worth mentioning that the datasets used in our experiments
are more much sparser than the one used in [S1], which means that it
is more difficult to predict links on our datasets. As a result, the top-$k$
precision on our datasets, when $k$ is fixed to the number of links in the
ground truth data, is too low to be useful in practice.

[S1] Y. Yang, R. N. Lichtenwalter, and N. V. Chawla. Evaluating link prediction
methods. Knowl Inf Syst, 45:751每782, 2015.

[35] D. Song, D. Meyer, and D. Tao. Top-k link recommendation in social
networks. In ICDM, 2015.

[39] R. West, A. Paranjape, and J. Leskovec. Mining missing hyperlinks from
human navigation traces: A case study of wikipedia. In WWW, 2015.

\textbf{[R2D1]} \emph{There seem to be two "contradictory" sides to this paper. From one side, this is a great "applications" paper where existing techniques and some good intuition is used to get better results into an existing (practical) problem. From a purely research and technical perspective, the paper is on the weak side. Pagerank and (incremental) versions of it already exist and the paper makes little contributions there. The claim (made twice) in the related work section that "Different from previous work" this paper focuses on citations statistics doesn't hold water. The fact that the authors are considering a different application domain is not a contribution compared to past (incremental) pagerank papers. Unless there is a better claim to be made about the algorithmic side of the paper, as things stand, the paper makes minimal technical contributions.}

We have added an accuracy comparison of our methods and
BIGCLAM with varied hop distances in Section 4.2.4. The results show
that all these methods are more accurate in predicting 2 or 3 hop distance
links, and they are not good at predicting links with large hop distances.
This is a general limitation of most (if not all) existing methods, which deserves  a full treatment in the future.

Thanks for helping us to identify the limitation of our method!

\textbf{[R2D2]} \emph{The abstract starts with the sentence "Ranking query independent scholarly articles is a critical and challenging task, due to the heterogeneous, evolving and dynamic nature of entities involved in scholarly articles". If three types of data (articles, authors and venues) that are updated (maybe) weekly is considered challenging in terms of heterogeneity and dynamicity then one must wonder what one can say about real-life scenarios with thousands of data types where hundreds/thousands of new items are inserted daily (consider any online merchant system) and were ranking is important (recommendations). In summary, this sentence should go. Not to mention that the task is not really "critical".}

We have added a remark in the end of Section 3.6 such that our ensemble-enabled approach
is a general method for decomposing the large network link prediction
problem into smaller subproblems, which is not limited to NMF, and may be applied to other link prediction methods such as AA and RA.

We have revised the bagging+ and bagging methods by replacing NMF with AA and RA, respectively, and  we evaluated and reported their performance
in the Appendix C of the supplementary material. Our preliminary results indeed show that the
ensemble-enabled AA and RA are very promising, though more sophisticated sampling techniques are needed for achieving better performances.  Thanks for this great comment!

\textbf{[R2D3]} \emph{On page 4, you say "However, the resulting author citation graph to compute the prestige is typically too large to handle". This is a questionable statement. Maybe it is too large to handle "on a PC with 2 Intel Xeon E5每2630 2.4GHz CPUs and 64 GB of memory" but approaches like PageRank has been used for web-scale data so unless there is something that I am missing, this statement should also go (or explained better).}

%******************* reviewer 3 ***********************************************
\line(1,0){500}

\textbf{Response to the comments of Referee 3.}

\textbf{[R3C1]} \emph{The section could be preceded by clearly noting
the two challenges (prediction/training complexity) in large networks,
and how separate tools are used to handle each.}

The parameters are designed to fit variety ranking with different demands. For example, the ground-truth RECOM prefer venue component while PFCTN prefer citation component. Furthermore, our parameters are quite flexible to choose in a certain range for suiting different ranking which we have discussed in Exp-4.3.

\line(1,0){500}

Your sincerely,

Shuai Ma, Chen Gong, Renjun Hu, Dongsheng Luo, Chunming Hu, Jinpeng Huai

\end{document}

### 2017-12-24 icde/revision/Response.tex

@@
 
-%The paper has been substantially revised according to the referees＊ comments.
+%The paper has been substantially revised according to the referees¡¯ comments.
 In particular, (1) we have added an example to explain the procedure of the top-$(\epsilon, k)$ prediction, (2) we have compared the suggested Resource Allocation (RA) algorithm in the experimental study, (3) we have added an accuracy comparison with varied hop distances of our methods and BIGCLAM in the experimental study, (4) we have compared our methods with the state-of-the-art methods when $k$ is fixed to the number of links in the ground truth data and reported the accuracy results together with the 95\% confidence intervals in Appendixes A\&B of the supplementary material for the lack of space, (5) we have implemented and evaluated the ensemble-enabled approach with Adamic/Adar (AA) and RA in Appendix C of the supplementary material, and (6) we have also taken this opportunity to rewrite several parts of the paper to improve the presentation.
@@
 
-We have added this survey in the related work (Section 5). Thanks!
+The parameters are designed to fit variety ranking with different demands.
+For example, the ground-truth RECOM prefer venue component while PFCTN prefer citation component.
+Furthermore, our parameters are quite flexible to choose in a certain range for suiting different ranking which we have discussed in Exp-4.3.
 
@@
 
-Yes, we have discussed the complexities of AA and RA when we introduce them in Section 4.1. Moreover, $O(n^2)$ typically refers to the number of possible links in our paper.
+We focus on query independent ranking because of its application in Google Schorlar and MicroSoft Academic Search.
+As to extension of query dependent ranking, our ranking scores can combine with the relevance scores given a specific query.
+For other heterogeneous information network, the extension of our method is not known.
 
@@
 
-We have added Example 1 (Section 2.1) to illustrate the procedure for
-top-$(\epsilon, k)$ prediction searching. Thanks for the suggestion!
+Actually, changing the values on nodes is the key of our ranking method which evaluate the weight of nodes.
+Moreover, the change of nodes is difficult to handle due to the multiple iterations and probably cause the result fail to converge.
+To our knowledge, there is no related work on changing node weight and it is unclear how to change it.
+Finally, we set the weight of edges to achieve the change of impacts since they are essentially propagable in the network through edges.
 
-\textbf{[R1D2]} \emph{This paper has an important observation that ※the impact of an article tends to decay with time after the peak time only.§ However, I cannot see that from Figure 1.
+\textbf{[R1D2]} \emph{This paper has an important observation that ¡°the impact of an article tends to decay with time after the peak time only.¡± However, I cannot see that from Figure 1.
 It is better to add some references to support the claim.}
 
-We have explained the setting of the parameter $\theta$ in the second last paragraph of Section 3.6, and removed Proposition 2. Thanks for the suggestion!
+Figure 1 shows the logscale number of citations grow exponentially with time, instead of impacts of individual articles.
 
@@
 
-The snowball sampling has been introduced in the graph sampling
-survey [4] in our references. Indeed, the edge bagging method
-is different from the snowball sampling because the edge bagging only
-selects a random adjacent node when the sampled node set is growing.
-Hence, we did not cite the recommended paper directly due to space limitations (as you may notice, we already provide a supplementary material).  Thanks!
+The PeakMul pattern is defined in [19]:  the height of a peak should be at least 75\% of the maximum peak height, and two consecutive peaks should be separated by more than two years.
+In our work, we have simplified the pattern and only use the latest peak time which we have discussed in section II-A.
 
-[4] N. K. Ahmed, J. Neville, and R. Kompella. Network sampling: From
-static to streaming graphs. Transactions on Knowledge Discovery from
-Data (TKDD), 8(2):7:1每7:56, 2014.
+[19]  T. Chakraborty, S. Kumar, P. Goyal, N. Ganguly, and A. Mukherjee, ¡°On the categorization of scientific citation profiles in computer science,¡± Commun. ACM, vol. 58, no. 9, 2015.
 
@@
 
-We focus on predicting future links that split by timestamps (the datasets that we used have timestamps of edge arrivals) rather than missing links
-that selected randomly from the network as the testing set [17][24]. Hence, we believe these methods are not comparable.
+Yes, we agree that distributed processing is an important and independent problem which will be studied in future work and we have discussed it in Section VII. Thanks for the suggestion!
 
@@
 
-We have added
-the link predictability work [30] in the related work (Section 5), and the survey papers [17]\&[31].
+Yes, but the citation graph does have cycles and is not a DAG.
+Compare to general web graphs, the computation of TWPageRank in scholarly graphs is more efficient as a result of the less SCC edge ratio which is shown in Table I.
+In addition, we have designed the incremental algorithm based on this feature of scholalry graphs and it works better.
 
-[17] M. A. Hasan and M. J. Zaki. A survey of link prediction in social
-networks. In Social Network Data Analytics, 2011.
+\textbf{[R1D6]} \emph{MAG is used before description in Page 1. Some cells in Table 1 have two values, while others have one value. The meaning should be given explicitly}
 
-[30] L. L\"{u}, L. Pan, T. Zhou, Y. Zhang, and H. Stanley. Toward link
-predictablility of complex networks. PNAS, 118(8):2325每2330, 2015.
-
-[31] L. L\"{u} and T. Zhou. Link prediction in complex networks: A survey.
-Physica A, pages 1150每1170, 2011.
-
-\textbf{[R1D6]} \emph{MAG is used before description in Page 1.
-Some cells in Table 1 have two values, while others have one value. The meaning should be given explicitly}
-
-Yes, we have added RA as a comparison algorithm in the experimental study. However,
-we did not adopt the other algorithms for comparison since the complexities of these
-algorithms are at least $O(n^2)$ and they cannot work on large
-networks with millions of nodes. Thanks for the suggestion!
+Yes, we have revised as suggested. Thanks for the suggestion!
 
@@
 
-We have added the accuracy test with the 95\% confidence intervals when $k$ is fixed
-to its default value and the number of links in the ground truth data (R2C2).
-Due to space limitations, we choose to report these experimental results in the Appendix B
-of the supplementary material, in which the results justify the effectiveness of our methods compared with the state-of-the-art methods.
-Thanks for the suggestion!
+We think that the techniques proposed also have their own interests: (1) An ensemble based ranking model itself is hard to define, (2) an incremental algorithm that makes use of the particular properties of the scholar graph, and (3) a through experimental study.
+That is, this paper certainly has its contributions to the technical part.
 
@@
 
-We agree that small changes of the value $k$ may lead to different conclusions.
-This is why we tested the impact of varying $k$ in the experimental study.
-
-Similar to [35][39] that do not use the number of links in the
-ground truth data for testing accuracy, we keep the results using default values for $k$ in the experimental study.
-However, we further tested the ensemble-enabled approach with $k$ fixed to the number of links in
-the ground truth data. Due to space limitations, we choose to report these experimental results in the Appendix A
-of the supplementary material, in which the results justify the effectiveness and efficiency of our methods compared with the state-of-the-art methods.
-Thanks for the suggestion!
-
-It is worth mentioning that the datasets used in our experiments
-are more much sparser than the one used in [S1], which means that it
-is more difficult to predict links on our datasets. As a result, the top-$k$
-precision on our datasets, when $k$ is fixed to the number of links in the
-ground truth data, is too low to be useful in practice.
-
-[S1] Y. Yang, R. N. Lichtenwalter, and N. V. Chawla. Evaluating link prediction
-methods. Knowl Inf Syst, 45:751每782, 2015.
-
-[35] D. Song, D. Meyer, and D. Tao. Top-k link recommendation in social
-networks. In ICDM, 2015.
-
-[39] R. West, A. Paranjape, and J. Leskovec. Mining missing hyperlinks from
-human navigation traces: A case study of wikipedia. In WWW, 2015.
+Yes, we have gone over the paper and improved the presentation to make it more understandable. Thanks for the suggestion!
 
@@
 
-We have added an accuracy comparison of our methods and
-BIGCLAM with varied hop distances in Section 4.2.4. The results show
-that all these methods are more accurate in predicting 2 or 3 hop distance
-links, and they are not good at predicting links with large hop distances.
-This is a general limitation of most (if not all) existing methods, which deserves  a full treatment in the future.
-
-Thanks for helping us to identify the limitation of our method!
+We thank the reviewer for appreciating the practice merit of our work. And we believe this paper also stands from research and technique perspective: (1)
 
@@
 
-We have added a remark in the end of Section 3.6 such that our ensemble-enabled approach
-is a general method for decomposing the large network link prediction
-problem into smaller subproblems, which is not limited to NMF, and may be applied to other link prediction methods such as AA and RA.
-
-We have revised the bagging+ and bagging methods by replacing NMF with AA and RA, respectively, and  we evaluated and reported their performance
-in the Appendix C of the supplementary material. Our preliminary results indeed show that the
-ensemble-enabled AA and RA are very promising, though more sophisticated sampling techniques are needed for achieving better performances.  Thanks for this great comment!
+Yes, we have downgraded the tone and changed it into practical and difficult. Thanks for the suggestion!
 
@@
 This is a questionable statement.
-Maybe it is too large to handle "on a PC with 2 Intel Xeon E5每2630 2.4GHz CPUs and 64 GB of memory" but approaches like PageRank has been used for web-scale data so unless there is something that I am missing, this statement should also go (or explained better).}
+Maybe it is too large to handle "on a PC with 2 Intel Xeon E5¨C2630 2.4GHz CPUs and 64 GB of memory" but approaches like PageRank has been used for web-scale data so unless there is something that I am missing, this statement should also go (or explained better).}
+
+We have remove the sentence and explained the statement better.
+We have added the explanation of the generation of author citation graph and the size of the graph which makes it computationally expensive.
 
@@
 
-\textbf{[R3C1]} \emph{The section could be preceded by clearly noting
-the two challenges (prediction/training complexity) in large networks,
-and how separate tools are used to handle each.}
+\textbf{[R3W1\&D2]} \emph{More examples are suggested, especially when introducing the definitions, to make it easier for readers to understand.}
 
-The parameters are designed to fit variety ranking with different demands.
-For example, the ground-truth RECOM prefer venue component while PFCTN prefer citation component.
-Furthermore, our parameters are quite flexible to choose in a certain range for suiting different ranking which we have discussed in Exp-4.3.
+Yes, we agree that there should be more examples and add figures to illustrate how to generate components from scholarly data.
+However, due to the space limitation, we choose to report the examples in extended version.
+
+\textbf{[R3W2\&D4]} \emph{The memory cost of the algorithms is better to be reported in the experiments.}
+
+We have added the report of the memory cost in experiment Exp-x.x by numbers instead of figures due to the space limitation.Thanks for the suggestion!
+
+\textbf{[R3D1]} \emph{Although the authors have a detailed introduction about the growing data, detailed figures about the data are recommended in the introduction.}
+
+We have added a figure x to show the volume statistics of the data.
+
+\textbf{[R3D3]} \emph{It is suggested that the authors should include some references to papers addressing the time delaying problem such as temporal graph, since it is related to the topic.}
+
+We have added citations [xx][yy] about time delaying problem and discussed it in Section VI Related Work.
 

### 2017-12-24 icde/revision/Response.tex

@@
 
-We thank the reviewer for appreciating the practice merit of our work. And we believe this paper also stands from research and technique perspective: (1)
+We thank the reviewer for appreciating the practice merit of our work.
+And we believe this paper also stands from research and technique perspective: (1)  .
+We have further clarified our contributions in Section I Introduction and claimed the technique difference of our algorithm in Section VI Related Work.
 
@@
 
-We have remove the sentence and explained the statement better.
+We have removed the sentence and explained the statement better.
 We have added the explanation of the generation of author citation graph and the size of the graph which makes it computationally expensive.

### 2017-12-24 icde/revision/Response.tex

@@
 Editor-in-Chief,\\
-%IEEE Transactions on Knowledge and Data Engineering\\
+IEEE International Conference on Data Engineering\\
 
@@
 
-%Attached please find a revised version of our submission to IEEE Transactions on Knowledge and Data Engineering, \emph{An Ensemble Approach to Link Prediction}.
+Attached please find a revised version of our submission to IEEE International Conference on Data Engineering, \emph{Query Independent Scholarly Article Ranking}.
 
-%The paper has been substantially revised according to the referees¡¯ comments.
-In particular, (1) we have added an example to explain the procedure of the top-$(\epsilon, k)$ prediction, (2) we have compared the suggested Resource Allocation (RA) algorithm in the experimental study, (3) we have added an accuracy comparison with varied hop distances of our methods and BIGCLAM in the experimental study, (4) we have compared our methods with the state-of-the-art methods when $k$ is fixed to the number of links in the ground truth data and reported the accuracy results together with the 95\% confidence intervals in Appendixes A\&B of the supplementary material for the lack of space, (5) we have implemented and evaluated the ensemble-enabled approach with Adamic/Adar (AA) and RA in Appendix C of the supplementary material, and (6) we have also taken this opportunity to rewrite several parts of the paper to improve the presentation.
+The paper has been substantially revised according to the referees¡¯ comments.
+In particular, (1) we have further clarified our contributions, (2) we have explained the author component better, (3) we have added figures to show the statistics of data, (4) we have reported the memory cost in experience, (5) we have added related work of time delaying problem, and (6) we have also taken this opportunity to rewrite several parts of the paper to improve the presentation.
 
@@
 
-Yes, we agree that distributed processing is an important and independent problem which will be studied in future work and we have discussed it in Section VII. Thanks for the suggestion!
+Yes, we agree that distributed processing is an important and independent problem which will be studied in future work and we have discussed it in Section VII Conclusion. Thanks for the suggestion!
 
@@
 We thank the reviewer for appreciating the practice merit of our work.
-And we believe this paper also stands from research and technique perspective: (1)  .
+And we believe this paper also stands from research and technique perspective.
+To our knowledge, the incremental algorithm of time-weighted PageRank has not gained enough attention and is lack of research.
+Furthermore, the exist incremental PageRank for dynamic scholarly article ranking which mentioned in [22] is based on a impractical assumption.
+Therefore, we have designed the incremental time-weighted PageRank algorithm for scholarly article ranking which has its unique features.
 We have further clarified our contributions in Section I Introduction and claimed the technique difference of our algorithm in Section VI Related Work.
+
+[22]  R. Ghosh, T. Kuo, C. Hsu, S. Lin, and K. Lerman, ¡°Time-aware ranking in dynamic citation networks,¡± in ICDM Workshops, 2011.
 
@@
 
-Yes, we have downgraded the tone and changed it into practical and difficult. Thanks for the suggestion!
+Yes, we have downgraded the tone and changed it into "practical and difficult". Thanks for the suggestion!
 
@@
 
-We have added a figure x to show the volume statistics of the data.
+Yes, we have added a figure x to show the volume statistics of the data.
 

### 2017-12-24 icde/revision/Response.tex

@@
 \usepackage{xspace}
+\usepackage{color}
+
+\newcommand{\kw}[1]{{\ensuremath {\mathsf{#1}}}\xspace}
+\newcommand{\PairAcc}{\kw{PairAcc}}
+\newcommand{\recom}{{\sc Recom}\xspace}
+\newcommand{\fcita}{{\sc PFCtn}\xspace}
+\newcommand{\marked}[1]{\textcolor{red}{#1}}
 
@@
 
-Prof. xxx,\\
-Editor-in-Chief,\\
-IEEE International Conference on Data Engineering\\
+%Prof. xxx,\\
+%Editor-in-Chief,\\
+%IEEE International Conference on Data Engineering\\
 
-Dear Prof. xxx,
+Dear Reviewers,
 
-Attached please find a revised version of our submission to IEEE International Conference on Data Engineering, \emph{Query Independent Scholarly Article Ranking}.
+This is the response letter concerning the revised version of our submission to IEEE International Conference on Data Engineering 2018, \emph{Query Independent Scholarly Article Ranking}.
 
@@
 
-Below please find our responses to the comments by the referees.
+Below please find our detailed responses to the comments by the referees.
 
@@
 
-The parameters are designed to fit variety ranking with different demands.
+We discuss the necessity and the selection of parameters right after Eq.
+(7) (left column, page 4).
+More specifically, these parameters enable our model to fit to the various ranking scenarios in real-life applications, which hardly can be covered with one set of parameters.
+As be shown in the experiments, our model performs well in two reasonable ranking scenarios (with \recom and \fcita) by selecting quite different aggregating parameters, and, moreover, these parameters are indeed quite flexible to choose within a certain range, \ie $[0,1]$, as a) the optimal \PairAcc is obtained within a single region, b) the \PairAcc keeps at a high level within a certain ($\alpha$, $\beta$) combination space around the optimal region, and c) the optimal parameters on the same set of ground-truth are very similar across different datasets.
+
+%The parameters are designed to fit variety ranking with different demands.
 For example, the ground-truth RECOM prefer venue component while PFCTN prefer citation component.
@@
 
-We focus on query independent ranking because of its application in Google Schorlar and MicroSoft Academic Search.
-As to extension of query dependent ranking, our ranking scores can combine with the relevance scores given a specific query.
-For other heterogeneous information network, the extension of our method is not known.
+This work focuses on query independent ranking because of its wide application in modern scholarly search engines such as Google Scholar, Semantic Scholar and Microsoft Academic Search. 
+%
+We discuss the extension of query dependent ranking in the revised paper (left column, page 2), that our ranking can serve as an indicator of the importance of items, and, given a specific query, it can either be directly used to rank a subset of relevant items or combine with any relevance scores for ranking.
+%
+The extension in other heterogeneous information networks is currently unclear, since the TWPageRank is derived from the analysis of impacts of articles (left column, page 2).
+We shall identify such possible applications in the future.
 
@@
 
-Actually, changing the values on nodes is the key of our ranking method which evaluate the weight of nodes.
-Moreover, the change of nodes is difficult to handle due to the multiple iterations and probably cause the result fail to converge.
-To our knowledge, there is no related work on changing node weight and it is unclear how to change it.
-Finally, we set the weight of edges to achieve the change of impacts since they are essentially propagable in the network through edges.
+We clarify the reasons of not changing values on nodes at the revised version (left column, page 3). 
+The goal of our TWPageRank is to change the values, \ie importance, on nodes.
+One may wonder why not directly change node values.
+However, it is difficult to handle as importance does not have a clear and closed-form definition and it may also cause problems for convergence.
+To our knowledge, there is no related work on changing node weights and it is yet unclear how to handle it.
+Finally, we set the weight of edges to achieve the goal since importance is essentially propagable through edges and it is also fair for all nodes.
 
@@
 
-Figure 1 shows the logscale number of citations grow exponentially with time, instead of impacts of individual articles.
+Figure 1 shows the logscale number of citations which grows exponentially with time 
+%(due to the exponential growth of volume of  scientific publications)
+(which is highlighted in the revised version), instead of numbers of citations (\ie impacts) of individual articles.
+\marked{We add references [x,y] to support our observation.}
 
@@
 
-The PeakMul pattern is defined in [19]:  the height of a peak should be at least 75\% of the maximum peak height, and two consecutive peaks should be separated by more than two years.
-In our work, we have simplified the pattern and only use the latest peak time which we have discussed in section II-A.
+The PeakMul pattern is originally defined in [19]:  the height of a peak should be at least 75\% of the maximum peak height, and two consecutive peaks should be separated by more than two years.
+In our work, we have simplified the pattern and only use the latest peak time which we have discussed in Section II-A (left column, page 3).
 
@@
 
-Yes, we agree that distributed processing is an important and independent problem which will be studied in future work and we have discussed it in Section VII Conclusion. Thanks for the suggestion!
+Yes, we agree that distributed processing is an important while independent problem which we have already placed in our future work (Conclusions, left column, page 12). %Thanks for the suggestion!
 
@@
 
-Yes, but the citation graph does have cycles and is not a DAG.
-Compare to general web graphs, the computation of TWPageRank in scholarly graphs is more efficient as a result of the less SCC edge ratio which is shown in Table I.
-In addition, we have designed the incremental algorithm based on this feature of scholalry graphs and it works better.
+Yes. This work does not assume the DAG structure of scholar graphs, where cycles are allowed to exist (Observation, left column, page 5). 
+Compared to general web graphs, the computation of TWPageRank on scholarly graphs is more efficient as a result of the temporal order of citations, which gives less SCC edge ratio shown in Table I (page 5).
+In addition, we further design incremental algorithms based on the temporal order, which also makes the computation more efficient.
+We have highlighted the statements about temporal order in the revised version.
 
@@
 
-Yes, we have revised as suggested. Thanks for the suggestion!
+Yes, we have revised as suggested (right column, page 1 \& right column, page 4). Thanks for the suggestion!
 
@@
 
-We think that the techniques proposed also have their own interests: (1) An ensemble based ranking model itself is hard to define, (2) an incremental algorithm that makes use of the particular properties of the scholar graph, and (3) a through experimental study.
+We think that the techniques proposed also have their own interests: a) An ensemble based ranking model itself is hard to define and tune, b) an incremental algorithm that makes use of the particular properties of the scholarly graphs, and c) a through experimental study.
 That is, this paper certainly has its contributions to the technical part.
+%\marked{In the revised version, we highlight our technical contributions.}
 
@@
 
-\textbf{[R2D1]} \emph{There seem to be two "contradictory" sides to this paper.
-From one side, this is a great "applications" paper where existing techniques and some good intuition is used to get better results into an existing (practical) problem.
+\textbf{[R2D1]} \emph{There seem to be two ``contradictory" sides to this paper.
+From one side, this is a great ``applications" paper where existing techniques and some good intuition is used to get better results into an existing (practical) problem.
 From a purely research and technical perspective, the paper is on the weak side.
@@
 
-We thank the reviewer for appreciating the practice merit of our work.
+We thank the reviewer for appreciating the practice merit of our work which is drawn from an important and practical problem. 
+%
 And we believe this paper also stands from research and technique perspective.
-To our knowledge, the incremental algorithm of time-weighted PageRank has not gained enough attention and is lack of research.
-Furthermore, the exist incremental PageRank for dynamic scholarly article ranking which mentioned in [22] is based on a impractical assumption.
+To our knowledge, incremental algorithms of time-weighted PageRank has not gained enough attentions.
+Furthermore, the only existing dynamic scholarly article ranking solution [22] is based on a impractical assumption that there is no citations between articles of the same year.
 Therefore, we have designed the incremental time-weighted PageRank algorithm for scholarly article ranking which has its unique features.
-We have further clarified our contributions in Section I Introduction and claimed the technique difference of our algorithm in Section VI Related Work.
+To conclude, we are not simply applying existing techniques into a different domain.
+%
+We have further clarified \marked{our contributions in Introduction} and claimed the technique difference of our algorithm in Related Work.
 
@@
 
-Yes, we have downgraded the tone and changed it into "practical and difficult". Thanks for the suggestion!
+We have downgraded the tone and changed it into ``practical and difficult". Thanks for the suggestion!
 
@@
 We have removed the sentence and explained the statement better.
-We have added the explanation of the generation of author citation graph and the size of the graph which makes it computationally expensive.
+Moreover specifically, we add the details of the generation of the author citation graph and \marked{the size of the graph} which makes it computationally expensive (Author Component, left column, page 3).
 
@@
 
-Yes, we agree that there should be more examples and add figures to illustrate how to generate components from scholarly data.
-However, due to the space limitation, we choose to report the examples in extended version.
+Yes, we agree that more examples (especially on how to generate components from scholarly data) will make our paper easier to understand.
+Due to the space limitation, we choose to add the examples in the extended version.
 
@@
 
-We have added the report of the memory cost in experiment Exp-x.x by numbers instead of figures due to the space limitation.Thanks for the suggestion!
+We have added the memory cost in experiment Exp-x.x. Thanks for the suggestion!
 
@@
 
-Yes, we have added a figure x to show the volume statistics of the data.
+Yes, \marked{we add the volume statistics of the growing data in Figure 1.}
 
@@
 
-We have added citations [xx][yy] about time delaying problem and discussed it in Section VI Related Work.
+Yes. We include references to temporal graphs in Related Work (page 12).
 

### 2017-12-24 icde/revision/sec-alg.tex

--- 2017-09-21 icde/sec-alg.tex
@@
 
-The main result here is to speed up computing TWPageRank by exploiting the {\em temporal order} of scholarly articles.
+The main result here is to speed up computing TWPageRank by exploiting the {\em temporal order} of scholarly article citations.
 
@@
 
-\stitle{Observation.} It is well-known that article citations obey a natural temporal order, \ie an article only cites those published earlier, and it is really rare for the mutual citations between two articles published in the same time.
+\stitle{Observation.} It is well-known that article citations obey a natural {\em temporal order}, \ie an article only cites those published earlier, and it is really rare for the mutual citations between two articles published in the same time.
 That is, $|E_i|$ is essentially small for the citation graphs of scholarly articles.
 
-To verify this observation, we also collect the statistics of citation graphs, venue graphs and Web graphs (illustrated in Table~\ref{tab-batch}), where Web graphs are extracted from berkely.edu and stanford.edu domains in 2002 and from the Google programming contest in 2002, respectively~\cite{LeskovecLDM09}.
+To verify this observation, we also collect the statistics of citation graphs, venue graphs and Web graphs and illustrate in Table~\ref{tab-batch}, where Web graphs are extracted from berkely.edu and stanford.edu domains in 2002 and from the Google programming contest in 2002, respectively~\cite{LeskovecLDM09}, \markedb{and numbers $x/y$ in the first three rows are the corresponding statistics on citation/venue graphs.}
 Due to the existence of the ``bow tie'' structure and the giant \scc in Web graphs~\cite{BroderKMRRSTW00}, the edge ratios $|E_i|/|E|$ are greater than 59\% for Web graphs.
-In contrast, the \sccs in citation and venue graphs are quite small as a result of the temporal order of citations, and $|E_i|/|E|$ is less than 3\% for all tested citation and venue graphs.
+In contrast, the \sccs in citation and venue graphs are quite small as a result of the {\em temporal order of citations}, and $|E_i|/|E|$ is less than 3\% for all tested citation and venue graphs.
 %

### 2017-12-24 icde/revision/sec-intro.tex

@@
 That is, scholarly article ranking is essentially a problem of assessing the importance of nodes in a heterogeneous network.
-However, effective and efficient ranking of nodes in such a large complex network is a challenging task due to the heterogeneous, evolving and dynamic natures of involved entities~\cite{AggarwalS14-survey,fcs-biggraph}.
+However, effective and efficient ranking of nodes in such a large complex network is a different task due to the heterogeneous, evolving and dynamic natures of involved entities~\cite{AggarwalS14-survey,fcs-biggraph}.
 
@@
 Finally, academic data is dynamic and continuously growing.
-Indeed, the number of articles in \magdata has exceeded 126 million, and keeps increasing at around 5.7 million per year~\cite{Sinha15:MAG}.
+Indeed, the number of articles in Microsoft Academic Graph has exceeded 126 million, and keeps increasing at around 5.7 million per year~\cite{Sinha15:MAG}.
 This may cause certain long-term biases into data, \eg the number of citations increases significantly over time~\cite{BornmannM15}, which should be properly considered for scholarly article ranking.
 
-Query independent ranking of scholarly articles remains challenging~\cite{wsdmcup}, although there exists quite a bit of work on scholarly article ranking, \eg~\cite{Garfield471,Liang16AAAI,Jiang12-MRank,Waltman2014}.
+Query independent ranking of scholarly articles remains difficult~\cite{wsdmcup}, although there exists quite a bit of work on scholarly article ranking, \eg~\cite{Garfield471,Liang16AAAI,Jiang12-MRank,Waltman2014}.
 Most previous work exploits the time-dependent information of scholarly data in the form of exponential decay~\cite{Li08TSRanking,Wang13AAAI,sayyadi09,WalkerXKM07}, which fails to capture the diverse citation patterns of individual articles~\cite{Chakraborty15}.

### 2017-12-24 icde/revision/sec-model.tex

--- 2017-09-30 icde/sec-model.tex
@@
 In this section, we first present Time-Weighted PageRank for evaluating  the importance of entities, defined as a combination of the prestige and popularity, and then introduce our ranking model \ensemblerank that assembles the importance of articles, venues and authors involved in scholarly articles.
+%
+\markedb{Before going into details, we would like to point out that although this work focuses on query independent ranking, it can also be used for query dependent ranking.
+Our ranking can serve as an indicator of the importance of items, and, given a specific query, it can either be directly used to rank a subset of relevant items or combine with any relevance scores.}
 
@@
 \vspace{-1ex}
-\caption{\small Citation statistics of scholarly articles that reports the (logscale) percentage of the number of citations of each year \wrt\ the total number of citations on \aan, \aminer and \magdata, respectively.}
+\caption{\small Citation statistics of scholarly articles that reports the {\em logscale percentage of the number of citations of each year} \wrt\ the total number of citations on \aan, \aminer and \magdata, respectively.}
 \label{fig-reference}
@@
 \vspace{-1ex}
+\stitle{Remarks}. 
+\markedb{
+The goal of our TWPageRank is to change the values, \ie importance, on nodes.
+One may wonder why not directly change node values.
+However, it is difficult to handle as importance does not have a clear and closed-form definition and it may also cause problems for convergence.
+To our knowledge, there is no related work on changing node weights and it is yet unclear how to handle it.
+Finally, we set the weight of edges to achieve the goal since importance is essentially propagable through edges and it is also fair for all nodes.
+}
+
 \subsection{Ranking with Importance Assembling}
@@
 
-However, the resulting author citation graph to compute the prestige is typically too large to handle.
+%However, the resulting author citation graph to compute the prestige is typically too large to handle. 
+\markedb{To evaluate the importance of each author, an author citation graph needs firstly to be constructed such that (a) a node represents an author, and (b) a direct edge $(s,t)$ denotes that there exist articles published by author $s$ citing articles published by author $t$.
+It is not hard to image that the number of edges in the author citation graph is much larger than the number in the citation graph, which reaches xxx on \magdata.
+Handing such a graph is computationally expensive.
+}
 Hence, we evaluate the prestige of an author, by using the average prestige of all articles published by the author.
@@
 \noindent Here aggregating parameters $\alpha$ and $\beta$ and value $(1 - \alpha - \beta)$ regularize the contributions of the citation, venue and author information.
-Intuitively, these parameters indicate the intensity of the correlation between the importance of scholarly articles and the specific information.
+%
+\markedb{
+By this, our model is able to fit to the various ranking scenarios in real-life applications, which hardly can be covered with one set of parameters.
+As will be shown in the experiments, our model performs well in two reasonable ranking scenarios by selecting quite different aggregating parameters, and, moreover, these parameters are indeed quite flexible to choose within a certain range, \ie $[0,1]$.
+}
+%Intuitively, these parameters indicate the intensity of the correlation between the importance of scholarly articles and the specific information.
 

### 2017-12-24 icde/revision/sec-related.tex

--- 2017-09-30 icde/sec-related.tex
@@
 While PageRank equally propagates scores along outlinks, Weighted PageRank extends PageRank by distributing scores based on certain criteria such as popularity of pages~\cite{Xing04:WPR} or authority of authors~\cite{Ding11}.
-Both these approaches fail to capture the time-dependent characteristics, a key factor for scholarly article ranking.
+%Both these approaches fail to capture the time-dependent characteristics, a key factor for scholarly article ranking. 
+\markedb{Scholarly graph is a kind of temporal graphs [xx] and temporal information is a key factor for scholarly article ranking.}
 There has been work extending temporal information into PageRank, \eg exponentially decayed weights~\cite{Li08TSRanking}, exponentially decayed initial vectors~\cite{WalkerXKM07} and time-dependent weights based on co-authorship~\cite{FIALA2012370}.
-Different from previous work, the Time-Weighted PageRank of this work discriminately propagates scores in terms of citation statistics.
+Different from previous work, the Time-Weighted PageRank of this work \markedb{is inspired by the impacts of articles} and discriminately propagates scores in terms of \markedb{temporal statistics of citations}.
 

### 2017-12-26 icde/revision/Response.tex

@@
 
-This is the response letter concerning the revised version of our submission to IEEE International Conference on Data Engineering 2018, \emph{Query Independent Scholarly Article Ranking}.
+This is the response letter regarding the revised version of our submission to IEEE International Conference on Data Engineering 2018, \emph{Query Independent Scholarly Article Ranking}.
 
 The paper has been substantially revised according to the referees¡¯ comments.
-In particular, (1) we have further clarified our contributions, (2) we have explained the author component better, (3) we have added figures to show the statistics of data, (4) we have reported the memory cost in experience, (5) we have added related work of time delaying problem, and (6) we have also taken this opportunity to rewrite several parts of the paper to improve the presentation.
+In particular, we have (1) further clarified our contributions (Section I), (2) added figures to show the statistics of data (3) explained the author component better,  (4) reported the memory cost in experiments, (5) added related work of time delaying problem, and (6) taken this opportunity to rewrite several parts of our paper to improve the presentation.
 
@@
 More specifically, these parameters enable our model to fit to the various ranking scenarios in real-life applications, which hardly can be covered with one set of parameters.
-As be shown in the experiments, our model performs well in two reasonable ranking scenarios (with \recom and \fcita) by selecting quite different aggregating parameters, and, moreover, these parameters are indeed quite flexible to choose within a certain range, \ie $[0,1]$, as a) the optimal \PairAcc is obtained within a single region, b) the \PairAcc keeps at a high level within a certain ($\alpha$, $\beta$) combination space around the optimal region, and c) the optimal parameters on the same set of ground-truth are very similar across different datasets.
+As be shown in the experiments, our model performs well in two reasonable ranking scenarios (with \recom and \fcita) by using quite different aggregating parameters, and, moreover, these parameters are indeed quite flexible to choose within a certain range, \ie $[0,1]$, as a) the optimal \PairAcc is obtained within a single region, b) the \PairAcc keeps at a high level within a certain ($\alpha$, $\beta$) combination space around the optimal region, and c) the optimal parameters on the same set of ground-truth are very similar across different datasets (please also refer to Exp-4.3).
 
@@
 
-We clarify the reasons of not changing values on nodes at the revised version (left column, page 3). 
-The goal of our TWPageRank is to change the values, \ie importance, on nodes.
-One may wonder why not directly change node values.
-However, it is difficult to handle as importance does not have a clear and closed-form definition and it may also cause problems for convergence.
+We clarify the reasons of not changing values on nodes at the revised version (Remarks, left column, page 3). 
+The goal of our TWPageRank is to change node values, \ie importance.
+%One may wonder why not directly change node values. 
+Directly changing node values, however, is difficult to handle as importance does not have a clear and closed-form definition and it may also cause problems for convergence.
 To our knowledge, there is no related work on changing node weights and it is yet unclear how to handle it.
-Finally, we set the weight of edges to achieve the goal since importance is essentially propagable through edges and it is also fair for all nodes.
+Finally, we use impact weights to achieve the goal since importance is essentially propagable through edges and it is also fair for all nodes.
 
@@
 
-Figure 1 shows the logscale number of citations which grows exponentially with time 
-%(due to the exponential growth of volume of  scientific publications)
-(which is highlighted in the revised version), instead of numbers of citations (\ie impacts) of individual articles.
-\marked{We add references [x,y] to support our observation.}
+Figure 1 shows the logscale percentage of the number of citations of each year which grows exponentially with time (due to the exponential growth of volume of  scientific publications), instead of numbers of citations (\ie impacts) of individual articles.
+We have highlighted it in the revised version (Figure 1, page 2).
+\marked{Moreover, we add references [x,y] to support our observation.}
 
@@
 The PeakMul pattern is originally defined in [19]:  the height of a peak should be at least 75\% of the maximum peak height, and two consecutive peaks should be separated by more than two years.
-In our work, we have simplified the pattern and only use the latest peak time which we have discussed in Section II-A (left column, page 3).
+In our work, we unify the five patterns and only use the latest peak time which we have discussed in Section II-A (para 1, left column, page 3).
 
@@
 
-Yes, we agree that distributed processing is an important while independent problem which we have already placed in our future work (Conclusions, left column, page 12). %Thanks for the suggestion!
+Yes, we agree that distributed processing is an important while independent problem which we have already placed in our future work (Conclusions, page 12). %Thanks for the suggestion!
 
@@
 
-Yes. This work does not assume the DAG structure of scholar graphs, where cycles are allowed to exist (Observation, left column, page 5). 
-Compared to general web graphs, the computation of TWPageRank on scholarly graphs is more efficient as a result of the temporal order of citations, which gives less SCC edge ratio shown in Table I (page 5).
+Yes. This work does NOT assume the DAG structure of scholar graphs, where cycles are allowed to exist (Observation, left column, page 5).
+Compared to general web graphs, the computation of TWPageRank on scholarly graphs is more efficient as a result of the temporal order of citations, which gives less SCC edge ratio as shown in Table I (page 5).
 In addition, we further design incremental algorithms based on the temporal order, which also makes the computation more efficient.
-We have highlighted the statements about temporal order in the revised version.
+%We have highlighted the statements about temporal order in the revised version.
 
@@
 
-Yes, we have revised as suggested (right column, page 1 \& right column, page 4). Thanks for the suggestion!
+Yes, we have revised our paper as suggested (right column, page 1 \& right column, page 5). Thanks for the suggestion!
 
@@
 
-Yes, we have gone over the paper and improved the presentation to make it more understandable. Thanks for the suggestion!
+\marked{Yes, we have gone over the paper and improved the presentation to make it more understandable. }
+%Thanks for the suggestion!
 
@@
 %
-And we believe this paper also stands from research and technique perspective.
-To our knowledge, incremental algorithms of time-weighted PageRank has not gained enough attentions.
-Furthermore, the only existing dynamic scholarly article ranking solution [22] is based on a impractical assumption that there is no citations between articles of the same year.
-Therefore, we have designed the incremental time-weighted PageRank algorithm for scholarly article ranking which has its unique features.
+And we believe this paper also stands from research and technique perspective (Please also refer to our response to R2W1). 
+%
+The property of scholarly data makes the incremental computation of (time-weighted) PageRank quite different from on general graphs, which, to our knowledge, has not gained enough attentions.
+Furthermore, the only existing dynamic scholarly article ranking solution [22] is based on a impractical assumption that there is no citations between articles of the same years.
+%
+Therefore, we have designed the incremental time-weighted PageRank algorithm for scholarly graphs which has its own unique features.
 To conclude, we are not simply applying existing techniques into a different domain.
@@
 We have further clarified \marked{our contributions in Introduction} and claimed the technique difference of our algorithm in Related Work. 
+%
 
@@
 
-We have added the memory cost in experiment Exp-x.x. Thanks for the suggestion!
+\marked{We have added the memory cost of our algorithm which uses 49.4GB when using data before 2017 in experiment Exp-x.x. }
 
@@
 
-Yes. We include references to temporal graphs in Related Work (page 12).
+Yes. We have discussed the correlation between our work and temporal graph and include necessary references in Related Work.
 

### 2017-12-26 icde/revision/sec-alg.tex

@@
 To verify this observation, we also collect the statistics of citation graphs, venue graphs and Web graphs and illustrate in Table~\ref{tab-batch}, where Web graphs are extracted from berkely.edu and stanford.edu domains in 2002 and from the Google programming contest in 2002, respectively~\cite{LeskovecLDM09}, \markedb{and numbers $x/y$ in the first three rows are the corresponding statistics on citation/venue graphs.}
-Due to the existence of the ``bow tie'' structure and the giant \scc in Web graphs~\cite{BroderKMRRSTW00}, the edge ratios $|E_i|/|E|$ are greater than 59\% for Web graphs.
+Due to the existence of the ``bow tie'' structure and the giant \scc in Web graphs~\cite{BroderKMRRSTW00}, the edge ratios $|E_i|/|E|$ are greater than 59\%.
 In contrast, the \sccs in citation and venue graphs are quite small as a result of the {\em temporal order of citations}, and $|E_i|/|E|$ is less than 3\% for all tested citation and venue graphs.

### 2017-12-26 icde/revision/sec-model.tex

@@
 %
-\markedb{Before going into details, we would like to point out that although this work focuses on query independent ranking, it can also be used for query dependent ranking.
+\markedb{Before going into details, it is worthy pointing out that although this work focuses on query independent ranking, it can also be used for query dependent ranking.
 Our ranking can serve as an indicator of the importance of items, and, given a specific query, it can either be directly used to rank a subset of relevant items or combine with any relevance scores.}
@@
 \markedb{
-The goal of our TWPageRank is to change the values, \ie importance, on nodes.
+The goal of our TWPageRank is to change node values, \ie importance.
 One may wonder why not directly change node values.
@@
 To our knowledge, there is no related work on changing node weights and it is yet unclear how to handle it.
-Finally, we set the weight of edges to achieve the goal since importance is essentially propagable through edges and it is also fair for all nodes.
+Finally, we use impact weights to achieve the goal since importance is essentially propagable through edges and it is also fair for all nodes.
 }
@@
 By this, our model is able to fit to the various ranking scenarios in real-life applications, which hardly can be covered with one set of parameters.
-As will be shown in the experiments, our model performs well in two reasonable ranking scenarios by selecting quite different aggregating parameters, and, moreover, these parameters are indeed quite flexible to choose within a certain range, \ie $[0,1]$.
+As will be shown in the experiments, our model performs well in two reasonable ranking scenarios by using quite different aggregating parameters, and, moreover, these parameters are indeed quite flexible to choose within a certain range, \ie $[0,1]$.
 }

### 2017-12-26 icde/revision/sec-related.tex

@@
 
-%PageRank \cite{Brin98:PageRank} and its extensions have been extensively used for citation analyses \cite{Waltman2014}.
-While PageRank equally propagates scores along outlinks, Weighted PageRank \cite{Xing04:WPR} extends PageRank by distributing scores based on the popularity of pages.
-Different from previous work, the Time-Weighted PageRank proposed in this work discriminately propagates scores in terms of citation statistics.
-
 PageRank \cite{Brin98:PageRank} and its extensions have been extensively used for citation analyses \cite{Waltman2014}.
@@
 %Both these approaches fail to capture the time-dependent characteristics, a key factor for scholarly article ranking.
-\markedb{Scholarly graph is a kind of temporal graphs [xx] and temporal information is a key factor for scholarly article ranking.}
+\markedb{Scholarly graph is a kind of temporal graphs~\cite{temporalgraph} and temporal information is a key factor for scholarly article ranking.}
 There has been work extending temporal information into PageRank, \eg exponentially decayed weights~\cite{Li08TSRanking}, exponentially decayed initial vectors~\cite{WalkerXKM07} and time-dependent weights based on co-authorship~\cite{FIALA2012370}.
@@
 %\stitle{Dynamic algorithms}.
-
 Dynamic algorithms have proven useful for various tasks by avoiding computing from scratch~\cite{RamalingamR93}.
-% and only recomputing those affected by updates
-%Dynamic algorithms have proven useful for graph analysis tasks, \eg incremental graph pattern matching~\cite{FanWW13} and  incremental simrank computation~\cite{YuLZ14}.
 To our knowledge, little concern has been paid to dynamic scholarly article ranking except that~\cite{GhoshKHLL11} uses PageRank in dynamic citation networks.
@@
 %
-Different from previous work, we study scholarly article ranking in a dynamic environment in terms of
-the citation characteristics of scholarly articles, which has never been exploited before.
-
-%Our approach only makes the assumption that there are no mutual references within the citation network, which, we admit, violates xx\% of total citations on \magdata, and is significantly different (yy\% on \magdata) from~\cite{GhoshKHLL11}.
-- move to Section 3
+\markedb{In this work, we study dynamic scholarly article ranking in the general case and develop our incremental algorithm in terms of the citation characteristics, which has never been exploited before.}
+%Different from previous work, we study scholarly article ranking in a dynamic environment in terms of the citation characteristics of scholarly articles, which has never been exploited before.
 
 Ensemble methods use multiple learners to obtain better performance than could be obtained from a constituent learner alone~\cite{zhihua-book}.
-%In this work, we leverage ensembles to produce better and robust results for scholarly article ranking~\cite{zhihua-book,wsdmcup,DuanAMHH16}.
 In this work, we leverage  importance assembling  to produce better and more robust results for scholarly article ranking~\cite{zhihua-book,wsdmcup,DuanAMHH16}.

### 2017-12-26 icde/revision/sec-model.tex

@@
 \markedb{To evaluate the importance of each author, an author citation graph needs firstly to be constructed such that (a) a node represents an author, and (b) a direct edge $(s,t)$ denotes that there exist articles published by author $s$ citing articles published by author $t$.
-It is not hard to image that the number of edges in the author citation graph is much larger than the number in the citation graph, which reaches xxx on \magdata.
+It is not hard to image that the number of edges in the author citation graph is much larger than the number in the citation graph, which reaches to 4.5 billion on \magdata.
 Handing such a graph is computationally expensive.

### 2017-12-26 icde/revision/Response.tex

@@
 
-\marked{We have added the memory cost of our algorithm which uses 49.4GB when using data before 2017 in experiment Exp-x.x. }
+\marked{We have added the memory cost in experiment Exp-3.
+Indeed, the memory cost of (PRank, FRank, SARank) is (12.65GB, 16.42GB, 49.42GB) while set the $Y_s=2015$ on MAG, respectively, and the memory cost of HRank is while set the the $Y_s=2014$ on MAG.
+}
 

### 2017-12-26 icde/revision/Response.tex

--- 2017-12-26 icde/revision/Response.tex
@@
 We have removed the sentence and explained the statement better.
-Moreover specifically, we add the details of the generation of the author citation graph and \marked{the size of the graph} which makes it computationally expensive (Author Component, left column, page 3).
+Moreover specifically, we add the details of the generation of the author citation graph \marked{with and 115 billion edges 7.12 billion edges} which makes it computationally expensive (Author Component, left column, page 3).
 
@@
 
-\marked{We have added the memory cost of our algorithm which uses 49.4GB when using data before 2017 in experiment Exp-x.x. }
+\marked{We have added the memory cost in experiment Exp-3.
+Indeed, the memory cost of (PRank, FRank, SARank) is (12.65GB, 16.42GB, 49.42GB) while set the $Y_s=2015$ on MAG, respectively, and the memory cost of HRank is while set the $Y_s=2014$ on MAG.
+}
 

### 2017-12-26 icde/revision/Response.tex

@@
 \marked{We have added the memory cost in experiment Exp-3.
-Indeed, the memory cost of (PRank, FRank, SARank) is (12.65GB, 16.42GB, 49.42GB) while set the $Y_s=2015$ on MAG, respectively, and the memory cost of HRank is while set the $Y_s=2014$ on MAG.
+Indeed, the memory cost of (PRank, FRank, SARank) is (12.65GB, 16.42GB, 49.42GB) while set the $Y_s=2015$ on MAG, respectively, and the memory cost of HRank is 61.37GB while set the $Y_s=2014$ on MAG.
 }

### 2017-12-26 icde/revision/Response.tex

--- 2017-12-26 icde/revision/Response.tex
@@
 \newcommand{\fcita}{{\sc PFCtn}\xspace}
+\newcommand{\pagerank}{\kw{PRank}} %PageRank
+\newcommand{\futurerank}{\kw{FRank}} %FutureRank
+\newcommand{\hhgrank}{\kw{HRank}} %HHGBiRank
+\newcommand{\ensemblerank}{\kw{SARank}}
 \newcommand{\marked}[1]{\textcolor{red}{#1}}
+\newcommand{\magdata}{{\sc MAG}\xspace}
 
@@
 
-Yes, we have revised our paper as suggested (right column, page 1 \& right column, page 5). Thanks for the suggestion!
+Yes, we have revised our paper as suggested (right column, page 1 \& right column, page 5). 
+%Thanks for the suggestion!
 
@@
 
-We think that the techniques proposed also have their own interests: a) An ensemble based ranking model itself is hard to define and tune, b) an incremental algorithm that makes use of the particular properties of the scholarly graphs, and c) a through experimental study.
+We think that the techniques proposed also have their own interests: a) An importance assembling based ranking model itself is hard to define and tune, b) an incremental algorithm that makes use of the particular properties of the scholarly graphs, and c) a thorough experimental study.
 That is, this paper certainly has its contributions to the technical part.
@@
 Pagerank and (incremental) versions of it already exist and the paper makes little contributions there.
-The claim (made twice) in the related work section that "Different from previous work" this paper focuses on citations statistics doesn't hold water.
+The claim (made twice) in the related work section that ``Different from previous work" this paper focuses on citations statistics doesn't hold water.
 The fact that the authors are considering a different application domain is not a contribution compared to past (incremental) pagerank papers.
@@
 %
-And we believe this paper also stands from research and technique perspective (Please also refer to our response to R2W1).
+And we believe this paper also stands from research and technique perspective.
 %
-The property of scholarly data makes the incremental computation of (time-weighted) PageRank quite different from on general graphs, which, to our knowledge, has not gained enough attentions.
+The property of scholarly data makes the incremental computation of (time-weighted) PageRank quite different from those on general graphs, which, to our knowledge, has not gained enough attentions.
 Furthermore, the only existing dynamic scholarly article ranking solution [22] is based on a impractical assumption that there is no citations between articles of the same years.
@@
 %
+Please also refer to our response to R2W1.
 
@@
 
-\textbf{[R2D2]} \emph{The abstract starts with the sentence "Ranking query independent scholarly articles is a critical and challenging task, due to the heterogeneous, evolving and dynamic nature of entities involved in scholarly articles".
+\textbf{[R2D2]} \emph{The abstract starts with the sentence ``Ranking query independent scholarly articles is a critical and challenging task, due to the heterogeneous, evolving and dynamic nature of entities involved in scholarly articles".
 If three types of data (articles, authors and venues) that are updated (maybe) weekly is considered challenging in terms of heterogeneity and dynamicity then one must wonder what one can say about real-life scenarios with thousands of data types where hundreds/thousands of new items are inserted daily (consider any online merchant system) and were ranking is important (recommendations).
 In summary, this sentence should go.
-Not to mention that the task is not really "critical".}
+Not to mention that the task is not really ``critical".}
 
@@
 
-\textbf{[R2D3]} \emph{On page 4, you say "However, the resulting author citation graph to compute the prestige is typically too large to handle".
+\textbf{[R2D3]} \emph{On page 4, you say ``However, the resulting author citation graph to compute the prestige is typically too large to handle".
 This is a questionable statement.
-Maybe it is too large to handle "on a PC with 2 Intel Xeon E5¨C2630 2.4GHz CPUs and 64 GB of memory" but approaches like PageRank has been used for web-scale data so unless there is something that I am missing, this statement should also go (or explained better).}
+Maybe it is too large to handle ``on a PC with 2 Intel Xeon E5¨C2630 2.4GHz CPUs and 64 GB of memory" but approaches like PageRank has been used for web-scale data so unless there is something that I am missing, this statement should also go (or explained better).}
 
-We have removed the sentence and explained the statement better.
-Moreover specifically, we add the details of the generation of the author citation graph and \marked{the size of the graph} which makes it computationally expensive (Author Component, left column, page 3).
+We have removed the sentence and explained more details about the statement.
+Moreover specifically, we add the details of the generation of the author citation graph.
+The generated graph has 7.12 billion edges on the largest \magdata (\ie the memory cost of storage only is 57GB), which makes it computationally expensive to compute prestige of authors  with TWPageRank on that graph (Author Component, left column, page 3).
+We hence turn to the alternative light-weight method to achieve the goal.
 
@@
 
-\marked{We have added the memory cost in experiment Exp-3.
-Indeed, the memory cost of (PRank, FRank, SARank) is (12.65GB, 16.42GB, 49.42GB) while set the $Y_s=2015$ on MAG, respectively, and the memory cost of HRank is while set the the $Y_s=2014$ on MAG.
-}
+We have reported the memory cost in Exp-3 (page 10) that on the largest \magdata, (\futurerank, \ensemblerank) cost (16.42GB, 49.42GB) memory when $Y_s=2015$, and \hhgrank costs 61.37GB memory when $Y_s=2014$.
+Interestingly, our \ensemblerank model costs more memory than \futurerank due to its model complexity, while it is more efficient with our batch and incremental algorithms.
+%the memory cost of (\pagerank, \futurerank, \ensemblerank) is (12.65GB, 16.42GB, 49.42GB) when $Y_s=2015$, and the one of \hhgrank is 61.37GB when $Y_s=2014$.
 
@@
 
-Yes, \marked{we add the volume statistics of the growing data in Figure 1.}
+Yes, we add the volume statistics (the number of articles published at each year) of the growing data  in Figure 1.
 
@@
 
-Yes. We have discussed the correlation between our work and temporal graph and include necessary references in Related Work.
+Yes. We have discussed the correlation between our work and temporal graphs and included necessary references in Related Work.
 

### 2017-12-26 icde/revision/sec-exp.tex

--- 2017-09-30 icde/sec-exp.tex
@@
 Aggregating parameters were selected as follows: $(\alpha, \beta, \gamma)$ = $(0.7, 0.1, 0.2)$ for \futurerank, $(a_{i1}, a_{i2}, a_{i3})$ = $(0.3, 0.6, 0.1)$ for \hhgrank ($i\in[1, 3]$), and $(\alpha, \beta)$ = $(0.8, 0.1)$ for \ensemblerank.
+\markedb{Note that with \fcita the selected $(\alpha, \beta)$ for \ensemblerank are quite different from the ones with \recom.}
 %Here the citation component contributed most in \ensemblerank, since \fcita is based on citation information.
@@
 For scholarly article ranking, algorithm \incensemble is on average (1.7, 3.1, 2.8, 117) and (2.0, 3.0, 4.4, 245) times faster than (\batensemble, \powensemble, \futurerank, \hhgrank) on \aminer and \magdata, respectively.
+
+\markedb{The memory cost is an important factor of efficiency.
+We thus collect the memory use on the largest \magdata that (\futurerank, \ensemblerank) cost (16.42GB, 49.42GB) memory when $Y_s=2015$, and \hhgrank costs 61.37GB when $Y_s=2014$.
+Interestingly, our \ensemblerank model costs more memory than \futurerank due to its model complexity, while it is more efficient with our batch and incremental algorithms.}
 

### 2017-12-26 icde/revision/sec-model.tex

--- 2017-12-26 icde/revision/sec-model.tex
@@
 \centering
-\includegraphics[scale=0.48]{fig/yearly-references.eps}
-\vspace{-1ex}
-\caption{\small Citation statistics of scholarly articles that reports the {\em logscale percentage of the number of citations of each year} \wrt\ the total number of citations on \aan, \aminer and \magdata, respectively.}
-\label{fig-reference}
+\hspace{-4ex}
+\subfigure{\label{fig-paper}
+\includegraphics[scale=0.41]{fig/yearly-papers.eps}}
+\hspace{-4ex}
+\subfigure{\label{fig-citation}
+\includegraphics[scale=0.41]{fig/yearly-references.eps}}
+\caption{\small Statistics of scholarly articles that reports the {\em logscale percentage of the number of papers (left) and citations (right) of each year} \wrt\ the total number of papers and citations on \aan, \aminer and \magdata, respectively.}
+\label{fig-data-analysis}
 \vspace{-3ex}
 \end{figure}
+%[{\scriptsize a}] [{\scriptsize b}]
 
@@
 Basically, it could simply be the year when article $v$ obtains the largest number of citations.
-However, recent work reveals that the volume of scientific publications as well as the number of citations grow exponentially with time~\cite{Dong2017KDD,BornmannM15}.
-We also collect and report the citation statistics on three scholarly datasets in Fig.~\ref{fig-reference}, which verifies the exponential distribution.
+However, recent work reveals that the volume of scientific publications and the number of citations grow exponentially with time~\cite{Dong2017KDD,BornmannM15}.
+We also collect and report the volume and citation statistics on three scholarly datasets in Fig.~\ref{fig-data-analysis}, which verifies the exponential distribution.
 Hence, we adopt the {\em scaled} number of citations $\Psi_v^{(t)}=\Phi_v^{(t)} / \log Z^{(t)}$ such that $\Phi_v^{(t)}$ and $Z^{(t)}$ are the number of citations of article $v$ at year $t$ and the total number of citations at year $t$, respectively.
@@
 %However, the resulting author citation graph to compute the prestige is typically too large to handle.
-\markedb{To evaluate the importance of each author, an author citation graph needs firstly to be constructed such that (a) a node represents an author, and (b) a direct edge $(s,t)$ denotes that there exist articles published by author $s$ citing articles published by author $t$.
-It is not hard to image that the number of edges in the author citation graph is much larger than the number in the citation graph, which reaches xxx on \magdata.
-Handing such a graph is computationally expensive.
-}
+\markedb{To do this, an author citation graph needs to be constructed such that (a) a node represents an author, and (b) a direct edge $(s,t)$ denotes that there exist articles of author $s$ citing articles of author $t$.
+It is not hard to image that the number of edges in the author citation graph is much larger than the number in the citation graph, which reaches to 7.12  billion on the largest \magdata (\ie the memory cost of storage only is 57GB).
+It is computationally expensive to compute prestige of authors with TWPageRank on that graph.}
 Hence, we evaluate the prestige of an author, by using the average prestige of all articles published by the author.

### 2017-12-26 icde/revision/sec-related.tex

@@
 There has been work extending temporal information into PageRank, \eg exponentially decayed weights~\cite{Li08TSRanking}, exponentially decayed initial vectors~\cite{WalkerXKM07} and time-dependent weights based on co-authorship~\cite{FIALA2012370}.
-Different from previous work, the Time-Weighted PageRank of this work \markedb{is inspired by the impacts of articles} and discriminately propagates scores in terms of \markedb{temporal statistics of citations}.
+%Different from previous work, 
+Differently, our Time-Weighted PageRank \markedb{is inspired by an analysis of impacts of articles} and discriminately propagates scores in terms of statistics of citations.
 

### 2017-12-27 icde/revision/Response.tex

@@
 The paper has been substantially revised according to the referees¡¯ comments.
-In particular, we have (1) further clarified our contributions (Section I), (2) added figures to show the statistics of data (3) explained the author component better,  (4) reported the memory cost in experiments, (5) added related work of time delaying problem, and (6) taken this opportunity to rewrite several parts of our paper to improve the presentation.
+In particular, we have (1) further clarified our contributions, (2) added figures to better illustrate the data growing (3) explained the author component better,  (4) reported the memory cost in experiments, (5) modified related work to differentiate our technique with existing ones, (6) answered the questions raised by referees, and (7) taken this opportunity to rewrite several parts of our paper to improve the presentation.
 
@@
 
-Figure 1 shows the logscale percentage of the number of citations of each year which grows exponentially with time (due to the exponential growth of volume of  scientific publications), instead of numbers of citations (\ie impacts) of individual articles.
+Figure 1 shows the logscale percentage of the number of articles/citations of each year which grows exponentially with time, instead of numbers of citations (\ie impacts) of individual articles.
 We have highlighted it in the revised version (Figure 1, page 2).
-\marked{Moreover, we add references [x,y] to support our observation.}
+
+We have explained our claim better.
+The observation is inspired by the five distinct citation patterns.
+Considering that the direct decay model only conforms with {\em MonDec}, we thus propose our claim that can better explain the five citation patterns.
+Moreover, reference [18] exploits a log-normal survival probability which also decays with time after the citation peak.
+%(it increases before reaching the peak since it aims to predict the number of citations instead of impacts of articles).
+
+[18]  D. Wang, C. Song, and A. Barab¨¢si, ¡°Quantifying long-term scientific impact,¡± Science, vol. 342, no. 6154, pp. 127-132, 2013.
 
@@
 %
-We have further clarified \marked{our contributions in Introduction} and claimed the technique difference of our algorithm in Related Work.
+We have further clarified our contributions in Introduction and claimed the technique difference of our algorithm in Related Work.
 %

### 2017-12-27 icde/revision/sec-intro.tex

@@
 %
-To our knowledge, the Time-Weighted PageRank is among the first to incorporate the diverse citation patterns of individual articles for scholarly article ranking.
+To our knowledge, the Time-Weighted PageRank is among the first to \markedb{use citation statistics to incorporate the diverse citation patterns of individual articles for scholarly article ranking.}
 %and the long-term bias caused by the dynamic nature of data
 
-\sstab(2)  We then develop  a batch algorithm for scholarly article ranking (Section \ref{sec-alg}), in which we propose a block-wise method for Time-Weighted PageRank in terms of an analysis of the citation characteristics of scholarly articles.
+\sstab(2)  We then develop  a batch algorithm for scholarly article ranking (Section \ref{sec-alg}), in which we propose a block-wise method for Time-Weighted PageRank \markedb{and show its advantage in terms of an efficiency analysis based on citation characteristics of scholarly articles.}
+%in which we propose a block-wise method for Time-Weighted PageRank in terms of an analysis of the citation characteristics of scholarly articles.
 

### 2017-12-27 icde/revision/Response.tex

@@
 
+We would like to thank all the referees for their thorough reading of our paper and for their valuable comments.
+
 The paper has been substantially revised according to the referees¡¯ comments.
-In particular, we have (1) further clarified our contributions, (2) added figures to better illustrate the data growing (3) explained the author component better,  (4) reported the memory cost in experiments, (5) modified related work to differentiate our technique with existing ones, (6) answered the questions raised by referees, and (7) taken this opportunity to rewrite several parts of our paper to improve the presentation.
-
-We would like to thank all the referees for their thorough reading of our paper and for their valuable comments.
+In particular, we have (1) further clarified our contributions, (2) added figures to better illustrate the data growing, (3) explained the author component better,  (4) reported the memory cost in experiments, (5) modified related work to differentiate our technique with existing ones, (6) answered the questions raised by referees, and (7) taken this opportunity to rewrite several parts of our paper to improve the presentation.
 
@@
 More specifically, these parameters enable our model to fit to the various ranking scenarios in real-life applications, which hardly can be covered with one set of parameters.
-As be shown in the experiments, our model performs well in two reasonable ranking scenarios (with \recom and \fcita) by using quite different aggregating parameters, and, moreover, these parameters are indeed quite flexible to choose within a certain range, \ie $[0,1]$, as a) the optimal \PairAcc is obtained within a single region, b) the \PairAcc keeps at a high level within a certain ($\alpha$, $\beta$) combination space around the optimal region, and c) the optimal parameters on the same set of ground-truth are very similar across different datasets (please also refer to Exp-4.3).
+As be shown in the experiments, our model performs well in two reasonable ranking scenarios (with \recom and \fcita) by using quite different aggregating parameters, and, moreover, these parameters are indeed quite flexible to choose within a certain range, \ie $[0,1]$, as a) the optimal \PairAcc is obtained within a single region, b) the \PairAcc keeps at a high level within a certain ($\alpha$, $\beta$) combination space around the optimal region, and c) the optimal parameters on the same set of ground-truth are very similar across different datasets (please also refer to our analysis in Exp-4.3).
 
@@
 
+We discuss the extension of query dependent ranking in the revised paper (left column, page 2).
+%
 This work focuses on query independent ranking because of its wide application in modern scholarly search engines such as Google Scholar, Semantic Scholar and Microsoft Academic Search.
+And our ranking can serve as an indicator of the importance of items, and, given a specific query, it can either be directly used to rank a subset of relevant items or combine with any relevance scores for ranking.
 %
-We discuss the extension of query dependent ranking in the revised paper (left column, page 2), that our ranking can serve as an indicator of the importance of items, and, given a specific query, it can either be directly used to rank a subset of relevant items or combine with any relevance scores for ranking.
-%
-The extension in other heterogeneous information networks is currently unclear, since the TWPageRank is derived from the analysis of impacts of articles (left column, page 2).
-We shall identify such possible applications in the future.
+The extension in other heterogeneous information networks is currently unclear, since the TWPageRank is derived from an analysis of impacts of articles (left column, page 2).
+We shall identify possible applications in the future.
 
@@
 Considering that the direct decay model only conforms with {\em MonDec}, we thus propose our claim that can better explain the five citation patterns.
-Moreover, reference [18] exploits a log-normal survival probability which also decays with time after the citation peak.
+Moreover, reference [17] exploits a log-normal survival probability which also decays with time after the citation peak.
 %(it increases before reaching the peak since it aims to predict the number of citations instead of impacts of articles).
 
-[18]  D. Wang, C. Song, and A. Barab¨¢si, ¡°Quantifying long-term scientific impact,¡± Science, vol. 342, no. 6154, pp. 127-132, 2013.
+[17]  D. Wang, C. Song, and A. Barab¨¢si, ¡°Quantifying long-term scientific impact,¡± Science, vol. 342, no. 6154, pp. 127-132, 2013.
 
@@
 
-The PeakMul pattern is originally defined in [19]:  the height of a peak should be at least 75\% of the maximum peak height, and two consecutive peaks should be separated by more than two years.
+The PeakMul pattern is originally defined in [18]:  the height of a peak should be at least 75\% of the maximum peak height, and two consecutive peaks should be separated by more than two years.
 In our work, we unify the five patterns and only use the latest peak time which we have discussed in Section II-A (para 1, left column, page 3).
 
-[19]  T. Chakraborty, S. Kumar, P. Goyal, N. Ganguly, and A. Mukherjee, ¡°On the categorization of scientific citation profiles in computer science,¡± Commun. ACM, vol. 58, no. 9, 2015.
+[18]  T. Chakraborty, S. Kumar, P. Goyal, N. Ganguly, and A. Mukherjee, ¡°On the categorization of scientific citation profiles in computer science,¡± Commun. ACM, vol. 58, no. 9, 2015.
 
@@
 The property of scholarly data makes the incremental computation of (time-weighted) PageRank quite different from those on general graphs, which, to our knowledge, has not gained enough attentions.
-Furthermore, the only existing dynamic scholarly article ranking solution [22] is based on a impractical assumption that there is no citations between articles of the same years.
+Furthermore, the only existing dynamic scholarly article ranking solution [21] is based on a impractical assumption that there is no citations between articles of the same years.
 %
@@
 
-[22]  R. Ghosh, T. Kuo, C. Hsu, S. Lin, and K. Lerman, ¡°Time-aware ranking in dynamic citation networks,¡± in ICDM Workshops, 2011.
+[21]  R. Ghosh, T. Kuo, C. Hsu, S. Lin, and K. Lerman, ¡°Time-aware ranking in dynamic citation networks,¡± in ICDM Workshops, 2011.
 

### 2017-12-27 icde/revision/sec-alg.tex

@@
 
+\eat{
 \begin{proofSketch}
@@
 \end{proofSketch}
+}
 
@@
 \aan  & 18,041/565 & 82.9K/22.5K &  20/18  & 0.9\%/2.8\%      \\  %\hline
-\aminer  & 3.14M/56K & 14.3M/7.1M   & 23/1.5 &  1.6\%/2.1\%     \\ %\hline    % 1.5K = 1467
+\aminer  & 3.14M/56K & 14.3M/7.1M   & 23/1.5K &  1.6\%/2.1\%     \\ %\hline    % 1.5K = 1467
 \magdata  & 127M/584K & 526M/162M & 351/10K & 0.1\%/1.8\%    \\ \hline
@@
 
+\eat{   %% time & space complexity
 \stitle{Time \& space complexity analyses of the batch algorithm}.
@@
 Compared with the traditional power method~\cite{Brin98:PageRank}, our block-wise algorithm \twprscc uses $(2|V^c{'}|+|E^c{'}|)$ and $(2|V^v{'}|+|E^v{'}|)$ extra space to store the block-wise graphs $G^c{'}(V^c{'},E^c{'})$ of $G^c$ and $G^v{'}(V^v{'},E^v{'})$ of $G^v$ and their topological orders, while speeds up computation by $O((t-1)(|E^c_a|+|E^v_a|))$.
+}  %%% eat
+
+\stitle{Time complexity analysis of the batch algorithm}.
+%
+By Lemma~\ref{prop-venue-time-complexity} and the analyses in Section~\ref{subsec-bat-alg}, one can verify that algorithm \batensemble takes $O(|V^c|+|V^v|+|E^c_a|+|E^v_a|+t|E^c_i|+t|E^v_i|+|PA|)$ time, where $|PA|$ is the total number of author-article relationships.
+%
+The key of algorithm \batensemble is to compute TWPageRank with algorithm \twprscc.
+Compared with the traditional power method~\cite{Brin98:PageRank}, our block-wise algorithm \twprscc speeds up computation by $O((t-1)(|E^c_a|+|E^v_a|))$ at an extra space cost for the block-wise graphs of $G^c$ and $G^v$ and their topological orders.
 

### 2017-12-27 icde/revision/sec-exp.tex

@@
 %\begin{small}
-%\vspace{-.5ex}
+\vspace{-.5ex}
 \begin{tabular}{|c|c|c|c|c|}
@@
 \end{center}
-\vspace{-4ex}
+\vspace{-6ex}
 \end{table}
@@
 \label{exp-time}
-\vspace{-2ex}
+\vspace{-3ex}
 \end{figure*}
@@
 
-When varying $dif$, the \PairAcc of all algorithms increases with the increment of $dif$, since scholarly article pairs with larger $dif$ are easier to rank.
-Moreover, \ensemblerank consistently ranks better than all competitors, regardless of easy or difficult article pairs.
+When varying $dif$, the \PairAcc of all algorithms increases with the increment of $dif$, since pairs with larger $dif$ are easier to rank.
+Moreover, \ensemblerank consistently ranks better, regardless of easy or difficult article pairs.
 Indeed, \ensemblerank improves the \PairAcc over (\pagerank, \futurerank, \hhgrank) by (12.0\%, 3.0\%, 3.2\%) on \aan, (14.0\%, 6.5\%, 4.6\%) on \aminer, and (13.4\%, 6.0\%, 2.4\%) on \magdata, on average, respectively.
@@
 Our algorithm \ensemblerank improves the pair accuracy over \pagerank, \futurerank and \hhgrank by $(15.7\%, 2.8\%, 3.9\%)$ on \aan, $(17.3\%, 7.6\%, 5.8\%)$ on \aminer, and $(10.3\%, 4.4\%, 1.6\%)$ on \magdata, when evaluate all the pairs which have difference of future citation count greater than 0, which means \ensemblerank can evaluate and distinguish the articles only have small difference better.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newcommand{\graphscaleexpapp}{0.24}
+\newcommand{\graphmarginexpapp}{3ex}
+%%% all in 1 Figure
+\begin{figure*}[tb!]
+\addtolength{\subfigcapskip}{-1ex}
+\begin{center}
+\subfigure[{\scriptsize \aan with \recom}]{\label{exp-aan-ab-recom}
+\includegraphics[scale=\graphscaleexpapp]{./exp/AAN-para-recm.eps}}
+%\quad\quad
+\hspace{\graphmarginexpapp}
+%\hfill
+\subfigure[{\scriptsize \aminer with \recom}]{\label{exp-aminer-ab-recom}
+\includegraphics[scale=\graphscaleexpapp]{./exp/AMiner-para-recm.eps}}
+%\quad\quad
+\hspace{\graphmarginexpapp}
+%\hfill
+\subfigure[{\scriptsize \magdata with \recom}]{\label{exp-mag-ab-recom}
+\includegraphics[scale=\graphscaleexpapp]{./exp/MAG-para-recm.eps}}
+\\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\vspace{-2ex}
+%\hspace{-10ex}
+\subfigure[{\scriptsize \aan  with \fcita}]{\label{exp-aan-ab-fcita}
+\includegraphics[scale=\graphscaleexpapp]{./exp/AAN-para-fcita.eps}}
+%\quad\quad
+\hspace{\graphmarginexpapp}
+%\hfill
+\subfigure[{\scriptsize \aminer with \fcita}]{\label{exp-aminer-ab-fcita}
+\includegraphics[scale=\graphscaleexpapp]{./exp/AMiner-para-fcita.eps}}
+%\quad\quad
+\hspace{\graphmarginexpapp}
+%\hfill
+\subfigure[{\scriptsize \magdata with \fcita}]{\label{exp-mag-ab-fcita}
+\includegraphics[scale=\graphscaleexpapp]{./exp/MAG-para-fcita.eps}}
+\end{center}
+\vspace{-1.5ex}
+\caption{\small Accuracy evaluation: varying aggregating parameters $\alpha$ and $\beta$}
+\label{exp-ab}
+\vspace{-2ex}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newcommand{\graphscaleexpapp}{0.25}
-\newcommand{\graphmarginexpapp}{-2ex}
-%%% all in 1 Figure
-\begin{figure*}[tb!]
-\addtolength{\subfigcapskip}{-1ex}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[tb!]
+%\vspace{-2ex}
 \begin{center}
-\subfigure[{\scriptsize \aan with \recom}]{\label{exp-aan-ab-recom}
-\includegraphics[scale=\graphscaleexpapp]{./exp/AAN-para-recm.eps}}
-%\quad\quad
-%\hspace{\graphmarginexpapp}
-\hfill
-\subfigure[{\scriptsize \aminer with \recom}]{\label{exp-aminer-ab-recom}
-\includegraphics[scale=\graphscaleexpapp]{./exp/AMiner-para-recm.eps}}
-%\quad\quad
-%\hspace{\graphmarginexpapp}
-\hfill
-\subfigure[{\scriptsize \magdata with \recom}]{\label{exp-mag-ab-recom}
-\includegraphics[scale=\graphscaleexpapp]{./exp/MAG-para-recm.eps}}
-\\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace{-2ex}
-%\hspace{-10ex}
-\subfigure[{\scriptsize \aan  with \fcita}]{\label{exp-aan-ab-fcita}
-\includegraphics[scale=\graphscaleexpapp]{./exp/AAN-para-fcita.eps}}
-%\quad\quad
-%\hspace{\graphmarginexpapp}
-\hfill
-\subfigure[{\scriptsize \aminer with \fcita}]{\label{exp-aminer-ab-fcita}
-\includegraphics[scale=\graphscaleexpapp]{./exp/AMiner-para-fcita.eps}}
-%\quad\quad
-%\hspace{\graphmarginexpapp}
-\hfill
-\subfigure[{\scriptsize \magdata with \fcita}]{\label{exp-mag-ab-fcita}
-\includegraphics[scale=\graphscaleexpapp]{./exp/MAG-para-fcita.eps}}
+\caption{\small Accuracy evaluation using different components with \recom (rows 2--4) and \fcita (rows 5--7).}
+\label{tab-recom}
+%\begin{small}
+\vspace{-.5ex}
+\begin{tabular}{|c| c |c | c|}
+\hline
+{\bf Datasets} & {\bf C}\hspace{5ex}{\bf V}\hspace{5ex}{\bf A} & {\bf CV}\hspace{3ex}{\bf CA}\hspace{3ex}{\bf VA} & {\bf CVA} \\
+\hline \hline
+% \recom
+\aan & 0.752 \ 0.616 \ 0.649 & 0.809 \ 0.764 \ 0.747 & {\bf 0.810} \\
+\aminer & 0.735 \  0.581 \  0.640 & 0.784 \ 0.749 \ 0.729 & {\bf 0.785} \\
+\magdata & 0.635 \ 0.534 \ 0.553 & 0.697 \ 0.673 \  0.648 & {\bf 0.698} \\ \hline
+% \ficta
+\aan & 0.785 \ 0.557 \ 0.761 & 0.849 \ 0.866 \ 0.771 & {\bf 0.870} \\
+\aminer & 0.713 \  0.603 \  0.725 & 0.843 \ 0.847 \ 0.740 & {\bf 0.856} \\
+\magdata & 0.736 \ 0.628 \ 0.718 & 0.848 \ 0.857 \ 0.751 & {\bf 0.874} \\
+\hline
+\end{tabular}
+%\end{small}
 \end{center}
-\vspace{-1.5ex}
-\caption{\small Accuracy evaluation: varying aggregating parameters $\alpha$ and $\beta$}
-\label{exp-ab}
-\vspace{-2ex}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\vspace{-6ex}
+\end{table}
+%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[tb!]
-%\vspace{-2ex}
-\begin{center}
-\caption{\small Accuracy evaluation using different components with \recom (rows 2--4) and \fcita (rows 5--7).}
-\label{tab-recom}
-%\begin{small}
-%\vspace{-.5ex}
-\begin{tabular}{|c| c |c | c|}
-\hline
-{\bf Datasets} & {\bf C}\hspace{5ex}{\bf V}\hspace{5ex}{\bf A} & {\bf CV}\hspace{3ex}{\bf CA}\hspace{3ex}{\bf VA} & {\bf CVA} \\
-\hline \hline
-% \recom
-\aan & 0.752 \ 0.616 \ 0.649 & 0.809 \ 0.764 \ 0.747 & {\bf 0.810} \\
-\aminer & 0.735 \  0.581 \  0.640 & 0.784 \ 0.749 \ 0.729 & {\bf 0.785} \\
-\magdata & 0.635 \ 0.534 \ 0.553 & 0.697 \ 0.673 \  0.648 & {\bf 0.698} \\ \hline
-% \ficta
-\aan & 0.785 \ 0.557 \ 0.761 & 0.849 \ 0.866 \ 0.771 & {\bf 0.870} \\
-\aminer & 0.713 \  0.603 \  0.725 & 0.843 \ 0.847 \ 0.740 & {\bf 0.856} \\
-\magdata & 0.736 \ 0.628 \ 0.718 & 0.848 \ 0.857 \ 0.751 & {\bf 0.874} \\
-\hline
-\end{tabular}
-%\end{small}
-\end{center}
-\vspace{-4ex}
-\end{table}
-%%%%%%%%%%%%%%%%%%%
+\etitle{Exp-4.2}.
+%\stitle{Exp-4.2}.
+To evaluate the impacts of importance weighting factor $\lambda$, we varied $\lambda$ from 0 to 1.
+%while fixed $Y_s$ to default values, $T_i=+\infty$, $dif=1$ and $\sigma=-1.0$.
+The results of \PairAcc are reported in Figs.~\ref{exp-aan-lambda}, \ref{exp-aminer-lambda} and \ref{exp-mag-lambda}. Note that parameter $\lambda$ has no impacts on efficiency.
+%with both sets of ground-truth
+
+When varying $\lambda$, the \PairAcc of \ensemblerank first increases and then decreases on all datasets with both \fcita and \recom, except on \aminer with \recom.
+%\marked{The value of $\lambda$ for \ensemblerank to achieve the best effectiveness is (0.6, 0, 0.2) and (0.6, 0.4, 0.1) on (\aan, \aminer, \magdata) with \recom and \fcita, respectively.}
+This result indicates that combining prestige and popularity generally produces more robust results than using either of prestige and popularity.
+Indeed, with \recom and \fcita, the \PairAcc of combining prestige and popularity is (10.2\%, 10.7\%, 5.5\%) and (8.0\%, 8.7\%, 9.0\%) higher than using prestige alone, and is (1.2\%, -0.1\%, 1.0\%) and (1.0\%, 1.0\%, 0.3\%) higher than using popularity alone on (\aan, \aminer, \magdata), respectively.
+
+%The selection of $\lambda$ is influenced by ground-truth, such that the best $\lambda$ falls into $[xx,xx]$ and $[yy,yy]$ on \fcita and \recom, respectively.
+Moreover, equally weighting, \ie $\lambda=0.5$, is a good default setting when no query information is available in advance.
+%Indeed, the best obtained \PairAcc using (\fcita, \recom) is only (0.10\%, 0.38\%), (0.04\%, 2.59\%) and (0.06\%, 0.91\%)  higher than the \PairAcc of equally weighting on \aan, \aminer and \magdata, respectively.
 
@@
 \\%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace{-.5ex}
+\vspace{-1.5ex}
 \subfigure[{\scriptsize \aan with \fcita}]{\label{exp-aan-fcita-drank}
@@
 \vspace{-1.5ex}
-\caption{\small Impacts of TWPageRank on accuracy: varying importance weighting
-factor $\lambda$}
+\caption{\small Impacts of TWPageRank on accuracy: varying importance weighting factor $\lambda$}
 \label{exp-drank}
-\vspace{-2ex}
+\vspace{-3ex}
 \end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\etitle{Exp-4.2}.
-%\stitle{Exp-4.2}.
-To evaluate the impacts of importance weighting factor $\lambda$, we varied $\lambda$ from 0 to 1.
-%while fixed $Y_s$ to default values, $T_i=+\infty$, $dif=1$ and $\sigma=-1.0$.
-The results of \PairAcc are reported in Figs.~\ref{exp-aan-lambda}, \ref{exp-aminer-lambda} and \ref{exp-mag-lambda}. Note that parameter $\lambda$ has no impacts on efficiency.
-%with both sets of ground-truth
-
-When varying $\lambda$, the \PairAcc of \ensemblerank first increases and then decreases on all datasets with both \fcita and \recom, except on \aminer with \recom.
-%\marked{The value of $\lambda$ for \ensemblerank to achieve the best effectiveness is (0.6, 0, 0.2) and (0.6, 0.4, 0.1) on (\aan, \aminer, \magdata) with \recom and \fcita, respectively.}
-This result indicates that combining prestige and popularity generally produces more robust results than using either of prestige and popularity.
-Indeed, with \recom and \fcita, the \PairAcc of combining prestige and popularity is (10.2\%, 10.7\%, 5.5\%) and (8.0\%, 8.7\%, 9.0\%) higher than using prestige alone, and is (1.2\%, -0.1\%, 1.0\%) and (1.0\%, 1.0\%, 0.3\%) higher than using popularity alone on (\aan, \aminer, \magdata), respectively.
-
-%The selection of $\lambda$ is influenced by ground-truth, such that the best $\lambda$ falls into $[xx,xx]$ and $[yy,yy]$ on \fcita and \recom, respectively.
-Moreover, equally weighting, \ie $\lambda=0.5$, is a good default setting when no query information is available in advance.
-%Indeed, the best obtained \PairAcc using (\fcita, \recom) is only (0.10\%, 0.38\%), (0.04\%, 2.59\%) and (0.06\%, 0.91\%)  higher than the \PairAcc of equally weighting on \aan, \aminer and \magdata, respectively.
 
@@
 
-When varying $\lambda$, the \PairAcc of \ensemblerank is better than the one of \drank in most cases, which shows the superiority of the TWPageRank than exploiting exponentially decayed weights directly without introducing the peak time.
+When varying $\lambda$, the \PairAcc of \ensemblerank is better than the one of \drank in most cases, which shows the superiority of the TWPageRank than directly decaying without introducing the peak time.
 The \PairAcc difference of these two algorithms is higher with \recom than with \fcita, since the two algorithms are just using citation information to predict past and future citations with \fcita.

### 2017-12-27 icde/revision/sec-incAlg.tex

--- 2017-09-30 icde/sec-incAlg.tex
@@
 \end{small}
-\noindent
-where $Pop_c(v)$ (resp. $Pop_c^+(v)$) is the popularity of node $v$ on $G^c$ (resp. $G^{c,+}$), and
+%
+\noindent where $Pop_c(v)$ (resp. $Pop_c^+(v)$) is the popularity of node $v$ on $G^c$ (resp. $G^{c,+}$), and
 $T_0$ (resp. $T^+_0$) is the current time on $G^c$ (resp. $G^{c,+}$).
@@
 {\sl Output:\/} TWPageRank vector $PR^+$ of the updated graph $G^+$. \\
-\\
 \bcc \hspace{1.5ex}\=  $G_C'$ := the block-wise graph of $G_C$; \\
@@
 
-\begin{figure}[tb!]
-\centering
-\includegraphics[scale=0.7]{fig/General_framework_peak.eps}
-\vspace{-1ex}
-\caption{\small An example of incremental TWPageRank computation}
-\label{fig-inc-division}
-\vspace{-3ex}
-\end{figure}
-
 \begin{example} \label{eg-layer-dag}
@@
 \end{proofSketch}
+}
+
+\begin{figure}[tb!]
+\centering
+\includegraphics[scale=0.7]{fig/General_framework_peak.eps}
+\vspace{-1ex}
+\caption{\small An example of incremental TWPageRank computation}
+\label{fig-inc-division}
+\vspace{-3ex}
+\end{figure}
 
@@
 
+\eat{  %% time & space complexity
+\stitle{Time \& space complexity analyses of the incremental algorithm}.
+By the analyses above, the time complexity of \incensemble is the same as \batensemble, except that \incensemble saves $O(|E^c_A\cup E^c_{AB}|)$ and $O(|E^v_A\cup E^v_{AB}|)$ time on the updated citation and venue graphs.
+And its space complexity is also the same as \batensemble, except that it uses $(|V^c\cup \Delta V^c|+|V^v\cup\Delta V^v|)$ extra space to store the affected/unaffected areas and $(|E^c\cup \Delta E^c|+|E^v\cup \Delta E^v|)$ extra space to store the original edge weights before update.
+} %% eat
+
+\stitle{Time complexity analysis of the incremental algorithm}.
+By the analyses above, the time complexity of \incensemble is the same as \batensemble, except that \incensemble saves $O(|E^c_A\cup E^c_{AB}|)$ and $O(|E^v_A\cup E^v_{AB}|)$ time on the updated citation and venue graphs at an extra space cost for the affected/unaffected areas and the original edge weights.
+
+Despite of its similar time complexity to \batensemble, algorithm \incensemble typically achieves a substantial efficiency improvement over \batensemble, according to our statistics of affected/unaffected areas given a yearly update, \ie articles of 2011 on \aan and 2015 on \aminer and \magdata, respectively, shown in Table~II.
+%
+(a) It saves $O(|V^c|+|E^c|)$ and $O(|V^v|+|E^v|)$ time when maintaining \sccs and the topological order based on $\Delta^c$ and $\Delta^v$ only, where ($|V^c|$, $|E^c|$, $|V^v|$, $|E^v|$) are more than (92\%, 89\%, 93\%, 89\%) of ($|V^{c,+}|$, $|E^{c,+}|$, $|V^{v,+}|$, $|E^{v,+}|$) on all tested graphs;
+(b) It saves $O(|E^c_A \cup E^c_{AB}|)$ time when updating scores on $V^c$, where edges in $E^c_A\cup E^c_{AB}$ account for more than 28\% of total edges;
+(c) It saves $O(|E^c|)$ time when computing popularity of articles, which accounts for more than 89\% of $|E^{c,+}|$;
+And, finally, (d) It is likely to compute TWPageRank scores on $V^c_B$ and $V^v_B$ with less iterations.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{center}
-\caption{\small Statistics of affected/unaffected areas given a yearly update, \ie articles of 2011 on \aan and 2015 on \aminer and \magdata, respectively.}
+\caption{\small Statistics of affected/unaffected areas}
 \label{tab-inc}
@@
 %%%%%%%%%%%%%%%%%%%
-
-\stitle{Time \& space complexity analyses of the incremental algorithm}.
-By the analyses above, the time complexity of \incensemble is the same as \batensemble, except that \incensemble saves $O(|E^c_A\cup E^c_{AB}|)$ and $O(|E^v_A\cup E^v_{AB}|)$ time on the updated citation and venue graphs.
-And its space complexity is also the same as \batensemble, except that it uses $(|V^c\cup \Delta V^c|+|V^v\cup\Delta V^v|)$ extra space to store the affected/unaffected areas and $(|E^c\cup \Delta E^c|+|E^v\cup \Delta E^v|)$ extra space to store the original edge weights before update.
-
-Despite of its similar time complexity to \batensemble, algorithm \incensemble typically achieves a substantial efficiency improvement over \batensemble, according to our statistics of affected/unaffected areas shown in Table~II.
-%
-(a) It saves $O(|V^c|+|E^c|)$ and $O(|V^v|+|E^v|)$ time when maintaining \sccs and the topological order based on $\Delta^c$ and $\Delta^v$ only, where ($|V^c|$, $|E^c|$, $|V^v|$, $|E^v|$) are more than (92\%, 89\%, 93\%, 89\%) of ($|V^{c,+}|$, $|E^{c,+}|$, $|V^{v,+}|$, $|E^{v,+}|$) on all tested graphs;
-(b) It saves $O(|E^c_A \cup E^c_{AB}|)$ time when updating scores on $V^c$, where edges in $E^c_A\cup E^c_{AB}$ account for more than 28\% of total edges;
-(c) It saves $O(|E^c|)$ time when computing popularity of articles, which accounts for more than 89\% of $|E^{c,+}|$;
-And, finally, (d) It is likely to compute TWPageRank scores on $V^c_B$ and $V^v_B$ with less iterations.

### 2017-12-27 icde/revision/sec-intro.tex

@@
 Query independent ranking of scholarly articles has drawn significant attentions from both academia~\cite{Garfield471,Hirsch15112005,Liang16AAAI,Jiang12-MRank,Waltman2014,Wang16TIST,Ng11KDD,Li08TSRanking,
-Wang13AAAI,sayyadi09,WalkerXKM07,TanLMGSW16} and industry~\cite{g-scholar,Sinha15:MAG,sem-scholar}.
+Wang13AAAI,sayyadi09,WalkerXKM07} and industry~\cite{g-scholar,Sinha15:MAG,sem-scholar}.
 Generally speaking, a ranking is {\em a function that assigns each item a numerical score}.
@@
 Such a ranking plays a key role in literature recommendation systems, especially in the {\em cold start} scenario.
+%,TanLMGSW16
 
@@
 %
-To our knowledge, the Time-Weighted PageRank is among the first to \markedb{use citation statistics to incorporate the diverse citation patterns of individual articles for scholarly article ranking.}
+To our knowledge, the Time-Weighted PageRank is among the first to incorporate the diverse citation patterns of individual articles \markedb{and exploit citation statistics for scholarly article ranking.}
 %and the long-term bias caused by the dynamic nature of data
 
-\sstab(2)  We then develop  a batch algorithm for scholarly article ranking (Section \ref{sec-alg}), in which we propose a block-wise method for Time-Weighted PageRank \markedb{and show its advantage in terms of an efficiency analysis based on citation characteristics of scholarly articles.}
+\sstab(2)  We then develop  a batch algorithm for scholarly article ranking (Section \ref{sec-alg}), in which we propose a block-wise method for Time-Weighted PageRank \markedb{and show its efficiency advantage in terms of an analysis of the citation characteristics and a specific structural property of scholarly graphs.}
 %in which we propose a block-wise method for Time-Weighted PageRank in terms of an analysis of the citation characteristics of scholarly articles.
@@
 
-All the detailed proofs can be found in \cite{SARank-full}.
+%All the detailed proofs can be found in \cite{SARank-full}.
+All the proofs can be found in \cite{SARank-full}.
 

### 2017-12-27 icde/revision/sec-model.tex

@@
 Though the number of citations is an indicator of the impact of an article~\cite{WangSB13,Garfield471}, its impact is time-dependent and is not simply in the form of exponential decay.
-In general, {\em the impact of an article tends to decay with time after the peak time only}.
+% In general,
+\markedb{Inspired by these citation patterns,} {\em the impact of an article tends to decay with time after the peak time only}~\cite{WangSB13}.
 That is, the impacts of articles directly decay with time only for those in {\em MonDec}, and decay with time after the peak time for those in {\em PeakInit}, {\em PeakLate} and {\em PeakMul}, and do not decay for ones in {\em MonIncr} (which is rare).
@@
 Note that the time decaying factor $\sigma$ is introduced to provide flexibility for TWPageRank in various applications, and its value is typically within a small interval, \eg $[-2,0]$, such that $w(u,v)$ does not decay when $\sigma=0$ and already decays more than a half per year when $\sigma=-1$.
-For the sake of completeness, we further set $w(u,v)$ to $0$ if there does not exist an edge from $u$ to $v$ in the graph.
+%For the sake of completeness, we further set $w(u,v)$ to $0$ if there does not exist an edge from $u$ to $v$ in the graph.
 
@@
 %\includegraphics[scale=0.15]{fig/framework.eps}
-\includegraphics[scale=0.175]{fig/framework-lite-2.eps}
+\includegraphics[scale=0.15]{fig/framework-lite-2.eps}
 \vspace{-1ex}
@@
 %However, the resulting author citation graph to compute the prestige is typically too large to handle.
-\markedb{To do this, an author citation graph needs to be constructed such that (a) a node represents an author, and (b) a direct edge $(s,t)$ denotes that there exist articles of author $s$ citing articles of author $t$.
+\markedb{To do this, an {\em author citation graph} needs to be constructed such that (a) a node represents an author, and (b) a direct edge $(s,t)$ denotes that there exist articles of author $s$ citing articles of author $t$.
 It is not hard to image that the number of edges in the author citation graph is much larger than the number in the citation graph, which reaches to 7.12  billion on the largest \magdata (\ie the memory cost of storage only is 57GB).
@@
 Let the scaled importance scores of article $v$ be $R_c(v)$, $R_v(v)$, and $R_a(v)$ from the citation, venue and author components, respectively.
-
-The final ranking score $R(v)$ of an article $v$ is aggregated as follows:
+%
+The final ranking score $R(v)$ is aggregated as follows:
 

### 2017-12-27 icde/revision/sec-related.tex

@@
 %
-\markedb{In this work, we study dynamic scholarly article ranking in the general case and develop our incremental algorithm in terms of the citation characteristics, which has never been exploited before.}
+\markedb{In this work, we study dynamic scholarly article ranking in the general case and develop our incremental algorithm based on the citation characteristics, which has never been exploited before.}
 %Different from previous work, we study scholarly article ranking in a dynamic environment in terms of the citation characteristics of scholarly articles, which has never been exploited before.

### 2017-12-27 icde/revision/Response.tex

@@
 
-We have explained our claim better.
+We have explained our claim better (Time-Weighted PageRank, right column, page 2).
 The observation is inspired by the five distinct citation patterns.
@@
 The PeakMul pattern is originally defined in [18]:  the height of a peak should be at least 75\% of the maximum peak height, and two consecutive peaks should be separated by more than two years.
-In our work, we unify the five patterns and only use the latest peak time which we have discussed in Section II-A (para 1, left column, page 3).
+In our work, we unify the five patterns and only use the latest peak time which we have discussed in Section II-A (para 2, left column, page 3).
 
@@
 
-Yes. This work does NOT assume the DAG structure of scholar graphs, where cycles are allowed to exist (Observation, left column, page 5).
-Compared to general web graphs, the computation of TWPageRank on scholarly graphs is more efficient as a result of the temporal order of citations, which gives less SCC edge ratio as shown in Table I (page 5).
-In addition, we further design incremental algorithms based on the temporal order, which also makes the computation more efficient.
+This work does NOT assume the DAG structure of scholarly graphs, where cycles are allowed to exist (Observation, left column, page 5).
+Compared to general Web graphs, the computation of TWPageRank on scholarly graphs is more efficient as a result of the {\em temporal order of citations}, which gives less SCC edge ratio as shown in Table I (page 5).
+In addition, we further design incremental algorithms based on the temporal order of citations, which also makes the computation more efficient.
 %We have highlighted the statements about temporal order in the revised version.
 
-\textbf{[R1D6]} \emph{MAG is used before description in Page 1. Some cells in Table 1 have two values, while others have one value. The meaning should be given explicitly}
+\textbf{[R1D6]} \emph{MAG is used before description in Page 1. Some cells in Table 1 have two values, while others have one value. The meaning should be given explicitly.}
 
@@
 The property of scholarly data makes the incremental computation of (time-weighted) PageRank quite different from those on general graphs, which, to our knowledge, has not gained enough attentions.
-Furthermore, the only existing dynamic scholarly article ranking solution [21] is based on a impractical assumption that there is no citations between articles of the same years.
+Furthermore, the only existing dynamic scholarly article ranking solution [21] is based on an impractical assumption that there is no citations between articles of the same years.
 %
@@
 
-We have removed the sentence and explained more details about the statement.
+We have removed the sentence and explained more details about the statement (Author Component, left column, page 3).
 Moreover specifically, we add the details of the generation of the author citation graph.
-The generated graph has 7.12 billion edges on the largest \magdata (\ie the memory cost of storage only is 57GB), which makes it computationally expensive to compute prestige of authors  with TWPageRank on that graph (Author Component, left column, page 3).
+The generated graph has 7.12 billion edges on the largest \magdata (\ie the memory cost of storage only is 57GB), which makes it computationally expensive to compute prestige of authors  with TWPageRank on that graph.
 We hence turn to the alternative light-weight method to achieve the goal.

### 2017-12-27 icde/revision/sec-model.tex

@@
 Recall that articles are categorized  into six citation patterns featured by the time when the articles reach their citation peaks~\cite{Chakraborty15}: (a) {\em PeakInit} with a single citation-count peak in the first five years (but not the first year) after publication, (b) {\em PeakMul} with distinct multiple peaks, (c) {\em PeakLate} with a single peak in at least five years   (but not the last year) after publication, (d) {\em MonDec} with monotonically decreasing citations, (e) {\em MonIncr} with monotonically increasing citations, and, (f) {\em Other} for articles whose average numbers of citations per year are less than 1.
-Though the number of citations is an indicator of the impact of an article~\cite{WangSB13,Garfield471}, its impact is time-dependent and is not simply in the form of exponential decay.
-% In general,
-\markedb{Inspired by these citation patterns,} {\em the impact of an article tends to decay with time after the peak time only}~\cite{WangSB13}.
+Though the number of citations is an indicator of the impact of an article~\cite{WangSB13,Garfield471}, its impact is time-dependent but not simply in the form of exponential decay, \markedb{which only conforms with the case of {\em MonDec}}.
+%
+\markedb{Inspired by these distinct citation patterns, we claims that} {\em the impact of an article tends to decay with time after the peak time only}~\cite{WangSB13}.
 That is, the impacts of articles directly decay with time only for those in {\em MonDec}, and decay with time after the peak time for those in {\em PeakInit}, {\em PeakLate} and {\em PeakMul}, and do not decay for ones in {\em MonIncr} (which is rare).

### 2017-12-28 icde/revision/sec-alg.tex

@@
 
-Our batch algorithm \batensemble  combines the importance scores computed by the citation, venue and author components with Eq.~(\ref{eq-ensemble}).
-It takes as input academic graph data $D$ and an iteration threshold $\epsilon$ and returns the scholarly article ranking of $D$.
-It first constructs the citation and venue graphs $G^c(V^c,E^c)$ and $G^v(V^v,E^v)$.
+Our batch algorithm \batensemble  combines the importance scores computed by the citation, venue and author components.
+It takes as input academic graph data $D$ and an iteration threshold $\epsilon$ for TWPageRank and returns the scholarly article ranking.
+It first constructs the citation graph $G^c(V^c,E^c)$ and venue graph $G^v(V^v,E^v)$.
 Then it computes the prestige and popularity of citation, venue and author components.
@@
 For popularity computation, it is easy to see that
-(a) the popularity of articles can be computed by scanning through all citations once and adding the freshness of citations to their corresponding articles, by Eq.~(\ref{eq-pop}), and (b) the popularity of venues in a specific year or authors is computed by averaging the popularity of the articles published in the venues or by the authors.
+(a) the popularity of articles can be computed by scanning through all citations once and adding the freshness of citations to their corresponding articles by Eq.~(\ref{eq-pop}), and (b) the popularity of venues in a specific year or authors is computed by averaging the popularity of the articles published in the venues or by the authors.
 That is, the popularity computation can be done by scanning through all citations once.
@@
 %\stitle{Prestige computation}. As the prestige of authors is defined as the average prestige of their published articles,
-For prestige computation, as the one of authors is defined as the average prestige of their published articles,
+For prestige computation, (a) as the one of authors is defined as the average prestige of their published articles,
 it suffices to scan through all author-article  relationships for computing the prestige of authors.
-The prestige of  articles and venues in a specific year is computed by TWPageRank on citation graphs and venue graphs, which is usually computed in an iterative manner~\cite{Brin98:PageRank} and is the most expensive computation.
+(b) The prestige of  articles and venues in a specific year is computed by TWPageRank on citation graphs and venue graphs, which is usually computed in an iterative manner~\cite{Brin98:PageRank} and is the most expensive computation.
 Hence, the key of the computation of our approach is a good solution for computing TWPageRank.
@@
 
-The main result here is to speed up computing TWPageRank by exploiting the {\em temporal order} of scholarly article citations.
+The main result of this section is to speed up computing TWPageRank on scholarly data.
+%by exploiting the {\em temporal order} of scholarly article citations.
 
@@
 
-The main idea of the block-wise PageRank computation is that each strongly connected component (\scc) of the input graph is treated as a block, and blocks are processed one by one following the {\em topological order} of the block-wise graph, \ie each node represents a block of the original graph~\cite{Berkhin05}.
+The core idea of the block-wise PageRank computation is that each strongly connected component (\scc) of the input graph is treated as a block, and blocks are processed one by one following the {\em topological order} of the block-wise graph, \ie each node represents a block of the original graph~\cite{Berkhin05}.
 We next show Claim~\ref{thm-prestige} by introducing and analyzing such a block-wise computation method.
@@
 
-\stitle{Block-wise algorithm~\twprscc}.  It takes as input a citation or venue graph $G$ and an iteration threshold $\epsilon$, and returns the TWPageRank vector of $G$.
-To process an \scc instead of the entire graph, the edges of the citation or venue graph $G(V, E)$ are partitioned into the sets $E_i$ and $E_a$ of edges inside and across \sccs  such that $E_i\cap E_a = \emptyset$ and $E = E_i \cup E_a$.
-The update rule in Eq.~(\ref{eq-twpr-update})  is revised accordingly to treat $E_i$ and $E_a$ separately as follows.
+\stitle{Block-wise algorithm~\twprscc}.  It takes as input a citation or venue graph $G(V, E)$ and an iteration threshold $\epsilon$, and returns the TWPageRank vector of $PR$ of $G$.
+%To process an \scc instead of the entire graph, 
+To update scores of nodes in an \scc at a time, the edges of $G$ are partitioned into: (a) the set $E_i$ of edges inside \sccs and (b) the set $E_a$ of edges across \sccs  such that $E_i\cap E_a = \emptyset$ and $E = E_i \cup E_a$.
+The update rule in Eq.~(\ref{eq-twpr-update})  is revised accordingly to separate $E$ into $E_i$ and $E_a$  as follows.
 
@@
 \noindent
-It first computes the block-wise graph $G'$ by treating \sccs in $G$ as single nodes, and then derives a topological order $O$ of nodes in $G'$.
+It first computes the block-wise graph $G'$ by treating \sccs in $G$ as single nodes, and derives a topological order $O$ of nodes in $G'$.
 It then processes each \scc in the topological order  $O$ with Eq.~(\ref{eq-prscc}).
 Finally, it returns the TWPageRank vector.
-When processing an \scc, it iteratively updates the TWPageRank scores of the nodes in the \scc, and the iteration continues until the sum of TWPageRank score changes is less than $\epsilon\cdot\frac{|scc|}{|V|}$, where $|scc|$ is the number of nodes in the \scc.
+When processing an \scc, it iteratively updates the TWPageRank scores of the nodes in the \scc, and the iteration continues until the sum changes of of TWPageRank scores is less than $\epsilon |scc|/|V|$, where $|scc|$ is the number of nodes in the \scc.
 Note that there must exist a topological order $O$, as the block-wise graph is a directed acyclic graph~\cite{CormenLRS01}.
@@
 
-\stitle{Analysis of the block-wise algorithm}.
+\vspace{-1ex}
+\stitle{Analysis of algorithm \twprscc}.
 While similar block-wise algorithms were originally proposed for Web graphs~\cite{Berkhin05}, we next show that they are even better for the TWPageRank computation associated with scholarly data.
 %
-The block-wise graph and its topological order can be done in $O(|V|+|E|)$ time~\cite{CormenLRS01}, and updating TWPageRank scores takes $O(|V|+|E_a|+t|E_i|)$ time as the edges in $E_a$ are only scanned once.
+Given inpute graph $G(V, E)$, the block-wise graph and its topological order can be computed in $O(|V|+|E|)$ time~\cite{CormenLRS01}, and the edges in $E_a$ are only scanned once when updating TWPageRank scores.
 From these, we have the following.
@@
 \label{prop-venue-time-complexity}
-Given a citation graph or venue graph $G(V, E)$, algorithm \twprscc runs in  $O(|V|+|E_a|+t|E_i|)$ time, where $t$ is  the maximum number of iterations among all \sccs.
+Given a citation or venue graph $G(V, E)$, algorithm \twprscc runs in  $O(|V|+|E_a|+t|E_i|)$ time, where $t$ is  the maximum number of iterations among all \sccs.
 \end{lemma}
@@
 
-\stitle{Observation.} It is well-known that article citations obey a natural {\em temporal order}, \ie an article only cites those published earlier, and it is really rare for the mutual citations between two articles published in the same time.
-That is, $|E_i|$ is essentially small for the citation graphs of scholarly articles.
+\stitle{Observation.} It is well-known that citations obey a natural {\em temporal order}, \ie an article only cites those published earlier, and it is really rare for the mutual citations between two articles published in the same time.
+That is, {\em $|E_i|$ is essentially small for the citation and venue graphs of scholarly data}.
 
-To verify this observation, we also collect the statistics of citation graphs, venue graphs and Web graphs and illustrate in Table~\ref{tab-batch}, where Web graphs are extracted from berkely.edu and stanford.edu domains in 2002 and from the Google programming contest in 2002, respectively~\cite{LeskovecLDM09}, \markedb{and numbers $x/y$ in the first three rows are the corresponding statistics on citation/venue graphs.}
-Due to the existence of the ``bow tie'' structure and the giant \scc in Web graphs~\cite{BroderKMRRSTW00}, the edge ratios $|E_i|/|E|$ are greater than 59\%.
+To verify this observation, we also collect the statistics of citation/venue graphs and Web graphs illustrated in Table~\ref{tab-batch}, where Web graphs are extracted from berkely.edu and stanford.edu domains in 2002 and from the Google programming contest in 2002, respectively~\cite{LeskovecLDM09}, \markedb{and numbers $x/y$ in the first three rows are the corresponding statistics on citation/venue graphs.}
+Due to the existence of the ``bow tie'' structure and the giant \scc in Web graphs~\cite{BroderKMRRSTW00}, the \scc edge ratios $|E_i|/|E|$ are greater than 59\%.
 In contrast, the \sccs in citation and venue graphs are quite small as a result of the {\em temporal order of citations}, and $|E_i|/|E|$ is less than 3\% for all tested citation and venue graphs.
@@
 This specific structure in scholarly data has been long ignored in the past literature, which indeed has a positive impact on computations.
-Taking $t=100$ for example, algorithm \twprscc needs to scan $3|E|$ and $4|E|$ edges on citation and venue graphs, respectively, but over $59|E|$ edges on Web graphs.
+Taking $t=100$ for example, algorithm \twprscc only needs to scan $4|E|$ edges on citation and venue graphs, but over $59|E|$ edges on Web graphs.
 
@@
 %
-By Lemma~\ref{prop-venue-time-complexity} and the analyses in Section~\ref{subsec-bat-alg}, one can verify that algorithm \batensemble takes $O(|V^c|+|V^v|+|E^c_a|+|E^v_a|+t|E^c_i|+t|E^v_i|+|PA|)$ time, where $|PA|$ is the total number of author-article relationships.
+By Lemma~\ref{prop-venue-time-complexity} and the analyses in Section~\ref{subsec-bat-alg}, one can verify that algorithm \batensemble takes $O(|V^c|+|E^c_a|+t|E^c_i|+|V^v|+|E^v_a|+t|E^v_i|+|PA|)$ time, where $|PA|$ is the number of author-article relationships.
 %

### 2017-12-28 icde/revision/sec-incAlg.tex

@@
 
-Scholarly articles are dynamic and continuously growing, and it is impractical to recompute ranking from scratch once they get updated.
+Scholarly data is dynamic and continuously growing, and it is impractical to recompute ranking from scratch once it gets updated.
 In this section, we present an incremental algorithm for our ranking model \ensemblerank.
@@
 
-Our incremental algorithm \incensemble incrementally computes the popularity and prestige of scholarly articles.
+Our incremental algorithm \incensemble incrementally computes the popularity and prestige of associate entities.
 We consider that an update $\Delta$ = $\Delta V\cup\Delta E$ is added to a (citation or venue) graph $G(V, E)$,
 and the resulting graph is $G^+(V\cup\Delta V, E\cup\Delta E)$, where
-$\Delta V$ is a set of nodes with $\Delta V\cap V = \emptyset$, and $\Delta E$ is a set of directed edges on $\Delta V$ and from $\Delta V$ to $V$ only, as article citation relationships obey a natural temporal order, \ie an article only cites those published earlier, and it is rare for the mutual citations between two articles published in the same time.
+$\Delta V$ is a set of nodes with $\Delta V\cap V = \emptyset$, and $\Delta E$ is a set of directed edges on $\Delta V$ and from $\Delta V$ to $V$ only, as citation relationships obey a natural temporal order, \ie an article only cites those published earlier, and it is rare for the mutual citations between two articles published in the same time.
 
 \stitle{Incremental popularity computation}.
-The popularity of venues and authors is computed along the same lines as their batch counterparts of algorithm \batensemble,
-as almost all venues and authors are affected  by the definitions of the popularity of venues and authors.
-
-As the popularity of articles is defined as the sum of the freshness of all their citations, it is convenient to maintain in a dynamic scenario.
+As the popularity of articles is defined as the sum of the freshness of their citations, it is convenient to maintain dynamically.
 Consider an updated citation graph $G^{c,+}(V^c\cup\Delta V^c, E^c\cup\Delta E^c)$ of $G^c(V^c, E^c)$, and the updated popularity $Pop_{c}^+(v)$ can be computed as:
@@
 %
-\noindent where $Pop_c(v)$ (resp. $Pop_c^+(v)$) is the popularity of node $v$ on $G^c$ (resp. $G^{c,+}$), and
-$T_0$ (resp. $T^+_0$) is the current time on $G^c$ (resp. $G^{c,+}$).
+\noindent where $Pop^+_c(v)$ (resp. $Pop_c(v)$) is the popularity of node $v$ on $G^{c,+}$ (resp. $G^c$), and
+$T^+_0$ (resp. $T_0$) is the current time on $G^{c,+}$ (resp. $G^c$).
 %
-By Eq.~(\ref{eq-inc-pop}), it is easy to see that it takes $O($ $|V^c|+|\Delta V^c|+|\Delta E^c|)$ time to update the popularity.
+By Eq.~(\ref{eq-inc-pop}), it is easy to see that updating the popularity of articles takes $O($ $|V^c|+|\Delta V^c|+|\Delta E^c|)$ time.
 %This further shows that Eq.~(\ref{eq-inc-pop}) is a desired solution for popularity maintenance.
+
+The popularity of venues and authors is computed along the same lines as their batch counterparts of algorithm \batensemble,
+as almost all venues and authors are affected  by the definitions of the popularity of venues and authors.
 
@@
 \stitle{Auxiliary data structure maintenance}.
-Two auxiliary data structures in the batch algorithm~\twprscc need to be maintained: (a) the block-wise graph and  a mapping that, given a node of graph $G$, returns the index of the \scc to which it belongs, and (b) the topological order of the nodes in the block-wise graph.
+Two auxiliary data structures in the batch algorithm~\twprscc need to be maintained: (a) the block-wise graph and  a mapping that, given a node of the citation or venue graph, returns the index of the \scc to which it belongs, and (b) the topological order of the nodes in the block-wise graph.
 %
@@
 %%% affected/unaffected division
-\stitle{Analyses of affected and unaffected areas}.
+\vspace{-1ex}
+\stitle{Analysis of affected and unaffected areas}.
 The TWPageRank vector $PR$ of graph $G$ is mainly affected in two ways.
@@
 %\begin{small}
-%\vspace{-.5ex}
+\vspace{-.5ex}
 \eat{

### 2017-12-28 icde/revision/sec-model.tex

@@
 %However, the resulting author citation graph to compute the prestige is typically too large to handle.
-\markedb{To do this, an {\em author citation graph} needs to be constructed such that (a) a node represents an author, and (b) a direct edge $(s,t)$ denotes that there exist articles of author $s$ citing articles of author $t$.
-It is not hard to image that the number of edges in the author citation graph is much larger than the number in the citation graph, which reaches to 7.12  billion on the largest \magdata (\ie the memory cost of storage only is 57GB).
+\markedb{To do this, an {\em author graph} needs to be constructed such that (a) a node represents an author, and (b) a direct edge $(s,t)$ denotes that there exist articles of author $s$ citing articles of author $t$.
+It is not hard to image that the number of edges in the author graph is much larger than the number in the citation graph, which reaches to 7.12  billion on the largest \magdata (\ie the memory cost of storage only is 57GB).
 It is computationally expensive to compute prestige of authors with TWPageRank on that graph.}

### 2017-12-28 icde/revision/sec-incAlg.tex

@@
 %
-We then have $G_C$ = $G^+[\Delta V]$, $\Delta E$ = $E_C\cup E_{CB}$, $V$ = $V_A\cup V_B$ and $E$ = $E_A\cup E_B\cup E_{AB}$.
+We then have $G^+[\Delta V]$ = $G_C$, $\Delta E$ = $E_C\cup E_{CB}$, $V$ = $V_A\cup V_B$ and $E$ = $E_A\cup E_B\cup E_{AB}$.
 
@@
 
-Observe that (a) a topological order of $G'_C$ can be computed in $O(|V_C|+|E_C|+|E_{CB}|)$ time,
-(b) updating the TWPageRank scores of nodes in subgraphs $G_B$ and $G_C$ costs $O(|V_B\cup V_C|+|E_{B,a}\cup E_{C,a}\cup E_{CB}|)+t^+|E_{B,i}\cup E_{C,i}|)$ time, and, finally, (c) updating the scores of nodes in $G_A$ costs $O(|V_A|)$ time.
+Observe that (a) a topological order of the block-wise graph of $G_C$ can be computed in $O(|\Delta V|+|\Delta E|)$ time,
+(b) updating the TWPageRank scores of nodes in $V_B$ and $V_C$ costs $O(|V_B\cup V_C|+|E_{B,a}\cup E_{C,a}\cup E_{CB}|)+t^+|E_{B,i}\cup E_{C,i}|)$ time, where $t^+$ is  the maximum number of iterations among all \sccs in $G_B$ and $G_C$, and, finally, (c) updating the scores of nodes in $V_A$ costs $O(|V_A|)$ time.
 From these, the following holds.
@@
 \begin{prop} \label{lemma-inc-citation-comp}
-Given an update $\Delta$ = $\Delta V\cup\Delta E$ of citation or venue graph $G(V,E)$, the TWPageRank vector of $G$ and the topological order of $G'$, algorithm \inctwprscc runs in $O(|V\cup \Delta V| + |E_B\cup E_C\cup E_{CB}| + t^+|E_{B,i}\cup E_{C,i}|)$ time.
+Given an update $\Delta$ = $\Delta V\cup\Delta E$ of citation or venue graph $G(V,E)$, the TWPageRank vector of $G$ and the topological order of $G'$, algorithm \inctwprscc runs in $O(|V\cup \Delta V| + |E_{B,a}\cup \Delta E| + t^+|E_{B,i}\cup E_{C,i}|)$ time.
 \end{prop}
@@
 Note that  (a) algorithm \inctwprscc computes \sccs and derives the topological order based  on $\Delta$ only, instead of $G^{+}$,
-(b) it skips edges in $E_A\cup E_{AB}$ when updating the scores of nodes in $G_A$ and $G_B$, and
-(c) the number $t^+$ is very likely smaller than the number $t$ of \twprscc when updating scores of nodes in $G_B$.
+(b) it skips edges in $E_A\cup E_{AB}$ when updating the scores of nodes in $V_A$ and $V_B$, and
+(c) the number $t^+$ is very likely smaller than the number $t$ of \twprscc when updating scores of nodes in $V_B$.
 %
@@
 \stitle{Time complexity analysis of the incremental algorithm}.
-By the analyses above, the time complexity of \incensemble is the same as \batensemble, except that \incensemble saves $O(|E^c_A\cup E^c_{AB}|)$ and $O(|E^v_A\cup E^v_{AB}|)$ time on the updated citation and venue graphs at an extra space cost for the affected/unaffected areas and the original edge weights.
+By the analyses above, the time complexity of \incensemble is the same as \batensemble, except that \incensemble saves $O(|E^c_A\cup E^c_{AB}|)$ and $O(|E^v_A\cup E^v_{AB}|)$ time when computing TWPageRank  on the updated citation and venue graphs at an extra space cost for the affected/unaffected division and the copy of original edge weights.
 
@@
 %
-(a) It saves $O(|V^c|+|E^c|)$ and $O(|V^v|+|E^v|)$ time when maintaining \sccs and the topological order based on $\Delta^c$ and $\Delta^v$ only, where ($|V^c|$, $|E^c|$, $|V^v|$, $|E^v|$) are more than (92\%, 89\%, 93\%, 89\%) of ($|V^{c,+}|$, $|E^{c,+}|$, $|V^{v,+}|$, $|E^{v,+}|$) on all tested graphs;
-(b) It saves $O(|E^c_A \cup E^c_{AB}|)$ time when updating scores on $V^c$, where edges in $E^c_A\cup E^c_{AB}$ account for more than 28\% of total edges;
-(c) It saves $O(|E^c|)$ time when computing popularity of articles, which accounts for more than 89\% of $|E^{c,+}|$;
+(a) It saves $O(|V^c|+|E^c|)$ and $O(|V^v|+|E^v|)$ time when maintaining \sccs and the topological order based on the update data only, 
+%where ($|V^c|$, $|E^c|$, $|V^v|$, $|E^v|$) are more than (92\%, 89\%, 93\%, 89\%) of ($|V^{c,+}|$, $|E^{c,+}|$, $|V^{v,+}|$, $|E^{v,+}|$) on all tested graphs;
+where ($|V|$, $|E|$) are more than (92\%, 89\%) of ($|V^{+}|$, $|E^{+}|$) on all tested citation and venue graphs;
+(b) It saves $O(|E^c_A \cup E^c_{AB}|)$ time when updating scores on $V^c$, where edges in $E^c_A\cup E^c_{AB}$ account for more than 28\% of total;
+(c) It saves $O(|E^c|)$ time when computing popularity of articles, which accounts for more than 89\% of total;
 And, finally, (d) It is likely to compute TWPageRank scores on $V^c_B$ and $V^v_B$ with less iterations.
@@
 $|V_C|$ & \ 5.8\% & \ 7.8\% & \ 4.5\% & \ 5.8\% & \ 6.4\% & \ 3.0\% \\ \hline
-% venue graphs
 $|E_A|$ & \ 3.0\% & 2.4\% & \ 0.9\% & \ 0.0\% & \ 0.0\% & \ 0.0\% \\

### 2017-12-29 icde/revision/sec-alg.tex

@@
 
-To verify this observation, we also collect the statistics of citation/venue graphs and Web graphs illustrated in Table~\ref{tab-batch}, where Web graphs are extracted from berkely.edu and stanford.edu domains in 2002 and from the Google programming contest in 2002, respectively~\cite{LeskovecLDM09}, \markedb{and numbers $x/y$ in the first three rows are the corresponding statistics on citation/venue graphs.}
+To verify this observation, we also collect the statistics of citation/venue graphs and Web graphs illustrated in Table~\ref{tab-batch}, where Web graphs are extracted from berkely.edu and stanford.edu domains in 2002 and from the Google programming contest in 2002, respectively~\cite{LeskovecLDM09}.
 Due to the existence of the ``bow tie'' structure and the giant \scc in Web graphs~\cite{BroderKMRRSTW00}, the \scc edge ratios $|E_i|/|E|$ are greater than 59\%.

### 2017-12-29 icde/revision/sec-incAlg.tex

@@
 
-Let $G_A=(V_A,E_A)$, $G_B=(V_B,E_B)$ and $G_C=(V_C,E_C)$, respectively, and
+Let $G_A=(V_A,E_A)$, $G_B=(V_B,E_B)$ and $G_C=(V_C$, $E_C)$, respectively, and
 let $E_{AB}$ and $E_{CB}$  be the sets of edges from $G_A$ to $G_B$ and from $G_C$ to $G_B$, respectively.

### 2017-12-29 icde/revision/sec-intro.tex

@@
 That is, scholarly article ranking is essentially a problem of assessing the importance of nodes in a heterogeneous network.
-However, effective and efficient ranking of nodes in such a large complex network is a different task due to the heterogeneous, evolving and dynamic natures of involved entities~\cite{AggarwalS14-survey,fcs-biggraph}.
+However, effective and efficient ranking of nodes in such a large complex network is a difficult task due to the heterogeneous, evolving and dynamic natures of involved entities~\cite{AggarwalS14-survey,fcs-biggraph}.
 
@@
 
-Query independent ranking of scholarly articles remains difficult~\cite{wsdmcup}, although there exists quite a bit of work on scholarly article ranking, \eg~\cite{Garfield471,Liang16AAAI,Jiang12-MRank,Waltman2014}.
+Query independent ranking of scholarly articles remains challenging~\cite{wsdmcup}, although there exists quite a bit of work on scholarly article ranking, \eg~\cite{Garfield471,Liang16AAAI,Jiang12-MRank,Waltman2014}.
 Most previous work exploits the time-dependent information of scholarly data in the form of exponential decay~\cite{Li08TSRanking,Wang13AAAI,sayyadi09,WalkerXKM07}, which fails to capture the diverse citation patterns of individual articles~\cite{Chakraborty15}.
@@
 %
-To our knowledge, the Time-Weighted PageRank is among the first to incorporate the diverse citation patterns of individual articles \markedb{and exploit citation statistics for scholarly article ranking.}
+To our knowledge, our Time-Weighted PageRank is among the first to incorporate diverse citation patterns of individual articles and to exploit citation statistics for scholarly article ranking.
 %and the long-term bias caused by the dynamic nature of data
 
-\sstab(2)  We then develop  a batch algorithm for scholarly article ranking (Section \ref{sec-alg}), in which we propose a block-wise method for Time-Weighted PageRank \markedb{and show its efficiency advantage in terms of an analysis of the citation characteristics and a specific structural property of scholarly graphs.}
-%in which we propose a block-wise method for Time-Weighted PageRank in terms of an analysis of the citation characteristics of scholarly articles.
+\sstab(2)  We then develop  a batch algorithm for scholarly article ranking (Section \ref{sec-alg}), in which we propose a block-wise method for Time-Weighted PageRank %\markedb{and show its efficiency advantage in terms of an analysis of the citation characteristics and a specific structural property of scholarly graphs.}
+in which we propose a block-wise method for Time-Weighted PageRank in terms of an analysis of the citation characteristics of scholarly articles.
 
@@
 
-%All the detailed proofs can be found in \cite{SARank-full}.
-All the proofs can be found in \cite{SARank-full}.
+All the detailed proofs can be found in \cite{SARank-full}.
+%All the proofs can be found in \cite{SARank-full}.
 

### 2017-12-29 icde/revision/sec-model.tex

--- 2017-12-27 icde/revision/sec-model.tex
@@
 %
-\markedb{Before going into details, it is worthy pointing out that although this work focuses on query independent ranking, it can also be used for query dependent ranking.
+%\markedb{Before going into details, it is worthy pointing out that although this work focuses on query independent ranking, it can also be used for query dependent ranking.
 Our ranking can serve as an indicator of the importance of items, and, given a specific query, it can either be directly used to rank a subset of relevant items or combine with any relevance scores.}
@@
 Recall that articles are categorized  into six citation patterns featured by the time when the articles reach their citation peaks~\cite{Chakraborty15}: (a) {\em PeakInit} with a single citation-count peak in the first five years (but not the first year) after publication, (b) {\em PeakMul} with distinct multiple peaks, (c) {\em PeakLate} with a single peak in at least five years   (but not the last year) after publication, (d) {\em MonDec} with monotonically decreasing citations, (e) {\em MonIncr} with monotonically increasing citations, and, (f) {\em Other} for articles whose average numbers of citations per year are less than 1.
-Though the number of citations is an indicator of the impact of an article~\cite{WangSB13,Garfield471}, its impact is time-dependent and is not simply in the form of exponential decay.
-% In general,
-\markedb{Inspired by these citation patterns,} {\em the impact of an article tends to decay with time after the peak time only}~\cite{WangSB13}.
-That is, the impacts of articles directly decay with time only for those in {\em MonDec}, and decay with time after the peak time for those in {\em PeakInit}, {\em PeakLate} and {\em PeakMul}, and do not decay for ones in {\em MonIncr} (which is rare).
+Though the number of citations is an indicator of the impact of an article~\cite{WangSB13,Garfield471}, its impact is time-dependent but not simply in the form of exponential decay that only considers  the case of {\em MonDec}.
+%
+To unify these distinct citation patterns, we adopt that {\em the impact of an article tends to decay with time after the peak time}, as pointed out in~\cite{WangSB13}.
+That is, the impacts of articles directly decay with time only for those in {\em MonDec}, and decay with time after the (highest) peak time for those in {\em PeakInit}, {\em PeakLate} and {\em PeakMul}, and do not decay for ones in {\em MonIncr} (which is rare).
 %Otherwise, its impact is fixed as a constant number. %, since we argue that the increment of its citations during this period is mainly due to the increase of its popularity.
@@
 \includegraphics[scale=0.41]{fig/yearly-references.eps}}
-\caption{\small Statistics of scholarly articles that reports the {\em logscale percentage of the number of papers (left) and citations (right) of each year} \wrt\ the total number of papers and citations on \aan, \aminer and \magdata, respectively.}
+\caption{\small Statistics of scholarly articles: (1) the (logscale) percentage of papers in each year \wrt\ all papers (left) and (2) the (logscale) percentage of citations in each year \wrt\ all citations (right) on datasets \aan, \aminer and \magdata, respectively.}
 \label{fig-data-analysis}
@@
 \end{small}
-%
-\noindent where $PR(u)$ and $PR(v)$ are the TWPageRank scores of $u$ and $v$, respectively, $E$ is the set of edges, $W(u)=\Sigma_{v} w(u,v)$ is the sum of the impact weights on all edges from $u$, $n$ is the number of nodes and $d$ is a damping parameter in $(0, 1)$.
+where $PR(u)$ and $PR(v)$ are the TWPageRank scores of $u$ and $v$, respectively, $E$ is the set of edges, $W(u)=\Sigma_{v} w(u,v)$ is the sum of the impact weights on all edges from $u$, $n$ is the number of nodes and $d$ is a damping parameter in $(0, 1)$.
 By Eq.~(\ref{eq-twpr}), we can see that prestige is updated based on the impact weights, not equally distributed.
@@
 
-\eat{
+\eat{%%%%%%%
 \begin{proof}
@@
 
-\vspace{-1ex}
-\stitle{Remarks}.
-\markedb{
-The goal of our TWPageRank is to change node values, \ie importance.
+%\vspace{-1ex}
+%\stitle{Remarks}.
+%\markedb{
+%The goal of our TWPageRank is to change node values, \ie importance.
 One may wonder why not directly change node values.
 However, it is difficult to handle as importance does not have a clear and closed-form definition and it may also cause problems for convergence.
-To our knowledge, there is no related work on changing node weights and it is yet unclear how to handle it.
-Finally, we use impact weights to achieve the goal since importance is essentially propagable through edges and it is also fair for all nodes.
-}
+%To our knowledge, there is no related work on changing node weights and it is yet unclear how to handle it.
+Finally, we use impact weights to achieve the goal since %importance is essentially propagable through edges and it is also fair for all nodes.
+%}
 
@@
 
-A {\em citation graph} $G^c(V^c, E^c)$ is firstly constructed using the citation information such that (a) a node in $V^c$ denotes an article, (b) a directed edge $(u,v)$ in $E^c$ denotes that $u$ cites $v$, and (c) each node is associated with two types of time information: the publication year and the latest year having the largest (logscale) number of citations.
+A {\em citation graph} $G^c(V^c, E^c)$ is firstly constructed using the citation information such that (a) a node in $V^c$ denotes an article, (b) a directed edge $(u,v)$ in $E^c$ denotes that $u$ cites $v$, and (c) each node is associated with two types of time information: the publication year and the latest year having the largest scaled number of citations.
 
@@
 %However, the resulting author citation graph to compute the prestige is typically too large to handle.
-\markedb{To do this, an {\em author citation graph} needs to be constructed such that (a) a node represents an author, and (b) a direct edge $(s,t)$ denotes that there exist articles of author $s$ citing articles of author $t$.
-It is not hard to image that the number of edges in the author citation graph is much larger than the number in the citation graph, which reaches to 7.12  billion on the largest \magdata (\ie the memory cost of storage only is 57GB).
-It is computationally expensive to compute prestige of authors with TWPageRank on that graph.}
-Hence, we evaluate the prestige of an author, by using the average prestige of all articles published by the author.
-Similar to the venue component, the popularity of an author is also defined as the average popularity of her/his published articles.
-Finally, the prestige and popularity are combined to derive the importance in the same way as the citation component.
+One way to do this is to construct an author citation graph  such that (a) a node represents an author, and (b) a direct edge $(s,t)$ denotes that there exist articles of author $s$ citing articles of author $t$.
+However, it is easy to see that all authors of a article forms a clique, which makes it computationally expensive to compute the prestige of authors on such an author citation graph with TWPageRank.
+
+Hence, we choose to evaluate the prestige of an author with the average prestige of all articles published by the author.
+Similar to the venue component, the popularity of an author is  defined as the average popularity of her/his published articles.
+Finally, the prestige and popularity are combined to derive the importance along the same way as the citation component.
 
@@
 \end{small}
-\noindent Here aggregating parameters $\alpha$ and $\beta$ and value $(1 - \alpha - \beta)$ regularize the contributions of the citation, venue and author information.
-%
-\markedb{
-By this, our model is able to fit to the various ranking scenarios in real-life applications, which hardly can be covered with one set of parameters.
-As will be shown in the experiments, our model performs well in two reasonable ranking scenarios by using quite different aggregating parameters, and, moreover, these parameters are indeed quite flexible to choose within a certain range, \ie $[0,1]$.
-}
-%Intuitively, these parameters indicate the intensity of the correlation between the importance of scholarly articles and the specific information.
+\noindent Here aggregating parameters $\alpha$ and $\beta$ and value $(1 - \alpha - \beta)$ regularize the contributions of the citation, venue and author information,
+which make our model be able to fit to the various ranking scenarios.
+As will be seen in the experiments, our model performs well in two reasonable ranking scenarios by using quite different aggregating parameters, and, moreover, these parameters are indeed quite flexible to choose within a certain range.
+Intuitively, these parameters indicate the intensity of the correlation between the importance of scholarly articles and the specific information.
 

### 2017-12-29 icde/revision/sec-related.tex

@@
 %Both these approaches fail to capture the time-dependent characteristics, a key factor for scholarly article ranking.
-\markedb{Scholarly graph is a kind of temporal graphs~\cite{temporalgraph} and temporal information is a key factor for scholarly article ranking.}
+Scholarly graphs belong to temporal graphs~\cite{temporalgraph}, and temporal information is a key factor for scholarly article ranking.
 There has been work extending temporal information into PageRank, \eg exponentially decayed weights~\cite{Li08TSRanking}, exponentially decayed initial vectors~\cite{WalkerXKM07} and time-dependent weights based on co-authorship~\cite{FIALA2012370}.
 %Different from previous work,
-Differently, our Time-Weighted PageRank \markedb{is inspired by an analysis of impacts of articles} and discriminately propagates scores in terms of statistics of citations.
+Differently, our Time-Weighted PageRank is designed based on a deep analysis of scholarly articles, and discriminately propagates scores in terms of citation statistics.
 
@@
 %
-\markedb{In this work, we study dynamic scholarly article ranking in the general case and develop our incremental algorithm based on the citation characteristics, which has never been exploited before.}
+In this work, we study dynamic scholarly article ranking in the general setting by eliminating the strong and impractical assumption, and our incremental algorithm
+is designed for the block-wise algorithm of Time-Weighted PageRank, and it is based on the citation characteristics, which has never been exploited before.
 %Different from previous work, we study scholarly article ranking in a dynamic environment in terms of the citation characteristics of scholarly articles, which has never been exploited before.

### 2017-12-29 icde/revision/sec-alg.tex

@@
 \hline \hline
-\aan  & 18,041/565 & 82.9K/22.5K &  20/18  & 0.9\%/2.8\%      \\  %\hline
-\aminer  & 3.14M/56K & 14.3M/7.1M   & 23/1.5K &  1.6\%/2.1\%     \\ %\hline    % 1.5K = 1467
-\magdata  & 127M/584K & 526M/162M & 351/10K & 0.1\%/1.8\%    \\ \hline
+citation-\aan   & 18,041 & 82,944 &  20  & 0.9\%      \\  %\hline
+citation-\aminer  & 3.14M & 14.3M   & 23 &  1.6\%     \\ %\hline   
+citation-\magdata  & 127M & 526M & 351 & 0.1\%   \\ \hline
+venue-\aan & 565 & 22.5K & 18 & 2.8\% \\
+venue-\aminer & 56K & 7.1M & 1,467 & 2.1\% \\
+venue-\magdata & 584K & 162M & 10K & 1.8\%  \\ \hline
 web-BS  &  685,230 & 7,600,595 & \multicolumn{1}{c|}{334,857} & \multicolumn{1}{c|}{59.51\%}\\  %\hline

### 2017-12-29 icde/revision/sec-incAlg.tex

@@
 
-\eat{
 \begin{figure}[tb!]
 \centering
-\includegraphics[scale=0.6]{fig/General_framework_peak_ABC.eps}
-\vspace{-3ex}
-\caption{\small An example of affected and unaffected areas}
+\includegraphics[scale=0.7]{fig/General_framework_peak.eps}
+\vspace{-1ex}
+\caption{\small An example of incremental TWPageRank computation}
 \label{fig-inc-division}
@@
 \end{figure}
-
-\begin{example} \label{eg-layer-dag}
-Figure~\ref{fig-inc-division} illustrates an example of affected and unaffected areas, in which subgraphs $G_A$, $G_B$ and $G_C$ are associated with node sets $V_A$, $V_B$ and $\Delta V$, respectively.
-Here the citation peak time of node $x$ is changed, which leads to the changes of the normalized weights of edges $(w,x)$, $(w,y)$ and $(w,z)$.
-\end{example}
-}
 
@@
 }
-
-\begin{figure}[tb!]
-\centering
-\includegraphics[scale=0.7]{fig/General_framework_peak.eps}
-\vspace{-1ex}
-\caption{\small An example of incremental TWPageRank computation}
-\label{fig-inc-division}
-\vspace{-3ex}
-\end{figure}
 

### 2017-12-29 icde/revision/sec-model.tex

@@
 %
-To unify these distinct citation patterns, we adopt that {\em the impact of an article tends to decay with time after the peak time}, as pointed out in~\cite{WangSB13}.
+To unify these distinct citation patterns and to make our ranking model succinct, we adopt that {\em the impact of an article tends to decay with time after the peak time}, as pointed out by the aging function in~\cite{WangSB13}.
 That is, the impacts of articles directly decay with time only for those in {\em MonDec}, and decay with time after the (highest) peak time for those in {\em PeakInit}, {\em PeakLate} and {\em PeakMul}, and do not decay for ones in {\em MonIncr} (which is rare).
@@
 One way to do this is to construct an author citation graph  such that (a) a node represents an author, and (b) a direct edge $(s,t)$ denotes that there exist articles of author $s$ citing articles of author $t$.
-However, it is easy to see that all authors of a article forms a clique, which makes it computationally expensive to compute the prestige of authors on such an author citation graph with TWPageRank.
+However, it is easy to see that for each citation, the corresponding two sets of authors are fully connected, which makes it computationally expensive to compute the prestige of authors on such an author citation graph with TWPageRank.
 

### 2017-12-29 icde/revision/sec-alg.tex

--- 2017-12-29 icde/revision/sec-alg.tex
@@
 \hline \hline
-\aan  & 18,041/565 & 82.9K/22.5K &  20/18  & 0.9\%/2.8\%      \\  %\hline
-\aminer  & 3.14M/56K & 14.3M/7.1M   & 23/1.5K &  1.6\%/2.1\%     \\ %\hline    % 1.5K = 1467
-\magdata  & 127M/584K & 526M/162M & 351/10K & 0.1\%/1.8\%    \\ \hline
+%\aan  & 18,041/565 & 82.9K/22.5K &  20/18  & 0.9\%/2.8\%      \\  %\hline
+%\aminer  & 3.14M/56K & 14.3M/7.1M   & 23/1.5 &  1.6\%/2.1\%     \\ %\hline    % 1.5K = 1467
+%\magdata  & 127M/584K & 526M/162M & 351/10K & 0.1\%/1.8\%    \\ \hline
+citation-\aan   & 18,041 & 82,944 &  20  & 0.9\%      \\  
+citation-\aminer  & 3.14M & 14.3M   & 23 &  1.6\%     \\  
+citation-\magdata  & 127M & 526M & 351 & 0.1\%   \\ \hline
+venue-\aan & 565 & 22,527 & 18 & 2.8\% \\
+venue-\aminer & 56,370 & 7.1M & 1,467 & 2.1\% \\
+venue-\magdata & 584,298 & 162M & 10,473 & 1.8\%  \\ \hline
 web-BS  &  685,230 & 7,600,595 & \multicolumn{1}{c|}{334,857} & \multicolumn{1}{c|}{59.51\%}\\  %\hline

### 2017-12-30 icde/revision/Response.tex

@@
 (7) (left column, page 4).
-More specifically, these parameters enable our model to fit to the various ranking scenarios in real-life applications, which hardly can be covered with one set of parameters.
-As be shown in the experiments, our model performs well in two reasonable ranking scenarios (with \recom and \fcita) by using quite different aggregating parameters, and, moreover, these parameters are indeed quite flexible to choose within a certain range, \ie $[0,1]$, as a) the optimal \PairAcc is obtained within a single region, b) the \PairAcc keeps at a high level within a certain ($\alpha$, $\beta$) combination space around the optimal region, and c) the optimal parameters on the same set of ground-truth are very similar across different datasets (please also refer to our analysis in Exp-4.3).
+More specifically, these parameters make our model be able to fit to the various ranking scenarios.
+As will be seen in the experiments, our model performs well in two reasonable ranking scenarios by using quite different aggregating parameters, and, moreover, these parameters are indeed quite flexible to choose within a certain range.
+%
+Note that a) the optimal \PairAcc is obtained within a single region, b) the \PairAcc keeps at a high level within a certain ($\alpha$, $\beta$) combination space around the optimal region, and c) the optimal parameters on the same set of ground-truth are very similar across different datasets (Exp-5.3, page 10).
 
@@
 
-We discuss the extension of query dependent ranking in the revised paper (left column, page 2).
+%We discuss the extension of query dependent ranking in the revised paper (left column, page 2).
 %
-This work focuses on query independent ranking because of its wide application in modern scholarly search engines such as Google Scholar, Semantic Scholar and Microsoft Academic Search.
-And our ranking can serve as an indicator of the importance of items, and, given a specific query, it can either be directly used to rank a subset of relevant items or combine with any relevance scores for ranking.
+This work focuses on {\em query independent ranking} because of its wide application in modern scholarly search engines such as Google Scholar, Semantic Scholar and Microsoft Academic Search.
 %
-The extension in other heterogeneous information networks is currently unclear, since the TWPageRank is derived from an analysis of impacts of articles (left column, page 2).
-We shall identify possible applications in the future.
+And it can be easily extended to {\em query dependent ranking}.
+Our ranking can serve as an indicator of the importance of items, and, given a specific query, it can either be directly used to rank a subset of relevant items or combine with any relevance scores for ranking.
+%
+The extension in {\em other heterogeneous information networks} is currently unclear, since the TWPageRank is designed based on a deep analysis of scholarly articles (left column, page 2).
+We shall identify the possible applications in other heterogeneous information networks in the future.
 
@@
 
-We clarify the reasons of not changing values on nodes at the revised version (Remarks, left column, page 3).
-The goal of our TWPageRank is to change node values, \ie importance.
+%We clarify the reasons of not changing values on nodes at the revised version (Remarks, left column, page 3).
+The goal of our TWPageRank is to change node values, \ie importance, through iterations.
 %One may wonder why not directly change node values.
-Directly changing node values, however, is difficult to handle as importance does not have a clear and closed-form definition and it may also cause problems for convergence.
-To our knowledge, there is no related work on changing node weights and it is yet unclear how to handle it.
-Finally, we use impact weights to achieve the goal since importance is essentially propagable through edges and it is also fair for all nodes.
+An alternative way to do that is to directly change node values.
+However, it is difficult to handle as importance does not have a clear and closed-form definition and it may also cause problems for convergence.
+To our knowledge, there is no related work on changing node weights to achieve this goal and it is yet unclear how to handle it.
+Finally, we use iterations with impact weights since importance is essentially propagable through edges and it is also fair for all nodes.
 
@@
 
-Figure 1 shows the logscale percentage of the number of articles/citations of each year which grows exponentially with time, instead of numbers of citations (\ie impacts) of individual articles.
-We have highlighted it in the revised version (Figure 1, page 2).
+Figure 1 shows the logscale percentage of the number of articles/citations of each year which grows exponentially with time, instead of the number of citations (\ie impacts) of individual articles.
+%We have highlighted it in the revised version (Figure 1, page 2).
 
-We have explained our claim better (Time-Weighted PageRank, right column, page 2).
-The observation is inspired by the five distinct citation patterns.
-Considering that the direct decay model only conforms with {\em MonDec}, we thus propose our claim that can better explain the five citation patterns.
-Moreover, reference [17] exploits a log-normal survival probability which also decays with time after the citation peak.
+We have explained our claim better (Time-Weighted PageRank, page 2). The direct decay model only considers the case of {\em MonDec}. 
+To unify these distinct citation patterns and to make our ranking model succinct, we adopt the claim that the impact of an article tends to decay with time after the peak time. 
+Moreover, the aging function in [17] exploits a log-normal survival probability which also only decays with time after the citation peak.
 %(it increases before reaching the peak since it aims to predict the number of citations instead of impacts of articles).
@@
 
-The PeakMul pattern is originally defined in [18]:  the height of a peak should be at least 75\% of the maximum peak height, and two consecutive peaks should be separated by more than two years.
-In our work, we unify the five patterns and only use the latest peak time which we have discussed in Section II-A (para 2, left column, page 3).
+The {\em PeakMul} pattern is originally defined in [18]:  the height of a peak should be at least 75\% of the maximum peak height, and two consecutive peaks should be separated by more than two years.
+In our work, we unify the five patterns and only use the highest peak time which has been formally defined in Section II-A (para 1, left column, page 3).
+Also note that: a) [18] allows multiple peaks to exist for an article while we only consider the highest peak, and b) [18] uses the original numbers of citations to compute peaks and we use the scaled numbers of citations \wrt the total number of citations of all articles at each year.
 
@@
 This work does NOT assume the DAG structure of scholarly graphs, where cycles are allowed to exist (Observation, left column, page 5).
-Compared to general Web graphs, the computation of TWPageRank on scholarly graphs is more efficient as a result of the {\em temporal order of citations}, which gives less SCC edge ratio as shown in Table I (page 5).
-In addition, we further design incremental algorithms based on the temporal order of citations, which also makes the computation more efficient.
+Compared with general Web graphs, the computation of TWPageRank on scholarly graphs is more efficient as a result of the {\em temporal order of citations}, which gives less SCC edge ratio as shown in Table I (page 5).
+In addition, we further design incremental algorithms based on the temporal order of citations, \eg for the maintenance of the topological order, which also makes the computation more efficient.
 %We have highlighted the statements about temporal order in the revised version.
@@
 
-Yes, we have revised our paper as suggested (right column, page 1 \& right column, page 5).
+Yes, we have revised our paper as suggested (right column, page 1 \& Table I, page 5).
 %Thanks for the suggestion!
@@
 
-\textbf{[R2W1]} \emph{While practically the paper makes a good case about the particular application domain and its contributions there, the paper lacks technical depth.}
-
-We think that the techniques proposed also have their own interests: a) An importance assembling based ranking model itself is hard to define and tune, b) an incremental algorithm that makes use of the particular properties of the scholarly graphs, and c) a thorough experimental study.
-That is, this paper certainly has its contributions to the technical part.
-%\marked{In the revised version, we highlight our technical contributions.}
-
-\textbf{[R2W2]} \emph{Presentation could improve a bit since the paper has too much notation making it hard to read/follow.}
-
-\marked{Yes, we have gone over the paper and improved the presentation to make it more understandable. }
-%Thanks for the suggestion!
-
+\textbf{[R2W1]} \emph{While practically the paper makes a good case about the particular application domain and its contributions there, the paper lacks technical depth.} \\
 \textbf{[R2D1]} \emph{There seem to be two ``contradictory" sides to this paper.
@@
 We thank the reviewer for appreciating the practice merit of our work which is drawn from an important and practical problem.
+
+%And we believe this paper also stands from research and technique perspective.
+And We think that the techniques proposed also have their own interests: a) An importance assembling based ranking model itself is hard to define and tune, b) an incremental algorithm for block-wise time-weighted PageRank computation that makes use of the particular properties of the scholarly graph, and c) a thorough experimental study.
+That is, this paper certainly has its contributions to the technical part.
+
+More specifically, the only existing dynamic scholarly article ranking solution [21] is based on an impractical assumption that there is no citations between articles of the same years.
+In this work, we study dynamic scholarly article ranking in the general setting by eliminating the strong and impractical assumption.
+Our incremental algorithm is designed for the block-wise algorithm of Time-Weighted PageRank, and is based on the citation characteristics (\eg for the maintenance of the topological order), both of which have never been exploited before.
 %
-And we believe this paper also stands from research and technique perspective.
-%
-The property of scholarly data makes the incremental computation of (time-weighted) PageRank quite different from those on general graphs, which, to our knowledge, has not gained enough attentions.
+To conclude, the incremental time-weighted PageRank algorithm for scholarly graphs has its own unique features, which is not simply applying existing techniques into a different domain.
+We have further %clarified our contributions in Introduction and 
+claimed the technique difference of our algorithm in Related Work.
+
+%The property of scholarly data makes the incremental computation of (time-weighted) PageRank quite different from those on general graphs, which, to our knowledge, has not gained enough attentions.
 Furthermore, the only existing dynamic scholarly article ranking solution [21] is based on an impractical assumption that there is no citations between articles of the same years.
-%
-Therefore, we have designed the incremental time-weighted PageRank algorithm for scholarly graphs which has its own unique features.
-To conclude, we are not simply applying existing techniques into a different domain.
-%
-We have further clarified our contributions in Introduction and claimed the technique difference of our algorithm in Related Work.
-%
-Please also refer to our response to R2W1.
+
+%\marked{In the revised version, we highlight our technical contributions.}
 
 [21]  R. Ghosh, T. Kuo, C. Hsu, S. Lin, and K. Lerman, ¡°Time-aware ranking in dynamic citation networks,¡± in ICDM Workshops, 2011.
+
+\textbf{[R2W2]} \emph{Presentation could improve a bit since the paper has too much notation making it hard to read/follow.}
+
+Yes, we have gone over the paper and improved the presentation to make it more understandable. 
+%Thanks for the suggestion!
 
@@
 
-We have removed the sentence and explained more details about the statement (Author Component, left column, page 3).
-Moreover specifically, we add the details of the generation of the author citation graph.
+We have removed the sentence and explained more details about the statement (Author Component, left column, page 4). 
+%
+One way to compute the prestige of authors is to construct an author citation graph  such that (a) a node represents an author, and (b) a direct edge $(s,t)$ denotes that there exist articles of author $s$ citing articles of author $t$.
+However, it is easy to see that for each citation, the corresponding two sets of authors are fully connected, which makes it computationally expensive to compute the prestige of authors on such an author citation graph with TWPageRank.
+%
+Indeed, the generated author citation graph has 7.12 billion edges on the largest \magdata, \ie the memory cost of storage only is 57GB. Please also refer to our new experiments on memory costs.
+
+%Moreover specifically, we add the details of the generation of the author citation graph.
 The generated graph has 7.12 billion edges on the largest \magdata (\ie the memory cost of storage only is 57GB), which makes it computationally expensive to compute prestige of authors  with TWPageRank on that graph.
@@
 
-We have reported the memory cost in Exp-3 (page 10) that on the largest \magdata, (\futurerank, \ensemblerank) cost (16.42GB, 49.42GB) memory when $Y_s=2015$, and \hhgrank costs 61.37GB memory when $Y_s=2014$.
-Interestingly, our \ensemblerank model costs more memory than \futurerank due to its model complexity, while it is more efficient with our batch and incremental algorithms.
+We have reported the memory costs in a new set of experiments Exp-4 (page 10).
+\marked{that on the largest \magdata, (\futurerank, \ensemblerank) cost (16.42GB, 49.42GB) memory when $Y_s=2015$, and \hhgrank costs 61.37GB memory when $Y_s=2014$.
+Interestingly, our \ensemblerank model costs more memory than \futurerank due to its model complexity, while it is more efficient with our batch and incremental algorithms.}
 %the memory cost of (\pagerank, \futurerank, \ensemblerank) is (12.65GB, 16.42GB, 49.42GB) when $Y_s=2015$, and the one of \hhgrank is 61.37GB when $Y_s=2014$.

### 2017-12-30 icde/revision/sec-related.tex

@@
 %
-In this work, we study dynamic scholarly article ranking in the general setting by eliminating the strong and impractical assumption, and our incremental algorithm
-is designed for the block-wise algorithm of Time-Weighted PageRank, and it is based on the citation characteristics, which has never been exploited before.
+In this work, we study dynamic scholarly article ranking in the general setting by eliminating the strong and impractical assumption.
+Our incremental algorithm is designed for the block-wise algorithm of Time-Weighted PageRank, and is based on the citation characteristics, both of which have never been exploited before.
 %Different from previous work, we study scholarly article ranking in a dynamic environment in terms of the citation characteristics of scholarly articles, which has never been exploited before.

### 2017-12-30 icde/revision/Response.tex

@@
 \marked{that on the largest \magdata, (\futurerank, \ensemblerank) cost (16.42GB, 49.42GB) memory when $Y_s=2015$, and \hhgrank costs 61.37GB memory when $Y_s=2014$.
-Interestingly, our \ensemblerank model costs more memory than \futurerank due to its model complexity, while it is more efficient with our batch and incremental algorithms.}
+Interestingly, our \ensemblerank model costs more memory than \futurerank due to its model complexity, while it is more efficient with our batch and incremental algorithms.
+seperate exp, between two baselines, author citation graph}
 %the memory cost of (\pagerank, \futurerank, \ensemblerank) is (12.65GB, 16.42GB, 49.42GB) when $Y_s=2015$, and the one of \hhgrank is 61.37GB when $Y_s=2014$.

### 2017-12-30 icde/revision/sec-alg.tex

@@
 citation-\aan   & 18,041 & 82,944 &  20  & 0.9\%      \\
-citation-\aminer  & 3.14M & 14.3M   & 23 &  1.6\%     \\  
-citation-\magdata  & 127M & 526M & 351 & 0.1\%   \\ \hline
+citation-\aminer  & 3,140,081 & 14,260,658   & 23 &  1.6\%     \\
+citation-\magdata  & 126,909,021 & 526,498,920 & 351 & 0.1\%   \\ \hline
 venue-\aan & 565 & 22,527 & 18 & 2.8\% \\
-venue-\aminer & 56,370 & 7.1M & 1,467 & 2.1\% \\
-venue-\magdata & 584,298 & 162M & 10,473 & 1.8\%  \\ \hline
+venue-\aminer & 56,370 & 7,094,231 & 1,467 & 2.1\% \\
+venue-\magdata & 584,298 & 162,431,575 & 10,473 & 1.8\%  \\ \hline
 web-BS  &  685,230 & 7,600,595 & \multicolumn{1}{c|}{334,857} & \multicolumn{1}{c|}{59.51\%}\\  %\hline

### 2017-12-30 icde/revision/sec-exp.tex

@@
 \end{center}
-\vspace{-1.5ex}
+\vspace{-2ex}
 \caption{\small Accuracy evaluation with \fcita (all) and \recom ((d)--(e), (i)--(j) and (n)--(o))}
@@
 \end{center}
-\vspace{-1.5ex}
+\vspace{-2ex}
 \caption{\small Efficiency evaluation on \aminer ((a)--(b)) and  \magdata ((c)--(d))}
@@
 Aggregating parameters were selected as follows: $(\alpha, \beta, \gamma)$ = $(0.7, 0.1, 0.2)$ for \futurerank, $(a_{i1}, a_{i2}, a_{i3})$ = $(0.3, 0.6, 0.1)$ for \hhgrank ($i\in[1, 3]$), and $(\alpha, \beta)$ = $(0.8, 0.1)$ for \ensemblerank.
-\markedb{Note that with \fcita the selected $(\alpha, \beta)$ for \ensemblerank are quite different from the ones with \recom.}
+Note that with \fcita the values of paraments $\alpha$ and $\beta$ for \ensemblerank are quite different from the ones with \recom.
 %Here the citation component contributed most in \ensemblerank, since \fcita is based on citation information.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newcommand{\graphscaleexpapp}{0.24}
+\newcommand{\graphscaleexpapp}{0.25}
 \newcommand{\graphmarginexpapp}{3ex}
@@
 
-\markedb{The memory cost is an important factor of efficiency.
-We thus collect the memory use on the largest \magdata that (\futurerank, \ensemblerank) cost (16.42GB, 49.42GB) memory when $Y_s=2015$, and \hhgrank costs 61.37GB when $Y_s=2014$.
-Interestingly, our \ensemblerank model costs more memory than \futurerank due to its model complexity, while it is more efficient with our batch and incremental algorithms.}
-
 %\etitle{Remarks}.
@@
 And algorithm \incensemble further improves the efficiency by 22\% on average, compared with \batensemble.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[t!]
+%\vspace{-2ex}
+\label{tab-result}
+\begin{center}
+\caption{\small Memory cost of algorithms}
+%\begin{small}
+\vspace{-.5ex}
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+{\bf Datasets}   &  \hspace{1ex}\pagerank\hspace{1ex}     & \hspace{1ex}\futurerank\hspace{1ex}  &  \hspace{1ex}\hhgrank\hspace{1ex}  &   \hspace{1ex}\ensemblerank\hspace{1ex}    \\
+\hline \hline
+\aan  & $0.671$   & $0.738$   & $0.758$     & {\bf 0.805}      \\  %\hline
+\aminer  & $0.651$   & $0.729$   & $0.730$     & {\bf 0.778}      \\ %\hline
+\magdata  & $0.615$   & $0.655$   & $0.658$     & {\bf 0.680}      \\ \hline
+\end{tabular}
+%\vspace{-.5ex}
+%\end{small}
+\end{center}
+\vspace{-6ex}
+\end{table}
+%%%%%%%%%%%%%%%%%%%
+
+\stitle{Exp-4: Memory cost}.
+In the fourth set of tests, we evaluated the memory cost of our algorithm.
+For a fair comparison, all algorithms used data before 2014, since the \hhgrank will run out of memory in 2015.
+The results of memory cost are reported in Table~IV.
+The original data including
+\markedb{The memory cost is an important factor of efficiency.
+We thus collect the memory use on the largest \magdata that (\futurerank, \ensemblerank) cost (16.42GB, 49.42GB) memory when $Y_s=2015$, and \hhgrank costs 61.37GB when $Y_s=2014$.
+Interestingly, our \ensemblerank model costs more memory than \futurerank due to its model complexity, while it is more efficient with our batch and incremental algorithms.}
 
@@
 
-\stitle{Exp-4: Impacts of parameters}.
+\stitle{Exp-5: Impacts of parameters}.
 %\subsubsection{Exp-4: Impacts of parameters}.

### 2017-12-30 icde/revision/Response.tex

@@
 %And we believe this paper also stands from research and technique perspective.
-And We think that the techniques proposed also have their own interests: a) An importance assembling based ranking model itself is hard to define and tune, b) an incremental algorithm for block-wise time-weighted PageRank computation that makes use of the particular properties of the scholarly graph, and c) a thorough experimental study.
+And We think that the techniques proposed also have their own interests: a) An importance assembling based ranking model itself is hard to define and tune, b) an incremental algorithm for block-wise time-weighted PageRank computation that makes use of the particular properties of the scholarly graphs, and c) a thorough experimental study.
 That is, this paper certainly has its contributions to the technical part.
@@
 
+%******************* meta-reviewer ***********************************************
+\line(1,0){500}
+
+\textbf{Response to the comments of META-REVIEWER.}
+
+\textbf{[D1]} \emph{The reviewers see some merit in the approach, but they have also raised important concerns regarding the technical depth and novelty of the approach.
+In particular, the authors use known techniques for an application (scientific article ranking) for which there is abundance of previous work (it even has its own field, called scientometrics, or  bibliometrics).}
+
+The techniques used in our work are not simply existing techniques:
+a) an importance assembling based ranking model is still novel in the field of scientometrics and bibliometrics and we further consider the efficient batch and dynamic computation problem which rarely has been exploited in these two fields, b) an incremental algorithm for block-wise time-weighted PageRank computation that makes use of the particular properties of the scholarly graphs, and c) a thorough experimental study.
+That is, although bearing similarities, this paper certainly has its contributions to the technical part and brings certain novelty for the task.
+
+Please also refer to our response to R2W1\&D1 for more details.
+
 \line(1,0){500}

### 2017-12-30 icde/revision/sec-exp.tex

@@
 \vspace{-.5ex}
-\begin{tabular}{|c|c|c|c|c|}
+\begin{tabular}{|c|c|c|c|c|c|}
 \hline
-{\bf Datasets}   &  \hspace{1ex}\pagerank\hspace{1ex}     & \hspace{1ex}\futurerank\hspace{1ex}  &  \hspace{1ex}\hhgrank\hspace{1ex}  &   \hspace{1ex}\ensemblerank\hspace{1ex}    \\
+{\bf Datasets}   &  \hspace{1ex}Original\hspace{1ex}     &  \hspace{1ex}\pagerank\hspace{1ex}     & \hspace{1ex}\futurerank\hspace{1ex}  &  \hspace{1ex}\hhgrank\hspace{1ex}  &   \hspace{1ex}\ensemblerank\hspace{1ex}    \\
 \hline \hline
-\aan  & $0.671$   & $0.738$   & $0.758$     & {\bf 0.805}      \\  %\hline
-\aminer  & $0.651$   & $0.729$   & $0.730$     & {\bf 0.778}      \\ %\hline
-\magdata  & $0.615$   & $0.655$   & $0.658$     & {\bf 0.680}      \\ \hline
+\aan  & 6.80MB   & 5.03MB   & 5.86MB   & 11.06MB     & 13.09MB      \\  %\hline
+\aminer  & 288.87MB   & 263.81MB   & 404.46MB   & 1.34GB     & 1.28GB      \\ %\hline
+\magdata  & 10.46GB   & 8.67GB   & 14.32GB   & 61.37GB     & 48.13GB      \\ \hline
 \end{tabular}
@@
 \stitle{Exp-4: Memory cost}.
+
 In the fourth set of tests, we evaluated the memory cost of our algorithm.
-For a fair comparison, all algorithms used data before 2014, since the \hhgrank will run out of memory in 2015.
+For a fair comparison, all algorithms used all data on both \aan and \aminer, and used data before 2014 on \magdata, since the \hhgrank will run out of memory in when $Y_s=2015$.
+The original data including paper citation graph, paper-author graph, paper-venue graph and time information of articles.
 The results of memory cost are reported in Table~IV.
-The original data including
-\markedb{The memory cost is an important factor of efficiency.
-We thus collect the memory use on the largest \magdata that (\futurerank, \ensemblerank) cost (16.42GB, 49.42GB) memory when $Y_s=2015$, and \hhgrank costs 61.37GB when $Y_s=2014$.
-Interestingly, our \ensemblerank model costs more memory than \futurerank due to its model complexity, while it is more efficient with our batch and incremental algorithms.}
+
+For all algorithms, the memory cost increases with the original graph.
+Moreover, the more complexity the algorithm is, the more memory it costs.
+The memory cost of \pagerank is much lower than the one of other algorithms, since it only uses the citation information alone.
+Moreover, \ensemblerank costs more memory than \futurerank due to it also uses venue information besides of author information which \futurerank uses.
+The memory cost of \hhgrank is much higher than the one of other algorithms except on \aan possibly because the hypernetwork it generates will be more complicated with bigger original graph.
+Consider that, we choose to evaluate the prestige of an author with the average prestige of all articles published by the author instead of constructing an author citation graph with author component.
 

### 2017-12-30 icde/revision/sec-exp.tex

@@
 
-\etitle{Exp-4.1}.
+\etitle{Exp-5.1}.
 %\stitle{Exp-4.1}.
@@
 
-\etitle{Exp-4.2}.
+\etitle{Exp-5.2}.
 %\stitle{Exp-4.2}.
@@
 
-\etitle{Exp-4.3}.
+\etitle{Exp-5.3}.
 To evaluate the impacts of aggregating parameters $\alpha$ and $\beta$, we varied $\alpha$ and $\beta$ at the granularity of 0.01.
@@
 
-Moreover, this enables to verify the effectiveness of importance assembling from different components, whose results are reported in Table~IV, in which letters C, V and A stand for citation, venue and author components, respectively.
+Moreover, this enables to verify the effectiveness of importance assembling from different components, whose results are reported in Table~V, in which letters C, V and A stand for citation, venue and author components, respectively.
 The ranking based on all components consistently performs the best, using both \recom and \fcita, which justifies the use of importance assembling for ranking scholarly articles.
@@
 
-\etitle{Exp-4.4}.
+\etitle{Exp-5.4}.
 To evaluate the impacts of our TWPageRank, we compared our \ensemblerank with \drank, an alternative of \ensemblerank by removing the peak time in  Eq.~(\ref{eq-infl-weights}) of  TWPageRank, \ie $w(u,v)=e^{\sigma(T_u-T_v)}$.

### 2017-12-30 icde/revision/Response.tex

@@
 \newcommand{\magdata}{{\sc MAG}\xspace}
+\newcommand{\aminer}{{\sc DBLP}\xspace}
 
@@
 
-We have reported the memory costs in a new set of experiments Exp-4 (page 10).
-\marked{that on the largest \magdata, (\futurerank, \ensemblerank) cost (16.42GB, 49.42GB) memory when $Y_s=2015$, and \hhgrank costs 61.37GB memory when $Y_s=2014$.
+We have reported the memory costs in a new set of experiments, \ie Exp-4 (page 10). 
+On the large \aminer and \magdata, algorithm \pagerank uses the least memory, followed by algorithms \futurerank, \ensemblerank and \hhgrank, respectively.
+%
+The memory used by \pagerank is even less than the size of the academic graph data as it is based on the citation graph only.
+%
+Our \ensemblerank model costs more memory than \futurerank since it also combines article-venue relationships ignored by \futurerank and it assembles multiple rankings based on prestige and popularity.
+However, our \ensemblerank model is still more memory-efficient than \hhgrank.
+%
+To conclude, the \ensemblerank model uses reasonable amount of  memory to achieve the better effectiveness.
+
+%that on the largest \magdata, (\futurerank, \ensemblerank) cost (16.42GB, 49.42GB) memory when $Y_s=2015$, and \hhgrank costs 61.37GB memory when $Y_s=2014$.
 Interestingly, our \ensemblerank model costs more memory than \futurerank due to its model complexity, while it is more efficient with our batch and incremental algorithms.
-seperate exp, between two baselines, author citation graph}
+seperate exp, between two baselines, author citation graph
 %the memory cost of (\pagerank, \futurerank, \ensemblerank) is (12.65GB, 16.42GB, 49.42GB) when $Y_s=2015$, and the one of \hhgrank is 61.37GB when $Y_s=2014$.

### 2017-12-30 icde/revision/sec-exp.tex

--- 2017-12-30 icde/revision/sec-exp.tex
@@
 In this section, we present an extensive experimental study of our approach \ensemblerank, compared with three competitive methods.
-Using three real-life scholarly datasets (\aan, \aminer and \magdata) and two sets of ground-truth (\recom and \fcita), we conducted four sets of experiments to evaluate: (1) the effectiveness of \ensemblerank,
+Using three real-life scholarly datasets (\aan, \aminer and \magdata) and two sets of ground-truth (\recom and \fcita), we conducted five sets of experiments to evaluate: (1) the effectiveness of \ensemblerank,
 %two sets of benchmark article pairs (\recom and \fcita) ranked by numbers of recommendations and future citations,
-(2) the efficiency of our batch algorithm \batensemble and incremental algorithm \incensemble, and (3) the impacts of parameters.
+(2) the efficiency of our batch algorithm \batensemble and incremental algorithm \incensemble, (3) the memory cost, and (4) the impacts of parameters.
 %\ie time decaying factor $\sigma$, importance weighting factor $\lambda$ and aggregating parameters $\alpha$ and $\beta$.
@@
 \label{exp-ab}
-\vspace{-2ex}
+\vspace{-3ex}
 \end{figure*}
@@
 \begin{center}
-\caption{\small Memory cost of algorithms}
+\caption{\small Memory costs on \aminer and \magdata}
 %\begin{small}
 \vspace{-.5ex}
-\begin{tabular}{|c|c|c|c|c|}
+\begin{tabular}{|c|c|c|c|c|c|}
 \hline
-{\bf Datasets}   &  \hspace{1ex}\pagerank\hspace{1ex}     & \hspace{1ex}\futurerank\hspace{1ex}  &  \hspace{1ex}\hhgrank\hspace{1ex}  &   \hspace{1ex}\ensemblerank\hspace{1ex}    \\
+{\bf Datasets}   &  Data     &  \pagerank     & \futurerank  &  \hhgrank  &   \ensemblerank    \\
 \hline \hline
-\aan  & $0.671$   & $0.738$   & $0.758$     & {\bf 0.805}      \\  %\hline
-\aminer  & $0.651$   & $0.729$   & $0.730$     & {\bf 0.778}      \\ %\hline
-\magdata  & $0.615$   & $0.655$   & $0.658$     & {\bf 0.680}      \\ \hline
+%\aan  & 6.80MB   & 5.03MB   & 5.86MB   & 11.06MB     & 13.09MB      \\  %\hline
+%\aminer  & 288.87MB   & 263.81MB   & 404.46MB   & 1.34GB     & 1.28GB      \\ %\hline
+%\magdata  & 10.46GB   & 8.67GB   & 14.32GB   & 61.37GB     & 48.13GB      \\ \hline
+%\aan  & 6.8MB   & 5.03MB   & 5.86MB   & 11.06MB     & 13.09MB      \\  %\hline
+\aminer  & 289MB   & 264MB   & 404MB   & 1.34GB     & 1.28GB      \\ %\hline
+\magdata  & 10.5GB   & 8.7GB   & 14.3GB   & 61.4GB     & 48.1GB      \\ \hline
 \end{tabular}
@@
 \stitle{Exp-4: Memory cost}.
-In the fourth set of tests, we evaluated the memory cost of our algorithm.
-For a fair comparison, all algorithms used data before 2014, since the \hhgrank will run out of memory in 2015.
-The results of memory cost are reported in Table~IV.
-The original data including
-\markedb{The memory cost is an important factor of efficiency.
-We thus collect the memory use on the largest \magdata that (\futurerank, \ensemblerank) cost (16.42GB, 49.42GB) memory when $Y_s=2015$, and \hhgrank costs 61.37GB when $Y_s=2014$.
-Interestingly, our \ensemblerank model costs more memory than \futurerank due to its model complexity, while it is more efficient with our batch and incremental algorithms.}
+%
+In the fourth set of tests, we evaluated the memory cost of our algorithm on the large \aminer and \magdata.
+For a fair comparison, we used all data on \aminer and data before 2014 on \magdata such that \hhgrank can finish the test.
+The results are reported in Table~IV, where the Data column records the size of the academic graph data, \ie the citation graph, author-article relationships, article-venue relationships and time information of articles.
+
+On both datasets, algorithm \pagerank uses the least memory, followed by algorithms \futurerank, \ensemblerank and \hhgrank, respectively. 
+%
+The memory used by \pagerank is even less than the size of data as it is based on the citation graph only.
+%
+Our \ensemblerank model costs more memory than \futurerank since it also combines article-venue relationships ignored by \futurerank and it assembles multiple rankings based on prestige and popularity.
+However, our \ensemblerank model is still more memory-efficient than \hhgrank.
+%
+To conclude, the \ensemblerank model uses reasonable amount of  memory to achieve the better effectiveness.
+
+%For all algorithms, the memory cost increases with the original graph.
+Moreover, the more complexity the algorithm is, the more memory it costs.
+The memory cost of \pagerank is much lower than the one of other algorithms, since it only uses the citation information alone.
+Moreover, \ensemblerank costs more memory than \futurerank due to it also uses venue information besides of author information which \futurerank uses.
+The memory cost of \hhgrank is much higher than the one of other algorithms except on \aan possibly because the hypernetwork it generates will be more complicated with bigger original graph.
+Consider that, we choose to evaluate the prestige of an author with the average prestige of all articles published by the author instead of constructing an author citation graph with author component.
 

### 2017-12-30 icde/revision/sec-incAlg.tex

@@
 and the resulting graph is $G^+(V\cup\Delta V, E\cup\Delta E)$, where
-$\Delta V$ is a set of nodes with $\Delta V\cap V = \emptyset$, and $\Delta E$ is a set of directed edges on $\Delta V$ and from $\Delta V$ to $V$ only, as citation relationships obey a natural temporal order, \ie an article only cites those published earlier, and it is rare for the mutual citations between two articles published in the same time.
+$\Delta V$ is a set of nodes with $\Delta V\cap V = \emptyset$, and $\Delta E$ is a set of directed edges on $\Delta V$ and from $\Delta V$ to $V$ only, as citations obey a natural temporal order, \ie an article only cites those published earlier.
+%, and it is rare for the mutual citations between two articles published in the same time.
 

### 2017-12-31 icde/revision/sec-exp.tex

@@
 %\vspace{-2ex}
-\label{tab-result}
+\label{tab-mem-result}
 \begin{center}
@@
 In the fourth set of tests, we evaluated the memory cost of our algorithm on the large \aminer and \magdata.
-For a fair comparison, we used all data on \aminer and data before 2014 on \magdata such that \hhgrank can finish the test.
-The results are reported in Table~IV, where the Data column records the size of the academic graph data, \ie the citation graph, author-article relationships, article-venue relationships and time information of articles.
+For a fair comparison, we used all data on \aminer and data before 2014 on \magdata such that \hhgrank could finish the test.
+The results are reported in Table~IV, where column `Data' records the size of the academic graph data, \ie the citation graph, author-article relationships, article-venue relationships and time information of articles.
 
-On both datasets, algorithm \pagerank uses the least memory, followed by algorithms \futurerank, \ensemblerank and \hhgrank, respectively. 
+Algorithm \pagerank uses the least memory, followed by algorithms \futurerank, \ensemblerank and \hhgrank, respectively.
 %
-The memory used by \pagerank is even less than the size of data as it is based on the citation graph only.
+The memory used by \pagerank is even less than the data size as it uses the citation graph only.
 %
-Our \ensemblerank model costs more memory than \futurerank since it also combines article-venue relationships ignored by \futurerank and it assembles multiple rankings based on prestige and popularity.
-However, our \ensemblerank model is still more memory-efficient than \hhgrank.
-%
-To conclude, the \ensemblerank model uses reasonable amount of  memory to achieve the better effectiveness.
+Our \ensemblerank model costs more memory than \futurerank, but less than \hhgrank.
+This is because \ensemblerank further combines article-venue relationships ignored by \futurerank, and assembles multiple rankings based on prestige and popularity,
+a price paid to achieve better effectiveness.
 

### 2017-12-31 icde/revision/sec-app.tex

--- 2017-12-29 icde/revision/sec-model.tex
@@
-\section{Ranking Model}
-\label{sec-model}
+\newpage
+\clearpage
 
-In this section, we first present Time-Weighted PageRank for evaluating  the importance of entities, defined as a combination of the prestige and popularity, and then introduce our ranking model \ensemblerank that assembles the importance of articles, venues and authors involved in scholarly articles.
+\section*{APPENDIX A: Proofs}
+\label{sec-proof}
+
+\subsection*{1. Proof of Corollary \ref{prop-prscc}}
+The vector $PR$ returned by~\twprscc converges such that $||PR-PR^*||_1 < \epsilon$ given the convergent vector $PR^*$.
+
+\vspace{.5ex}
+\begin{proofS}
+%By lemma~\ref{prop-converg}, we know that TWPageRank converges on venue graphs.
+We first prove that the sum of changes after another iteration from $PR$ is smaller than $\epsilon$, \ie $||PR'-PR||_1 < \epsilon$ where $PR'=d M^T\cdot PR + \frac{1-d}{n} e$, and then prove that $||PR^*-PR||_1$ is smaller than $||PR'-PR||_1$.
+%the sum of changes.
+
+Consider $scc_1$, $\dots$, $scc_m$ of the (citation or venue) graph $G$ such that $v_1'/\dots$ $/v_m'$ is indeed a valid topological order of the block-wise graph $G'$ of $G$, where %$m$ is the number of \sccs in $G$ and
+$v_k'$ ($k\in [1,m]$) is the corresponding node of $scc_k$ in $G'$.
+
+Let $PR_k$ and $PR_k^-$ be the current and the previous TWPageRank vectors of nodes in $scc_k$ produced
+by \twprscc, and $PR_k'$ be the TWPageRank vector of nodes in $scc_k$ extracted from $PR'$.
+Further let $\Delta_k=PR_k-PR^-_k$ and we have:
+$\sum_{k=1}^m ||\Delta_k||_1 < \epsilon$.
 %
-%\markedb{Before going into details, it is worthy pointing out that although this work focuses on query independent ranking, it can also be used for query dependent ranking.
-Our ranking can serve as an indicator of the importance of items, and, given a specific query, it can either be directly used to rank a subset of relevant items or combine with any relevance scores.}
-
-%It further assembles the importance of heterogeneous entities involved to rank scholarly articles.
-%The model is based on PageRank~\cite{Brin98:PageRank}, which was initially designed for web pages and widely applied to many other tasks, including article ranking~\cite{Li08TSRanking,Richardson06:BPR,sayyadi09,Zhou07-CoRank}.
-
-\subsection{Time-Weighted PageRank}
-\label{subsec-twpr}
-
-We first present Time-Weighted PageRank (TWPageRank) based on citation statistics, as the direct use of PageRank for ranking scholarly articles is problematic as discussed below.
-
-%PageRank~\cite{Brin98:PageRank} has been extensively applied to the ranking of scholarly articles~\cite{Waltman2014,sayyadi09,Zhou07-CoRank,ChenXMR07}, as hyperlinks among Web pages can be easily replaced with citation relationships among articles, and citation analysis plays a key role to evaluate the importance of scholarly articles.
-However,
-
-\noindent(1) Different articles typically have different impacts in practice, and there is a need to differentiate, while PageRank essentially assumes equal impacts.
-
-%, such that each article can distribute more of its authority to those that are more influential to it.
-
-\noindent(2) The semantics of citation relationships are time-dependent, which means that citations at different periods of time may reveal different information.
-Note that this has already been exploited for scholarly article ranking~\cite{Li08TSRanking,Wang13AAAI,WalkerXKM07}, while PageRank does not consider this temporal factor at all.
-% and each individual article reaches their periods in different time
-
-\stitle{Time-Weighted PageRank (TWPageRank)}.
-Most previous work simply exploits temporal information in the form of exponential decay~\cite{Li08TSRanking,Wang13AAAI,sayyadi09,WalkerXKM07}.
-We rethink the usage of time information in terms of the impacts of scholarly articles.
-Recall that articles are categorized  into six citation patterns featured by the time when the articles reach their citation peaks~\cite{Chakraborty15}: (a) {\em PeakInit} with a single citation-count peak in the first five years (but not the first year) after publication, (b) {\em PeakMul} with distinct multiple peaks, (c) {\em PeakLate} with a single peak in at least five years   (but not the last year) after publication, (d) {\em MonDec} with monotonically decreasing citations, (e) {\em MonIncr} with monotonically increasing citations, and, (f) {\em Other} for articles whose average numbers of citations per year are less than 1.
-Though the number of citations is an indicator of the impact of an article~\cite{WangSB13,Garfield471}, its impact is time-dependent but not simply in the form of exponential decay that only considers  the case of {\em MonDec}.
-%
-To unify these distinct citation patterns and to make our ranking model succinct, we adopt that {\em the impact of an article tends to decay with time after the peak time}, as pointed out by the aging function in~\cite{WangSB13}.
-That is, the impacts of articles directly decay with time only for those in {\em MonDec}, and decay with time after the (highest) peak time for those in {\em PeakInit}, {\em PeakLate} and {\em PeakMul}, and do not decay for ones in {\em MonIncr} (which is rare).
-%Otherwise, its impact is fixed as a constant number. %, since we argue that the increment of its citations during this period is mainly due to the increase of its popularity.
-Also observe that {\em each individual article has its own peak time} as articles may reach their citation peaks in different patterns and time.
-%using the peak year in Fig.~\ref{fig-citation} is not appropriate for all articles. On the contrary, we compute a peak year for each article.
-
-\eat{
- the proportion of total citations \wrt the number of years after publication.
-%Here we use the number of citations to evaluate the impacts of articles.
-\marked{As we can see, the number of citations reaches a peak in the first 1 or 2 years, and gradually decreases after that, which also conforms to our perception of the impacts of articles~\cite{WangSB13}.
-Note that the peak time differs from one dataset to another.}
-
-According to Fig.~\ref{fig-citation}, the impact of an article does depend on time, but not simply in the form of exponential decay.
-Specifically, if an article is cited after the citation peak, its impact should decay with time.
-Otherwise, its impact is fixed as a constant number.
-%, since we argue that the increment of its citations during this period is mainly due to the increase of its popularity.
-Moreover, considering that articles might reach their citation peaks in different time, we compute {\em the peak time for each individual article}, rather than using the same citation peak for all articles.
-%using the peak year in Fig.~\ref{fig-citation} is not appropriate for all articles. On the contrary, we compute a peak year for each article.
-}
-
-\begin{figure}
-\centering
-\hspace{-4ex}
-\subfigure{\label{fig-paper}
-\includegraphics[scale=0.41]{fig/yearly-papers.eps}}
-\hspace{-4ex}
-\subfigure{\label{fig-citation}
-\includegraphics[scale=0.41]{fig/yearly-references.eps}}
-\caption{\small Statistics of scholarly articles: (1) the (logscale) percentage of papers in each year \wrt\ all papers (left) and (2) the (logscale) percentage of citations in each year \wrt\ all citations (right) on datasets \aan, \aminer and \magdata, respectively.}
-\label{fig-data-analysis}
-\vspace{-3ex}
-\end{figure}
-%[{\scriptsize a}] [{\scriptsize b}]
-
-Based on the above discussion, we propose TWPageRank that evaluates the prestige of nodes (\eg scholarly articles) in a directed graph, such that each node is attached with time information.
-It differs from PageRank by weighing the influence propagation using the {\em impact weights on edges}, which represent the relative amounts of time-dependent prestige that should be propagated from the edge sources to targets.
-%
-Formally, the impact weight on a directed edge $(u,v)$, \ie an edge from $u$ to $v$, is defined as:
+Consider $M_{ij}$ ($i,j\in[1,m]$), the submatrix of $M$ denoting the transition probability from nodes in $scc_i$ to nodes in $scc_j$.
+We have $M_{ij}=\bf{0}$ when $i>j$, since there exists no edges from nodes in $scc_i$ to $scc_j$.
+And, hence, $PR_k$ and $PR_k'$ are updated as:
 
@@
 \begin{small}
-\begin{equation} \label{eq-infl-weights}
-w(u,v)  =  \begin{cases}  \hspace{7ex} 1 & T_u <  Peak_v \\
-  e^{\sigma(T_u-Peak_v)} & T_u \geq Peak_v,
-\end{cases}
-\end{equation}
+\begin{equation*}
+\begin{split}
+PR_k=&\frac{1-d}{n} e_k+ d \sum_{j=1}^{k-1} M_{jk}^T PR_j + d M_{kk}^T PR_k^-,\\
+PR_k'=&\frac{1-d}{n}  e_k+ d \sum_{j=1}^{k-1} M_{jk}^T PR_j + d M_{kk}^T PR_k,
+\end{split}
+\end{equation*}
 \end{small}
-%
-\noindent where $T_u$ is the time of node $u$, $Peak_v$ is the peak time of node $v$ after which the impact weights of edges to $v$ decay with time, and $\sigma$ is a negative number controlling the decaying speed of the impacts.
-By default, Eq.~(\ref{eq-infl-weights}) uses years as its time granularity.
-Note that the time decaying factor $\sigma$ is introduced to provide flexibility for TWPageRank in various applications, and its value is typically within a small interval, \eg $[-2,0]$, such that $w(u,v)$ does not decay when $\sigma=0$ and already decays more than a half per year when $\sigma=-1$.
-%For the sake of completeness, we further set $w(u,v)$ to $0$ if there does not exist an edge from $u$ to $v$ in the graph.
+\noindent
+respectively, where $e_k=[1]_{|scc_k|\times 1}$.
+%, and, obviously, $\Delta_k^+=PR_k^+-PR_k=d M_{kk}^T \Delta_k^-$.
 
-For scholarly article ranking, $T_u$ is the publication time of article $u$ and $Peak_v$ should be ideally set to the time when article $v$ has the highest impact.
-Basically, it could simply be the year when article $v$ obtains the largest number of citations.
-However, recent work reveals that the volume of scientific publications and the number of citations grow exponentially with time~\cite{Dong2017KDD,BornmannM15}.
-We also collect and report the volume and citation statistics on three scholarly datasets in Fig.~\ref{fig-data-analysis}, which verifies the exponential distribution.
-Hence, we adopt the {\em scaled} number of citations $\Psi_v^{(t)}=\Phi_v^{(t)} / \log Z^{(t)}$ such that $\Phi_v^{(t)}$ and $Z^{(t)}$ are the number of citations of article $v$ at year $t$ and the total number of citations at year $t$, respectively.
-The peak time $Peak_v$ is the time that maximizes $\Psi_v^{(t)}$.
-%(\aan, \aminer and \magdata)
-% since scholarly data is dynamic and continuously growing
-%, and the increased number of references of each article over time
-%Recent work observes that the volume of scientific publications doubled every 12 years between 1900 and 2015~\cite{Dong2017KDD}.
-It is not surprising that the number of references also grows exponentially~\cite{BornmannM15}.
-
-The update rule of TWPageRank is:
+Given these, the sum of changes between $PR'$ and $PR$ is:
 
@@
 \begin{small}
-\begin{equation}\label{eq-twpr}
-PR(v)=d\sum_{(u,v)\in E} \frac{w(u,v)PR(u)}{W(u)}+\frac{1-d}{n},
-\end{equation}
+\begin{equation*}
+\begin{split}
+||PR'-PR||_1 & =\sum_{k=1}^m ||PR_k'-PR_k||_1 = \sum_{k=1}^m ||d M_{kk}^T \Delta_k||_1 \\
+& \le d\sum_{k=1}^m ||\Delta_k||_1 < \epsilon,
+\end{split}
+\end{equation*}
 \end{small}
-where $PR(u)$ and $PR(v)$ are the TWPageRank scores of $u$ and $v$, respectively, $E$ is the set of edges, $W(u)=\Sigma_{v} w(u,v)$ is the sum of the impact weights on all edges from $u$, $n$ is the number of nodes and $d$ is a damping parameter in $(0, 1)$.
-By Eq.~(\ref{eq-twpr}), we can see that prestige is updated based on the impact weights, not equally distributed.
+\noindent
+based on the fact that the row sums of $M_{kk}$ are always $\le 1$. %less than or equal to 1.
 
-% in Eq.~(\ref{eq-twpr}) into
-Correspondingly, the matrix form of the update rule is:
+Moreover, $||PR'-PR||_1 = ||PR' - PR^* + PR^* -PR||_1 = ||d M^T (PR-PR^*)||_1 + ||PR-PR^*||_1<\epsilon$, which gives $||PR-PR^*||_1<\epsilon$ and proves the conclusion.
+\end{proofS}
+
+\subsection*{2. Proof of Proposition \ref{lemma-inc-topo}}
+$O^+=\Delta O/O$ is indeed a valid topological order of the block-wise graph of $G^+$.
+
+\vspace{.5ex}
+\begin{proofS}
+Let $G'_\Delta(V'_\Delta, E'_\Delta)$ be the block-wise graph of $G^+[\Delta V]$; further let $E'_c$ denote the set of crossing edges from $V'_\Delta$ to $V'$.
+It suffices to show that for each $(u,v)\in E'\cup E'_\Delta \cup E'_c$, $u$ comes before $v$ in $O^+$,
+which obviously holds (a) for  $E'\cup E'_\Delta$ as $O$ and $\Delta O$ are topological orders of $G'$ and $G'_\Delta$, respectively, and (b) for $E_{c}'$ as nodes in $G'_\Delta$ come before nodes in $G'$.
+\end{proofS}
+
+\subsection*{3. Proof of Theorem \ref{lemma-subgraphA}}
+The TWPageRank vector $PR^+$ returned by~\inctwprscc converges such that $||PR^+-PR^{*}||_1 < \epsilon$, where $PR^{*}$ is the convergent TWPageRank vector.
+
+\vspace{.5ex}
+\begin{proofS}
+Assume a topological order $v_1'/\dots/v_{l}'$ of block-wise graph $G^+{'}$ where $l=|O^+|$.
+We prove that the sum of change of $PR^+(v)$ where $v\in scc_k$ is no more than $\epsilon\cdot\frac{|scc_k|}{|V^+|}$ for $scc_k$ corresponding to $v_k'$ ($k\in [1,l]$) by induction.
+Note that it obvious holds for $scc_k$ belonging to $G_B$ and $G_C$ by algorithm~\inctwprscc.
+
+\noindent(1) When $k=1$, it holds since $scc_1$ belongs to $G_C$;
+
+\noindent(2) Assume that it holds when $1\le k\le q$. We then show that it also holds for $k=q+1$. It suffices to show the case when $scc_k$ belongs to $G_A$. Recall that:
 
 \vspace{-1ex}
-\begin{small}
-\begin{equation}
-\label{eq-twpr-update}
-PR^{(t)}=d M^T  PR^{(t-1)} + (1-d) e/n.
-\end{equation}
-\end{small}
-%
+\begin{scriptsize}
+\begin{equation*}
+\begin{split}
+PR(v) & =  d \sum_{(u,v)\in E_i} M_{u,v} PR(u) + d \sum_{(u,v)\in E_a} M_{u,v} PR(u) +  \frac{1-d}{n},\\
+PR^+(v) & =  d \sum_{(u,v)\in E^+_i} M^+_{u,v} PR^+(u) + d \sum_{(u,v)\in E^+_a} M^+_{u,v} PR^+(u) +  \frac{1-d}{n^+}.
+\end{split}
+\end{equation*}
+\end{scriptsize}
 \noindent
-Here $PR^{(k)}$ is the TWPageRank vector after $k$ iterations,  $M$ is the transition matrix such that $M_{u,v}=w(u,v)/W(u)$ and  $e$ is an $n$-dimensional all-one vector $[1]_{n\times1}$.
+Consider $scc_k$ belonging to $G_A$ and node $v\in scc_k$.
+We have $\{(u,v)|(u,v)\in E_i\}$ = $\{(u,v)|$ $(u,v)\in E^+_i\}$, $\{(u,v)|(u,v)\in E_a\}$ = $\{(u,v)|(u,v)\in E^+_a\}$ and $M_{u,v}=M^+_{u,v}$ when $(u,v)\in E_i\cup E_a$.
+Also note that $PR^+(u)=\frac{n}{n^+}PR(u)$ when $(u,v)\in E_a$ according to algorithm~\inctwprscc.
+Let $PR_{k,0}$, $PR_{k,1}$, $\dots$, $PR_{k,t}$ be the convergent sequence of TWPageRank vectors for $scc_k$ computed by algorithm \twprscc on $G$.
+Then $\frac{n}{n^+}PR_{k,0}$, $\frac{n}{n^+}PR_{k,1}$, $\dots$, $\frac{n}{n^+}PR_{k,t}$ is a valid convergent sequence of TWPageRank vectors for $scc_k$ computed by algorithm \inctwprscc on $G^+$ given the initial TWPageRank vector $\frac{n}{n^+}PR_{k,0}$.
+Hence, the sum of changes of $PR^+(v)$ where $v\in scc_k$ is $\frac{n}{n^+}||PR_{k,t}-PR_{k,t-1}||_1 < \epsilon\cdot\frac{|scc_k|}{|V^+|}$.
 
-%We next present the convergence  of TWPageRank as follows.
-The linear system in Eq.~(\ref{eq-twpr-update}) is equivalent to {\em irreducible} and {\em aperiodic} Markov chains~\cite{CorsoGR05}, which guarantees the following.
+Combining with Corollary \ref{prop-prscc}, we have the conclusion.
+\end{proofS}
 
-\begin{prop}
-\label{prop-converg}
-TWPageRank converges to a unique  vector on any graph, regardless of the initial vector.
-\end{prop}
-
-\eat{%%%%%%%
-\begin{proof}
-It is known that a sequence of vectors $x^{(k)}$ such that $x^{(k+1)}=A\cdot x^{(k)}+b$ (where $k=0,1,\dots$) converges to a unique vector $x^*$,  regardless of the initial vector $x^0$, if and only if $\rho(A)<1$~\cite{kelley1999iterative}, where $\rho(A)$ is the spectral radius of matrix $A$.
-Hence, it suffices to show $\rho(d\cdot M^T) < 1$ by Eq.~(\ref{eq-twpr-update}).
-
-As the column sums of $d\cdot M^T$ are all less than or equal to $d$, $||d\cdot M^T||_1 \le d$ where $||d\cdot M^T||_1$ is the 1-norm of matrix $d\cdot M^T$ and is defined as the maximum absolute column sum of $d\cdot M^T$.
-We then have $\rho(d\cdot M^T) \le ||d\cdot M^T||_1 \le d < 1$, as the spectral radius of a matrix is always no more than its consistent matrix norms~\cite{spe-radius}, \eg $||\cdot||_1$, which gives the conclusion.
-\end{proof}
-}
-
-%\stitle{Remarks}.
-Note that Eq.~(\ref{eq-twpr}) is indeed a general update rule of Weighted PageRank~\cite{Xing04:WPR,Ding11}, and the name of Time-Weighted PageRank comes from the use of time information of citations in the initial impact weight  $w(u,v)$ of Eq.~(\ref{eq-infl-weights}).
-
-%\vspace{-1ex}
-%\stitle{Remarks}.
-%\markedb{
-%The goal of our TWPageRank is to change node values, \ie importance.
-One may wonder why not directly change node values.
-However, it is difficult to handle as importance does not have a clear and closed-form definition and it may also cause problems for convergence.
-%To our knowledge, there is no related work on changing node weights and it is yet unclear how to handle it.
-Finally, we use impact weights to achieve the goal since %importance is essentially propagable through edges and it is also fair for all nodes.
-%}
+\section*{APPENDIX B: Detailed of Model}
+\label{sec-exp-app}
 
@@
 We next introduce the details of the three components.
+
+\begin{figure}[tb!]
+\centering
+%\includegraphics[scale=0.15]{fig/framework.eps}
+\includegraphics[scale=0.35]{fig/example-graph.eps}
+\vspace{-1ex}
+\caption{\small Ranking model \ensemblerank} \label{fig-rankmodel}
+\vspace{-3ex}
+\end{figure}
+
+\begin{figure}[tb!]
+\centering
+%\includegraphics[scale=0.15]{fig/framework.eps}
+\includegraphics[scale=0.35]{fig/example-ranking.eps}
+\vspace{-1ex}
+\caption{\small Ranking model \ensemblerank} \label{fig-rankmodel}
+\vspace{-3ex}
+\end{figure}
 
@@
 However, it is also possible to learn a discriminative model that directly optimizes certain loss functions for ranking, similar to \cite{Richardson06:BPR} for ranking Web pages.
-
-%\subsection{Framework}
-%\label{subsec-framework}
-
-%Our ensemble enabled ranking model~\ensemblerank is illustrated in Fig.~\ref{fig-rankmodel}, which contains three distinct ensembles derived from academic graph data, \ie the citation ensemble, venue ensemble and author ensemble.
-The citation ensemble directly uses TWPageRank, while the other two are partially based on TWPageRank.
-Moreover, the citation ensemble also helps to derive the venue ensemble and author ensemble.
-These ensembles are further assembled to produce the final ranking.
-
-%As illustrated in Fig.~\ref{fig-rankmodel}, external data is also exploited in \ewpr. How to collect and use external data will be introduced in the coming section.
-
-\eat{
-\stitle{Remarks}.
-Traditional PageRank equally distributes the prestige of nodes, and PageRank based models suffer from the problem that older articles are preferred since they have accumulated a large number of citations~\cite{Li08TSRanking}, and TWPageRank based models alleviate the problem to a certain degree by lowering the impact weights of articles when they are cited after their peak time, \ie $T_u\geq Peak_v$.
-We further propose the venue and author ensembles to improve the ranking accuracy.
-}
-
-%\stitle{Remarks}.
-%Recall that articles in our data are also associated with affiliation information.
-Following the way of the venue or author ensemble, we can derive another ensemble, \ie affiliation ensemble.
-However, we argue that the use of affiliation ensemble may have negative effects since the correlation between the importance of an article and the average authority of its affiliation(s) is not as strong as others such like authors and venues.
-As shown by the experimental study in Section~\ref{sec-exp},  the incorporation of the affiliation ensemble impairs the ranking accuracy.
-Hence, we choose not to use the affiliation ensemble in our model.
-
-%our method used for author ensemble is both lightweight and effective, as will be shown in the experimental study.
-
-%Two methods are used to evaluate the authority of venues and authors, respectively.
-We point out that the ensembles are quite flexible to the selection of these methods, and others may also be incorporated in the ensembles if appropriate.
-
-\eat{
-\subsection{Dealing with Missing Data}
-\label{subsec-impl}
-
-Data quality is one of the most challenging issues in large scale data management, especially for data from open domains and multiple sources, \eg the Microsoft Academic Graph (MAG)~\cite{Sinha15:MAG}.
-The early version of MAG has $120$ million scholarly articles, among which we find that there are about $73$ million articles without references and about $77$ million ones without venues.
-The ranks of those articles with missing information are underestimated by our model \ewpr, since ensembles assign the minimum scores to articles.
-As a result, data missing seriously impairs the ranking accuracy.
-
-As for references and venues, the later are easier to obtain, and each filled venue can have a direct and substantial impact on the article ranking, \ie $R_v(u)$ of Eq.~(\ref{eq-ensemble}).
-In contrast, a filled reference only has an indirect and slight impact.
-Hence, we decide to use external data to fill in missing venues.
-
-%\subsection{Data Collecting}
-%\label{subsec-datacraw}
-\stitle{Data collecting}.
-The raw external data is collected from publicly available Digital Libraries, such as IEEE Xplore ({\footnotesize http://ieeexplo-re.ieee.org/gateway/}),  PubMed ({\footnotesize http://www.ncbi.nlm.nih.gov/pub-med/}) and DBLP ({\footnotesize http://dblp.uni-trier.de/db/}).
-In total, we collect $2.8$ million articles with venue information as our external data, in which there are $57,000$ different venues.
-
-%\subsection{Data Preprocessing}
-%\label{subsec-dataprep}
-\stitle{Data preprocessing}.
-The venues in MAG are well processed, and are replaced by their series names.
-For example, {\em ``9th International Conference on Web Search and Data Mining, 2016''} is replaced with {\em ``Web Search and Data Mining''}.
-This makes it hard to directly link with the collected raw venue names.
-Hence, we preprocess raw venue names for the simplification of subsequent venue linking.
-%
-We first remove stop words such as {``on''} and common words like {``Conference''}, as well as years and some special characters from collected raw venue names.
-Then the same venues are merged, and the number of different venue names is reduced to $42,000$.
-
-%\subsection{Data Linking}
-%\label{subsec-datamap}
-\stitle{Data linking}.
-The final and also the most important step of filling missing venue information is to link each collected venue name to an existing one in MAG.
-Intuitively, linking based on name similarity is the most effective way such that two venues are linked if their names bear high similarity.
-We exploit the Jaro metric to evaluate the name similarity, which is based on the number and order of the common characters between two strings, and obtains good results in tasks such as record linkage and name matching~\cite{Cohen03strcompa}.
-Formally, a collected venue name is linked to an existing one in MAG if their Jaro similarity exceeds a pre-define threshold.
-
-However, such a threshold is nontrivial to determine in practice.
-A high threshold can guarantee the accuracy of linked pairs, while only a tiny proportion of collected venue names are linked.
-On the other hand, a low threshold increases the number of linked pairs, which, in the same time, also introduces many errors.
-In order to reach a good balance between the number of linked pairs and the accuracy, we propose to combine another constraint on topic similarity of venues for linking, and only weaker filter conditions need be used in both constraints.
-
-In MAG, fields of study (FOS) represent research topics of articles, such as {\em Web pages}, and {\em language technology}.
-Hence, we use FOS to evaluate the topic similarity of two venues.
-There are about $54,000$ FOS in MAG and most articles are assigned with two or three FOS.
-Let the set of FOS of each venue be the union of the sets of FOS of articles published in that venue.
-And the topic similarity of two venues based on FOS is defined as:
-\begin{small}
-\begin{equation} \label{eq-fos}
-TS(s,t)=({|F_s\bigcap F_t|})/{\sqrt{|F_s|\cdot|F_t|}},
-\end{equation}
-\end{small}
-\noindent in which $s$ and $t$ are two venues, and $F_s$ and $F_t$ are the sets of FOS of $s$ and $t$, respectively.
-
-When we link a collected venue name, it is directly linked to the most similar one in terms of name similarity, if their Jaro similarity exceeds a high threshold $\lambda$.
-Otherwise, we first use the topic similarity constraint to select several candidates in MAG, \ie venues whose topic similarities with the collected venue exceed a threshold $\theta$.
-Intuitively, these candidates are in the similar fields of the collected one.
-We then select the most similar candidate in terms of name similarity as its linked venue, if their Jaro similarity exceeds another threshold $\phi$.
-Hence, the collected venue is linked to the one to which it is similar in terms of both topics and names.
-
-In our model \ewpr, threshold $\lambda$ is set to $0.95$, while thresholds $\theta$ and $\phi$ need not be very high, which are $0.5$ and $0.7$, respectively.
-Finally, $6,000$ among the $42,000$ collected venues are linked, resulting in $340,000$ (about $12\%$) articles with enriched venue information.
-Note that a majority of the collected venue names are not valid venues, such as booktitles and names of workshops, and cannot be linked to any one in MAG.
-}

### 2017-12-31 icde/revision/sec-exp-app.tex

\eat{
\begin{figure*}[tb!]
\vspace{-2ex}
\begin{minipage}[t]{0.5\textwidth}
\begin{center}
\subfigure[{\scriptsize TWPageRank (batch vs. inc.)}]{\label{fig-aminer-time2}
\includegraphics[scale=0.38]{./exp/AMiner_time_twpr.eps}}
%\quad\quad
\hspace{-0.5ex}
\subfigure[{\scriptsize Comparison of ranking algorithms}]{\label{fig-aminer-time1}
\includegraphics[scale=0.38]{./exp/AMiner_time.eps}}
\end{center}
\vspace{-5ex}
\caption{\small Efficiency tests on \aminer}
\label{fig-aminer-time}
\end{minipage}
\hspace{-2ex}
\begin{minipage}[t]{0.5\textwidth}
\begin{center}
\subfigure[{\scriptsize \aminer}]{\label{fig-aminer-time-sigma}
\includegraphics[scale=0.38]{./exp/AMiner_sigma_time.eps}}
%\quad\quad
\hspace{-0.5ex}
\subfigure[{\scriptsize \magdata}]{\label{fig-mag-time-sigma}
\includegraphics[scale=0.38]{./exp/MAG_sigma_time.eps}}
\end{center}
\vspace{-5ex}
\caption{\small Efficiency tests: varying $\sigma$}
\label{fig-time-sigma}
\end{minipage}
\vspace{-1ex}
\end{figure*}
}

\newcommand{\graphscaleexpapp}{0.262}
\newcommand{\graphmarginexpapp}{-2ex}
%%% all in 1 Figure
\begin{figure*}[tb!]
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
\subfigure[{\scriptsize \aan}]{\label{fig-aan-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/AAN-para-recm.eps}}
%\quad\quad
\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \aminer}]{\label{fig-aminer-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/AMiner-para-recm.eps}}
%\quad\quad
\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \magdata}]{\label{fig-mag-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/MAG-para-recm.eps}}
\\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-2ex}
%\hspace{-10ex}
\subfigure[{\scriptsize \aan}]{\label{fig-aan-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/AAN-para-fcita.eps}}
%\quad\quad
\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \aminer}]{\label{fig-aminer-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/AMiner-para-fcita.eps}}
%\quad\quad
\hspace{\graphmarginexpapp}
\subfigure[{\scriptsize \magdata}]{\label{fig-mag-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/MAG-para-fcita.eps}}
\end{center}
\vspace{-3.5ex}
\caption{\small Accuracy tests with \recom ((a)--(c)) and \fcita ((d)--(f)): varying aggregating parameters $\alpha$ and $\beta$}
\label{fig-ab}
\vspace{-3ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[tb!]
%\vspace{-2ex}
\begin{center}
\begin{small}
\vspace{1ex}
\begin{tabular}{|c|c c c|c c c| c|}
\hline
{\bf Datasets} & {\bf C} & {\bf V} & {\bf A} & {\bf CV} & {\bf CA} & {\bf VA} & {\bf CVA} \\
\hline \hline
% \recom
\aan & 0.746 & 0.616 & 0.647 & 0.806 & 0.760 & 0.746 & {\bf \ 0.810\ } \\
\aminer & 0.783 & 0.576 & 0.664 & 0.805 & 0.798 & 0.735 & {\bf 0.815} \\
\magdata & 0.669 & 0.534 & 0.552 & 0.693 & 0.670 & 0.640 & {\bf 0.694} \\ \hline
% \ficta
\aan & 0.708 & 0.566 & 0.744 & 0.778 & 0.796 & 0.755 & {\bf 0.804} \\
\aminer & 0.690 & 0.733 & 0.761 & 0.854 & 0.839 & 0.794 & {\bf 0.857} \\
\magdata & 0.761 & 0.657 & 0.737 & 0.835 & 0.842 & 0.753 & {\bf 0.849} \\
\hline
\end{tabular}
\end{small}
\end{center}
\caption{\small Accuracy tests on using different components with \recom (rows 2--4) and \fcita (rows 5--7), in which letters C, V and A stand for citation, venue and author components, respectively.}
\label{tab-inc}
\vspace{-6ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

\vspace{-1ex}
\section*{APPENDIX A: Detailed results of Exp-4.3}
\label{sec-exp-app}

%\subsection*{1. Detailed results of Exp-4.3} %$\alpha$ and $\beta$ (detailed)

%We present detailed results of {\em Exp-4.3}, which are omitted earlier due to the space constraints, \ie the impacts of aggregating parameters $\alpha$ and $\beta$ on effectiveness.

\eat{
\etitle{Exp-4.1}. To evaluate the impacts of the time decaying factor $\sigma$, we varied $\sigma$ from -1.6 to -0.4, while fixed $Y_s$ to default values, $b=+\infty$ and $dif=1$. The efficiency results are reported in Fig.~\ref{fig-time-sigma}.
Note that the running time of algorithm \batensemble is different on \recom and \fcita because of the different splitting year $Y_s$.

When varying $\sigma$, the running time of \batensemble is almost stable on both \aminer and \magdata using \fcita and \recom. Indeed, the running time using (\fcita, \recom) only varies (1.4\%, 0.5\%) on \aminer, and (2.1\%, 2.2\%) on \magdata, on average, respectively.
}

\etitle{Exp-4.3}.
To evaluate the impacts of aggregating parameters $\alpha$ and $\beta$, we varied $\alpha$ and $\beta$ at the granularity of 0.01.
The detailed results are reported in Fig.~\ref{fig-ab}, where the parameters selected earlier and their corresponding \PairAcc are marked with $*$.

When varying $\alpha$ and $\beta$, the \PairAcc of \ensemblerank changes gently, as shown in Fig.~\ref{fig-ab}.
The optimal \PairAcc is obtained within a single region, rather than a complex collection of optimal regions.
%
Moreover, the \PairAcc keeps at a high level within a certain ($\alpha$, $\beta$) combination space around the optimal region, as shown in Fig.~\ref{fig-ab}.
%For instance, consider a square of length 0.3, which covers 8.5\% of the parameter combination space. The fraction of parameters such that the \PairAcc is no worse than 1\% of the corresponding \PairAcc with marker $*$ is (73\%, 94\%) on \aan, (96\%, 87\%) on \aminer and (83\%, 95\%) on \magdata, using (\recom, \fcita), respectively.
%
Further, the optimal parameters on the same sets of ground-truth are very similar for (\aan, \aminer and \magdata), indicating that the setting of $\alpha$ and $\beta$ can be easily transferred across different datasets.
To conclude, \ensemblerank is very robust to parameters $\alpha$ and $\beta$, and it is quite flexible for choosing proper values of parameters $\alpha$ and $\beta$.

Moreover, varying $\alpha$ and $\beta$ also enables to verify the effectiveness of importance assembling from different components, whose results are reported in Table~4.
The ranking based on all components consistently performs the best, which, using \recom and \fcita, improves the \PairAcc over using components (C, V, A, CV, CA, VA) by (6.33\%, 19.4\%, 16.3\%, 0.33\%, 4.97\%, 6.33\%) and (9.58\%, 23.8\%, 5.98\%, 2.56\%, 0.74\%, 4.82\%) on \aan, (3.21\%, 23.9\%, 15.1\%, 0.93\%, 1.66\%, 7.97\%) and (16.8\%, 12.5\%, 9.60\%, 0.34\%, 1.87\%, 6.37\%) on \aminer, and ( 2.43\%, 16.0\%, 14.2\%, 0.05\%, 2.38\%, 5.38\%) and (8.89\%, 19.3\%, 11.2\%, 1.43\%, 0.77\%, 9.65\%) on \magdata, respectively.
%Here the letters C, V and A stand for citation component, venue components and author component, respectively.

### 2017-12-31 icde/revision/sec-incAlg.tex

@@
 %%% affected/unaffected division
-\vspace{-1ex}
+\vspace{-.5ex}
 \stitle{Analysis of affected and unaffected areas}.
@@
 \stitle{Time complexity analysis of the incremental algorithm}.
-By the analyses above, the time complexity of \incensemble is the same as \batensemble, except that \incensemble saves $O(|E^c_A\cup E^c_{AB}|)$ and $O(|E^v_A\cup E^v_{AB}|)$ time when computing TWPageRank  on the updated citation and venue graphs at an extra space cost for the affected/unaffected division and the copy of original edge weights.
+By the analyses above, the time complexity of \incensemble is the same as \batensemble, except that \incensemble saves $O(|E^c_A\cup E^c_{AB}|)$ and $O(|E^v_A\cup E^v_{AB}|)$ time when computing TWPageRank  on the updated citation and venue graphs with an extra space cost for the affected/unaffected division and the copy of original edge weights.
 
@@
 (c) It saves $O(|E^c|)$ time when computing popularity of articles, which accounts for more than 89\% of total;
-And, finally, (d) It is likely to compute TWPageRank scores on $V^c_B$ and $V^v_B$ with less iterations.
+Finally, (d) it is likely to compute TWPageRank scores on $V^c_B$ and $V^v_B$ with less iterations.
 

### 2017-12-31 icde/revision/sec-related.tex

@@
 PageRank \cite{Brin98:PageRank} and its extensions have been extensively used for citation analyses \cite{Waltman2014}.
-While PageRank equally propagates scores along outlinks, Weighted PageRank extends PageRank by distributing scores based on certain criteria such as popularity of pages~\cite{Xing04:WPR} or authority of authors~\cite{Ding11}.
+While PageRank equally propagates scores along outlinks, Weighted PageRank extends PageRank by distributing scores based on certain criteria such as popularity of pages~\cite{Xing04:WPR} or authority of authors \cite{Ding11}.
 %Both these approaches fail to capture the time-dependent characteristics, a key factor for scholarly article ranking.
@@
 Ensemble methods use multiple learners to obtain better performance than could be obtained from a constituent learner alone~\cite{zhihua-book}.
-In this work, we leverage  importance assembling  to produce better and more robust results for scholarly article ranking~\cite{zhihua-book,wsdmcup,DuanAMHH16}.
+In this work, we leverage  importance assembling  to produce better and more robust ranking for scholarly articles~\cite{zhihua-book,wsdmcup,DuanAMHH16}.

### 2018-01-01 icde/revision/Response.tex

@@
 
-Dear Reviewers,
+Dear Meta-Reviewer and Reviewers,
 
-This is the response letter regarding the revised version of our submission to IEEE International Conference on Data Engineering 2018, \emph{Query Independent Scholarly Article Ranking}.
+We have revised our submission, \emph{Query Independent Scholarly Article Ranking}, to IEEE International Conference on Data Engineering 2018.
 
@@
 Below please find our detailed responses to the comments by the referees.
+
+\line(1,0){500}
+
+\textbf{Response to the comments of Meta-Reviewer.}
+
+\textbf{[M1]} \emph{The reviewers see some merit in the approach, but they have also raised important concerns regarding the technical depth and novelty of the approach.
+In particular, the authors use known techniques for an application (scientific article ranking) for which there is abundance of previous work (it even has its own field, called scientometrics, or  bibliometrics).}
+
+We do believe that there are technical contributions: (1) An ensemble based ranking model (a great effort needs to be paid to develop such a ranking model);  (2) An incremental algorithm designed for dynamic scholarly article ranking in the general setting, which is designed for the block-wise algorithm of Time-Weighted PageRank, and is based on the citation characteristics.
+These have never been exploited in existing studies.
+That is, we are not simply using known techniques for an application.
+
+We also believe that our ensemble based ranking model and the citation statistics revealed in our study have their own interests to the researchers in the field of scientometrics or  bibliometrics.
+
+ We have clarified these in our paper. Thanks for pointing these out!
+
+\textbf{[M2]} \emph{In revising their paper, the authors should try to address all reviewers¡¯ comments and in particular address the required changes for revision by Reviewer 1.}
+
+Yes, we have addressed these. Please refer to our responses below.
 
@@
 More specifically, these parameters make our model be able to fit to the various ranking scenarios.
-As will be seen in the experiments, our model performs well in two reasonable ranking scenarios by using quite different aggregating parameters, and, moreover, these parameters are indeed quite flexible to choose within a certain range.
-%
-Note that a) the optimal \PairAcc is obtained within a single region, b) the \PairAcc keeps at a high level within a certain ($\alpha$, $\beta$) combination space around the optimal region, and c) the optimal parameters on the same set of ground-truth are very similar across different datasets (Exp-5.3, page 10).
+As shown in the experiment study (Exp-1 and Exp-2), our model performs well in two reasonable ranking scenarios by using quite different aggregating parameters.
+
+Moreover, these parameters are indeed quite flexible to choose within a certain range (Exp-5.3, page 10).
+Note that (a) the optimal \PairAcc is obtained within a single region, (b) the \PairAcc keeps at a high level within a certain ($\alpha$, $\beta$) combination space around the optimal region, and (c) the optimal parameters on the same set of ground-truth are very similar across different datasets.
 
@@
 %
-This work focuses on {\em query independent ranking} because of its wide application in modern scholarly search engines such as Google Scholar, Semantic Scholar and Microsoft Academic Search.
+This work focuses on {\em query independent ranking} because of its wide application in modern scholarly search engines such as Google Scholar, Semantic Scholar and Microsoft Academic Search (as we discussed in the first two paragraphs in Section 1).
 %
-And it can be easily extended to {\em query dependent ranking}.
-Our ranking can serve as an indicator of the importance of items, and, given a specific query, it can either be directly used to rank a subset of relevant items or combine with any relevance scores for ranking.
-%
+The combination of query dependent ranking and query independent ranking  is well known, e.g., typical search engines such as Google : keyword search (query dependent ranking) is combined with Pagerank (query independent ranking).
+Our ranking can serve as an indicator of the importance of items, and, given a specific query, it can either be directly used to rank a subset of relevant items or combine with any relevance scores for ranking along the same lines as keyword search.
+
 The extension in {\em other heterogeneous information networks} is currently unclear, since the TWPageRank is designed based on a deep analysis of scholarly articles (left column, page 2).
@@
 An alternative way to do that is to directly change node values.
-However, it is difficult to handle as importance does not have a clear and closed-form definition and it may also cause problems for convergence.
-To our knowledge, there is no related work on changing node weights to achieve this goal and it is yet unclear how to handle it.
-Finally, we use iterations with impact weights since importance is essentially propagable through edges and it is also fair for all nodes.
+However, it is difficult to handle as importance does not have a clear and closed-form definition.
+It may also cause problems for convergence.
+To our knowledge, there is no related work on changing node weights to achieve this goal, and it is indeed unclear how to handle it.
+% Finally, we use iterations with impact weights since importance is essentially propagable through edges and it is also fair for all nodes.
 
@@
 
-Figure 1 shows the logscale percentage of the number of articles/citations of each year which grows exponentially with time, instead of the number of citations (\ie impacts) of individual articles.
+Figure 1 shows the logscale percentage of the number of articles/citations of each year that grows exponentially with time, instead of the number of citations (\ie impacts) of individual articles.
 %We have highlighted it in the revised version (Figure 1, page 2).
@@
 To unify these distinct citation patterns and to make our ranking model succinct, we adopt the claim that the impact of an article tends to decay with time after the peak time.
-Moreover, the aging function in [17] exploits a log-normal survival probability which also only decays with time after the citation peak.
+Moreover, the aging function in [17] exploits a log-normal survival probability that also only decays with time after the citation peak.
 %(it increases before reaching the peak since it aims to predict the number of citations instead of impacts of articles).
@@
 The {\em PeakMul} pattern is originally defined in [18]:  the height of a peak should be at least 75\% of the maximum peak height, and two consecutive peaks should be separated by more than two years.
-In our work, we unify the five patterns and only use the highest peak time which has been formally defined in Section II-A (para 1, left column, page 3).
-Also note that: a) [18] allows multiple peaks to exist for an article while we only consider the highest peak, and b) [18] uses the original numbers of citations to compute peaks and we use the scaled numbers of citations \wrt the total number of citations of all articles at each year.
+In our work, we unify the five patterns, and we only use the highest peak time that has been formally defined in Section II-A (para 1, left column, page 3).
+Also note that: (a) [18] allows multiple peaks to exist for an article while we only consider the highest peak, and (b) [18] uses the original numbers of citations to compute peaks, and we use the scaled numbers of citations \wrt the total number of citations of all articles at each year.
 
@@
 
-Yes, we agree that distributed processing is an important while independent problem which we have already placed in our future work (Conclusions, page 12). %Thanks for the suggestion!
+Yes, we agree that distributed processing is an important way for large scholar graphs.
+But this topic is beyond the reach of this study, and we plan to do this in our future work (Conclusions, page 12).
+Thanks for the suggestion!
 
@@
 
-Yes, we have revised our paper as suggested (right column, page 1 \& Table I, page 5).
+Yes, we have revised our paper as suggested (right column, page 1 \& Table I, page 5). Thanks!
 %Thanks for the suggestion!
@@
 
-\textbf{Response to the comments of META-REVIEWER.}
-
-\textbf{[D1]} \emph{The reviewers see some merit in the approach, but they have also raised important concerns regarding the technical depth and novelty of the approach.
-In particular, the authors use known techniques for an application (scientific article ranking) for which there is abundance of previous work (it even has its own field, called scientometrics, or  bibliometrics).}
-
-The techniques used in our work are not simply existing techniques:
-a) an importance assembling based ranking model is still novel in the field of scientometrics and bibliometrics and we further consider the efficient batch and dynamic computation problem which rarely has been exploited in these two fields, b) an incremental algorithm for block-wise time-weighted PageRank computation that makes use of the particular properties of the scholarly graphs, and c) a thorough experimental study.
-That is, although bearing similarities, this paper certainly has its contributions to the technical part and brings certain novelty for the task.
-
-Please also refer to our response to R2W1\&D1 for more details.
-
 \line(1,0){500}

### 2018-01-01 icde/revision/Response.tex

@@
 
-Yes, we agree that more examples (especially on how to generate components from scholarly data) will make our paper easier to understand.
-Due to the space limitation, we choose to add the examples in the extended version.
+Yes, thanks for the nice suggestion! Due to the space limitation, we have added the examples to the full version (https://hurenjun.github.io/SARank-full.pdf).
 
@@
 
-We have reported the memory costs in a new set of experiments, \ie Exp-4 (page 10).
-On the large \aminer and \magdata, algorithm \pagerank uses the least memory, followed by algorithms \futurerank, \ensemblerank and \hhgrank, respectively.
-%
-The memory used by \pagerank is even less than the size of the academic graph data as it is based on the citation graph only.
-%
-Our \ensemblerank model costs more memory than \futurerank since it also combines article-venue relationships ignored by \futurerank and it assembles multiple rankings based on prestige and popularity.
-However, our \ensemblerank model is still more memory-efficient than \hhgrank.
-%
-To conclude, the \ensemblerank model uses reasonable amount of  memory to achieve the better effectiveness.
-
+We have reported the memory costs in a new set of experiments, \ie Exp-4 (page 10). Thanks for the suggestion!
 %that on the largest \magdata, (\futurerank, \ensemblerank) cost (16.42GB, 49.42GB) memory when $Y_s=2015$, and \hhgrank costs 61.37GB memory when $Y_s=2014$.
@@
 
-Yes, we add the volume statistics (the number of articles published at each year) of the growing data  in Figure 1.
+Yes, we  have added the volume statistics (the number of articles published at each year) of the growing data in Figure 1. Thanks!
 
@@
 
-Yes. We have discussed the correlation between our work and temporal graphs and included necessary references in Related Work.
-
-%******************* meta-reviewer ***********************************************
-\line(1,0){500}
+Yes.
+We have discussed the correlation between our work and temporal graphs, and cited necessary references (e.g., P.
+Holme and J.
+Saramaki, ¡°Temporal networks,¡± Physics Reports, vol.
+519, no.
+3, pp.
+97 ¨C 125, 2012) in related work (Section VI).
 

### 2018-01-01 icde/revision/Response.tex

@@
 
-\textbf{[R2W1]} \emph{While practically the paper makes a good case about the particular application domain and its contributions there, the paper lacks technical depth.} \\
-\textbf{[R2D1]} \emph{There seem to be two ``contradictory" sides to this paper.
+\textbf{[R2W1\&D1]} 
+\emph{While practically the paper makes a good case about the particular application domain and its contributions there, the paper lacks technical depth.} \\
+\emph{There seem to be two ``contradictory" sides to this paper.
 From one side, this is a great ``applications" paper where existing techniques and some good intuition is used to get better results into an existing (practical) problem.
@@
 
-We thank the reviewer for appreciating the practice merit of our work which is drawn from an important and practical problem.
+Yes, our work comes from a practical need from industries. We thank the reviewer for appreciating this merit of our work.
 
-%And we believe this paper also stands from research and technique perspective.
-And We think that the techniques proposed also have their own interests: a) An importance assembling based ranking model itself is hard to define and tune, b) an incremental algorithm for block-wise time-weighted PageRank computation that makes use of the particular properties of the scholarly graphs, and c) a thorough experimental study.
-That is, this paper certainly has its contributions to the technical part.
+We do believe that there are technical contributions: (1) An ensemble based ranking model (a great effort needs to be paid to develop such a ranking model);  (2) An incremental algorithm designed for dynamic scholarly article ranking in the general setting, which is designed for the block-wise algorithm of Time-Weighted PageRank, and is based on the citation characteristics.
+These have never been exploited in existing studies.
+That is, we are not simply using known techniques for an application.
 
@@
 Our incremental algorithm is designed for the block-wise algorithm of Time-Weighted PageRank, and is based on the citation characteristics (\eg for the maintenance of the topological order), both of which have never been exploited before.
+
+We also believe that our ensemble based ranking model and the citation statistics revealed in our study have their own interests to the researchers in the field of scientometrics or  bibliometrics.
+
+We have further clarified this both in the contributions and in the related work.
+
 %
-To conclude, the incremental time-weighted PageRank algorithm for scholarly graphs has its own unique features, which is not simply applying existing techniques into a different domain.
-We have further %clarified our contributions in Introduction and
-claimed the technique difference of our algorithm in Related Work.
+%To conclude, the incremental time-weighted PageRank algorithm for scholarly graphs has its own unique features, which is not simply applying existing techniques into a different domain.
+%We have further %clarified our contributions in Introduction and claimed the technique difference of our algorithm in Related Work.
 
@@
 
-[21]  R. Ghosh, T. Kuo, C. Hsu, S. Lin, and K. Lerman, ¡°Time-aware ranking in dynamic citation networks,¡± in ICDM Workshops, 2011.
+%[21]  R. Ghosh, T. Kuo, C. Hsu, S. Lin, and K. Lerman, ¡°Time-aware ranking in dynamic citation networks,¡± in ICDM Workshops, 2011.
 
@@
 
-Yes, we have gone over the paper and improved the presentation to make it more understandable.
+Yes, we have gone over the paper, and tried our test to improve its presentation.
 %Thanks for the suggestion!
@@
 
-We have downgraded the tone and changed it into ``practical and difficult". Thanks for the suggestion!
+We have downgraded the tone and changed it into ``a practical and difficult problem''. Thanks for the suggestion!
 
@@
 
-We have removed the sentence and explained more details about the statement (Author Component, left column, page 4).
-%
+We agree that this sentence does not make sense, and, hence, we have removed the sentence, and explained more details about the statement (Author Component, left column, page 4). Thanks!
+
+Yes, distributed processing is adopted for Pangrank computation at Google, and we plan to develop a distributed version of our algorithm as well. 
+However, even this, memory cost should also be deliberately considered in a centralized case.
+
 One way to compute the prestige of authors is to construct an author citation graph  such that (a) a node represents an author, and (b) a direct edge $(s,t)$ denotes that there exist articles of author $s$ citing articles of author $t$.
 However, it is easy to see that for each citation, the corresponding two sets of authors are fully connected, which makes it computationally expensive to compute the prestige of authors on such an author citation graph with TWPageRank.
-%
-Indeed, the generated author citation graph has 7.12 billion edges on the largest \magdata, \ie the memory cost of storage only is 57GB. Please also refer to our new experiments on memory costs.
+
+This needs quite a few space, and  the generated author citation graph has 7.12 billion edges on the largest \magdata (its memory cost of storage is 57GB).
+This is why we choose to evaluate the prestige of an author with the average prestige of all articles published by the author.
 
@@
 
-We have reported the memory costs in a new set of experiments, \ie Exp-4 (page 10). Thanks for the suggestion!
+We have reported the memory costs with a new set of tests in the experimental study (Exp-4, page 10). Thanks for the suggestion!
 %that on the largest \magdata, (\futurerank, \ensemblerank) cost (16.42GB, 49.42GB) memory when $Y_s=2015$, and \hhgrank costs 61.37GB memory when $Y_s=2014$.

### 2018-01-02 icde/revision/Response.tex

@@
 
-The paper has been substantially revised according to the referees¡¯ comments.
-In particular, we have (1) further clarified our contributions, (2) added figures to better illustrate the data growing, (3) explained the author component better,  (4) reported the memory cost in experiments, (5) modified related work to differentiate our technique with existing ones, (6) answered the questions raised by referees, and (7) taken this opportunity to rewrite several parts of our paper to improve the presentation.
+The paper has been substantially revised according to the referees' comments.
+In particular, we have (1) further clarified our contributions, (2) added figures to better illustrate the data growing, (3) explained the author component better,  (4) reported the memory cost in experiments, (5) modified related work to differentiate our techniques with existing ones, (6) answered the questions raised by referees, and (7) taken this opportunity to rewrite several parts of our paper to improve the presentation.
 
@@
 More specifically, these parameters make our model be able to fit to the various ranking scenarios.
-As shown in the experiment study (Exp-1 and Exp-2), our model performs well in two reasonable ranking scenarios by using quite different aggregating parameters.
+As shown in the experimental study (Exp-1 and Exp-2), our model performs well in two reasonable ranking scenarios by using quite different aggregating parameters.
 
 Moreover, these parameters are indeed quite flexible to choose within a certain range (Exp-5.3, page 10).
-Note that (a) the optimal \PairAcc is obtained within a single region, (b) the \PairAcc keeps at a high level within a certain ($\alpha$, $\beta$) combination space around the optimal region, and (c) the optimal parameters on the same set of ground-truth are very similar across different datasets.
+Note that (1) the optimal \PairAcc is obtained within a single region, (2) the \PairAcc keeps at a high level within a certain ($\alpha$, $\beta$) combination space around the optimal region, and (3) the optimal parameters on the same set of ground-truth are very similar across different datasets.
 
@@
 %
-This work focuses on {\em query independent ranking} because of its wide application in modern scholarly search engines such as Google Scholar, Semantic Scholar and Microsoft Academic Search (as we discussed in the first two paragraphs in Section 1).
+This work focuses on {\em query independent ranking} because of its wide application in modern scholarly search engines such as Google Scholar, Semantic Scholar and Microsoft Academic Search (as we discussed in the first two paragraphs in Section I).
 %
-The combination of query dependent ranking and query independent ranking  is well known, e.g., typical search engines such as Google : keyword search (query dependent ranking) is combined with Pagerank (query independent ranking).
+The combination of query dependent ranking and query independent ranking  is well known, e.g., typical search engines such as Google: keyword search (query dependent ranking) is combined with PageRank (query independent ranking).
 Our ranking can serve as an indicator of the importance of items, and, given a specific query, it can either be directly used to rank a subset of relevant items or combine with any relevance scores for ranking along the same lines as keyword search.
@@
 The {\em PeakMul} pattern is originally defined in [18]:  the height of a peak should be at least 75\% of the maximum peak height, and two consecutive peaks should be separated by more than two years.
-In our work, we unify the five patterns, and we only use the highest peak time that has been formally defined in Section II-A (para 1, left column, page 3).
-Also note that: (a) [18] allows multiple peaks to exist for an article while we only consider the highest peak, and (b) [18] uses the original numbers of citations to compute peaks, and we use the scaled numbers of citations \wrt the total number of citations of all articles at each year.
+In our work, we unify the five patterns, and we only use the highest peak that has been formally defined in Section II-A (para 1, left column, page 3).
+Also note that: (1) [18] allows multiple peaks to exist for an article while we only consider the highest peak, and (2) [18] uses the original numbers of citations to compute peaks, and we use the scaled numbers of citations \wrt the total number of citations of all articles at each year.
 
@@
 From a purely research and technical perspective, the paper is on the weak side.
-Pagerank and (incremental) versions of it already exist and the paper makes little contributions there.
+PageRank and (incremental) versions of it already exist and the paper makes little contributions there.
 The claim (made twice) in the related work section that ``Different from previous work" this paper focuses on citations statistics doesn't hold water.
@@
 
-%[21]  R. Ghosh, T. Kuo, C. Hsu, S. Lin, and K. Lerman, ¡°Time-aware ranking in dynamic citation networks,¡± in ICDM Workshops, 2011.
+[21]  R. Ghosh, T. Kuo, C. Hsu, S. Lin, and K. Lerman, ¡°Time-aware ranking in dynamic citation networks,¡± in ICDM Workshops, 2011.
 
@@
 
-Yes, we have gone over the paper, and tried our test to improve its presentation.
+Yes, we have gone over the paper, and tried our best to improve its presentation.
 %Thanks for the suggestion!
@@
 
-Yes, distributed processing is adopted for Pangrank computation at Google, and we plan to develop a distributed version of our algorithm as well. 
+Yes, distributed processing is adopted for PangRank computation at Google, and we plan to develop a distributed version of our algorithm as well.
 However, even this, memory cost should also be deliberately considered in a centralized case.
@@
 
-We have reported the memory costs with a new set of tests in the experimental study (Exp-4, page 10). Thanks for the suggestion!
+We have reported the memory costs with a new set of tests in the experimental study (Exp-4, page 9). Thanks for the suggestion!
 %that on the largest \magdata, (\futurerank, \ensemblerank) cost (16.42GB, 49.42GB) memory when $Y_s=2015$, and \hhgrank costs 61.37GB memory when $Y_s=2014$.

### 2018-01-02 icde/revision/sec-app.tex

@@
 
+\begin{figure}[tb!]
+\centering
+%\includegraphics[scale=0.15]{fig/framework.eps}
+\includegraphics[scale=0.35]{fig/example-graph.eps}
+\vspace{-1ex}
+\caption{\small An example of graph generation} \label{fig-example-graph}
+\vspace{-3ex}
+\end{figure}
+
+\begin{figure}[tb!]
+\centering
+%\includegraphics[scale=0.15]{fig/framework.eps}
+\includegraphics[scale=0.35]{fig/example-ranking.eps}
+\vspace{-1ex}
+\caption{\small An example of ranking model \ensemblerank} \label{fig-example-model}
+\vspace{-3ex}
+\end{figure}
+
 %In our model, the importance of scholarly articles is defined as a combination of the prestige and popularity of its associated articles, venues and authors.
@@
 
-\begin{figure}[tb!]
-\centering
-%\includegraphics[scale=0.15]{fig/framework.eps}
-\includegraphics[scale=0.35]{fig/example-graph.eps}
-\vspace{-1ex}
-\caption{\small Ranking model \ensemblerank} \label{fig-rankmodel}
-\vspace{-3ex}
-\end{figure}
+\begin{example} \label{eg-layer-dag}
+Figure~\ref{fig-example-graph} illustrates an example of graph generation.
+We choose four articles of real-life data to show how to generate the citation graph, venue graph and author citation graph while the original academic graph data only has citation information, author-article relationships, article-venue relationships and time information of articles.
+As shown in Figure~\ref{fig-example-graph}, the articles A, B, C and D represent "Role Discovery in Networks", "On the Use of Side Information for Mining Text Data", "On Text Clustering with Side Information" and "Efficient streaming text clustering", respectively.
+We next introduce the details of graph generation.
 
-\begin{figure}[tb!]
-\centering
-%\includegraphics[scale=0.15]{fig/framework.eps}
-\includegraphics[scale=0.35]{fig/example-ranking.eps}
-\vspace{-1ex}
-\caption{\small Ranking model \ensemblerank} \label{fig-rankmodel}
-\vspace{-3ex}
-\end{figure}
+The citation graph is constructed using the citation information such that each node denotes an individual article and the edge $(A,B)$ denotes that article A have cited article B.
+The venue graph is constructed using the citation information among venues.
+As shown in Figure~\ref{fig-example-graph}, each node denotes a venue in a specific year such that TKDE-14 and TKDE-15 are two different nodes.
+Further, each edge denotes that there are citations between the articles published in the two venues.
+The author citation graph is constructed using the citation information among authors.
+As shown in Figure~\ref{fig-example-graph}, the article citation between article A and article B will generate 6 different edges in author citation graph, which makes it much more complicated than citation graph.
+As a result, the citation graph of 4 articles and 4 edges have generated a author citation graph of 6 nodes and 18 edges (the bidirectional arrow denotes two edges) although the article B and article C have shared same authors.
 
-\stitle{Citation component}.
-The first component computes the importance of articles using the citation information.
+\end{example}
 
-A {\em citation graph} $G^c(V^c, E^c)$ is firstly constructed using the citation information such that (a) a node in $V^c$ denotes an article, (b) a directed edge $(u,v)$ in $E^c$ denotes that $u$ cites $v$, and (c) each node is associated with two types of time information: the publication year and the latest year having the largest scaled number of citations.
+\begin{example} \label{eg-layer-dag}
+Figure~\ref{fig-example-model} illustrates an example of article ranking model. Consider an article $v$ published by authors $t$ and $u$ in venue $k$.
 
-\sstab(1) The prestige of articles is derived by applying TWPageRank on the citation graph $G^c$, and each article $v$ is assigned the corresponding TWPageRank score as its prestige $Prs_c(v)$.
-
-\sstab(2)  The popularity of an article is the sum of all its citation freshness, \ie the closeness to the current year:
-
-\vspace{-1ex}
-\begin{small}
-\begin{equation}\label{eq-pop}
-Pop_c(v) = \sum_{{(u,v)\in E^c}} {e^{\sigma (T_0-T_u)}}.
-\end{equation}
-\end{small}
-\noindent
-Here $T_0$ is the current year, \ie the largest $T_u$ among all articles in $V^c$, $\sigma$ is the negative decaying factor used in Eq.~(\ref{eq-infl-weights}), and $e^{\sigma (T_0-T_u)}$ represents the freshness of citation $(u,v)$.
-
-%Alternatively, one may want to define $Pop_c(v) = e^{\sigma \cdot (T_0-T_v)}$, \ie decaying with the publication year $T_v$ of article $v$ directly~\cite{sayyadi09,WalkerXKM07}.
-We propose to use the publication years $T_u$ of citations, instead of $T_v$, since $T_u$ reflects the ages of articles to some extent, \eg articles are probably cited in the next few years after publication(Fig.~\ref{fig-citation}).
-
-Intuitively, the more recent citations an article has, the higher its popularity is, no matter how long it has been published.
-Here popularity is introduced to capture the recent importance of articles, and articles with more recent citations have higher popularity scores.
-%, which is somehow biased to recent articles.
-Hence, we do not explicitly handle the bias for popularity computation.
-%
-%\marked{Different from $Peak_v$ in Eq.~(\ref{eq-infl-weights}), the bias of references has little impacts on the popularity.
-Moreover, the motivation of popularity is to assign higher ranks to articles of recent attention, which is somehow biased to recent articles.
-Hence, we do not explicitly handle the bias for popularity computation.}
-%
-Note that the popularity is also normalized such that the sum of  all articles is equal to $1$, similar to the prestige produced by TWPageRank.
-
-\sstab(3) The prestige and popularity are finally combined to produce the importance of articles.
-Intuitively, an important article is both prestigious and popular.
-Hence, the {\em citation importance score} $Imp_c(v)$ of an article is defined as a weighted combination of its prestige and popularity:
-
-\vspace{-1ex}
-\begin{small}
-\begin{equation}\label{eq-imp}
-%Imp_c(v) = \sqrt{Prs_c(v) \cdot Pop_c(v)}.
-Imp_c(v) = Prs_c(v)^\lambda Pop_c(v)^{1-\lambda},
-\end{equation}
-\end{small}
-\noindent where $\lambda \in [0,1]$ is the importance weighting factor.
-The rationales behind Eq.~(\ref{eq-imp}) are as follows.
-(a) Prestigious articles with many recent citations are ranked at the top, as researchers are very willing to find them; (b) Prestigious articles with rare current citations are ranked lower, as researchers may lose interests in these old articles; And (c) articles with many recent citations are ranked higher, as researchers have potential interests in those of recent attention.
-
-%Here the prestige and popularity are equally weighted to produce the importance of an article, as we focus on query independent ranking.
-They may be properly weighted when the query information is available, which is beyond the scope of this work.
-
-\begin{figure}[tb!]
-\centering
-%\includegraphics[scale=0.15]{fig/framework.eps}
-\includegraphics[scale=0.15]{fig/framework-lite-2.eps}
-\vspace{-1ex}
-\caption{\small Ranking model \ensemblerank} \label{fig-rankmodel}
-\vspace{-3ex}
-\end{figure}
-
-\stitle{Venue component}.
-The second component computes the importance of venues with their associated articles.
-As the importance of a venue  evolves with time, we treat the venue in each year individually, and its importance is the sum of importance in all individual years.
-
-A {\em venue graph} $G^v(V^v, E^v)$ is firstly constructed using the citation information among venues such that (a) a node in $V^v$ represents a venue in a specific year, (b) a direct edge $(s,t)$ in $E^v$ denotes that there exist articles published in venue (in a specific year) $s$ citing articles published in venue (in a specific year) $t$, and (c) we use the {\em impact weight} $w_v(s,t)$ to denote the weight  from venues $s$ to $t$, which is the sum of the impact weights from articles published in $s$ to $t$, \ie
-
-\vspace{-1ex}
-\begin{small}
-\begin{equation} \label{eq-infl-weights-v}
-w_v(s,t)  = \sum_{u\in C(s), v\in C(t)} w(u,v).
-\end{equation}
-\end{small}
-\noindent
-Here, $C(s)$ and $C(t)$ are the sets of articles published in $s$ and $t$, respectively, and $w(u,v)$ is the impact weight of edge $(u, v)$ produced in the citation component.
-
-The prestige of a venue in a specific year is computed using the impact weights and the update rule in Eq.~(\ref{eq-twpr}), and the popularity of a venue in a specific year is defined as the average popularity of its articles.
-The prestige and popularity are combined to derive the importance of a venue in a specific year in the same way as the citation component.
-Finally, the importance of a venue is treated as the {\em venue importance score} for all articles published in this venue.
-
-\stitle{Author component}.
-The author component computes the importance of authors with their published articles.
-%
-Similar to the venue component, we evaluate the importance of each author, and compute the average importance of the authors of an article as its {\em author importance score}.
-
-%However, the resulting author citation graph to compute the prestige is typically too large to handle.
-One way to do this is to construct an author citation graph  such that (a) a node represents an author, and (b) a direct edge $(s,t)$ denotes that there exist articles of author $s$ citing articles of author $t$.
-However, it is easy to see that for each citation, the corresponding two sets of authors are fully connected, which makes it computationally expensive to compute the prestige of authors on such an author citation graph with TWPageRank.
-
-Hence, we choose to evaluate the prestige of an author with the average prestige of all articles published by the author.
-Similar to the venue component, the popularity of an author is  defined as the average popularity of her/his published articles.
-Finally, the prestige and popularity are combined to derive the importance along the same way as the citation component.
-
-%, which can be directly obtained from the citation component,
-%to evaluate the authority of that author.
-
-\eat{
-\stitle{Affiliation ensemble}.
-Recall that articles in our data are also associated with affiliation information.
-Following the way of the venue or author ensemble, we can derive another ensemble, \ie affiliation ensemble.
-However, we argue that the use of affiliation ensemble may have negative effects since the correlation between the importance of an article and the average authority of its affiliation(s) is not as strong as others such like authors and venues.
-As shown by the experimental study in Section~\ref{sec-exp},  the incorporation of the affiliation ensemble impairs the ranking accuracy.
-Hence, we choose not to use the affiliation ensemble in our model.
-}
-
-%\subsection{Ranking with Importance}
-%{\label{subsec-eerank}}
-
-\stitle{Ranking with importance assembling}.
-The aforementioned importance is finally assembled to produce the final ranking, as illustrated in Fig.~\ref{fig-rankmodel}.
-Before assembling, each component is properly scaled such that the average importance scores of citations, venues and authors are the same.
-Let the scaled importance scores of article $v$ be $R_c(v)$, $R_v(v)$, and $R_a(v)$ from the citation, venue and author components, respectively.
-%
-The final ranking score $R(v)$ is aggregated as follows:
-
-\vspace{-1ex}
-\begin{small}
-\begin{equation} \label{eq-ensemble}
-R(v) =  \alpha R_c(v) + \beta R_v(v) + (1 - \alpha - \beta) R_a(v).
-\end{equation}
-\end{small}
-\noindent Here aggregating parameters $\alpha$ and $\beta$ and value $(1 - \alpha - \beta)$ regularize the contributions of the citation, venue and author information,
-which make our model be able to fit to the various ranking scenarios.
-As will be seen in the experiments, our model performs well in two reasonable ranking scenarios by using quite different aggregating parameters, and, moreover, these parameters are indeed quite flexible to choose within a certain range.
-Intuitively, these parameters indicate the intensity of the correlation between the importance of scholarly articles and the specific information.
-
-\stitle{Remarks}.
-This work follows the graph-based formalization, and further develops efficient batch and incremental algorithms based on graphs for scholarly article ranking (Sections~\ref{sec-alg} \& \ref{sec-incAlg}).
-However, it is also possible to learn a discriminative model that directly optimizes certain loss functions for ranking, similar to \cite{Richardson06:BPR} for ranking Web pages.
+\end{example}

### 2018-01-02 icde/revision/sec-app.tex

@@
 
+%In our model, the importance of scholarly articles is defined as a combination of the prestige and popularity of its associated articles, venues and authors.
+Intuitively, prestige favors those with many citations soon after the publication of articles for citation component or associated articles for venue and author components, and popularity favors those with recent citations.
+Both prestige and popularity capture the temporal nature of entities in scholarly data.
+In our model, the importance is defined as a combination of the prestige and popularity.
+Intuitively, prestige favors those with many citations soon after the publication of articles or associated articles of venues and authors, and popularity favors those with recent citations.
+Both prestige and popularity capture the temporal nature of entities.
+%in scholarly data.
+
+Our ranking model \ensemblerank,  illustrated in Fig.~\ref{fig-rankmodel}, assembles the importance of article, venue and author entities for scholarly article ranking, which is computed by the citation, venue and author components, respectively.
+%
+We next introduce the details of the three components.
 \begin{figure}[tb!]
@@
 
-%In our model, the importance of scholarly articles is defined as a combination of the prestige and popularity of its associated articles, venues and authors.
-Intuitively, prestige favors those with many citations soon after the publication of articles for citation component or associated articles for venue and author components, and popularity favors those with recent citations.
-Both prestige and popularity capture the temporal nature of entities in scholarly data.
-In our model, the importance is defined as a combination of the prestige and popularity.
-Intuitively, prestige favors those with many citations soon after the publication of articles or associated articles of venues and authors, and popularity favors those with recent citations.
-Both prestige and popularity capture the temporal nature of entities.
-%in scholarly data.
-
-Our ranking model \ensemblerank,  illustrated in Fig.~\ref{fig-rankmodel}, assembles the importance of article, venue and author entities for scholarly article ranking, which is computed by the citation, venue and author components, respectively.
-%
-We next introduce the details of the three components.
-
 \begin{example} \label{eg-layer-dag}
@@
 As a result, the citation graph of 4 articles and 4 edges have generated a author citation graph of 6 nodes and 18 edges (the bidirectional arrow denotes two edges) although the article B and article C have shared same authors.
-
 \end{example}
@@
 \begin{example} \label{eg-layer-dag}
-Figure~\ref{fig-example-model} illustrates an example of article ranking model. Consider an article $v$ published by authors $t$ and $u$ in venue $k$.
-
+Figure~\ref{fig-example-model} illustrates an example of article ranking model.
+Consider an article $v$ published by authors $t$ and $u$ in venue $k$.
+Select the citation important score of $v$, the venue importance score of $k$ and the average of author importance scores of $t$ and $u$ from three components to assembled to produce the final ranking.
+Before assembling, each component is properly scaled such that the average importance scores are the same.
+Finally, calculate the final ranking score of article $v$ as Eq.~(\ref{eq-ensemble}).
 \end{example}

### 2018-01-02 icde/revision/sec-app.tex

--- 2017-12-31 icde/revision/sec-app.tex
@@
 
-\section*{APPENDIX B: Detailed of Model}
-\label{sec-exp-app}
+\section*{APPENDIX B: Ranking with Importance Assembling and Examples}
+\label{sec-model-app}
 
-\subsection{Ranking with Importance Assembling}
-\label{subsec-ensemble}
-
-%In our model, the importance of scholarly articles is defined as a combination of the prestige and popularity of its associated articles, venues and authors.
-Intuitively, prestige favors those with many citations soon after the publication of articles for citation component or associated articles for venue and author components, and popularity favors those with recent citations.
-Both prestige and popularity capture the temporal nature of entities in scholarly data.
 In our model, the importance is defined as a combination of the prestige and popularity.
@@
 
-\begin{figure}[tb!]
-\centering
-%\includegraphics[scale=0.15]{fig/framework.eps}
-\includegraphics[scale=0.35]{fig/example-graph.eps}
-\vspace{-1ex}
-\caption{\small Ranking model \ensemblerank} \label{fig-rankmodel}
-\vspace{-3ex}
-\end{figure}
-
-\begin{figure}[tb!]
-\centering
-%\includegraphics[scale=0.15]{fig/framework.eps}
-\includegraphics[scale=0.35]{fig/example-ranking.eps}
-\vspace{-1ex}
-\caption{\small Ranking model \ensemblerank} \label{fig-rankmodel}
-\vspace{-3ex}
-\end{figure}
-
 \stitle{Citation component}.
@@
 A {\em citation graph} $G^c(V^c, E^c)$ is firstly constructed using the citation information such that (a) a node in $V^c$ denotes an article, (b) a directed edge $(u,v)$ in $E^c$ denotes that $u$ cites $v$, and (c) each node is associated with two types of time information: the publication year and the latest year having the largest scaled number of citations.
+
+%\markedb{We next illustrate how to generate the citation graph from the academic graph data with an example below.}
+
+\begin{example} \label{eg-model-citation}
+\markedb{Figure~\ref{fig-example-graph} shows a real-life example of the heterogeneous academic graph, which is drawn based on the following four articles as well as their citation relationships:}
+
+\begin{small}
+\bi
+\item A: Ryan A. Rossi, and Nesreen K. Ahmed, ``Role Discovery in Networks," {\em TKDE}, 2015.
+\item B: Charu C. Aggarwal, Yuchen Zhao, and Philip S. Yu, ``On the Use of Side Information for Mining Text Data," {\em TKDE}, 2014.
+\item C: Charu C. Aggarwal, Yuchen Zhao, and Philip S. Yu, ``On Text Clustering with Side Information," In {\em ICDE}, 2012.
+\item D: Shi Zhong, ``Efficient streaming text clustering," {\em Neural Networks}, 2005.
+\ei
+\end{small}
+
+\markedb{The corresponding citation graph is also presented in Fig.~\ref{fig-example-graph} where the four nodes represent articles A, B, C and D, and edges represent the citations between them.
+Note that each node is also associated with time information (we omit the peak time on each node since it can only be computed when all the citations are given).}
+\end{example}
+
+\markedb{The importance of articles is then computed as follows.}
 
@@
 \begin{small}
-\begin{equation}\label{eq-pop}
+\begin{equation}\label{eq-pop-app}
 Pop_c(v) = \sum_{{(u,v)\in E^c}} {e^{\sigma (T_0-T_u)}}.
@@
 
-%Alternatively, one may want to define $Pop_c(v) = e^{\sigma \cdot (T_0-T_v)}$, \ie decaying with the publication year $T_v$ of article $v$ directly~\cite{sayyadi09,WalkerXKM07}.
-We propose to use the publication years $T_u$ of citations, instead of $T_v$, since $T_u$ reflects the ages of articles to some extent, \eg articles are probably cited in the next few years after publication(Fig.~\ref{fig-citation}).
-
 Intuitively, the more recent citations an article has, the higher its popularity is, no matter how long it has been published.
 Here popularity is introduced to capture the recent importance of articles, and articles with more recent citations have higher popularity scores. 
-%, which is somehow biased to recent articles.
-Hence, we do not explicitly handle the bias for popularity computation.
-%
-%\marked{Different from $Peak_v$ in Eq.~(\ref{eq-infl-weights}), the bias of references has little impacts on the popularity.
-Moreover, the motivation of popularity is to assign higher ranks to articles of recent attention, which is somehow biased to recent articles.
-Hence, we do not explicitly handle the bias for popularity computation.}
 %
@@
 \begin{small}
-\begin{equation}\label{eq-imp}
-%Imp_c(v) = \sqrt{Prs_c(v) \cdot Pop_c(v)}.
+\begin{equation}\label{eq-imp-app}
 Imp_c(v) = Prs_c(v)^\lambda Pop_c(v)^{1-\lambda},
@@
 \noindent where $\lambda \in [0,1]$ is the importance weighting factor.
-The rationales behind Eq.~(\ref{eq-imp}) are as follows.
+The rationales behind Eq.~(\ref{eq-imp-app}) are as follows.
 (a) Prestigious articles with many recent citations are ranked at the top, as researchers are very willing to find them; (b) Prestigious articles with rare current citations are ranked lower, as researchers may lose interests in these old articles; And (c) articles with many recent citations are ranked higher, as researchers have potential interests in those of recent attention.
-
-%Here the prestige and popularity are equally weighted to produce the importance of an article, as we focus on query independent ranking.
-They may be properly weighted when the query information is available, which is beyond the scope of this work.
 
@@
 \centering
-%\includegraphics[scale=0.15]{fig/framework.eps}
-\includegraphics[scale=0.15]{fig/framework-lite-2.eps}
-\vspace{-1ex}
-\caption{\small Ranking model \ensemblerank} \label{fig-rankmodel}
+\includegraphics[scale=0.34]{fig/example-graph.eps}
+\vspace{-3.3ex}
+\caption{\small An example of citation, venue and author citation graphs} \label{fig-example-graph}
 \vspace{-3ex}
@@
 \begin{small}
-\begin{equation} \label{eq-infl-weights-v}
+\begin{equation} \label{eq-infl-weights-v-app}
 w_v(s,t)  = \sum_{u\in C(s), v\in C(t)} w(u,v).
@@
 Here, $C(s)$ and $C(t)$ are the sets of articles published in $s$ and $t$, respectively, and $w(u,v)$ is the impact weight of edge $(u, v)$ produced in the citation component.
+
+\begin{example} \label{eg-model-venue}
+\markedb{Recall the heterogeneous academic graph in Fig.~\ref{fig-example-graph}.
+Its corresponding venue graph is also presented.
+Note that two nodes in the venue graph are related to venue {\em TKDE} since each node denotes a venue in a specific year.
+There is an edge from nodes {\em TKDE-15} to {\em TKDE-14} since article A published in {\em TKDE-15} cites article B published in {\em TKDE-14}.
+And it is similar to derive other edges in the venue graph.}
+\end{example}
 
@@
 
+\begin{example} \label{eg-model-author}
+\markedb{We also include the corresponding author citation graph in Fig.~\ref{fig-example-graph}.
+Observe that six links in the author citation graph are generated between authors \{{\em Ryan}, {\em Nesreen}\} to \{{\em Charu}, {\em Yuchen}, {\em Philip}\} given a single citation from articles A to B.
+And it is quite obvious that the number of edges in the author citation graph is much larger than the one in the citation graph, which verifies our claim above.}
+\end{example}
+
 Hence, we choose to evaluate the prestige of an author with the average prestige of all articles published by the author.
@@
 Finally, the prestige and popularity are combined to derive the importance along the same way as the citation component.
-
-%, which can be directly obtained from the citation component,
-%to evaluate the authority of that author.
-
-\eat{
-\stitle{Affiliation ensemble}.
-Recall that articles in our data are also associated with affiliation information.
-Following the way of the venue or author ensemble, we can derive another ensemble, \ie affiliation ensemble.
-However, we argue that the use of affiliation ensemble may have negative effects since the correlation between the importance of an article and the average authority of its affiliation(s) is not as strong as others such like authors and venues.
-As shown by the experimental study in Section~\ref{sec-exp},  the incorporation of the affiliation ensemble impairs the ranking accuracy.
-Hence, we choose not to use the affiliation ensemble in our model.
-}
-
-%\subsection{Ranking with Importance}
-%{\label{subsec-eerank}}
 
@@
 \begin{small}
-\begin{equation} \label{eq-ensemble}
+\begin{equation} \label{eq-ensemble-app}
 R(v) =  \alpha R_c(v) + \beta R_v(v) + (1 - \alpha - \beta) R_a(v).
@@
 
+\begin{figure}[tb!]
+\centering
+\includegraphics[scale=0.37]{fig/example-ranking.eps}
+\vspace{-2ex}
+\caption{\small An example of importance assembling} \label{fig-example-ranking}
+\vspace{-3ex}
+\end{figure}
+
+\begin{example} \label{eg-ranking}
+\markedb{Figure~\ref{fig-example-ranking} illustrates an example of the importance assembling procedure. 
+Consider an article $v$ published by authors $t$ and $u$ in venue $k$. 
+(a) It first extracts the importance $c_v$ of article $v$ computed by the  citation component and properly scales $c_v$ to citation importance score $R_c(v)$.
+Similarly, (b) it derives the venue importance score $R_v(v)$ based on the venue importance $v_k$ of venue $k$ computed  by the venue component.
+(c) The author importance score $R_a(v)$ averages and scales the author importance $a_t$ and $a_u$ of authors $t$ and $u$ computed  by the author component.
+Finally, (d) the three importance scores are aggregated to the final ranking score $R(v)$. }
+\end{example}
+
 \stitle{Remarks}.

### 2018-01-03 icde/revision/sec-alg.tex

@@
 
-\stitle{Block-wise algorithm~\twprscc}.  It takes as input a citation or venue graph $G(V, E)$ and an iteration threshold $\epsilon$, and returns the TWPageRank vector of $PR$ of $G$.
+\stitle{Block-wise algorithm~\twprscc}.  It takes as input a citation or venue graph $G(V, E)$ and an iteration threshold $\epsilon$, and returns the TWPageRank vector $PR$ of $G$.
 %To process an \scc instead of the entire graph,
@@
 Finally, it returns the TWPageRank vector.
-When processing an \scc, it iteratively updates the TWPageRank scores of the nodes in the \scc, and the iteration continues until the sum changes of of TWPageRank scores is less than $\epsilon |scc|/|V|$, where $|scc|$ is the number of nodes in the \scc.
+When processing an \scc, it iteratively updates the TWPageRank scores of the nodes in the \scc, and the iteration continues until the sum changes of TWPageRank scores is less than $\epsilon |scc|/|V|$, where $|scc|$ is the number of nodes in the \scc.
 Note that there must exist a topological order $O$, as the block-wise graph is a directed acyclic graph~\cite{CormenLRS01}.
@@
 
-\vspace{-1ex}
+\vspace{-0.5ex}
 \stitle{Analysis of algorithm \twprscc}.

### 2018-01-03 icde/revision/Response.tex

@@
 
-One way to compute the prestige of authors is to construct an author citation graph  such that (a) a node represents an author, and (b) a direct edge $(s,t)$ denotes that there exist articles of author $s$ citing articles of author $t$.
+One way to compute the prestige of authors is to construct an author citation graph  such that (1) a node represents an author, and (2) a direct edge $(s,t)$ denotes that there exist articles of author $s$ citing articles of author $t$.
 However, it is easy to see that for each citation, the corresponding two sets of authors are fully connected, which makes it computationally expensive to compute the prestige of authors on such an author citation graph with TWPageRank.
@@
 
-Yes.
-We have discussed the correlation between our work and temporal graphs, and cited necessary references (e.g., P.
+Yes, we have discussed the correlation between our work and temporal graphs, and cited necessary references (e.g., P.
 Holme and J.

### 2018-01-03 icde/revision/Response.tex

@@
 
-We have downgraded the tone and changed it into ``a practical and difficult problem''. Thanks for the suggestion!
+We have downgraded the tone to ``a practical and difficult problem''. Thanks for the suggestion!
 
@@
 Yes, distributed processing is adopted for PangRank computation at Google, and we plan to develop a distributed version of our algorithm as well.
-However, even this, memory cost should also be deliberately considered in a centralized case.
+However, even this, memory cost should also be deliberately considered in the centralized case.
 
@@
 
-We have reported the memory costs with a new set of tests in the experimental study (Exp-4, page 9). Thanks for the suggestion!
+We have reported the memory cost with a new set of tests in the experimental study (Exp-4, page 9). Thanks for the suggestion!
 %that on the largest \magdata, (\futurerank, \ensemblerank) cost (16.42GB, 49.42GB) memory when $Y_s=2015$, and \hhgrank costs 61.37GB memory when $Y_s=2014$.

### 2018-01-03 icde/revision/Response.tex

@@
 We do believe that there are technical contributions: (1) An ensemble based ranking model (a great effort needs to be paid to develop such a ranking model);  (2) An incremental algorithm designed for dynamic scholarly article ranking in the general setting, which is designed for the block-wise algorithm of Time-Weighted PageRank, and is based on the citation characteristics.
-These have never been exploited in existing studies.
+These have never been exploited in previous studies.
 That is, we are not simply using known techniques for an application.
 
-More specifically, the only existing dynamic scholarly article ranking solution [21] is based on an impractical assumption that there is no citations between articles of the same years.
+More specifically, the only existing dynamic scholarly article ranking solution [21] is based on an impractical assumption that there are no citations between articles of the same years.
 In this work, we study dynamic scholarly article ranking in the general setting by eliminating the strong and impractical assumption.

### 2018-01-04 icde/revision/sec-alg.tex

@@
 %
-Given inpute graph $G(V, E)$, the block-wise graph and its topological order can be computed in $O(|V|+|E|)$ time~\cite{CormenLRS01}, and the edges in $E_a$ are only scanned once when updating TWPageRank scores.
+%Given inpute graph $G(V, E)$, the block-wise graph and its topological order can be computed in $O(|V|+|E|)$ time~\cite{CormenLRS01}, and the edges in $E_a$ are only scanned once when updating TWPageRank scores.
+\markedb{Given inpute graph $G(V, E)$, the block-wise graph and its topological order can be computed in $O(|G|)$ time where $|G|=|V|+|E|$~\cite{CormenLRS01}, and the edges in $E_a$ are only scanned once when updating TWPageRank scores.}
 From these, we have the following.

### 2018-01-04 icde/revision/sec-incAlg.tex

@@
 and the resulting graph is $G^+(V\cup\Delta V, E\cup\Delta E)$, where
-$\Delta V$ is a set of nodes with $\Delta V\cap V = \emptyset$, and $\Delta E$ is a set of directed edges on $\Delta V$ and from $\Delta V$ to $V$ only, as citations obey a natural temporal order, \ie an article only cites those published earlier.
-%, and it is rare for the mutual citations between two articles published in the same time.
+$\Delta V$ is a set of nodes with $\Delta V\cap V = \emptyset$, and $\Delta E$ is a set of directed edges on $\Delta V$ and from $\Delta V$ to $V$ only, as citations obey a natural temporal order, \ie an article only cites those published earlier, %, and it is rare for the mutual citations between two articles published in the same time.
+\markedb{and set $|\Delta |= |\Delta V|+|\Delta E|$.}
 
@@
 %
-By Eq.~(\ref{eq-inc-pop}), it is easy to see that updating the popularity of articles takes $O($ $|V^c|+|\Delta V^c|+|\Delta E^c|)$ time.
+\eat{By Eq.~(\ref{eq-inc-pop}), it is easy to see that updating the popularity of articles takes $O($ $|V^c|+|\Delta V^c|+|\Delta E^c|)$ time.}
 %This further shows that Eq.~(\ref{eq-inc-pop}) is a desired solution for popularity maintenance.
+\markedb{By Eq.~(\ref{eq-inc-pop}), it is easy to see that updating the popularity of articles takes $O($ $|V^c|+|\Delta G^c|)$ time.}
 
@@
 
-Observe that (a) a topological order of the block-wise graph of $G_C$ can be computed in $O(|\Delta V|+|\Delta E|)$ time,
+%Observe that (a) a topological order of the block-wise graph of $G_C$ can be computed in $O(|\Delta V|+|\Delta E|)$ time,
+\markedb{Observe that (a) a topological order of the block-wise graph of $G_C$ can be computed in $O(|\Delta G|)$ time,}
 (b) updating the TWPageRank scores of nodes in $V_B$ and $V_C$ costs $O(|V_B\cup V_C|+|E_{B,a}\cup E_{C,a}\cup E_{CB}|)+t^+|E_{B,i}\cup E_{C,i}|)$ time, where $t^+$ is  the maximum number of iterations among all \sccs in $G_B$ and $G_C$, and, finally, (c) updating the scores of nodes in $V_A$ costs $O(|V_A|)$ time.
@@
 %
-(a) It saves $O(|V^c|+|E^c|)$ and $O(|V^v|+|E^v|)$ time when maintaining \sccs and the topological order based on the update data only,
+%(a) It saves $O(|V^c|+|E^c|)$ and $O(|V^v|+|E^v|)$ time when maintaining \sccs and the topological order based on the update data only,
+\markedb{(a) It saves $O(|G^c|)$ and $O(|G^v|)$ time when maintaining \sccs and the topological order based on the update data only,}
 %where ($|V^c|$, $|E^c|$, $|V^v|$, $|E^v|$) are more than (92\%, 89\%, 93\%, 89\%) of ($|V^{c,+}|$, $|E^{c,+}|$, $|V^{v,+}|$, $|E^{v,+}|$) on all tested graphs;

### 2018-01-04 icde/revision/sec-alg.tex

@@
 
-The core idea of the block-wise PageRank computation is that each strongly connected component (\scc) of the input graph is treated as a block, and blocks are processed one by one following the {\em topological order} of the block-wise graph, \ie each node represents a block of the original graph~\cite{Berkhin05}.
+The main idea of the block-wise PageRank computation is that each strongly connected component (\scc) of the input graph is treated as a block, and blocks are processed one by one following the {\em topological order} of the block-wise graph, \ie each node represents a block of the original graph~\cite{Berkhin05}.
 We next show Claim~\ref{thm-prestige} by introducing and analyzing such a block-wise computation method.

### 2018-01-04 icde/revision/sec-alg.tex

--- 2018-01-03 icde/revision/sec-alg.tex
@@
 Given inpute graph $G(V, E)$, the block-wise graph and its topological order can be computed in $O(|V|+|E|)$ time~\cite{CormenLRS01}, and the edges in $E_a$ are only scanned once when updating TWPageRank scores.
+%\markedb{Given inpute graph $G(V, E)$, the block-wise graph and its topological order can be computed in $O(|G|)$ time where $|G|=|V|+|E|$~\cite{CormenLRS01}, and the edges in $E_a$ are only scanned once when updating TWPageRank scores.}
 From these, we have the following.

### 2018-01-06 icde/revision/sec-app.tex

@@
 \begin{example} \label{eg-model-citation}
-\markedb{Figure~\ref{fig-example-graph} shows a real-life example of the heterogeneous academic graph, which is drawn based on the following four articles as well as their citation relationships:}
+Figure~\ref{fig-example-graph} shows a real-life example of the heterogeneous academic graph, which is drawn based on the following four articles as well as their citation relationships:
 
@@
 
-\markedb{The corresponding citation graph is also presented in Fig.~\ref{fig-example-graph} where the four nodes represent articles A, B, C and D, and edges represent the citations between them.
-Note that each node is also associated with time information (we omit the peak time on each node since it can only be computed when all the citations are given).}
+The corresponding citation graph is also presented in Fig.~\ref{fig-example-graph} where the four nodes represent articles A, B, C and D, and edges represent the citations between them.
+Note that each node is also associated with time information (we omit the peak time on each node since it can only be computed when all the citations are given).
 \end{example}
 
-\markedb{The importance of articles is then computed as follows.}
+The importance of articles is then computed as follows.
 
@@
 \begin{example} \label{eg-model-venue}
-\markedb{Recall the heterogeneous academic graph in Fig.~\ref{fig-example-graph}.
+Recall the heterogeneous academic graph in Fig.~\ref{fig-example-graph}.
 Its corresponding venue graph is also presented.
@@
 There is an edge from nodes {\em TKDE-15} to {\em TKDE-14} since article A published in {\em TKDE-15} cites article B published in {\em TKDE-14}.
-And it is similar to derive other edges in the venue graph.}
+And it is similar to derive other edges in the venue graph.
 \end{example}
@@
 \begin{example} \label{eg-model-author}
-\markedb{We also include the corresponding author citation graph in Fig.~\ref{fig-example-graph}.
+We also include the corresponding author citation graph in Fig.~\ref{fig-example-graph}.
 Observe that six links in the author citation graph are generated between authors \{{\em Ryan}, {\em Nesreen}\} to \{{\em Charu}, {\em Yuchen}, {\em Philip}\} given a single citation from articles A to B.
-And it is quite obvious that the number of edges in the author citation graph is much larger than the one in the citation graph, which verifies our claim above.}
+And it is quite obvious that the number of edges in the author citation graph is much larger than the one in the citation graph, which verifies our claim above.
 \end{example}
@@
 \begin{example} \label{eg-ranking}
-\markedb{Figure~\ref{fig-example-ranking} illustrates an example of the importance assembling procedure. 
+Figure~\ref{fig-example-ranking} illustrates an example of the importance assembling procedure.
 Consider an article $v$ published by authors $t$ and $u$ in venue $k$.
@@
 (c) The author importance score $R_a(v)$ averages and scales the author importance $a_t$ and $a_u$ of authors $t$ and $u$ computed  by the author component.
-Finally, (d) the three importance scores are aggregated to the final ranking score $R(v)$. }
+Finally, (d) the three importance scores are aggregated to the final ranking score $R(v)$. 
 \end{example}

### 2018-01-22 ApproxComp/sec-beyond.tex

\section{Beyond Query and Data Approximations}
\label{sec-beyond}

There exist no single techniques fit all for big data analytics, and  it is often necessary to combine different techniques to obtain satisfiable solutions. 
We have seen that data sampling and data compression techniques help to achieve a balance between efficiency and effectiveness. 
We next roughly introduce three other potential techniques used for big data analytics.

When there are data updates, query answers typically need to be re-computed to reflect the changes. Incremental computation is a technique that attempts to reduce computations by reusing previous computing efforts and only computing those answers that ``depend on'' the changed data.

 incremental algorithms have been developed for
various applications.  Thomas W. Reps has done pioneering work on the study of incremental computation, and he observed that
the complexity of incremental algorithms was more accurately characterized
in terms of the size of the area affected by the updates, rather than the size
of the entire input~\cite{Reps96}.

One may notice that incremental algorithms can be utilized to achieve query approximation.

Data partitioning, Data indexing and Distributed computing~\cite{MaLHLH16} can also be combined to design query approximation and data approximation approaches for big data analytics.

### 2018-01-22 ApproxComp/sec-conclusion.tex

\section{Conclusion}
\label{sec-conclusion}

In this article we have introduced approximation computation techniques toward efficient and effective big data analytics.

First we see the importance of graph search by investigating the applications in industry, academia research developments, and the historical development of search.
And then, we have introduced and analyzed three types of graph search: cohesive subgraph,keyword search on graphs and graph
pattern matching. Finally, we have pointed out the problems and challenges graph search confronts and presented some useful techniques to deal with the problems.\par
\, As a a new paradigm for social computing, graph search has received extensive attentions. However, there are still a lot of questions to be solved in graph search, which is also a challenge for us.\par

### 2018-01-22 ApproxComp/sec-data.tex

\section{Data Approximation}
\label{sec-data}

\begin{figure}[tb!]
  \vspace{-1ex}
  \begin{center}
  \includegraphics[scale=0.45]{./dataApprox.png}
  \end{center}
  \vspace{-3ex}
  \caption{Data approximation}\label{fig-tech-dataappro}
  \vspace{-2ex}
\end{figure}

Big data has large volume, and, hence, the space complexity of big data analytic tasks starts raising more concerns.
Given a class $Q$ of queries on a data set $D$, data approximation is to transform $D$ into a smaller data set $D'$ such that $Q$ on $D'$ returns a satisfiable approximate answer in a more efficient way. Further, it is typically common that query $Q$ needs to be (slightly) modified to $Q'$ to accommodate  the changes of $D$ to $D'$, as shown in Fig.~\ref{fig-tech-dataappro}. Similar to query approximation, data approximation needs to reach a balance between the query efficiency and answer accuracy.

The rationale of data approximation has roots in the Pareto principle\footnote{\small \url{https://en.wikipedia.org/wiki/Pareto_principle}} that ``states that, for many events, roughly 80\% of the effects come from 20\% of the causes''. By this principle, for many big analytic tasks, one may only need to keep a small amount of the data to derive ``satisfiable'' answers.
For example, when we are to build a predictive model on the stock of razers for an online store based on the order history of customers, orders from men are good enough. While on the stock of lipsticks, those from women are good enough. That is to say,  it is not necessary to use the entire data for certain data analytic tasks.

However, it should be pointed out that there are data analytic tasks such that data approximation could not work well. For example, an online store needs to count the total number of goods in its catalog.  Essentially the entire goods should be considered for this task, and if a (small) portion of goods are chosen, it is hard to have a ``satisfiable'' result.

We next explain data approximation computation in more detail with three different data analytic tasks.

\stitle{(2) Proxies for Shortest Paths/Distances~\cite{MaFLWCH16}}

We study the {\em node-to-node shortest path} ({\em distance}) problem on large graphs: given a weighted undirected graph $G(V, E)$ with non-negative edge weights, and two nodes of $G$, the source $s$ and the target $t$, find the shortest path (distance) from $s$ to $t$ in $G$.
The Dijkstra's algorithm with Fibonacci heaps runs in $O(n\log n + m)$ due to Fredman \& Tarjan~\cite{CormenLRS01}, where $n$ and $m$ denote the numbers of nodes and edges in a graph, respectively, which remains asymptotically the fastest known solution on arbitrary undirected graphs with non-negative edge weights.
%The challenge of computing shortest paths on large graphs.
However, computing shortest  paths and distances remains a challenging problem, in terms of both time and space cost, on large-scale graphs. Hence, various optimizations have been developed to speed-up the computation.

To speed-up shortest  path and distance queries, our approach is to use {\em representatives}, each of which captures a set of nodes in a graph. The task of finding a proper form of representatives is, however, {\em nontrivial}. Intuitively, we expect representatives to have the following properties.
%
(1) A small number of representatives can represent a large number of nodes in a graph;
%
(2) Shortest paths and distances involved within the set of nodes being represented by the same representative can be answered efficiently; And,
%
(3) the representatives and the set of nodes being represented can be computed efficiently.

\stitle{1. Preprocessing}. Given graph $G(V, E)$, the preprocessing module executes the following.

\sstab (1) It first computes all \dras and their maximal proxies with a linear algorithm, referred to as  $\compDRAs$ \cite{journal-version2016}.

\sstab (2) It then pre-computes and stores all the shortest paths and distances between any node in a \dra and its proxy.
%
To support shortest distance queries, for each node in a \dra, we store its proxy $u$, its distance to $u$ and the component of $A^{+}_u$ to which it belongs,
and to support shortest path queries, we further keep the shortest paths from proxy $u$ to all nodes in the \dra.

\sstab (3) It finally computes the reduced subgraph $G'$ by removing all \dras, but keeping their proxies, from graph $G$.

\stitle{2. Query answering}. Given two nodes $s$ and $t$ in graph $G(V$, $E)$  and the pre-computed information, the query answering module executes the following.

\sstab (1) When nodes $s$ and $t$ belong to the same \dra $G[A^+_u]$ with proxy $u$ such that $A^+_u$ = $A^1_u\cup\ldots A^h_u$.

If $s$ and $t$ further fall into the same component $A^i_u$ ($i\in[1,h]$), it invokes the Dijkstra's algorithm on the subgraph $G[A^i_u]$ to compute the shortest path and distance between $s$ and $t$. Otherwise, it simply returns $\path(s, u)/\path(u, t)$ or $\dist(s, u)$ + $\dist(u, t)$ in constant time.

\sstab (2)  When $s$ and $t$ belong to two \dras $G[A^+_{u_s}]$ and $G[A^+_{u_t}]$ with proxies $u_s$ and $u_t$, respectively.

 As shown in Section~\ref{sec-proxy}, we know that $\path(s, t)$ = $\path(s, u_s)/$ $\path(u_s, u_t)/$ $\path(u_t, t)$, in which $\path(s, u_s)$ and $\path(u_t, t)$ are already known. Hence, it simply invokes an algorithm (\eg~\arcflag \cite{MohringSSWW05}, \tnr~\cite{bast2014route}, \ah~\cite{zhu2013shortest}) on the reduced graph $G'$ for computing $\path(u_s, u_t)$.
%
Similarly, it computes $\dist(s, t)$ = $\dist(s, u_s)$ + $\dist(u_s, u_t)$ + $\dist(u_t, t)$.

We have studied how to speed-up (exact)  shortest path and distance queries on large weighted undirected graphs.
To do this, we have proposed  a light-weight data reduction technique, a notion of proxies such that each proxy represents a small subgraph, referred to as \dras, and proxies and \dras can be computed efficiently in linear time.  We have also verified,
both analytically and experimentally, that proxies significantly reduce graph sizes and improve efficiency of existing methods.

\stitle{(3) Ensemble Enabled Link Prediction~\cite{DuanMAMH17}}

The problem of {\em link prediction} or {\em link inference} is that of predicting the formation of future links in a dynamic and
evolving network. The link prediction problem has numerous
applications, such as the recommendation of friends in a social
network, the recommendation of images in a multimedia network, or
the recommendation of collaborators in a scientific network, therefore, link
prediction methods have been extensively studied  because of their numerous applications in various network-centered domains.

Link prediction methods are often applied to very large networks, which are also sparse.  The massive sizes of such networks can
create challenges for the prediction process in spite of their sparsity. This is because the {\em search space} for the link
prediction problem is of the size $O(n^2)$, where $n$ is the number of nodes. Quadratic scalability can rapidly become untenable for
larger networks. In fact, an often overlooked fact is that most {\em current link prediction algorithms evaluate the link
propensities only over a subset of possibilities rather than exhaustively search for link propensities over the entire network}, \eg \cite{dwang,lee,zhao2016,zhu2016}.

In order to understand why this is the case,
consider a network with $10^6$ nodes. Note that a size such as
$10^6$ is not large at all by modern standards, and even common
bibliographic networks such as DBLP now exceed this size. Even
for this modest network, the number of {\em possibilities} for links
is of the order of $10^{12}$. Therefore, a 1GHz processor would
require at least $10^3$ seconds just to allocate one {\em machine cycle} to
every pair of nodes. This implies that in order to determine the
top-ranked link predictions over the {\em entire network}, the
running time will be much larger than $10^3$ seconds.  It is
instructive, therefore, to examine how this (lower bound on) running
time scales with increasing network size. Table~\ref{time} shows the
time requirements for allocating a single machine cycle to each
pair-wise possibility. The running time in this table represent
very optimistic lower bounds on the required time because link
prediction algorithms are complex and require far more than a single
machine cycle for processing a node-pair. Note that for larger
networks, even the presented lower bounds on the running time are
impractical.
\begin{table}
\caption{The $O(n^2)$ problem in link prediction: Time required to
allocate a {\em single machine cycle} to every node-pair possibility
in networks of varying sizes and processors of various speeds.}
\label{time}
\vspace{0ex}
\centering
\begin{tabular}{cccc}
\hline \hline Network Sizes & 1 GHz &  3 GHz & 10 GHz \\
\hline \hline $10^6$ nodes & 1000 sec. & 333 sec. & 100 sec.\\
\hline $10^7$ nodes & 27.8 hrs &  9.3 hrs &  2.78 hrs\\
\hline $10^8$ nodes & $>100$ days &  $>35$ days & $> 10$ days\\
\hline $10^9$ nodes & $>10000$ days & $>3500$ days & $> 1000$ days\\
\hline \hline
\end{tabular}
\vspace{-2ex}
\end{table}

It is noteworthy that most link prediction algorithms in the
literature are not designed to search over the entire space of
$O(n^2)$ possibilities. A closer examination of the relevant
publications shows that even for networks of modest size, these
algorithms perform benchmarking  only by evaluating over a {\em
sample of the possibilities} for links. This is only to be expected
in light of the lower bounds shown in Table~\ref{time}.  In other
words, the {\em complete ranking problem} for link prediction in
very large networks remains largely unsolved at least from a
computational point of view. It is evident from the presented lower
bounds in Table~\ref{time} that any ranking-based link prediction
algorithm {\em must integrate search space pruning} within the
prediction algorithm in order to even  have any  hope of exploring
the $O(n^2)$ search space in a reasonable amount of time. The
algorithmic design of most link prediction algorithms largely
overlooks this basic requirement~\cite{chancc,propflow}.

To this end, we explore an {\em ensemble approach} to
achieving the aforementioned goals.

We show how to make latent factor models
practical for link prediction by decomposing the search space into a
 set of smaller matrices. As a result, large parts of the $O(n^2)$
search space can be pruned without even having to evaluate the
relevant node pairs. An optimizing method is also provided for
speeding up the search process when a threshold is available.
This provides an efficient approach for the
top-$k$ problem in link prediction.

Furthermore, our problem
decomposition method is an ensemble approach enabled with three
structural bagging methods with performance guarantees, which has obvious {\em
effectiveness} advantages. By incorporating with the characteristics of  link prediction, the bagging methods maintain high prediction
accuracy while reducing the network size via graph sampling techniques.
Note that the same bias-variance
tradeoffs apply to the link-prediction problem, as they apply to the
standard classification problem. Therefore, the use of an ensemble
approach has obvious effectiveness advantages as well.

Using real-life datasets, we finally conduct an extensive experimental study, and show that our ensemble approach for link prediction is both effective and efficient.

\eat{
\stitle{(1) Network Anomaly Detection~\cite{HuAMH16}}
We have adopted the idea in the process of dealing with large graphs in the study of anomaly detection in graph streams, when dealing with the matrix representation of a social graph, and  we have both theoretically and experimentally shown that simplifying the matrix by replacing a part of small entry values  with zero has few affects on the computation of eigenvectors~\cite{YuAMW13}.
}%%%%%%%%%%%%EAT

\stitle{Experiences}.  Determining the task relevance is data is the key for data approximation.

### 2018-01-22 ApproxComp/sec-introduction.tex

\section{Introduction}
\label{sec-intro}

1. history  of big data - governmental policy.

%2012年3月29日，美国总统科技政策办公室OSTP（Office of Science and Technology Policy）宣布了每年投资两亿美元的“大数据研究计划”（Big Data R&D Initiative）
%同天，我国科技部发布的“‘十二五’国家科技计划信息技术领域2013年度备选项目征集指南”把“大数据研究”列在首位

%美国2016年5月发布《联邦大数据研究与开发战略计划》
%其目标是对联邦机构的大数据相关项目和投资进行指导,主要围绕代表大数据研发关键领域的七个战略进行，包括促进人类对科学、医学和安全所有分支的认识;确保美国在研发领域继续发挥领导作用；通过研发来提高美国和世界解决紧迫社会和环境问题的能力。

2. progress of applications of big data techniques

3. (machine learning, systems -hadoop, spark)

A fundamental issue for big data analytics is the efficiency. There are different recent advances towards attacking this issues, from theory to algorithms to platforms~\cite{FanGN13,Jordan15,ZahariaXWDADMRV16}.  In this article, we present the idea of two classes of techniques for efficient and effective big
data analytics: query approximation and data approximation, based on our recent research. Different from existing approximation techniques~\cite{CormenLRS01,approx03,FanH14}, the approximation techniques that we are going to introduce are not unnecessarily theoretically bounded with respect to optimal solutions, but are practically useful and interesting.

~\cite{MaLHLH16}

Full-length Contributed Articles should consist of up to 4,000 words, contain no more than 25 references, 3-4 tables, 3-4 figures, and be submitted to: http://cacm.acm.org/submissions.

https://cacm.acm.org/about-communications/author-center/author-guidelines

### 2018-01-22 ApproxComp/sec-query.tex

\section{Query Approximation}
\label{sec-query}

\begin{figure}[tb!]
  \vspace{-1ex}
  \begin{center}
  \includegraphics[scale=0.45]{./queryApprox.png}
  \end{center}
  \vspace{-3ex}
  \caption{Query approximation}\label{fig-tech-queryappro}
  \vspace{-2ex}
\end{figure}

Query approximation deals with complex queries involved with big data analytic tasks. Given a class $Q$ of data analytic queries with higher computational complexity,  query approximation is to transform into another class $Q'$ of queries with lower computational complexity and satisfiable approximate answers, as depicted in Fig.~\ref{fig-tech-queryappro} in which $Q$, $Q'$ and $D$ denote the original query, approximate query and data, respectively. Query approximation needs to reach a balance between the query efficiency and answer accuracy when approximating $Q$ with $Q'$.

The rationale behind query approximation has inexact or approximate answers are acceptable for many big data analytic tasks.
On one hand, when the volume of data is extremely large, it may be impossible or not necessary to compute the exact queries.
Observe that nobody would try each and every store to find a pair of shoes with the best cost-performance ratio.
That is, inexact (approximate) solutions are good candidates in this case.
%
On the other hand, when taking noises (common for big data) into account, it may not always a good idea to compute exact answers
for those data analytic tasks whose answers are rare or hard to identify, such as the detection of homegrown violent extremists (HVEs) who seek to commit acts of terrorism in the United States and abroad~\cite{HungJ16}, as exact solutions may have a high chance to miss possible candidates.

We next explain query approximation computation in more detail with three different data analytic tasks.

\stitle{(1) Strong simulation~\cite{tods-MaCFHW14}}. Given a pattern graph $Q$ and a data graph $G$,
{\em Graph pattern matching} is to find all subgraphs of $G$ that match $Q$, and is being increasingly used in various applications, \eg software, biology, social networks and intelligence analysis.

Here {\em matching} is typically defined in terms of
{\em subgraph isomorphism} \cite{Galla06}:
a subgraph $G_s$ of $G$ {\em matches} $Q$ if
there exists a {\em bijective function} $f$
from the nodes of $Q$ to the nodes in $G_s$ such that (a)  for each
pattern node $u$ in $Q$, $u$ and $f(u)$
have the same label,
and (b) there exists an edge $(u, u')$ in $Q$ if and only
if there exists an edge $(f(u), f(u'))$ in $G_s$.

The goodness of subgraph isomorphism is that all matched subgraphs  are exactly the same as the pattern graph, \ie completely preserving the  topology structure between the pattern graph and data graph. However, subgraph isomorphism is \NP-complete, and may return exponential many matched subgraphs.
Further, subgraph isomorphism is too restrictive to find sensible matches in certain scenarios, as observed in~\cite{FanLMTWW10}. Even worse, online data in many cases only represents a partial world (\eg terrorist collaboration networks and homosexual networks often involve with a large amount of off-line data).
Exact computations on such online data, whose accompanying off-line data is extremely hard to gather, typically decreases the chance of identifying candidate answers.
These hinder the usability of graph pattern matching in emerging applications.

To lower the high complexity of subgraph isomorphism, substitutes for subgraph isomorphism~\cite{FanLMTWW10,FanLMTW11} that allow graph pattern matching to be conducted in cubic-time have been proposed by extending graph simulation~\cite{infsimu95}. However, they fall short of capturing the topology of data graphs, i.e., graphs may have a structure drastically different from pattern graphs they match, and the matches found are often too large to analyze.

To rectify these problems, strong simulation, an ``approximate'' substitute for subgraph isomorphism, was  proposed for graph pattern matching, such that strong simulation (a) theoretically preserves the key topology of pattern graphs and finds a bounded number of matches, (b) retains the same complexity as earlier extensions of graph simulation~\cite{FanLMTWW10,FanLMTW11}, by providing a cubic-time algorithm for computing strong simulation, and (c) has the locality property that allows us to develop an effective distributed algorithm to conduct graph pattern matching on distributed graphs~\cite{tods-MaCFHW14}.

Strong simulation is experimentally verified that it is able to identify sensible matches that are not found by subgraph isomorphism, and it finds high
quality matches that retain graph topology. Indeed, 70\%-80\% of matches found by subgraph
isomorphism are retrieved by strong simulation, without paying the price of intractable complexity (100+ times faster) and large number (or
size) of matches.

\stitle{(3) One-pass Trajectory Compression~\cite{LinMZWH17}}. Nowadays, various sensors are collecting, storing and transmitting
tremendous trajectory data, and it is known that raw trajectory data seriously wastes the storage, network
band and computing resource.  Trajectory Compression techniques are an effective approach to attacking this issue by
compressing data points in a trajectory to a set of continuous
line segments, and are commonly used in practice.

 Though lossless compression methods have no information loss, their compression ratios are poor and queries on the compressed data are time consuming because data reconstructions from the compressed data are typically needed before the queries \cite{Nibali:Trajic} .
Hence, A large number of lossy trajectory compression techniques, most notably the piece-wise line simplification, have been developed.
These techniques focus on good compression ratios with bounded errors, and are the mainstream techniques for trajectory compression.
The idea of piece-wise line simplification (\lsa) comes from computational geometry, whose target is to approximate a given finer piece-wise linear curve by another coarser piece-wise linear curve ({normally} a sub set of the former), such that the maximum distance of the former from the later is bounded by a user specified constant. It is widely used due to its distinct advantages: (a) simple and easy to implement, (b) no need of extra knowledge and suitable for freely  moving  objects, and (c) bounded errors with good compression ratios.

The \lsa algorithms solving the \emph{min-$\#$} problem fall into two categories: {\em optimal} and {\em sub-optimal}.
The \textit{optimal} methods\cite{Imai:Optimal} are to find the minimal number of points or segments to represent the original polygonal lines \wrt an error bound $\epsilon$. The optimal \lsa algorithms have relative high time/space complexities which make them impractical for large trajectory data.
Hence, \textit{sub-optimal} \lsa algorithms have been developed and/or introduced for trajectory compression, including batch algorithms (\eg \cite{Douglas:Peucker}), online algorithms (\eg~\cite{Liu:BQS}) and one-pass algorithms (\eg~\cite{LinMZWH17}).

 We first develop a one-pass error bounded trajectory simplification algorithm that runs in $O(n)$ time and $O(1)$ space. \operb is based on a novel local distance checking method, and equipped with five optimization techniques to further improve its compression ratio. Essentially, fitting function: property...

\stab (2) We then propose an aggressive one-pass error bounded trajectory simplification algorithm (\operab) that remains in $O(n)$ time and $O(1)$ space.
\operba allows interpolating new data points into a trajectory under certain conditions and with practical considerations. The rational lies in that moving objects  have sudden track changes while data points may  not be sampled due to various reasons.

 finally conduct an extensive experimental study, by comparing our algorithms \operaa and \operab with \fbqsa (\emph{the fastest} existing \lsa algorithm) and \dpa (the {\em best} existing \lsa algorithm in terms of {\em compression ratio}). We find that \operaa and \operab are on average $(4.1, 4.1, 5.4, 5.2)$ times faster than \fbqsa on , respectively.
For compression ratios, \operaa is comparable with \dpa, and \operab is better than \dpa that is on average ($84.2\%, 86.4\%, 97.1\%, 94.7\%$) of \dpa , respectively.

\stitle{(2) Dense Temporal Subgraph Computation~\cite{MaHWLH17}}. Dense subgraph discovery and analysis have been widely studied in static networks, such as  finding maximal cliques, k-core analysis and  the Prize Collecting Steiner Tree problem. It is worth pointing out that dense subgraphs are a very general concept, and their concrete semantics highly depend on the studied problems and applications. How to properly transfer or define their semantics over to temporal networks is still in the early stage, not to mention effective and efficient analytic algorithms.

We investigate a special class of temporal networks (see a recent survey \cite{tn-survey}) such that their nodes and edges are kept fixed, but their edge weights constantly and regularly vary with timestamps. Essentially, a temporal network with $T$ timestamps can be viewed as $T$ snapshots of a static network such that the network nodes and edges are kept the same among these $T$ snapshots, while the edge weights vary with network snapthots.
%
Road traffic networks typically fall into this category, and  road traffic analyses are of particular importance for large cities, such as Beijing, New York, London and Paris, that are facing with heavy traffic congestions, one of the great challenges of urban computing.

We also focus on a certain form of dense temporal subgraphs, which was initially studied in \cite{BogdanovMS11}.
Formally speaking, a temporal subgraph corresponds to a connected subgraph measured by the sum of all its edge weights in a time interval, \ie  a continuous sequence of timestamps. Intuitively, a dense subgraph that we consider  corresponds to a  collection of connected highly slow or jam roads (\ie  a jam area) in road networks, lasting for a continuous sequence of snapshots.

However, the problem of  finding dense subgraphs in temporal networks is non-trivial, and it is already \NP-complete even for a temporal network with a single snapshot and with $+1$ or $-1$ edge weights only, as observed in \cite{BogdanovMS11}. Even worse, it remains hard to approximate for temporal networks  with single snapshots. Moreover, given a temporal network with $T$ timestamps, there are a total number of $T*(T+1)/2$ time intervals to consider, which further aggravates the difficulty. Finally, the state of the art solution {\sc meden} \cite{BogdanovMS11} adopts a filter-and-verification framework that {\em even if a large portion of time intervals are filtered, there often remain a large number of time intervals to verify}. Hence, {\sc meden} is not scalable when temporal networks have a large number of nodes/edges or a large number $T$ of timestamps.

 a highly efficient and effective data-driven approach, instead of filter-and-verification, which employs hidden data statistics to find dense temporal subgraphs in large temporal networks.  data-driven approach to identifying $k$ time intervals from a total of $T*(T+1)/2$ ones, striking a balance between quality and efficiency, in which $T$ is the number of snapshots and $k$ is a small constant, \eg 10. This is achieved by exploring the characteristics of time intervals involved with dense subgraphs based on a novel {\em evolving convergence phenomenon}.

Using both real-life and synthetic data, we conduct an extensive experimental study.
(a) We find that the dense subgraphs found by our method {\sc FIDES} have the best quality, \ie about 100.20\% and 100.15\% on average of those found by the state of the art solution {\sc meden}~\cite{BogdanovMS11}, respectively.
(b) Our method {\sc FIDES} is  on average 2,980 and 1,486 times  faster than {\sc meden}, respectively.
(c) Finally, {\sc meden} already ran out of memory for temporal graphs with 150,000 nodes and 2,000 snapshots only.

Temporal network -> dynamic road network -> dense temporal subgraph (definition) -> time interval (FAV)- not big data friendly

Temporal network analysis
has recently attracted more and more attentions

### 2018-01-23 ApproxComp/sec-beyond.tex

@@
 \label{sec-beyond}
+No One-Size-Fits-All
 
@@
 
-Data partitioning, Data indexing and Distributed computing~\cite{MaLHLH16} can also be combined to design query approximation and data approximation approaches for big data analytics.
+Techniques such as data partitioning, data indexing, distributed computing~\cite{MaLHLH16} can also be combined to design query approximation and data approximation approaches for big data analytics.

### 2018-01-23 ApproxComp/sec-introduction.tex

@@
 
-1. history  of big data - governmental policy.
-
-%2012年3月29日，美国总统科技政策办公室OSTP（Office of Science and Technology Policy）宣布了每年投资两亿美元的“大数据研究计划”（Big Data R&D Initiative）
-%同天，我国科技部发布的“‘十二五’国家科技计划信息技术领域2013年度备选项目征集指南”把“大数据研究”列在首位
-
-%美国2016年5月发布《联邦大数据研究与开发战略计划》
-%其目标是对联邦机构的大数据相关项目和投资进行指导,主要围绕代表大数据研发关键领域的七个战略进行，包括促进人类对科学、医学和安全所有分支的认识;确保美国在研发领域继续发挥领导作用；通过研发来提高美国和世界解决紧迫社会和环境问题的能力。
-
-2. progress of applications of big data techniques
-
-3. (machine learning, systems -hadoop, spark)
-
-A fundamental issue for big data analytics is the efficiency.
-There are different recent advances towards attacking this issues, from theory to algorithms to platforms~\cite{FanGN13,Jordan15,ZahariaXWDADMRV16}.
-In this article, we present the idea of two classes of techniques for efficient and effective big
-data analytics: query approximation and data approximation, based on our recent research.
+Over the past a few years, research and development progresses on big data analytics have made significant achievements with the supports from both governments and industries all over the world, such as Spark\footnote{\small \url{https://spark.apache.org}}, IBM Watson\footnote{\small \url{https://www.ibm.com/watson}} and Google AlphaGo\footnote{\small \url{https://deepmind.com/research/alphago}}.
+A fundamental issue for big data analytics is the efficiency, and there are different recent advances towards attacking this issues, from theory to algorithms to platforms~\cite{FanGN13,Jordan15,ZahariaXWDADMRV16}.
+In this article, we shall present the idea of two classes of techniques for efficient and effective big data analytics: query approximation and data approximation, based on our recent research.
 Different from existing approximation techniques~\cite{CormenLRS01,approx03,FanH14}, the approximation techniques that we are going to introduce are not unnecessarily theoretically bounded with respect to optimal solutions, but are practically useful and interesting.
 
-~\cite{MaLHLH16}
+\section{Key Insights}
+\label{sec-insight}
+
+contributions and summary of results
+
+\eat{
+Contributed Articles cover the wide and abundant spectrum of the computing field¡ªits open challenges, technical visions and perspectives, educational aspects, societal impact, significant applications and research results of high significance and broad interest.
+Following the roots of Communications, these submissions are peer-reviewed to ensure the highest quality.
+Topics covered must reach out to a very broad technical audience.
+While articles appearing in an ACM Transactions journal are aimed at a specialized audience, articles in Communications should be aimed at the broad computing and information technology community.
+
+A Contributed Article should set the background and provide introductory references, define fundamental concepts, compare alternate approaches, and explain the significance or application of a particular technology or result by means of well-reasoned text and pertinent graphical material.
+The use of sidebars to illustrate significant points is encouraged.
 
@@
 
-https://cacm.acm.org/about-communications/author-center/author-guidelines
+Submissions to the Contributed Articles section should be accompanied by a cover letter indicating:
+
+? Title and the central theme of the article;
+? Statement addressing why the material is important to the computing field and of value to the Communications reader; and,
+? Names and email addresses of three or more recognized experts who would be considered appropriate to review the submission.
+
+%https://cacm.acm.org/about-communications/author-center/author-guidelines
+
+%Lionel M. Ni
+%Elisa Bertino
+%Yannis Ioannidis
+
+}

### 2018-01-23 ApproxComp/sec-query.tex

@@
 \label{sec-query}
-
-\begin{figure}[tb!]
-  \vspace{-1ex}
-  \begin{center}
-  \includegraphics[scale=0.45]{./queryApprox.png}
-  \end{center}
-  \vspace{-3ex}
-  \caption{Query approximation}\label{fig-tech-queryappro}
-  \vspace{-2ex}
-\end{figure}
 
@@
 
-\stitle{(1) Strong simulation~\cite{tods-MaCFHW14}}. Given a pattern graph $Q$ and a data graph $G$,
+\begin{figure}[tb!]
+  \vspace{-1ex}
+  \begin{center}
+  \includegraphics[scale=0.45]{./queryApprox.png}
+  \end{center}
+  \vspace{-3ex}
+  \caption{Query approximation}\label{fig-tech-queryappro}
+  \vspace{-2ex}
+\end{figure}
+
+\stitle{(1) Strong Simulation~\cite{tods-MaCFHW14}}. Given a pattern graph $Q$ and a data graph $G$,
 {\em Graph pattern matching} is to find all subgraphs of $G$ that match $Q$, and is being increasingly used in various applications, \eg software, biology, social networks and intelligence analysis.
@@
 
-\stitle{(3) One-pass Trajectory Compression~\cite{LinMZWH17}}. Nowadays, various sensors are collecting, storing and transmitting
-tremendous trajectory data, and it is known that raw trajectory data seriously wastes the storage, network
-band and computing resource.  Trajectory Compression techniques are an effective approach to attacking this issue by
-compressing data points in a trajectory to a set of continuous
-line segments, and are commonly used in practice.
+\stitle{(3) One-Pass Trajectory Compression~\cite{LinMZWH17}}.
+Trajectory compression (also known as trajectory simplification) is to compress data points in a trajectory to a set of continuous line segments, and is commonly used  in practice.
 
- Though lossless compression methods have no information loss, their compression ratios are poor and queries on the compressed data are time consuming because data reconstructions from the compressed data are typically needed before the queries \cite{Nibali:Trajic} .
-Hence, A large number of lossy trajectory compression techniques, most notably the piece-wise line simplification, have been developed.
-These techniques focus on good compression ratios with bounded errors, and are the mainstream techniques for trajectory compression.
-The idea of piece-wise line simplification (\lsa) comes from computational geometry, whose target is to approximate a given finer piece-wise linear curve by another coarser piece-wise linear curve ({normally} a sub set of the former), such that the maximum distance of the former from the later is bounded by a user specified constant.
+Though lossless compression methods incur no information loss, their compression ratios are typically poor, and querying on the compressed data is time consuming due to the reconstruction of the original data \cite{Nibali:Trajic}.
+Hence, lossy techniques become the mainstream for trajectory compression,
+which provide approximate solutions with good compression ratios and bounded errors.
+
+Piece-wise line simplification (\lsa) comes from computational geometry, whose target is to approximate a given finer piece-wise linear curve by another coarser piece-wise linear curve ({normally} a sub set of the former), such that the maximum distance of the former from the later is bounded by a user specified constant.
 It is widely used due to its distinct advantages: (a) simple and easy to implement, (b) no need of extra knowledge and suitable for freely  moving  objects, and (c) bounded errors with good compression ratios.
 
-The \lsa algorithms solving the \emph{min-$\#$} problem fall into two categories: {\em optimal} and {\em sub-optimal}.
-The \textit{optimal} methods\cite{Imai:Optimal} are to find the minimal number of points or segments to represent the original polygonal lines \wrt an error bound $\epsilon$.
-The optimal \lsa algorithms have relative high time/space complexities which make them impractical for large trajectory data.
-Hence, \textit{sub-optimal} \lsa algorithms have been developed and/or introduced for trajectory compression, including batch algorithms (\eg \cite{Douglas:Peucker}), online algorithms (\eg~\cite{Liu:BQS}) and one-pass algorithms (\eg~\cite{LinMZWH17}).
+\lsa algorithms fall into two categories: {\em optimal} and {\em approximate}.
+Optimal methods\cite{Imai:Optimal} are to find the minimum number of points or segments to represent the original polygonal lines \wrt an error bound $\epsilon$.
+They have higher time and space complexities, and are not practical for large trajectory data.
+Hence,  various approximate \lsa algorithms have been developed, from batch algorithms (\eg \cite{Douglas:Peucker}) to online algorithms (\eg~\cite{Liu:BQS}) and to one-pass algorithms (\eg~\cite{LinMZWH17}).
 
- We first develop a one-pass error bounded trajectory simplification algorithm that runs in $O(n)$ time and $O(1)$ space.
-\operb is based on a novel local distance checking method, and equipped with five optimization techniques to further improve its compression ratio.
-Essentially, fitting function: property...
+An \lsa algorithm is {\em one-pass} if it processes each point in a trajectory once and only once when compressing the trajectory.
+Obviously, one-pass algorithms have low time and space complexities, and are more appropriate for online processing, and
+the difficulty comes from the need to achieve effective compression ratios.
+Existing trajectory simplification algorithms (\eg \cite{Douglas:Peucker} and online algorithms  (\eg \cite{Liu:BQS}) essentially employ a global distance checking approach to assuring error bounds, although online algorithms restrict the checking within a window.
+That is to say, whenever a new directed line segment is formed, these algorithms always check its distances to all or a subset of data points, and, therefore, a data point is checked multiple times, depending on its order in the trajectory and the number of directed line segments formed.
+Hence, {\em an appropriate local distance checking approach is needed in the first place for designing one-pass trajectory simplification algorithms}.
 
-\stab (2) We then propose an aggressive one-pass error bounded trajectory simplification algorithm (\operab) that remains in $O(n)$ time and $O(1)$ space.
-\operba allows interpolating new data points into a trajectory under certain conditions and with practical considerations.
-The rational lies in that moving objects  have sudden track changes while data points may  not be sampled due to various reasons.
-
- finally conduct an extensive experimental study, by comparing our algorithms \operaa and \operab with \fbqsa (\emph{the fastest} existing \lsa algorithm) and \dpa (the {\em best} existing \lsa algorithm in terms of {\em compression ratio}).
-We find that \operaa and \operab are on average $(4.1, 4.1, 5.4, 5.2)$ times faster than \fbqsa on , respectively.
-For compression ratios, \operaa is comparable with \dpa, and \operab is better than \dpa that is on average ($84.2\%, 86.4\%, 97.1\%, 94.7\%$) of \dpa , respectively.
+ We develop a  fitting function such that a data point is checked only once during the entire process of trajectory simplification.
+Based on the fitting function, we develop one-pass error bounded trajectory simplification algorithms that scan each data point in a trajectory once and only once.
+By comparing our algorithms with \fbqsa (\emph{the fastest} existing \lsa algorithm) and \dpa (the {\em best} existing \lsa algorithm in terms of {\em compression ratio}).
+We find that algorithms are more than four times faster than \fbqsa, and have  comparable compression ratios with \dpa.
 
@@
 data-driven approach to identifying $k$ time intervals from a total of $T*(T+1)/2$ ones, striking a balance between quality and efficiency, in which $T$ is the number of snapshots and $k$ is a small constant, \eg 10.
-This is achieved by exploring the characteristics of time intervals involved with dense subgraphs based on a novel {\em evolving convergence phenomenon}.
+This is achieved by exploring the characteristics of time intervals involved with dense subgraphs based on a novel {\em evolving convergence phenomenon}~\footnote{\small \url{https://en.wikipedia.org/wiki/Convergent_evolution}}.
 

### 2018-01-24 ApproxComp/sec-introduction.tex

@@
 In this article, we shall present the idea of two classes of techniques for efficient and effective big data analytics: query approximation and data approximation, based on our recent research.
-Different from existing approximation techniques~\cite{CormenLRS01,approx03,FanH14}, the approximation techniques that we are going to introduce are not unnecessarily theoretically bounded with respect to optimal solutions, but are practically useful and interesting.
+Different from existing approximation techniques~\cite{CormenLRS01,approx03,FanH14}, the approximation computation that we are going to introduce is not unnecessarily theoretically bounded with respect to optimal solutions, but are practically useful and interesting.
 

### 2018-01-24 ApproxComp/sec-query.tex

@@
 
-\stitle{(3) One-Pass Trajectory Compression~\cite{LinMZWH17}}.
+\stitle{(2) One-Pass Trajectory Compression~\cite{LinMZWH17}}.
 Trajectory compression (also known as trajectory simplification) is to compress data points in a trajectory to a set of continuous line segments, and is commonly used  in practice.
@@
 the difficulty comes from the need to achieve effective compression ratios.
-Existing trajectory simplification algorithms (\eg \cite{Douglas:Peucker} and online algorithms  (\eg \cite{Liu:BQS}) essentially employ a global distance checking approach to assuring error bounds, although online algorithms restrict the checking within a window.
+Existing trajectory simplification algorithms (\eg \cite{Douglas:Peucker}) and online algorithms  (\eg \cite{Liu:BQS}) essentially employ a global distance checking approach to assuring error bounds, although online algorithms restrict the checking within a window.
 That is to say, whenever a new directed line segment is formed, these algorithms always check its distances to all or a subset of data points, and, therefore, a data point is checked multiple times, depending on its order in the trajectory and the number of directed line segments formed.
@@
 Based on the fitting function, we develop one-pass error bounded trajectory simplification algorithms that scan each data point in a trajectory once and only once.
-By comparing our algorithms with \fbqsa (\emph{the fastest} existing \lsa algorithm) and \dpa (the {\em best} existing \lsa algorithm in terms of {\em compression ratio}).
-We find that algorithms are more than four times faster than \fbqsa, and have  comparable compression ratios with \dpa.
+By comparing our algorithms with \fbqsa (\emph{the fastest} existing \lsa online algorithm \cite{Liu:BQS}) and \dpa (the {\em best} existing \lsa batch algorithm in terms of {\em compression ratio} \cite{Douglas:Peucker}), our one-pass algorithms are over four times faster than \fbqsa, and have  comparable compression ratios with \dpa.
 
-\stitle{(2) Dense Temporal Subgraph Computation~\cite{MaHWLH17}}.
-Dense subgraph discovery and analysis have been widely studied in static networks, such as  finding maximal cliques, k-core analysis and  the Prize Collecting Steiner Tree problem.
-It is worth pointing out that dense subgraphs are a very general concept, and their concrete semantics highly depend on the studied problems and applications.
-How to properly transfer or define their semantics over to temporal networks is still in the early stage, not to mention effective and efficient analytic algorithms.
+\stitle{(3) Dense Temporal Subgraph Computation~\cite{MaHWLH17}}.
+We study dense subgraphs in {\em a special type of temporal networks} such that their nodes and edges are kept fixed, but their edge weights constantly and regularly vary with timestamps~\cite{MaHWLH17}.
+Essentially, a temporal network with $T$ timestamps can be viewed as $T$ snapshots of a static network such that the network nodes and edges are kept the same among these $T$ snapshots, while the edge weights vary with network snapthots.
+Road traffic networks typically fall into this category of temporal networks, and dense subgraphs are used for road traffic analyses that are of particular importance for large cities, such as Beijing, New York, London and Paris, that are facing with heavy traffic congestions, one of the great challenges of urban computing.
 
-We investigate a special class of temporal networks (see a recent survey \cite{tn-survey}) such that their nodes and edges are kept fixed, but their edge weights constantly and regularly vary with timestamps.
-Essentially, a temporal network with $T$ timestamps can be viewed as $T$ snapshots of a static network such that the network nodes and edges are kept the same among these $T$ snapshots, while the edge weights vary with network snapthots.
-%
-Road traffic networks typically fall into this category, and  road traffic analyses are of particular importance for large cities, such as Beijing, New York, London and Paris, that are facing with heavy traffic congestions, one of the great challenges of urban computing.
+Dense subgraphs are a general concept, and their concrete semantics highly depend on the studied problems and applications.
+Though  dense subgraph discovery and analysis have been widely studied in static networks, how to properly transfer or define their semantics over to temporal networks is still in the early stage, not to mention effective and efficient analytic algorithms.
 
-We also focus on a certain form of dense temporal subgraphs, which was initially studied in \cite{BogdanovMS11}.
-Formally speaking, a temporal subgraph corresponds to a connected subgraph measured by the sum of all its edge weights in a time interval, \ie  a continuous sequence of timestamps.
+We adopt the {\em form of dense temporal subgraphs} initially defined and studied in \cite{BogdanovMS11}, such that a temporal subgraph corresponds to a connected subgraph measured by the sum of all its edge weights in a time interval, \ie  a continuous sequence of timestamps.
 Intuitively, a dense subgraph that we consider  corresponds to a  collection of connected highly slow or jam roads (\ie  a jam area) in road networks, lasting for a continuous sequence of snapshots.
 
-However, the problem of  finding dense subgraphs in temporal networks is non-trivial, and it is already \NP-complete even for a temporal network with a single snapshot and with $+1$ or $-1$ edge weights only, as observed in \cite{BogdanovMS11}.
+The problem of  finding dense subgraphs in temporal networks is non-trivial, and it is already \NP-complete even for a temporal network with a single snapshot and with $+1$ or $-1$ edge weights only, as observed in \cite{BogdanovMS11}.
 Even worse, it remains hard to approximate for temporal networks  with single snapshots.
 Moreover, given a temporal network with $T$ timestamps, there are a total number of $T*(T+1)/2$ time intervals to consider, which further aggravates the difficulty.
-Finally, the state of the art solution {\sc meden} \cite{BogdanovMS11} adopts a filter-and-verification framework that {\em even if a large portion of time intervals are filtered, there often remain a large number of time intervals to verify}.
-Hence, {\sc meden} is not scalable when temporal networks have a large number of nodes/edges or a large number $T$ of timestamps.
 
- a highly efficient and effective data-driven approach, instead of filter-and-verification, which employs hidden data statistics to find dense temporal subgraphs in large temporal networks.
-data-driven approach to identifying $k$ time intervals from a total of $T*(T+1)/2$ ones, striking a balance between quality and efficiency, in which $T$ is the number of snapshots and $k$ is a small constant, \eg 10.
-This is achieved by exploring the characteristics of time intervals involved with dense subgraphs based on a novel {\em evolving convergence phenomenon}~\footnote{\small \url{https://en.wikipedia.org/wiki/Convergent_evolution}}.
+The state of the art solution {\sc meden} \cite{BogdanovMS11} adopts a filter-and-verification framework that {\em even if a large portion of time intervals are filtered, there often remain a large number of time intervals to verify}.
+This is not big data friendly, and it is not scalable when temporal networks have a large number of nodes/edges or a large number $T$ of timestamps.
 
-Using both real-life and synthetic data, we conduct an extensive experimental study.
-(a) We find that the dense subgraphs found by our method {\sc FIDES} have the best quality, \ie about 100.20\% and 100.15\% on average of those found by the state of the art solution {\sc meden}~\cite{BogdanovMS11}, respectively.
-(b) Our method {\sc FIDES} is  on average 2,980 and 1,486 times  faster than {\sc meden}, respectively.
-(c) Finally, {\sc meden} already ran out of memory for temporal graphs with 150,000 nodes and 2,000 snapshots only.
-
-Temporal network -> dynamic road network -> dense temporal subgraph (definition) -> time interval (FAV)- not big data friendly
-
-Temporal network analysis
-has recently attracted more and more attentions
+We develop a data-driven approach, instead of filter-and-verification, to  identifying the most possible $k$ time intervals from $T \times (T + 1)/2$ time intervals, in which $T$ is the number of snapshots and k is a small constant, \eg 10.
+This is achieved by exploring the characteristics of time intervals involved with dense subgraphs based on the observation of {\em evolving convergence phenomenon} in traffic data, inspired by the convergent evolution in nature~\footnote{\small \url{https://en.wikipedia.org/wiki/Convergent_evolution}}.
+Using both real-life and synthetic data, we experimentally show that Our method {\sc fides} is over 1000 times faster than the state of the art solution {\sc meden}~\cite{BogdanovMS11}, while the quality of dense subgraphs found is comparable with {\sc meden}.

### 2018-01-24 ApproxComp/sec-data.tex

@@
 \label{sec-data}
+
+Big data has large volume, and, hence, the space complexity of big data analytic tasks starts raising more concerns.
+Given a class $Q$ of queries on a data set $D$, data approximation is to transform $D$ into a smaller data set $D'$ such that $Q$ on $D'$ returns a satisfiable approximate answer in a more efficient way.
+Further, it is typically common that query $Q$ needs to be (slightly) modified to $Q'$ to accommodate  the changes of $D$ to $D'$, as shown in Fig.~\ref{fig-tech-dataappro}.
+Similar to query approximation, data approximation needs to reach a balance between the query efficiency and answer accuracy.
+
+The rationale of data approximation has roots in the Pareto principle\footnote{\small \url{https://en.wikipedia.org/wiki/Pareto_principle}} that ``states that, for many events, roughly 80\% of the effects come from 20\% of the causes''.
+The critical thing for data approximation is to determine which part of data is relevant to tasks (belong to the 20\%).
+ By this principle, for many big analytic tasks, one may only need to keep a small amount of the data to derive ``satisfiable'' answers.
+For example, when we are to build a predictive model on the stock of razers for an online store based on the order history of customers, orders from men are good enough.
+While on the stock of lipsticks, those from women are good enough.
+That is to say,  it is not necessary to use the entire data for certain data analytic tasks.
+
+However, it should be pointed out that there are data analytic tasks such that data approximation could not work well.
+For example, an online store needs to count the total number of goods in its catalog.
+Essentially the entire goods should be considered for this task, and if a (small) portion of goods are chosen, it is hard to have a ``satisfiable'' result.
+
+We next explain data approximation computation in more detail with three different data analytic tasks.
+
+\stitle{(1) Proxies for Shortest Paths and Distances~\cite{MaFLWCH16}}.
+Computing shortest paths and distances is one of the fundamental problems on graphs.
+We study the {\em node-to-node shortest path} ({\em distance}) problem on large graphs: given a weighted undirected graph $G(V, E)$ with non-negative edge weights, and two nodes of $G$, the source $s$ and the target $t$, find the shortest path (distance) from $s$ to $t$ in $G$.
+The Dijkstra's algorithm with Fibonacci heaps runs in $O(n\log n + m)$ due to Fredman \& Tarjan~\cite{CormenLRS01}, where $n$ and $m$ denote the numbers of nodes and edges in a graph, respectively, which remains asymptotically the fastest known solution on arbitrary undirected graphs with non-negative edge weights.
+%The challenge of computing shortest paths on large graphs.
+However, computing shortest  paths and distances remains a challenging problem, in terms of both time and space cost, on large-scale graphs.
+Hence, various optimizations have been developed to speed-up the computation.
+
+To speed-up shortest  path and distance queries, we propose {\em proxies} that have the following properties:
+%
+(a) each proxy captures a set of nodes in a graph, referred to as \dra, 
+%
+(b) a small number of proxies can represent a large number of nodes in a graph,
+%
+(c) shortest paths and distances involved within the set of nodes being represented by the same proxies can be answered efficiently, and,
+%
+(d) the proxies and the set of nodes being represented can be computed efficiently in {\em linear} time.
+
+The framework for speeding-up shortest path and distance queries with proxies consists of two modules: preprocessing and query answering
+
+\ni(a) {\em Preprocessing}: Given graph $G(V, E)$, it first computes all \dras and their maximal proxies in linear time, then it computes and stores all the shortest paths and distances between any node and its proxy.
+It finally computes the reduced subgraph $G'$ by removing all \dras, but keeping their proxies, from graph $G$.
+
+\ni(b) {\em Query answering}. Given two nodes $s$ and $t$ in graph $G(V$, $E)$  and the pre-computed information, the query answering module essentially executes the following.
+
+The shortest path $\path(s, t)$ = $\path(s, u_s)/$ $\path(u_s, u_t)/$ $\path(u_t, t)$, where $u_s$ and $u_t$ are the proxies of $s$ and $t$, respectively.
+Here  $\path(s, u_s)$ and $\path(u_t, t)$ are pre-computed, and $\path(u_s, u_t)$ can be computed on the reduced subgraph $G'$ by invoking any existing 
+(\eg \ah~\cite{zhu2013shortest}). 
+%
+The shortest distance $\dist(s, t)$ = $\dist(s, u_s)$ + $\dist(u_s, u_t)$ + $\dist(u_t, t)$ can be computed similarly.
+
+We show experimentally that about $1/3$  nodes of social networks and road networks  are captured by by proxies, leaving $2/3$ in the reduced graphs.
+Hence, we propose a light-weight data reduction technique for speeding-up (exact)  shortest path and distance queries on large weighted undirected graphs~\cite{MaFLWCH16}.
 
@@
 
-Big data has large volume, and, hence, the space complexity of big data analytic tasks starts raising more concerns.
-Given a class $Q$ of queries on a data set $D$, data approximation is to transform $D$ into a smaller data set $D'$ such that $Q$ on $D'$ returns a satisfiable approximate answer in a more efficient way.
-Further, it is typically common that query $Q$ needs to be (slightly) modified to $Q'$ to accommodate  the changes of $D$ to $D'$, as shown in Fig.~\ref{fig-tech-dataappro}.
-Similar to query approximation, data approximation needs to reach a balance between the query efficiency and answer accuracy.
-
-The rationale of data approximation has roots in the Pareto principle\footnote{\small \url{https://en.wikipedia.org/wiki/Pareto_principle}} that ``states that, for many events, roughly 80\% of the effects come from 20\% of the causes''.
-By this principle, for many big analytic tasks, one may only need to keep a small amount of the data to derive ``satisfiable'' answers.
-For example, when we are to build a predictive model on the stock of razers for an online store based on the order history of customers, orders from men are good enough.
-While on the stock of lipsticks, those from women are good enough.
-That is to say,  it is not necessary to use the entire data for certain data analytic tasks.
-
-However, it should be pointed out that there are data analytic tasks such that data approximation could not work well.
-For example, an online store needs to count the total number of goods in its catalog.
-Essentially the entire goods should be considered for this task, and if a (small) portion of goods are chosen, it is hard to have a ``satisfiable'' result.
-
-We next explain data approximation computation in more detail with three different data analytic tasks.
-
-\stitle{(2) Proxies for Shortest Paths/Distances~\cite{MaFLWCH16}}
-
-We study the {\em node-to-node shortest path} ({\em distance}) problem on large graphs: given a weighted undirected graph $G(V, E)$ with non-negative edge weights, and two nodes of $G$, the source $s$ and the target $t$, find the shortest path (distance) from $s$ to $t$ in $G$.
-The Dijkstra's algorithm with Fibonacci heaps runs in $O(n\log n + m)$ due to Fredman \& Tarjan~\cite{CormenLRS01}, where $n$ and $m$ denote the numbers of nodes and edges in a graph, respectively, which remains asymptotically the fastest known solution on arbitrary undirected graphs with non-negative edge weights.
-%The challenge of computing shortest paths on large graphs.
-However, computing shortest  paths and distances remains a challenging problem, in terms of both time and space cost, on large-scale graphs.
-Hence, various optimizations have been developed to speed-up the computation.
-
-To speed-up shortest  path and distance queries, our approach is to use {\em representatives}, each of which captures a set of nodes in a graph.
-The task of finding a proper form of representatives is, however, {\em nontrivial}.
-Intuitively, we expect representatives to have the following properties.
-%
-(1) A small number of representatives can represent a large number of nodes in a graph;
-%
-(2) Shortest paths and distances involved within the set of nodes being represented by the same representative can be answered efficiently; And,
-%
-(3) the representatives and the set of nodes being represented can be computed efficiently.
-
-\stitle{1. Preprocessing}. Given graph $G(V, E)$, the preprocessing module executes the following.
-
-\sstab (1) It first computes all \dras and their maximal proxies with a linear algorithm, referred to as  $\compDRAs$ \cite{journal-version2016}.
-
-\sstab (2) It then pre-computes and stores all the shortest paths and distances between any node in a \dra and its proxy.
-%
-To support shortest distance queries, for each node in a \dra, we store its proxy $u$, its distance to $u$ and the component of $A^{+}_u$ to which it belongs,
-and to support shortest path queries, we further keep the shortest paths from proxy $u$ to all nodes in the \dra.
-
-\sstab (3) It finally computes the reduced subgraph $G'$ by removing all \dras, but keeping their proxies, from graph $G$.
-
-\stitle{2. Query answering}. Given two nodes $s$ and $t$ in graph $G(V$, $E)$  and the pre-computed information, the query answering module executes the following.
-
-\sstab (1) When nodes $s$ and $t$ belong to the same \dra $G[A^+_u]$ with proxy $u$ such that $A^+_u$ = $A^1_u\cup\ldots A^h_u$.
-
-If $s$ and $t$ further fall into the same component $A^i_u$ ($i\in[1,h]$), it invokes the Dijkstra's algorithm on the subgraph $G[A^i_u]$ to compute the shortest path and distance between $s$ and $t$.
-Otherwise, it simply returns $\path(s, u)/\path(u, t)$ or $\dist(s, u)$ + $\dist(u, t)$ in constant time.
-
-\sstab (2)  When $s$ and $t$ belong to two \dras $G[A^+_{u_s}]$ and $G[A^+_{u_t}]$ with proxies $u_s$ and $u_t$, respectively.
-
- As shown in Section~\ref{sec-proxy}, we know that $\path(s, t)$ = $\path(s, u_s)/$ $\path(u_s, u_t)/$ $\path(u_t, t)$, in which $\path(s, u_s)$ and $\path(u_t, t)$ are already known.
-Hence, it simply invokes an algorithm (\eg~\arcflag \cite{MohringSSWW05}, \tnr~\cite{bast2014route}, \ah~\cite{zhu2013shortest}) on the reduced graph $G'$ for computing $\path(u_s, u_t)$.
-%
-Similarly, it computes $\dist(s, t)$ = $\dist(s, u_s)$ + $\dist(u_s, u_t)$ + $\dist(u_t, t)$.
-
-We have studied how to speed-up (exact)  shortest path and distance queries on large weighted undirected graphs.
-To do this, we have proposed  a light-weight data reduction technique, a notion of proxies such that each proxy represents a small subgraph, referred to as \dras, and proxies and \dras can be computed efficiently in linear time.
-We have also verified,
-both analytically and experimentally, that proxies significantly reduce graph sizes and improve efficiency of existing methods.
-
-\stitle{(3) Ensemble Enabled Link Prediction~\cite{DuanMAMH17}}
+\stitle{(2) Ensemble Enabled Link Prediction~\cite{DuanMAMH17}}
 
@@
 }%%%%%%%%%%%%EAT
-
-\stitle{Experiences}.  Determining the task relevance is data is the key for data approximation.

### 2018-01-25 ApproxComp/sec-data.tex

@@
 
-The framework for speeding-up shortest path and distance queries with proxies consists of two modules: preprocessing and query answering
+The framework for speeding-up shortest path and distance queries with proxies consists of modules preprocessing and query answering as follows.
 
@@
 
+without losing any accuracy
+
 \begin{figure}[tb!]
@@
 
-\stitle{(2) Ensemble Enabled Link Prediction~\cite{DuanMAMH17}}
+\stitle{(2) Ensemble Enabled Link Prediction~\cite{DuanMAMH17}}.
+Link prediction is the task to predict the formation of future links in a dynamic and evolving network, and has been extensively studied due to its numerous applications, such as the recommendation of friends in a social network, images in a multimedia network, or
+collaborators in a scientific network.
 
-The problem of {\em link prediction} or {\em link inference} is that of predicting the formation of future links in a dynamic and
-evolving network. The link prediction problem has numerous
-applications, such as the recommendation of friends in a social
-network, the recommendation of images in a multimedia network, or
-the recommendation of collaborators in a scientific network, therefore, link
-prediction methods have been extensively studied  because of their numerous applications in various network-centered domains.
-
-Link prediction methods are often applied to very large networks, which are also sparse.  The massive sizes of such networks can
-create challenges for the prediction process in spite of their sparsity. This is because the {\em search space} for the link
-prediction problem is of the size $O(n^2)$, where $n$ is the number of nodes. Quadratic scalability can rapidly become untenable for
-larger networks. In fact, an often overlooked fact is that most {\em current link prediction algorithms evaluate the link
-propensities only over a subset of possibilities rather than exhaustively search for link propensities over the entire network}, \eg \cite{dwang,lee,zhao2016,zhu2016}.
-
-In order to understand why this is the case,
-consider a network with $10^6$ nodes. Note that a size such as
-$10^6$ is not large at all by modern standards, and even common
-bibliographic networks such as DBLP now exceed this size. Even
-for this modest network, the number of {\em possibilities} for links
-is of the order of $10^{12}$. Therefore, a 1GHz processor would
-require at least $10^3$ seconds just to allocate one {\em machine cycle} to
+Link prediction methods are often applied to very large and sparse networks, which has a large {\em search space} $O(n^2)$, 
+where $n$ is the number of nodes.
+Hence, the scalability is a big challenge.
+In fact, an often overlooked fact is that most {\em exiting link prediction algorithms evaluate the link propensities only over a subset of possibilities rather than all propensities over the entire network}, \eg \cite{zhu2016}.
+In order to understand why this is the case, consider a large network with $10^8$ nodes. Its number of {\em possibilities} for links
+is of the order of $10^{16}$. Therefore, a 3GHz processor would
+require at least $35$ days just to allocate one {\em machine cycle} to
 every pair of nodes. This implies that in order to determine the
 top-ranked link predictions over the {\em entire network}, the
-running time will be much larger than $10^3$ seconds.  It is
-instructive, therefore, to examine how this (lower bound on) running
-time scales with increasing network size. Table~\ref{time} shows the
-time requirements for allocating a single machine cycle to each
-pair-wise possibility. The running time in this table represent
-very optimistic lower bounds on the required time because link
-prediction algorithms are complex and require far more than a single
-machine cycle for processing a node-pair. Note that for larger
-networks, even the presented lower bounds on the running time are
-impractical.
+running time will be much much larger than $35$ days.
+
+It is noteworthy that most existing link prediction algorithms are not designed to search over the entire 
+$O(n^2)$ possibilities. A closer examination of the relevant
+studies shows that even for networks of modest size, these
+algorithms perform benchmark evaluations over a {\em
+sample of the possibilities} for links.  In other
+words, the {\em complete ranking problem for link prediction in
+very large networks remains challenging at least from a
+computational point of view}.
+
+\eat{%%%%%%%
 \begin{table}
@@
 \end{table}
-
-It is noteworthy that most link prediction algorithms in the
-literature are not designed to search over the entire space of
-$O(n^2)$ possibilities. A closer examination of the relevant
-publications shows that even for networks of modest size, these
-algorithms perform benchmarking  only by evaluating over a {\em
-sample of the possibilities} for links. This is only to be expected
-in light of the lower bounds shown in Table~\ref{time}.  In other
-words, the {\em complete ranking problem} for link prediction in
-very large networks remains largely unsolved at least from a
-computational point of view. It is evident from the presented lower
-bounds in Table~\ref{time} that any ranking-based link prediction
-algorithm {\em must integrate search space pruning} within the
-prediction algorithm in order to even  have any  hope of exploring
-the $O(n^2)$ search space in a reasonable amount of time. The
-algorithmic design of most link prediction algorithms largely
-overlooks this basic requirement~\cite{chancc,propflow}.
+}%%%%%%%%%%%
 

### 2018-01-25 ApproxComp/sec-beyond.tex

--- 2018-01-22 ApproxComp/sec-beyond.tex
@@
 
-There exist no single techniques fit all for big data analytics, and  it is often necessary to combine different techniques to obtain satisfiable solutions. 
-We have seen that data sampling and data compression techniques help to achieve a balance between efficiency and effectiveness. 
-We next roughly introduce three other potential techniques used for big data analytics.
-
-When there are data updates, query answers typically need to be re-computed to reflect the changes.
-Incremental computation is a technique that attempts to reduce computations by reusing previous computing efforts and only computing those answers that ``depend on'' the changed data.
-
- incremental algorithms have been developed for
-various applications.  Thomas W. Reps has done pioneering work on the study of incremental computation, and he observed that
-the complexity of incremental algorithms was more accurately characterized
-in terms of the size of the area affected by the updates, rather than the size
-of the entire input~\cite{Reps96}.
-
-One may notice that incremental algorithms can be utilized to achieve query approximation.
-
-Data partitioning, Data indexing and Distributed computing~\cite{MaLHLH16} can also be combined to design query approximation and data approximation approaches for big data analytics.
+  For big data analytics, there are no one-size-fits-all techniques.  it is often necessary to combine different techniques to obtain good solutions.
+We have seen that data sampling helps to achieve a balance between efficiency and effectiveness for link prediction,
+and other techniques, \eg incremental computation, data partitioning, data indexing and distributed computing~\cite{MaLHLH16} can
+also be unitized to  design query and data approximation techniques for big data analytics. 
+For instance, it is easy to see that incremental algorithms can be utilized to achieve query approximation.

### 2018-01-25 ApproxComp/sec-conclusion.tex

@@
 
-In this article we have introduced approximation computation techniques toward efficient and effective big data analytics.
-
-First we see the importance of graph search by investigating the applications in industry, academia research developments, and the historical development of search.
-And then, we have introduced and analyzed three types of graph search: cohesive subgraph,keyword search on graphs and graph
-pattern matching. Finally, we have pointed out the problems and challenges graph search confronts and presented some useful techniques to deal with the problems.\par
-\, As a a new paradigm for social computing, graph search has received extensive attentions.
-However, there are still a lot of questions to be solved in graph search, which is also a challenge for us.\par
+In this article we have systematiclly introduced approximation computation techniques toward efficient and effective big data analytics.
+Furthermore, although approximate computation does not put
+theoretical bounds with respect to optimal solutions, it does expect a balance between efficiency and accuracy.
+Indeed, (1) our query approximation techniques~\cite{tods-MaCFHW14,LinMZWH17,MaHWLH17} show that efficiency can be obtained efficiency with high accuracy in practice, and (2) our data approximation techniques for shortest paths and distances and link prediction~\cite{MaFLWCH16,DuanMAMH17} show that efficiency and accuracy can be obtained for certain data analytic tasks.
+That is, the design policy approximate computation of is not to sacrifice accuracy for efficiency, but to achieve both efficiency and effectiveness in practice.

### 2018-01-25 ApproxComp/sec-data.tex

@@
 
-We show experimentally that about $1/3$  nodes of social networks and road networks  are captured by by proxies, leaving $2/3$ in the reduced graphs.
+We show experimentally show that about $1/3$  nodes of real-life social networks and road networks  are captured by by proxies, leaving $2/3$ in the reduced graphs.
 Hence, we propose a light-weight data reduction technique for speeding-up (exact)  shortest path and distance queries on large weighted undirected graphs~\cite{MaFLWCH16}.
-
-without losing any accuracy
 
@@
 Hence, the scalability is a big challenge.
-In fact, an often overlooked fact is that most {\em exiting link prediction algorithms evaluate the link propensities only over a subset of possibilities rather than all propensities over the entire network}, \eg \cite{zhu2016}.
+In fact, an often overlooked fact is that most {\em exiting link prediction algorithms evaluate the link propensities only over a subset of possibilities rather than all propensities over the entire network}.
 In order to understand why this is the case, consider a large network with $10^8$ nodes. Its number of {\em possibilities} for links
@@
 
+Latent factor models have been shown to be wildly successful in the domain of
+collaborative filtering, but not link prediction in spite of the obvious
+similarity between link prediction and collaborative filtering and
+the obvious effectiveness of latent factor models. One of the reasons why latent factor models are rarely used for
+link prediction is due to their complexity. In
+collaborative filtering applications, the item dimension is of the
+order of a few hundred thousand, whereas even the smallest  real-world networks contain more than a million nodes.
+Even worse, we also experientially find that the quality of link prediction for latent factor models decreases with the increase of data sparsity,
+and networks typically become sparser when their sizes grow larger.
+
 \eat{%%%%%%%
+
+The factorization of a matrix of
+size $O(n^2)$ is not only computationally expensive, but also
+memory-intensive.  As will be seen later in this article, one advantage
+of  latent-factor models is that they are able to  transform the
+adjacency matrix to a multidimensional space which can be searched
+efficiently {\em by pruning} large portions of the $O(n^2)$ search
+space in order to recommend the top-$k$ possibilities.
+
 \begin{table}
@@
 
-To this end, we explore an {\em ensemble approach} to
-achieving the aforementioned goals.
+We explore an {\em ensemble approach} to make latent factor models
+practical for link prediction by decomposing the search space into a
+ set of smaller matrices with three structural bagging methods with performance guarantees, which has obvious {\em
+effectiveness} advantages. In this way, latent factor models only need to deal with networks with small sizes (and denser), and retain
+their effectiveness and efficiency.  By incorporating with the characteristics of  link prediction, the bagging methods maintain high prediction
+accuracy while reducing the network size via graph sampling techniques. 
+Further, the same bias-variance tradeoffs apply to the link-prediction problem, as the
+standard classification problem. Therefore, the use of an ensemble
+approach has obvious robustness advantages as well.
 
-We show how to make latent factor models
-practical for link prediction by decomposing the search space into a
- set of smaller matrices. As a result, large parts of the $O(n^2)$
-search space can be pruned without even having to evaluate the
-relevant node pairs. An optimizing method is also provided for
-speeding up the search process when a threshold is available.
-This provides an efficient approach for the
-top-$k$ problem in link prediction.
-
-Furthermore, our problem
-decomposition method is an ensemble approach enabled with three
-structural bagging methods with performance guarantees, which has obvious {\em
-effectiveness} advantages. By incorporating with the characteristics of  link prediction, the bagging methods maintain high prediction
-accuracy while reducing the network size via graph sampling techniques.
-Note that the same bias-variance
-tradeoffs apply to the link-prediction problem, as they apply to the
-standard classification problem. Therefore, the use of an ensemble
-approach has obvious effectiveness advantages as well.
-
-Using real-life datasets, we finally conduct an extensive experimental study, and show that our ensemble approach for link prediction is both effective and efficient.
+We experimentally show that our ensemble approach is over $50$ times faster and  over $20\%$ more accurate than {\sc bigclam} \cite{yang-wsdm2013} on using real-life social networks.
 

### 2018-01-25 ApproxComp/sec-query.tex

@@
 
-To lower the high complexity of subgraph isomorphism, substitutes for subgraph isomorphism~\cite{FanLMTWW10,FanLMTW11} that allow graph pattern matching to be conducted in cubic-time have been proposed by extending graph simulation~\cite{infsimu95}.
+To lower the high complexity of subgraph isomorphism, substitutes for subgraph isomorphism \cite{FanLMTWW10,FanLMTW11}, that allow graph pattern matching to be conducted in cubic-time have been proposed by extending graph simulation~\cite{infsimu95}.
 However, they fall short of capturing the topology of data graphs, i.e., graphs may have a structure drastically different from pattern graphs they match, and the matches found are often too large to analyze.

### 2018-01-25 ApproxComp/sec-beyond.tex

@@
   For big data analytics, there are no one-size-fits-all techniques.  it is often necessary to combine different techniques to obtain good solutions.
+
 We have seen that data sampling helps to achieve a balance between efficiency and effectiveness for link prediction,
-and other techniques, \eg incremental computation, data partitioning, data indexing and distributed computing~\cite{MaLHLH16} can
-also be unitized to  design query and data approximation techniques for big data analytics. 
-For instance, it is easy to see that incremental algorithms can be utilized to achieve query approximation.
+and other techniques such as incremental computation, data partitioning, data indexing and distributed computing can
+also be unitized for big data analytics, and even for designing query and data approximation techniques for big data analytics.
+For instance, it is easy to see that incremental algorithms (see~\cite{Reps96} for a survey) can be utilized to achieve query approximation.
+
+It is also obvious that techniques beyond query and data approximation, such as theory and systems~\cite{FanGN13,Jordan15,ZahariaXWDADMRV16}, are must things for big data analytics.

### 2018-01-25 ApproxComp/sec-conclusion.tex

@@
 theoretical bounds with respect to optimal solutions, it does expect a balance between efficiency and accuracy.
-Indeed, (1) our query approximation techniques~\cite{tods-MaCFHW14,LinMZWH17,MaHWLH17} show that efficiency can be obtained efficiency with high accuracy in practice, and (2) our data approximation techniques for shortest paths and distances and link prediction~\cite{MaFLWCH16,DuanMAMH17} show that efficiency and accuracy can be obtained for certain data analytic tasks.
+Indeed, (1) our query approximation techniques~\cite{tods-MaCFHW14,LinMZWH17,MaHWLH17} show that efficiency can be obtained with high accuracy in practice, and (2) our data approximation techniques for shortest paths and distances and link prediction~\cite{MaFLWCH16,DuanMAMH17} show that efficiency and accuracy can be obtained for certain data analytic tasks.
 That is, the design policy approximate computation of is not to sacrifice accuracy for efficiency, but to achieve both efficiency and effectiveness in practice.

### 2018-01-25 ApproxComp/sec-data.tex

@@
 Hence, the scalability is a big challenge.
-In fact, an often overlooked fact is that most {\em exiting link prediction algorithms evaluate the link propensities only over a subset of possibilities rather than all propensities over the entire network}.
+In fact, an often overlooked fact is that most {\em exiting link prediction algorithms evaluate the link propensities only over a subset of possibilities rather than all propensities over the entire network},
+\eg \cite{zhu2016}..
 In order to understand why this is the case, consider a large network with $10^8$ nodes. Its number of {\em possibilities} for links
@@
 
-We explore an {\em ensemble approach} to make latent factor models
+We explore an {\em ensemble approach} to making latent factor models
 practical for link prediction by decomposing the search space into a

### 2018-01-25 ApproxComp/sec-introduction.tex

@@
 
-Over the past a few years, research and development progresses on big data analytics have made significant achievements with the supports from both governments and industries all over the world, such as Spark\footnote{\small \url{https://spark.apache.org}}, IBM Watson\footnote{\small \url{https://www.ibm.com/watson}} and Google AlphaGo\footnote{\small \url{https://deepmind.com/research/alphago}}.
+Over the past a few years, research and development has made significant progresses on big data analytics with the supports from both governments and industries all over the world, such as Spark\footnote{\small \url{https://spark.apache.org}}, IBM Watson\footnote{\small \url{https://www.ibm.com/watson}} and Google AlphaGo\footnote{\small \url{https://deepmind.com/research/alphago}}.
 A fundamental issue for big data analytics is the efficiency, and there are different recent advances towards attacking this issues, from theory to algorithms to platforms~\cite{FanGN13,Jordan15,ZahariaXWDADMRV16}.
-In this article, we shall present the idea of two classes of techniques for efficient and effective big data analytics: query approximation and data approximation, based on our recent research.
-Different from existing approximation techniques~\cite{CormenLRS01,approx03,FanH14}, the approximation computation that we are going to introduce is not unnecessarily theoretically bounded with respect to optimal solutions, but are practically useful and interesting.
+In this article, we shall present the idea of two classes of techniques for efficient and effective big data analytics: query approximation and data approximation, based on our recent research experiences.
+Different from existing approximation techniques~\cite{CormenLRS01,approx03,FanH14}, the approximation computation that we are going to introduce is not unnecessarily theoretically bounded with respect to optimal solutions, but targets at both efficiency and effectiveness in practice.
 
@@
 
-contributions and summary of results
+We systematically introduce approximate computation (\ie query and data approximation) for big data analytics, targeting at both efficiency and effectiveness in practice.
+
+We explain the idea and rational of query approximation,  and show efficiency can be obtained with high effectiveness in practice by its embodiment for graph pattern matching, trajectory compression and dense subgraph computation.
+
+We explain the idea and rational of data approximation,  and show efficiency can be obtained even without the sacrifice of effectiveness in practice by its embodiment for shortest paths/distances and link prediction.
 

### 2018-01-25 ApproxComp/sec-introduction.tex

@@
 Over the past a few years, research and development has made significant progresses on big data analytics with the supports from both governments and industries all over the world, such as Spark\footnote{\small \url{https://spark.apache.org}}, IBM Watson\footnote{\small \url{https://www.ibm.com/watson}} and Google AlphaGo\footnote{\small \url{https://deepmind.com/research/alphago}}.
-A fundamental issue for big data analytics is the efficiency, and there are different recent advances towards attacking this issues, from theory to algorithms to platforms~\cite{FanGN13,Jordan15,ZahariaXWDADMRV16}.
+A fundamental issue for big data analytics is the efficiency, and various advances towards attacking this issues have been achieved recently, from theory to algorithms to platforms~\cite{FanGN13,Jordan15,ZahariaXWDADMRV16}.
 In this article, we shall present the idea of two classes of techniques for efficient and effective big data analytics: query approximation and data approximation, based on our recent research experiences.
-Different from existing approximation techniques~\cite{CormenLRS01,approx03,FanH14}, the approximation computation that we are going to introduce is not unnecessarily theoretically bounded with respect to optimal solutions, but targets at both efficiency and effectiveness in practice.
+Different from existing approximation techniques~\cite{CormenLRS01,approx03,FanH14}, the approximation computation that we are going to introduce is not unnecessarily theoretically bounded with respect to optimal solutions, but asks for both efficiency and effectiveness in practice.
 

### 2018-01-25 ApproxComp/sec-conclusion.tex

@@
-\section{Conclusion}
+\section{Conclusions}
 \label{sec-conclusion}
@@
 Indeed, (1) our query approximation techniques~\cite{tods-MaCFHW14,LinMZWH17,MaHWLH17} show that efficiency can be obtained with high accuracy in practice, and (2) our data approximation techniques for shortest paths and distances and link prediction~\cite{MaFLWCH16,DuanMAMH17} show that efficiency and accuracy can be obtained for certain data analytic tasks.
-That is, the design policy approximate computation of is not to sacrifice accuracy for efficiency, but to achieve both efficiency and effectiveness in practice.
+That is, the design policy approximate computation of is not to sacrifice effectiveness for efficiency, but to achieve both efficiency and effectiveness in practice.

### 2018-01-25 ApproxComp/sec-introduction.tex

@@
 
-We explain the idea and rational of data approximation,  and show efficiency can be obtained even without the sacrifice of effectiveness in practice by its embodiment for shortest paths/distances and link prediction.
+We explain the idea and rational of data approximation,  and show efficiency can be obtained even without sacrificing for effectiveness in practice by its embodiment for shortest paths/distances and link prediction.
 

### 2018-01-26 ApproxComp/sec-conclusion.tex

@@
 Furthermore, although approximate computation does not put
-theoretical bounds with respect to optimal solutions, it does expect a balance between efficiency and accuracy.
-Indeed, (1) our query approximation techniques~\cite{tods-MaCFHW14,LinMZWH17,MaHWLH17} show that efficiency can be obtained with high accuracy in practice, and (2) our data approximation techniques for shortest paths and distances and link prediction~\cite{MaFLWCH16,DuanMAMH17} show that efficiency and accuracy can be obtained for certain data analytic tasks.
-That is, the design policy approximate computation of is not to sacrifice effectiveness for efficiency, but to achieve both efficiency and effectiveness in practice.
+theoretical bounds with respect to optimal solutions, it does expect a balance between efficiency and quality.
+Indeed, (a) our query approximation techniques~\cite{tods-MaCFHW14,LinMZWH17,MaHWLH17} show that efficiency can be obtained with high accuracy in practice, and (b) our data approximation techniques for shortest paths and distances and link prediction~\cite{MaFLWCH16,DuanMAMH17} show that efficiency and accuracy can be obtained simultaneously for certain data analytic tasks.
+That is, the design policy approximate computation is not to sacrifice effectiveness for efficiency, but to achieve both efficiency and effectiveness in practice.

### 2018-01-26 ApproxComp/sec-data.tex

@@
 
-Big data has large volume, and, hence, the space complexity of big data analytic tasks starts raising more concerns.
-Given a class $Q$ of queries on a data set $D$, data approximation is to transform $D$ into a smaller data set $D'$ such that $Q$ on $D'$ returns a satisfiable approximate answer in a more efficient way.
+Big data has large volume, and, hence, the space complexity~\cite{CormenLRS01} of big data analytic tasks starts raising more concerns.
+Given a class $Q$ of queries on data $D$, data approximation is to transform $D$ into smaller $D'$ such that $Q$ on $D'$ returns a sufficient or satisfiable approximate answer in a more efficient way.
 Further, it is typically common that query $Q$ needs to be (slightly) modified to $Q'$ to accommodate  the changes of $D$ to $D'$, as shown in Fig.~\ref{fig-tech-dataappro}.
-Similar to query approximation, data approximation needs to reach a balance between the query efficiency and answer accuracy.
+Similar to query approximation, data approximation needs to reach a balance between the query efficiency and answer quality.
 
-The rationale of data approximation has roots in the Pareto principle\footnote{\small \url{https://en.wikipedia.org/wiki/Pareto_principle}} that ``states that, for many events, roughly 80\% of the effects come from 20\% of the causes''.
+The rationale behind data approximation has roots in the Pareto principle\footnote{\small \url{https://en.wikipedia.org/wiki/Pareto_principle}} that ``states that, for many events, roughly 80\% of the effects come from 20\% of the causes''.
 The critical thing for data approximation is to determine which part of data is relevant to tasks (belong to the 20\%).
- By this principle, for many big analytic tasks, one may only need to keep a small amount of the data to derive ``satisfiable'' answers.
+ By this principle, for many big analytic tasks, one may only need to keep a small amount of the data to derive high quality answers.
 For example, when we are to build a predictive model on the stock of razers for an online store based on the order history of customers, orders from men are good enough.
@@
 For example, an online store needs to count the total number of goods in its catalog.
-Essentially the entire goods should be considered for this task, and if a (small) portion of goods are chosen, it is hard to have a ``satisfiable'' result.
+Essentially entire goods should be considered for this task, and if a (small) portion of goods are chosen, it is hard to have a ``satisfiable'' result.
 
-We next explain data approximation computation in more detail with three different data analytic tasks.
+We next explain data approximation computation in more detail using three different data analytic tasks.
 
@@
   \begin{center}
-  \includegraphics[scale=0.45]{./dataApprox.png}
+  \includegraphics[scale=0.5]{./dataApprox.png}
   \end{center}

### 2018-01-26 ApproxComp/sec-introduction.tex

@@
 
-We explain the idea and rational of query approximation,  and show efficiency can be obtained with high effectiveness in practice by its embodiment for graph pattern matching, trajectory compression and dense subgraph computation.
+We explain the idea and rationale of query approximation,  and show efficiency can be obtained with high effectiveness in practice by its embodiment for graph pattern matching, trajectory compression and dense subgraph computation.
 
-We explain the idea and rational of data approximation,  and show efficiency can be obtained even without sacrificing for effectiveness in practice by its embodiment for shortest paths/distances and link prediction.
+We explain the idea and rationale of data approximation,  and show efficiency can be obtained even without sacrificing for effectiveness in practice by its embodiment for shortest paths/distances and link prediction.
 

### 2018-01-26 ApproxComp/sec-query.tex

@@
 Query approximation deals with complex queries involved with big data analytic tasks.
-Given a class $Q$ of data analytic queries with higher computational complexity,  query approximation is to transform into another class $Q'$ of queries with lower computational complexity and satisfiable approximate answers, as depicted in Fig.~\ref{fig-tech-queryappro} in which $Q$, $Q'$ and $D$ denote the original query, approximate query and data, respectively.
-Query approximation needs to reach a balance between the query efficiency and answer accuracy when approximating $Q$ with $Q'$.
+Given a class $Q$ of data analytic queries with high a computational complexity,  query approximation is to transform into another class $Q'$ of queries with a low computational complexity and satisfiable approximate answers, as depicted in Fig.~\ref{fig-tech-queryappro} in which $Q$, $Q'$,  $D$ and $R$ denote the original query, approximate query, data and query result, respectively.
+Query approximation needs to reach a balance between the query efficiency and answer quality when approximating $Q$ with $Q'$.
 
-The rationale behind query approximation has inexact or approximate answers are acceptable for many big data analytic tasks.
-On one hand, when the volume of data is extremely large, it may be impossible or not necessary to compute the exact queries.
+The rationale behind query approximation lies in that inexact or approximate answers are sufficient or acceptable for many big data analytic tasks.
+On one hand, when the volume of data is extremely large, it may be impossible or not necessary to compute the exact answers.
 Observe that nobody would try each and every store to find a pair of shoes with the best cost-performance ratio.
-That is, inexact (approximate) solutions are good candidates in this case.
+That is, inexact (approximate) solutions are good enough in this case.
 %
-On the other hand, when taking noises (common for big data) into account, it may not always a good idea to compute exact answers
+On the other hand, when taking noises (common for big data) into account, it may not always be a good idea to compute exact answers
 for those data analytic tasks whose answers are rare or hard to identify, such as the detection of homegrown violent extremists (HVEs) who seek to commit acts of terrorism in the United States and abroad~\cite{HungJ16}, as exact solutions may have a high chance to miss possible candidates.
 
-We next explain query approximation computation in more detail with three different data analytic tasks.
+We next explain query approximation computation in more detail using three different data analytic tasks.
 
@@
   \begin{center}
-  \includegraphics[scale=0.45]{./queryApprox.png}
+  \includegraphics[scale=0.5]{./queryApprox.png}
   \end{center}

### 2018-01-26 ApproxComp/sec-query.tex

@@
 \stitle{(1) Strong Simulation~\cite{tods-MaCFHW14}}. Given a pattern graph $Q$ and a data graph $G$,
-{\em Graph pattern matching} is to find all subgraphs of $G$ that match $Q$, and is being increasingly used in various applications, \eg software, biology, social networks and intelligence analysis.
+{\em graph pattern matching} is to find all subgraphs of $G$ that match $Q$, and is being increasingly used in various applications, \eg software, biology, social networks and intelligence analysis.
 
@@
 
-To lower the high complexity of subgraph isomorphism, substitutes for subgraph isomorphism \cite{FanLMTWW10,FanLMTW11}, that allow graph pattern matching to be conducted in cubic-time have been proposed by extending graph simulation~\cite{infsimu95}.
-However, they fall short of capturing the topology of data graphs, i.e., graphs may have a structure drastically different from pattern graphs they match, and the matches found are often too large to analyze.
+To lower the high complexity of subgraph isomorphism, substitutes for subgraph isomorphism \cite{FanLMTWW10,FanLMTW11}, which allow graph pattern matching to be conducted in cubic-time, have been proposed by extending graph simulation~\cite{infsimu95}.
+However, they fall short of capturing the topology of data graphs, i.e., graphs may have a structure drastically different from pattern graphs that they match, and the matches found are often too large to analyze.
 
-To rectify these problems, strong simulation, an ``approximate'' substitute for subgraph isomorphism, was  proposed for graph pattern matching, such that strong simulation (a) theoretically preserves the key topology of pattern graphs and finds a bounded number of matches, (b) retains the same complexity as earlier extensions of graph simulation~\cite{FanLMTWW10,FanLMTW11}, by providing a cubic-time algorithm for computing strong simulation, and (c) has the locality property that allows us to develop an effective distributed algorithm to conduct graph pattern matching on distributed graphs~\cite{tods-MaCFHW14}.
+To rectify these problems, strong simulation, an ``approximate'' substitute for subgraph isomorphism, is proposed for graph pattern matching~\cite{tods-MaCFHW14}, such that strong simulation (a) theoretically preserves the key topology of pattern graphs and finds a bounded number of matches, (b) retains the same complexity as earlier extensions of graph simulation~\cite{FanLMTWW10,FanLMTW11}, by providing a cubic-time algorithm for computing strong simulation, and (c) has the locality property that allows us to develop an effective distributed algorithm to conduct graph pattern matching on distributed graphs.
 
@@
 quality matches that retain graph topology. Indeed, 70\%-80\% of matches found by subgraph
-isomorphism are retrieved by strong simulation, without paying the price of intractable complexity (100+ times faster) and large number (or
-size) of matches.
+isomorphism are retrieved by strong simulation. Further, strong simulation is over $100$ times faster than subgraph isomorphism, and has a bounded number of matches.
 
@@
 We develop a data-driven approach, instead of filter-and-verification, to  identifying the most possible $k$ time intervals from $T \times (T + 1)/2$ time intervals, in which $T$ is the number of snapshots and k is a small constant, \eg 10.
-This is achieved by exploring the characteristics of time intervals involved with dense subgraphs based on the observation of {\em evolving convergence phenomenon} in traffic data, inspired by the convergent evolution in nature~\footnote{\small \url{https://en.wikipedia.org/wiki/Convergent_evolution}}.
+This is achieved by exploring the characteristics of time intervals involved with dense subgraphs based on the observation of {\em evolving convergence phenomenon} in traffic data, inspired by the convergent evolution in nature\footnote{\small \url{https://en.wikipedia.org/wiki/Convergent_evolution}}.
 Using both real-life and synthetic data, we experimentally show that Our method {\sc fides} is over 1000 times faster than the state of the art solution {\sc meden}~\cite{BogdanovMS11}, while the quality of dense subgraphs found is comparable with {\sc meden}.

### 2018-01-26 ApproxComp/sec-query.tex

@@
 Hence, lossy techniques become the mainstream for trajectory compression,
-which provide approximate solutions with good compression ratios and bounded errors.
+which provide approximate solutions with good compression ratios and bounded errors in practice.
 
-Piece-wise line simplification (\lsa) comes from computational geometry, whose target is to approximate a given finer piece-wise linear curve by another coarser piece-wise linear curve ({normally} a sub set of the former), such that the maximum distance of the former from the later is bounded by a user specified constant.
+Piece-wise line simplification (\lsa) comes from computational geometry, whose target is to approximate a given finer piece-wise linear curve by another coarser piece-wise linear curve ({normally} a subset of the former), such that the maximum distance of the former from the later is bounded by a user specified constant.
 It is widely used due to its distinct advantages: (a) simple and easy to implement, (b) no need of extra knowledge and suitable for freely  moving  objects, and (c) bounded errors with good compression ratios.
@@
 An \lsa algorithm is {\em one-pass} if it processes each point in a trajectory once and only once when compressing the trajectory.
-Obviously, one-pass algorithms have low time and space complexities, and are more appropriate for online processing, and
-the difficulty comes from the need to achieve effective compression ratios.
+Obviously, one-pass algorithms have low time and space complexities, and are more appropriate for online processing. The difficulty comes from the need to achieve effective compression ratios.
 Existing trajectory simplification algorithms (\eg \cite{Douglas:Peucker}) and online algorithms  (\eg \cite{Liu:BQS}) essentially employ a global distance checking approach to assuring error bounds, although online algorithms restrict the checking within a window.
@@
 
- We develop a  fitting function such that a data point is checked only once during the entire process of trajectory simplification.
-Based on the fitting function, we develop one-pass error bounded trajectory simplification algorithms that scan each data point in a trajectory once and only once.
-By comparing our algorithms with \fbqsa (\emph{the fastest} existing \lsa online algorithm \cite{Liu:BQS}) and \dpa (the {\em best} existing \lsa batch algorithm in terms of {\em compression ratio} \cite{Douglas:Peucker}), our one-pass algorithms are over four times faster than \fbqsa, and have  comparable compression ratios with \dpa.
+ We develop a  {\em fitting function} such that a data point is checked only once during the entire process of trajectory simplification.
+Based on the fitting function, we develop one-pass error bounded trajectory simplification algorithms \operb and \operba that scan each data point in a trajectory once and only once, allowing interpolating new data points or not, respectively.
+By comparing our algorithms with \fbqsa (the fastest existing \lsa online algorithm \cite{Liu:BQS}) and \dpa (the best existing \lsa batch algorithm in terms of compression ratio \cite{Douglas:Peucker}), our one-pass algorithms  \operb and \operba are over four times faster than \fbqsa, and have  comparable compression ratios with \dpa.
 

### 2018-01-26 ApproxComp/sec-query.tex

@@
 Essentially, a temporal network with $T$ timestamps can be viewed as $T$ snapshots of a static network such that the network nodes and edges are kept the same among these $T$ snapshots, while the edge weights vary with network snapthots.
-Road traffic networks typically fall into this category of temporal networks, and dense subgraphs are used for road traffic analyses that are of particular importance for large cities, such as Beijing, New York, London and Paris, that are facing with heavy traffic congestions, one of the great challenges of urban computing.
+Road traffic networks typically fall into this category of temporal networks, and dense subgraphs are used for road traffic analyses that are of particular importance for large cities, such as Beijing, New York, London and Paris, that are facing with heavy traffic congestions, one of the great challenges in urban computing.
 
@@
 The problem of  finding dense subgraphs in temporal networks is non-trivial, and it is already \NP-complete even for a temporal network with a single snapshot and with $+1$ or $-1$ edge weights only, as observed in \cite{BogdanovMS11}.
-Even worse, it remains hard to approximate for temporal networks  with single snapshots.
+Even worse, it remains hard to approximate for temporal networks  with single snapshots~\cite{MaHWLH17}.
 Moreover, given a temporal network with $T$ timestamps, there are a total number of $T*(T+1)/2$ time intervals to consider, which further aggravates the difficulty.
-
-The state of the art solution {\sc meden} \cite{BogdanovMS11} adopts a filter-and-verification framework that {\em even if a large portion of time intervals are filtered, there often remain a large number of time intervals to verify}.
-This is not big data friendly, and it is not scalable when temporal networks have a large number of nodes/edges or a large number $T$ of timestamps.
+The state of the art solution \kw{MEDEN} \cite{BogdanovMS11} adopts a filter-and-verification ({\kw{FAV}) framework that {\em even if a large portion of time intervals are filtered, there often remain a large number of time intervals to verify}.
+Hence, this method is not big data friendly, and is not scalable when temporal networks have a large number of nodes/edges or a large number $T$ of timestamps.
 
@@
 This is achieved by exploring the characteristics of time intervals involved with dense subgraphs based on the observation of {\em evolving convergence phenomenon} in traffic data, inspired by the convergent evolution in nature\footnote{\small \url{https://en.wikipedia.org/wiki/Convergent_evolution}}.
-Using both real-life and synthetic data, we experimentally show that Our method {\sc fides} is over 1000 times faster than the state of the art solution {\sc meden}~\cite{BogdanovMS11}, while the quality of dense subgraphs found is comparable with {\sc meden}.
+Using both real-life and synthetic data, we experimentally show that Our method \kw{FIDES} is over 1000 times faster than the state of the art solution  \kw{MEDEN}~\cite{BogdanovMS11}, while the quality of dense subgraphs found is comparable with  \kw{MEDEN} .

### 2018-01-26 ApproxComp/sec-data.tex

@@
 For example, an online store needs to count the total number of goods in its catalog.
-Essentially entire goods should be considered for this task, and if a (small) portion of goods are chosen, it is hard to have a ``satisfiable'' result.
+Essentially entire goods should be considered for this task, and if a (small) portion of goods are chosen, it is hard to have a satisfiable result.
 
@@
 \ni(a) {\em Preprocessing}: Given graph $G(V, E)$, it first computes all \dras and their maximal proxies in linear time, then it computes and stores all the shortest paths and distances between any node and its proxy.
-It finally computes the reduced subgraph $G'$ by removing all \dras, but keeping their proxies, from graph $G$.
+It finally computes the reduced subgraph $G'$ by removing all \dras from graph $G$, \ie keeping the proxies only.
 
-\ni(b) {\em Query answering}. Given two nodes $s$ and $t$ in graph $G(V$, $E)$  and the pre-computed information, the query answering module essentially executes the following.
+\ni(b) {\em Query answering}. Given two nodes $s$ and $t$ in graph $G(V$, $E)$  and the pre-computed information above, the query answering module essentially executes the following.
 
 The shortest path $\path(s, t)$ = $\path(s, u_s)/$ $\path(u_s, u_t)/$ $\path(u_t, t)$, where $u_s$ and $u_t$ are the proxies of $s$ and $t$, respectively.
-Here  $\path(s, u_s)$ and $\path(u_t, t)$ are pre-computed, and $\path(u_s, u_t)$ can be computed on the reduced subgraph $G'$ by invoking any existing
+Here  $\path(s, u_s)$ and $\path(u_t, t)$ are pre-computed, and $\path(u_s, u_t)$ can be computed on the reduced subgraph $G'$ by invoking any existing algorithms
 (\eg \ah~\cite{zhu2013shortest}).
 %
-The shortest distance $\dist(s, t)$ = $\dist(s, u_s)$ + $\dist(u_s, u_t)$ + $\dist(u_t, t)$ can be computed similarly.
+The shortest distance $\dist(s, t)$ = $\dist(s, u_s)$ + $\dist(u_s, u_t)$ + $\dist(u_t, t)$ can be computed along the same line.
 
-We show experimentally show that about $1/3$  nodes of real-life social networks and road networks  are captured by by proxies, leaving $2/3$ in the reduced graphs.
-Hence, we propose a light-weight data reduction technique for speeding-up (exact)  shortest path and distance queries on large weighted undirected graphs~\cite{MaFLWCH16}.
+We show experimentally show that about $1/3$  nodes of real-life social networks and road networks  are captured by proxies, leaving $2/3$ in the reduced graphs.
+Essentially, we propose a light-weight data reduction technique for speeding-up (exact)  shortest path and distance queries on large weighted undirected graphs~\cite{MaFLWCH16}.
 

### 2018-01-26 ApproxComp/sec-data.tex

@@
 
-Link prediction methods are often applied to very large and sparse networks, which has a large {\em search space} $O(n^2)$,
+Link prediction methods are often applied to very large and sparse networks, which have a large {\em search space} $O(n^2)$,
 where $n$ is the number of nodes.
@@
 In fact, an often overlooked fact is that most {\em exiting link prediction algorithms evaluate the link propensities only over a subset of possibilities rather than all propensities over the entire network},
-\eg \cite{zhu2016}..
+\eg \cite{zhu2016}.
 In order to understand why this is the case, consider a large network with $10^8$ nodes. Its number of {\em possibilities} for links
@@
 
-Latent factor models have been shown to be wildly successful in the domain of
+Latent factor models have proven a great success in the domain of
 collaborative filtering, but not link prediction in spite of the obvious
@@
 
-We experimentally show that our ensemble approach is over $50$ times faster and  over $20\%$ more accurate than {\sc bigclam} \cite{yang-wsdm2013} on using real-life social networks.
+We experimentally show that our ensemble approach is over $50$ times faster and  over $20\%$ more accurate than {\sc bigclam} \cite{yang-wsdm2013} using real-life social networks.
 

### 2018-01-26 ApproxComp/sec-conclusion.tex

@@
 Furthermore, although approximate computation does not put
-theoretical bounds with respect to optimal solutions, it does expect a balance between efficiency and quality.
+theoretical bounds with respect to optimal solutions, it does expect a balance between efficiency and effectiveness.
 Indeed, (a) our query approximation techniques~\cite{tods-MaCFHW14,LinMZWH17,MaHWLH17} show that efficiency can be obtained with high accuracy in practice, and (b) our data approximation techniques for shortest paths and distances and link prediction~\cite{MaFLWCH16,DuanMAMH17} show that efficiency and accuracy can be obtained simultaneously for certain data analytic tasks.

### 2018-01-26 ApproxComp/sec-introduction.tex

@@
 
-We systematically introduce approximate computation (\ie query and data approximation) for big data analytics, targeting at both efficiency and effectiveness in practice.
+We systematically introduce approximate computation (\ie query approximation and data approximation) for efficiency and effectiveness big data analytics in practice.
 

### 2018-01-26 ApproxComp/sec-query.tex

@@
 
- We develop a  {\em fitting function} such that a data point is checked only once during the entire process of trajectory simplification.
+ We develop a local distance checking method, referred to as  {\em fitting function}, such that a data point is checked only once during the entire process of trajectory simplification.
 Based on the fitting function, we develop one-pass error bounded trajectory simplification algorithms \operb and \operba that scan each data point in a trajectory once and only once, allowing interpolating new data points or not, respectively.
@@
 This is achieved by exploring the characteristics of time intervals involved with dense subgraphs based on the observation of {\em evolving convergence phenomenon} in traffic data, inspired by the convergent evolution in nature\footnote{\small \url{https://en.wikipedia.org/wiki/Convergent_evolution}}.
+That is, our method provides time intervals with probabilistic grantees, instead of exact ones with \kw{FAV}.
 Using both real-life and synthetic data, we experimentally show that Our method \kw{FIDES} is over 1000 times faster than the state of the art solution  \kw{MEDEN}~\cite{BogdanovMS11}, while the quality of dense subgraphs found is comparable with  \kw{MEDEN} .

### 2018-01-26 ApproxComp/sec-introduction.tex

@@
 In this article, we shall present the idea of two classes of techniques for efficient and effective big data analytics: query approximation and data approximation, based on our recent research experiences.
-Different from existing approximation techniques~\cite{CormenLRS01,approx03,FanH14}, the approximation computation that we are going to introduce is not unnecessarily theoretically bounded with respect to optimal solutions, but asks for both efficiency and effectiveness in practice.
+Different from existing approximation techniques~\cite{CormenLRS01,approx03,FanH14}, the approximation computation that we are going to introduce is unnecessarily theoretically bounded with respect to optimal solutions, but asks for both efficiency and effectiveness in practice.
 

### 2018-01-26 ApproxComp/sec-data.tex

@@
 
-Big data has large volume, and, hence, the space complexity~\cite{CormenLRS01} of big data analytic tasks starts raising more concerns.
+Big data has a large volume, and, hence, the space complexity~\cite{CormenLRS01} of big data analytic tasks starts raising more concerns.
 Given a class $Q$ of queries on data $D$, data approximation is to transform $D$ into smaller $D'$ such that $Q$ on $D'$ returns a sufficient or satisfiable approximate answer in a more efficient way.
@@
 
-We show experimentally show that about $1/3$  nodes of real-life social networks and road networks  are captured by proxies, leaving $2/3$ in the reduced graphs.
+We experimentally show that about $1/3$  nodes of real-life social networks and road networks  are captured by proxies, leaving $2/3$ in the reduced graphs.
 Essentially, we propose a light-weight data reduction technique for speeding-up (exact)  shortest path and distance queries on large weighted undirected graphs~\cite{MaFLWCH16}.

### 2018-01-26 ApproxComp/sec-query.tex

@@
 Dense subgraphs are a general concept, and their concrete semantics highly depend on the studied problems and applications.
-Though  dense subgraph discovery and analysis have been widely studied in static networks, how to properly transfer or define their semantics over to temporal networks is still in the early stage, not to mention effective and efficient analytic algorithms.
+Though  dense subgraphs have been widely studied in static networks, how to properly define their semantics over temporal networks is still in the early stage, not to mention effective and efficient analytic algorithms.
 

### 2018-01-27 ApproxComp/sec-introduction.tex

@@
 Over the past a few years, research and development has made significant progresses on big data analytics with the supports from both governments and industries all over the world, such as Spark\footnote{\small \url{https://spark.apache.org}}, IBM Watson\footnote{\small \url{https://www.ibm.com/watson}} and Google AlphaGo\footnote{\small \url{https://deepmind.com/research/alphago}}.
-A fundamental issue for big data analytics is the efficiency, and various advances towards attacking this issues have been achieved recently, from theory to algorithms to platforms~\cite{FanGN13,Jordan15,ZahariaXWDADMRV16}.
+A fundamental issue for big data analytics is the efficiency, and various advances towards attacking this issues have been achieved recently, from theory to algorithms to systems~\cite{FanGN13,Jordan15,ZahariaXWDADMRV16}.
 In this article, we shall present the idea of two classes of techniques for efficient and effective big data analytics: query approximation and data approximation, based on our recent research experiences.

### 2018-01-27 ApproxComp/sec-data.tex

@@
 Hence, the scalability is a big challenge.
-In fact, an often overlooked fact is that most {\em exiting link prediction algorithms evaluate the link propensities only over a subset of possibilities rather than all propensities over the entire network},
-\eg \cite{zhu2016}.
-In order to understand why this is the case, consider a large network with $10^8$ nodes. Its number of {\em possibilities} for links
+In fact, an often overlooked fact is that most {\em exiting link prediction algorithms evaluate the link propensities only over a subset of possibilities rather than all propensities over the entire network}.
+%,\eg \cite{zhu2016}.
+Consider a large network with $10^8$ nodes. Its number of {\em possibilities} for links
 is of the order of $10^{16}$. Therefore, a 3GHz processor would
@@
 top-ranked link predictions over the {\em entire network}, the
-running time will be much much larger than $35$ days.
+running time would be much more than $35$ days.
 
@@
 
-Latent factor models have proven a great success in the domain of
+Latent factor models have proven a great success for
 collaborative filtering, but not link prediction in spite of the obvious
-similarity between link prediction and collaborative filtering and
+similarity and
 the obvious effectiveness of latent factor models. One of the reasons why latent factor models are rarely used for
@@
 accuracy while reducing the network size via graph sampling techniques.
-Further, the same bias-variance tradeoffs apply to the link-prediction problem, as the
-standard classification problem. Therefore, the use of an ensemble
+Further, the use of an ensemble
 approach has obvious robustness advantages as well.

### 2018-01-27 ApproxComp/sec-introduction.tex

@@
 A fundamental issue for big data analytics is the efficiency, and various advances towards attacking this issues have been achieved recently, from theory to algorithms to systems~\cite{FanGN13,Jordan15,ZahariaXWDADMRV16}.
-In this article, we shall present the idea of two classes of techniques for efficient and effective big data analytics: query approximation and data approximation, based on our recent research experiences.
+In this article, we present the idea of approximate computation for efficient and effective big data analytics: query approximation and data approximation, based on our recent research experiences.
 Different from existing approximation techniques~\cite{CormenLRS01,approx03,FanH14}, the approximation computation that we are going to introduce is unnecessarily theoretically bounded with respect to optimal solutions, but asks for both efficiency and effectiveness in practice.

### 2018-01-27 ApproxComp/sec-query.tex

@@
 \stitle{(2) One-Pass Trajectory Compression~\cite{LinMZWH17}}.
-Trajectory compression (also known as trajectory simplification) is to compress data points in a trajectory to a set of continuous line segments, and is commonly used  in practice.
+Trajectory compression (\aka trajectory simplification) is to compress data points in a trajectory to a set of continuous line segments, and is commonly used  in practice.
 
@@
 This is achieved by exploring the characteristics of time intervals involved with dense subgraphs based on the observation of {\em evolving convergence phenomenon} in traffic data, inspired by the convergent evolution in nature\footnote{\small \url{https://en.wikipedia.org/wiki/Convergent_evolution}}.
-That is, our method provides time intervals with probabilistic grantees, instead of exact ones with \kw{FAV}.
+That is, our method provides time intervals with probabilistic grantees, instead of exact ones like \kw{FAV}.
 Using both real-life and synthetic data, we experimentally show that Our method \kw{FIDES} is over 1000 times faster than the state of the art solution  \kw{MEDEN}~\cite{BogdanovMS11}, while the quality of dense subgraphs found is comparable with  \kw{MEDEN} .

### 2018-01-27 ApproxComp/coverletter.tex

\documentclass{letter}
\usepackage{geometry}

% duan
\usepackage{xspace}

\geometry{left=2.0cm, right=2.0cm, top=2.5cm, bottom=2.5cm}
\newcommand{\ie}{\emph{i.e.,}\xspace}
\newcommand{\eg}{\emph{e.g.,}\xspace}
\newcommand{\wrt}{\emph{w.r.t.}\xspace}
\newcommand{\aka}{\emph{a.k.a.}\xspace}
\newcommand{\kwlog}{\emph{w.l.o.g.}\xspace}
\newcommand{\etal}{\emph{et al.}\xspace}
\newcommand{\sstab}{\rule{0pt}{8pt}\\[-2.4ex]}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}

\begin{document}

Dear Editors,

I would like to request you to consider the attached manuscript entitled ``Approximate Computation for Big Data Analytics'' for publication in Communications of the ACM  as a contributed article.

The central theme of the article is big data analytics. A fundamental issue for big data analytics is the efficiency, and in this article we systematically introduce approximate computation (query approximation and data approximation) for efficiency and effectiveness big data analytics in practice.
I believe that the findings of this study are relevant to the scope of your journal, and will be of interests to the corresponding readers.

No conflicts of interest exits in the submission of this manuscript, and this manuscript is approved by all authors for publication, and  all the authors listed have approved the manuscript that is enclosed.

Below please find the names and email addresses of possessible appropriate reviewers:

\bi
\item[(1)] Prof. Sihem Amer-Yahia: Sihem.Amer-Yahia@imag.fr

\item[(2)]  Prof. Evaggelia Pitoura: pitoura@cs.uoi.gr

\item[(3)]  Prof. Lei Chen: leichen@cse.ust.hk

\item[(4)]  Prof. Feifei Li: lifeifei@cs.utah.edu
\ei

Looking forward to hearing from you.

Your sincerely,

Shuai Ma

Email: mashuai@buaa.edu.cn\\
Homepage: http://mashuai.buaa.edu.cn/
\end{document}

### 2018-01-27 ApproxComp/sec-data.tex

@@
 
-\ni(b) {\em Query answering}. Given two nodes $s$ and $t$ in graph $G(V$, $E)$  and the pre-computed information above, the query answering module essentially executes the following.
+\ni(b) {\em Query answering}. Given two nodes $s$ and $t$ in graph $G(V$, $E)$  and the pre-computed information, the query answering module essentially executes the following.
 
@@
 
-We experimentally show that about $1/3$  nodes of real-life social networks and road networks  are captured by proxies, leaving $2/3$ in the reduced graphs.
 Essentially, we propose a light-weight data reduction technique for speeding-up (exact)  shortest path and distance queries on large weighted undirected graphs~\cite{MaFLWCH16}.
+We experimentally show that about $1/3$  nodes of real-life social and road networks  are captured by proxies.
 
@@
   \begin{center}
-  \includegraphics[scale=0.5]{./dataApprox.png}
+  \includegraphics[scale=0.4]{./dataApprox.png}
   \end{center}
-  \vspace{-3ex}
+  \vspace{-4ex}
   \caption{Data approximation}\label{fig-tech-dataappro}
-  \vspace{-2ex}
+  \vspace{-4ex}
 \end{figure}

### 2018-01-27 ApproxComp/sec-query.tex

@@
   \begin{center}
-  \includegraphics[scale=0.5]{./queryApprox.png}
+  \includegraphics[scale=0.4]{./queryApprox.png}
   \end{center}
-  \vspace{-3ex}
+  \vspace{-4ex}
   \caption{Query approximation}\label{fig-tech-queryappro}
-  \vspace{-2ex}
+  \vspace{-4ex}
 \end{figure}
@@
 \stitle{(1) Strong Simulation~\cite{tods-MaCFHW14}}. Given a pattern graph $Q$ and a data graph $G$,
-{\em graph pattern matching} is to find all subgraphs of $G$ that match $Q$, and is being increasingly used in various applications, \eg software, biology, social networks and intelligence analysis.
+{\em graph pattern matching} is to find all subgraphs of $G$ that match $Q$, and is being increasingly used in various applications, \eg biology and social networks.
 
@@
 
-Though lossless compression methods incur no information loss, their compression ratios are typically poor, and querying on the compressed data is time consuming due to the reconstruction of the original data \cite{Nibali:Trajic}.
-Hence, lossy techniques become the mainstream for trajectory compression,
-which provide approximate solutions with good compression ratios and bounded errors in practice.
+The compression ratios of lossless methods are poor, and querying on the compressed data is time consuming due to the reconstruction of the original data \cite{Nibali:Trajic}.
+Hence, lossy techniques, which  provide approximate solutions with good compression ratios and bounded errors, is the mainstream.
 
 Piece-wise line simplification (\lsa) comes from computational geometry, whose target is to approximate a given finer piece-wise linear curve by another coarser piece-wise linear curve ({normally} a subset of the former), such that the maximum distance of the former from the later is bounded by a user specified constant.
-It is widely used due to its distinct advantages: (a) simple and easy to implement, (b) no need of extra knowledge and suitable for freely  moving  objects, and (c) bounded errors with good compression ratios.
+It is widely used due to its distinct advantages: (a) simple and easy to implement, (b) no need extra knowledge and suitable for freely  moving  objects, and (c) bounded errors with good compression ratios.
 
@@
 Obviously, one-pass algorithms have low time and space complexities, and are more appropriate for online processing. The difficulty comes from the need to achieve effective compression ratios.
-Existing trajectory simplification algorithms (\eg \cite{Douglas:Peucker}) and online algorithms  (\eg \cite{Liu:BQS}) essentially employ a global distance checking approach to assuring error bounds, although online algorithms restrict the checking within a window.
-That is to say, whenever a new directed line segment is formed, these algorithms always check its distances to all or a subset of data points, and, therefore, a data point is checked multiple times, depending on its order in the trajectory and the number of directed line segments formed.
-Hence, {\em an appropriate local distance checking approach is needed in the first place for designing one-pass trajectory simplification algorithms}.
+Existing trajectory simplification algorithms (\eg \cite{Douglas:Peucker}) and online algorithms  (\eg \cite{Liu:BQS}) essentially employ global distance checking, although online algorithms restrict the checking within a window.
+That is, whenever a new line segment is formed, these algorithms always check its distances to all or a subset of data points, and, therefore, a data point is checked multiple times, depending on its order in the trajectory and the number of directed line segments formed.
+Hence, {\em an appropriate local distance checking approach is needed in the first place for  one-pass trajectory simplification.}.
 
- We develop a local distance checking method, referred to as  {\em fitting function}, such that a data point is checked only once during the entire process of trajectory simplification.
+ We develop a local distance checking method, referred to as  {\em fitting function}, such that a data point is checked only once in the entire process.
 Based on the fitting function, we develop one-pass error bounded trajectory simplification algorithms \operb and \operba that scan each data point in a trajectory once and only once, allowing interpolating new data points or not, respectively.
@@
 \stitle{(3) Dense Temporal Subgraph Computation~\cite{MaHWLH17}}.
-We study dense subgraphs in {\em a special type of temporal networks} such that their nodes and edges are kept fixed, but their edge weights constantly and regularly vary with timestamps~\cite{MaHWLH17}.
+We study dense subgraphs in {\em a special type of temporal networks} whose nodes and edges are kept fixed, but edge weights constantly and regularly vary with timestamps~\cite{MaHWLH17}.
 Essentially, a temporal network with $T$ timestamps can be viewed as $T$ snapshots of a static network such that the network nodes and edges are kept the same among these $T$ snapshots, while the edge weights vary with network snapthots.
-Road traffic networks typically fall into this category of temporal networks, and dense subgraphs are used for road traffic analyses that are of particular importance for large cities, such as Beijing, New York, London and Paris, that are facing with heavy traffic congestions, one of the great challenges in urban computing.
+Road traffic networks typically fall into this category of temporal networks, and dense subgraphs are used for road traffic analyses that are of particular importance for transportation management of large cities.
 

### 2018-01-28 ApproxComp/sec-query.tex

@@
 This is achieved by exploring the characteristics of time intervals involved with dense subgraphs based on the observation of {\em evolving convergence phenomenon} in traffic data, inspired by the convergent evolution in nature\footnote{\small \url{https://en.wikipedia.org/wiki/Convergent_evolution}}.
-That is, our method provides time intervals with probabilistic grantees, instead of exact ones like \kw{FAV}.
-Using both real-life and synthetic data, we experimentally show that Our method \kw{FIDES} is over 1000 times faster than the state of the art solution  \kw{MEDEN}~\cite{BogdanovMS11}, while the quality of dense subgraphs found is comparable with  \kw{MEDEN} .
+That is, our method provides time intervals with probabilistic guarantees, instead of exact ones as \kw{FAV}.
+Using both real-life and synthetic data, we experimentally show that our method \kw{FIDES} is over 1000 times faster than \kw{MEDEN}~\cite{BogdanovMS11}, while the quality of dense subgraphs found is comparable with  \kw{MEDEN} .

### 2018-01-29 ApproxComp/sec-query.tex

@@
 The compression ratios of lossless methods are poor, and querying on the compressed data is time consuming due to the reconstruction of the original data \cite{Nibali:Trajic}.
-Hence, lossy techniques, which  provide approximate solutions with good compression ratios and bounded errors, is the mainstream.
+Hence, lossy techniques, which  provide approximate solutions with good compression ratios and bounded errors, are the mainstream.
 
@@
 Moreover, given a temporal network with $T$ timestamps, there are a total number of $T*(T+1)/2$ time intervals to consider, which further aggravates the difficulty.
-The state of the art solution \kw{MEDEN} \cite{BogdanovMS11} adopts a filter-and-verification ({\kw{FAV}) framework that {\em even if a large portion of time intervals are filtered, there often remain a large number of time intervals to verify}.
+The state of the art solution \kw{MEDEN} \cite{BogdanovMS11} adopts a Filter-And-Verification ({\kw{FAV}) framework that {\em even if a large portion of time intervals are filtered, there often remain a large number of time intervals to verify}.
 Hence, this method is not big data friendly, and is not scalable when temporal networks have a large number of nodes/edges or a large number $T$ of timestamps.

### 2018-01-31 ApproxComp/sec-beyond.tex

@@
-\section{Beyond Query and Data Approximations}
+\section{Beyond Query and Data Approximation}
 \label{sec-beyond}
 
-  For big data analytics, there are no one-size-fits-all techniques.  it is often necessary to combine different techniques to obtain good solutions.
+  For big data analytics, there are no one-size-fits-all techniques, and it is often necessary to combine different techniques to obtain good solutions.
 
@@
 
-It is also obvious that techniques beyond query and data approximation, such as theory and systems~\cite{FanGN13,Jordan15,ZahariaXWDADMRV16}, are must things for big data analytics.
+It is also obvious that techniques beyond query approximation and data approximation, such as theory and systems~\cite{FanGN13,Jordan15,ZahariaXWDADMRV16}, are must things for big data analytics.

### 2018-02-20 icde/cameraready/Response.tex

--- 2018-01-03 icde/revision/Response.tex
@@
 
-Yes, we agree that distributed processing is an important way for large scholar graphs.
+Yes, we agree that distributed processing is an important way for large scholarly graphs.
 But this topic is beyond the reach of this study, and we plan to do this in our future work (Conclusions, page 12).
@@
 
-We have further clarified this both in the contributions and in the related work.
+We have further clarified these both in the contributions and in the related work.
 

### 2018-02-20 icde/cameraready/sec-exp.tex

--- 2017-12-31 icde/revision/sec-exp.tex
@@
 In the last set of tests, we evaluated the impacts of time decaying factor $\sigma$, importance weighting factor $\lambda$, aggregating parameters $\alpha$ and $\beta$, and the TWPageRank.
-We fixed these parameters as well as $Y_s$ to their default values, used the TWPageRank proposed in this work by default, and tested the \PairAcc with the entire \recom and \fcita (\ie $T_p=+\infty$, $dif=1$).
+We fixed these parameters as well as $Y_s$ to their default values, used the TWPageRank proposed in this work by default, and tested the \PairAcc with the entire \recom and \fcita ($T_p=+\infty$, $dif=1$).
 
@@
 
-The TWPageRank has small impacts on efficiency, and the running time of the two algorithms only varies (6.34\%, 4.83\%) on (\aminer, \magdata) on average, respectively.
+The TWPageRank has a minor impact on efficiency, and the running time of the two algorithms only varies (6.34\%, 4.83\%) on (\aminer, \magdata) on average, respectively.
 
@@
 %
-Finally, the TWPageRank has little impacts on efficiency, and the running time of \ensemblerank and its counterparts only changes (6.34\%, 4.83\%) on (\aminer, \magdata) on average, respectively.
+Finally, the TWPageRank has few impacts on efficiency, and the running time of \ensemblerank and its counterparts only changes (6.34\%, 4.83\%) on (\aminer, \magdata) on average, respectively.
 }
@@
 \stitle{Summary}.
-From these tests we find the followings.
+From these tests, we find the followings.
 

### 2018-02-20 icde/cameraready/sec-incAlg.tex

--- 2017-12-31 icde/revision/sec-incAlg.tex
@@
 and the resulting graph is $G^+(V\cup\Delta V, E\cup\Delta E)$, where
-$\Delta V$ is a set of nodes with $\Delta V\cap V = \emptyset$, and $\Delta E$ is a set of directed edges on $\Delta V$ and from $\Delta V$ to $V$ only, as citations obey a natural temporal order, \ie an article only cites those published earlier.
-%, and it is rare for the mutual citations between two articles published in the same time.
+$\Delta V$ is a set of nodes with $\Delta V\cap V = \emptyset$, and $\Delta E$ is a set of directed edges on $\Delta V$ and from $\Delta V$ to $V$ only, as citation relationships obey a natural temporal order, \ie an article only cites those published earlier, and it is rare for the mutual citations between two articles published in the same time.
+%\markedb{and set $|\Delta |= |\Delta V|+|\Delta E|$.}
 
@@
 %This further shows that Eq.~(\ref{eq-inc-pop}) is a desired solution for popularity maintenance.
+%\markedb{By Eq.~(\ref{eq-inc-pop}), it is easy to see that updating the popularity of articles takes $O($ $|V^c|+|\Delta G^c|)$ time.}
 
@@
 Observe that (a) a topological order of the block-wise graph of $G_C$ can be computed in $O(|\Delta V|+|\Delta E|)$ time,
+%\markedb{Observe that (a) a topological order of the block-wise graph of $G_C$ can be computed in $O(|\Delta G|)$ time,}
 (b) updating the TWPageRank scores of nodes in $V_B$ and $V_C$ costs $O(|V_B\cup V_C|+|E_{B,a}\cup E_{C,a}\cup E_{CB}|)+t^+|E_{B,i}\cup E_{C,i}|)$ time, where $t^+$ is  the maximum number of iterations among all \sccs in $G_B$ and $G_C$, and, finally, (c) updating the scores of nodes in $V_A$ costs $O(|V_A|)$ time.
@@
 (a) It saves $O(|V^c|+|E^c|)$ and $O(|V^v|+|E^v|)$ time when maintaining \sccs and the topological order based on the update data only,
+%\markedb{(a) It saves $O(|G^c|)$ and $O(|G^v|)$ time when maintaining \sccs and the topological order based on the update data only,}
 %where ($|V^c|$, $|E^c|$, $|V^v|$, $|E^v|$) are more than (92\%, 89\%, 93\%, 89\%) of ($|V^{c,+}|$, $|E^{c,+}|$, $|V^{v,+}|$, $|E^{v,+}|$) on all tested graphs;

### 2018-02-20 icde/cameraready/sec-intro.tex

--- 2017-12-29 icde/revision/sec-intro.tex
@@
 %
-The popularity of an article is the sum of all its citation freshness (how close to the current year), while the one of venues and authors is the average popularity of their associated articles.
+The popularity of an article is the sum of all its citation freshness (closeness to the current year), while the one of venues and authors is the average popularity of their associated articles.
 %
@@
 \sstab(2)  We then develop  a batch algorithm for scholarly article ranking (Section \ref{sec-alg}), in which we propose a block-wise method for Time-Weighted PageRank %\markedb{and show its efficiency advantage in terms of an analysis of the citation characteristics and a specific structural property of scholarly graphs.}
-in which we propose a block-wise method for Time-Weighted PageRank in terms of an analysis of the citation characteristics of scholarly articles.
+%in which we propose a block-wise method for Time-Weighted PageRank
+in terms of an analysis of the citation characteristics of scholarly articles.
 
 \sstab(3)
-We further develop an incremental algorithm for dynamic scholarly article ranking (Section~\ref{sec-incAlg}), which partitions graphs into  {\em affected and unaffected areas}, and employs different updating strategies for nodes in affected and unaffected areas.
+We further develop an incremental algorithm for the block-wise algorithm
+to deal with dynamic scholarly article ranking (Section~\ref{sec-incAlg}), which partitions graphs into  {\em affected and unaffected areas}, and employs different updating strategies for nodes in affected and unaffected areas.
 

### 2018-09-19 ApproxComp/TKDE/sec-conclusion.tex

\section{Conclusions}
\label{sec-conclusion}

In this article we have systematiclly introduced approximation computation techniques for efficient and effective big data analytics.
Furthermore, although approximate computation does not put
theoretical bounds with respect to optimal solutions, it does expect a balance between efficiency and effectiveness. Indeed, (a) our query approximation techniques~\cite{tods-MaCFHW14,LinMZWH17,MaHWLH17} show that efficiency can be obtained with high accuracy in practice, and (b) our data approximation techniques for shortest paths/distances and link prediction~\cite{MaFLWCH16,DuanMAMH17} show that efficiency and accuracy can be obtained simultaneously for certain data analytic tasks. That is, the design policy of approximate computation is not to sacrifice effectiveness for efficiency, but to achieve both efficiency and effectiveness in practice.

### 2018-09-19 ApproxComp/TKDE/sec-data.tex

--- 2018-01-27 ApproxComp/sec-data.tex
@@
 
-\stitle{(1) Proxies for Shortest Paths and Distances~\cite{MaFLWCH16}}.
+\stitle{(1) Proxies for Shortest Paths and Distances~\cite{MaFLWCH16,MaFLWCH17}}.
 Computing shortest paths and distances is one of the fundamental problems on graphs.
@@
 \begin{figure}[tb!]
+  %\vspace{-1ex}
+  \begin{center}
+  \includegraphics[scale=0.45]{./dataApprox.png}
+  \end{center}
+  %\vspace{-1ex}
+  \caption{Data approximation}\label{fig-tech-dataappro}
   \vspace{-1ex}
-  \begin{center}
-  \includegraphics[scale=0.4]{./dataApprox.png}
-  \end{center}
-  \vspace{-4ex}
-  \caption{Data approximation}\label{fig-tech-dataappro}
-  \vspace{-4ex}
 \end{figure}
 
-\stitle{(2) Ensemble Enabled Link Prediction~\cite{DuanMAMH17}}.
+\stitle{(2) Network Anomaly Detection~\cite{HuAMH16}???}
+Anomaly (or outlier) detection aims at identifying those objects in a database that are unusual, i.e., different than the majority of the data and therefore suspicious resulting from a contamination, error, or fraud~\cite{Zimek2017}.
+Network anomaly detection has become very popular
+in recent years because of the importance of discovering key
+regions of structural inconsistency in the network. In addition
+to application-specific information carried by anomalies, the
+presence of such structural inconsistency is often an impediment
+to the effective application of data mining algorithms such as
+community detection and classification.
+
+Networks are inherently complex entities, and, hence, anomalies may be defined in a wide variety of ways.
+In this paper, our goal is to discover {\em  structural inconsistencies, i.e.,  the anomalous nodes that connect to a number of diverse influential communities}, inspired by the concept of social brokers across groups, which provide social capital in networks~\cite{s-hole04}.
+The presence of such structural inconsistencies may have a substantial impact on the structure of original networks, and prevent the effective application of the methods such as community detection to a variety of data mining problems.
+
+We have adopted the idea in the process of dealing with large graphs in the study of anomaly detection in graph streams, when dealing with the matrix representation of a social graph, and  we have both theoretically and experimentally shown that simplifying the matrix by replacing a part of small entry values  with zero has few affects on the computation of eigenvectors~\cite{YuAMW13}.
+
+\stitle{(3) Ensemble Enabled Link Prediction~\cite{DuanAMHH16,DuanMAMH17}}.
 Link prediction is the task to predict the formation of future links in a dynamic and evolving network, and has been extensively studied due to its numerous applications, such as the recommendation of friends in a social network, images in a multimedia network, or

### 2018-09-19 ApproxComp/TKDE/sec-introduction.tex

\section{Introduction}
\label{sec-intro}

Over the past a few years, research and development has made significant progresses on big data analytics with the supports from both governments and industries all over the world, such as Spark\footnote{\small \url{https://spark.apache.org}}, IBM Watson\footnote{\small \url{https://www.ibm.com/watson}} and Google AlphaGo\footnote{\small \url{https://deepmind.com/research/alphago}}. A fundamental issue for big data analytics is the efficiency, and various advances towards attacking this issues have been achieved recently, from theory to algorithms to systems~\cite{FanGN13,Jordan15,ZahariaXWDADMRV16}. However, if the optimal solution is unable to attain or not required or has a price to high to pay, it is reasonable to sacrifice optimality with a ``good'' feasible solution that can be computed efficiently. Hence, various approximation techniques have been developed, and can be classified into three aspects: algorithms, SQL aggregate queries and multiple layers of the system stack.
\bi
\item[(1)] {\em Approximation algorithms} were formalized in the 1970s~\cite{GareyGU72,Johnson74a}, and an approximation algorithm is necessarily polynomial, and is evaluated by the worst case possible relative error over all possible instances of the  NP-hard optimization problem, under the widely believed $P\ne NP$ conjecture. This is relatively mature research field algorithm community, many approximation algorithm have been designed for optimization problems~\cite{Dorit96,approx03,Ausiello99}.
\item[(2)] {\em Approximate query processing} supports a slightly constrained set of SQL-style declarative queries, and it specifically provides approximate results for standard SQL aggregate queries, \eg queries involving COUNT, AVG, SUM and PERCENTILE. Over the past two decades, approximate query processing has been successfully studied, among which sampling technique are heavily employed~\cite{ChaudhuriDK17,Mozafari17,Kraska17,GarofalakisG01}. There are not only classical DBMS systems such as Oracle that provide approximate functions to support approximate results~\footnote{\small \url{https://oracle-base.com/articles/12c/approximate-query-processing-12cr2}}, but also emerging new systems specially designed for approximate queries, such as BlinkDB~\footnote{\small \url{http://blindb.org/}}, Verdict~\footnote{\small \url{http://verdictdb.org/}}, Simba~~\footnote{\small \url{https://initialdlab.github.io/Simba/index.html}}. However, as pointed out in~\cite{ChaudhuriDK17}, `` it seems impossible to have an AQP system that supports the richness of SQL with significant saving of work while providing an accuracy guarantee that is acceptable to a broad set of application workloads.''

\item[(3)] {\em Approximation computing} is a recent computation technique that returns a possibly inaccurate result rather than a guaranteed accurate result from a system point of view.  It is involved with multiple layers of the system stack from software to hardware to systems (such as approximate circuits, approximate storage and loop perforation), and can be used for applications where an approximate result is sufficient for its purpose~\cite{AgrawalCGGNOPSS16,Mittal16b}. Recently, Workshop on approximate computing across the stack has been usefully held for research on hardware, programming languages and compiler support  for approximate computing  since 2014.  (2015~\footnote{\small \url{https://sampa.cs.washington.edu/new/wax2015/}},2016~\footnote{\small \url{http://approximate.computer/wax2016/}},2017~\footnote{\small  \url{http://approximate.computer/wax2017/}}, 2018~\footnote{\small  \url{http://approximate.computer/wax2018/}}). Besides the various task oriented quality metrics,  the quality-energy trade-off is also  concerned for approximate computing. For example, in k-means clustering algorithm, allowing only 5\% loss in classification accuracy can provide 50 times energy saving compared to the fully accurate classification~\cite{Mittal16b}
\ei

In this article, we present the idea of approximate computation for efficient and effective big data analytics: query approximation and data approximation, based on our recent research experiences. Different from existing approximation techniques~\cite{CormenLRS01,approx03,FanH14}, the approximation computation that we are going to introduce is unnecessarily theoretically bounded with respect to optimal solutions, but asks for both efficiency and effectiveness in practice.
????
\textbf{clarify differences
}
 is a computation which returns a possibly inaccurate result rather than a guaranteed accurate result, for a situation where an approximate result is sufficient for a purpose

### 2018-09-19 ApproxComp/TKDE/sec-data.tex

@@
 The shortest path $\path(s, t)$ = $\path(s, u_s)/$ $\path(u_s, u_t)/$ $\path(u_t, t)$, where $u_s$ and $u_t$ are the proxies of $s$ and $t$, respectively.
-Here  $\path(s, u_s)$ and $\path(u_t, t)$ are pre-computed, and $\path(u_s, u_t)$ can be computed on the reduced subgraph $G'$ by invoking any existing algorithms
+As  $\path(s, u_s)$ and $\path(u_t, t)$ are pre-computed, and $\path(u_s, u_t)$ can be computed on the reduced subgraph $G'$ by invoking any existing algorithms
 (\eg \ah~\cite{zhu2013shortest}).
@@
 
-\stitle{(2) Network Anomaly Detection~\cite{HuAMH16}???}
+\stitle{(2) Network Anomaly Detection~\cite{HuAMH16}}
 Anomaly (or outlier) detection aims at identifying those objects in a database that are unusual, i.e., different than the majority of the data and therefore suspicious resulting from a contamination, error, or fraud~\cite{Zimek2017}.
@@
 
-We have adopted the idea in the process of dealing with large graphs in the study of anomaly detection in graph streams, when dealing with the matrix representation of a social graph, and  we have both theoretically and experimentally shown that simplifying the matrix by replacing a part of small entry values  with zero has few affects on the computation of eigenvectors~\cite{YuAMW13}.
+While a variety of graph embeddings, such as multidimensional scaling~\cite{mds}, are available in the literature, they aim to preserve (global) pairwise similarities and are not optimized to networks and the problem of anomaly detection.
+Hence, they cannot be directly used for the detection of structural inconsistencies proposed in this paper.
+Therefore, a novel embedding method will be developed, which is specifically designed to ferret out the anomalous nodes in large networks.
+
+The embedding approach is  based on a model,
+in which each dimension of the embedding corresponds to a clustered
+region in the network.
+In other words, the similarity of different nodes along a particular dimension, indicates their similarity to a particular clustered region.
+Therefore, this embedding retains
+a very high level of interpretability in  terms of the original
+graph data, which is very useful from an application-specific perspective.
+The nature of  the embedding also  makes it  possible  to detect anomalous nodes, by examining the interaction of each node with the different regions in terms of the embedding.
+In particular, we measure the {\em level of anomalousness} of a node in terms of the embedding imposed on the node and its neighbors.
+
+Such an approach is however rather hard to apply to the case of large networks, because
+the complexity of the approach is in proportion to the square of the number of nodes when optimizing the embedding and
+because the noises in the embedding seriously impair the accuracy of detected anomalous nodes.
+Hence, we incorporate the sampling and  graph partitioning techniques, and, moreover, propose a novel dimension reduction technique to make the approach more scalable and effective for large networks.
+
+Using both real-life data and synthetic
+data , we conduct an extensive experimental study.
+We find that our embedding approach to network anomaly detection is both effective and efficient.
+(a) The modularity \cite{newman1} was increased about 2.9\% and 2.4\% for amazon, 4.9\% and 4.2\% for dblp and 6.3\% and 4.2\% for with our approach and oddball~\cite{akoglu14}, respectively; (b) The $F_1$ measure was about $88\%$ and $70\%$ for synthetic with our approach and oddball, respectively; And (c) the running time of our embedding approach increases reasonably with the increase of graph sizes, even with large number of communities, while traditional  multidimensional scaling approach~\cite{mds} ran out of memory.
 

### 2018-09-19 ApproxComp/TKDE/sec-query.tex

--- 2018-01-29 ApproxComp/sec-query.tex
@@
 Observe that nobody would try each and every store to find a pair of shoes with the best cost-performance ratio.
-That is, inexact (approximate) solutions are good enough in this case.
+That is, inexact (approximate) solutions are good enough for certain cases.
 %
-On the other hand, when taking noises (common for big data) into account, it may not always be a good idea to compute exact answers
-for those data analytic tasks whose answers are rare or hard to identify, such as the detection of homegrown violent extremists (HVEs) who seek to commit acts of terrorism in the United States and abroad~\cite{HungJ16}, as exact solutions may have a high chance to miss possible candidates.
+On the other hand, when taking noises (very common for big data) into account, it may not always be a good idea to compute exact answers
+for those data analytic tasks whose answers are rare or hard to identify, such as the detection of homegrown violent extremists (HVEs) who seek to commit acts of terrorism in the United States and abroad~\cite{HungJ16}, as exact solutions may have a high chance to miss/ignore possible candidates.
 
@@
 \begin{figure}[tb!]
+ % \vspace{-1ex}
+  \begin{center}
+  \includegraphics[scale=0.45]{./queryApprox.png}
+  %\vspace{-1ex}
+  \caption{Query approximation}\label{fig-tech-queryappro}
+  \end{center}
   \vspace{-1ex}
-  \begin{center}
-  \includegraphics[scale=0.4]{./queryApprox.png}
-  \end{center}
-  \vspace{-4ex}
-  \caption{Query approximation}\label{fig-tech-queryappro}
-  \vspace{-4ex}
 \end{figure}
 
-\stitle{(1) Strong Simulation~\cite{tods-MaCFHW14}}. Given a pattern graph $Q$ and a data graph $G$,
+\stitle{(1) Strong Simulation~\cite{ShuaiMaVLDB12,tods-MaCFHW14}}. Given a pattern graph $Q$ and a data graph $G$,
 {\em graph pattern matching} is to find all subgraphs of $G$ that match $Q$, and is being increasingly used in various applications, \eg biology and social networks.
@@
 Even worse, online data in many cases only represents a partial world (\eg terrorist collaboration networks and homosexual networks often involve with a large amount of off-line data).
-Exact computations on such online data, whose accompanying off-line data is extremely hard to gather, typically decreases the chance of identifying candidate answers.
+Exact computations on such online data, whose off-line counterpart is extremely hard to gather, typically decreases the chance of identifying candidate answers.
 These hinder the usability of graph pattern matching in emerging applications.
@@
 
-To rectify these problems, strong simulation, an ``approximate'' substitute for subgraph isomorphism, is proposed for graph pattern matching~\cite{tods-MaCFHW14}, such that strong simulation (a) theoretically preserves the key topology of pattern graphs and finds a bounded number of matches, (b) retains the same complexity as earlier extensions of graph simulation~\cite{FanLMTWW10,FanLMTW11}, by providing a cubic-time algorithm for computing strong simulation, and (c) has the locality property that allows us to develop an effective distributed algorithm to conduct graph pattern matching on distributed graphs.
+To rectify these problems, strong simulation, an ``approximate'' substitute for subgraph isomorphism, is proposed for graph pattern matching~\cite{tods-MaCFHW14}, which (a) theoretically preserves the key topology of pattern graphs and finds a bounded number of matches, (b) retains the same complexity as earlier extensions of graph simulation~\cite{FanLMTWW10,FanLMTW11}, by providing a cubic-time algorithm for strong simulation compuation, and (c) has the locality property that allows us to develop an effective distributed algorithm to conduct graph pattern matching on distributed graphs.
 
@@
 
-Piece-wise line simplification (\lsa) comes from computational geometry, whose target is to approximate a given finer piece-wise linear curve by another coarser piece-wise linear curve ({normally} a subset of the former), such that the maximum distance of the former from the later is bounded by a user specified constant.
+Piece-wise line simplification (\lsa) comes from the computational geometry, whose target is to approximate a given finer piece-wise linear curve by another coarser piece-wise linear curve ({normally} a subset of the former), such that the maximum distance of the former from the later is bounded by a user specified constant (\ie error bound).
 It is widely used due to its distinct advantages: (a) simple and easy to implement, (b) no need extra knowledge and suitable for freely  moving  objects, and (c) bounded errors with good compression ratios.

### 2018-09-20 ApproxComp/TKDE/sec-data.tex

@@
 Network anomaly detection has become very popular
-in recent years because of the importance of discovering key
+recently because of the importance of discovering key
 regions of structural inconsistency in the network. In addition
@@
 Networks are inherently complex entities, and, hence, anomalies may be defined in a wide variety of ways.
-In this paper, our goal is to discover {\em  structural inconsistencies, i.e.,  the anomalous nodes that connect to a number of diverse influential communities}, inspired by the concept of social brokers across groups, which provide social capital in networks~\cite{s-hole04}.
-The presence of such structural inconsistencies may have a substantial impact on the structure of original networks, and prevent the effective application of the methods such as community detection to a variety of data mining problems.
-
+Our goal is to discover {\em  structural inconsistencies, i.e.,  the anomalous nodes that connect to a number of diverse influential communities}, inspired by the concept of social brokers across groups, which provide social capital in networks~\cite{s-hole04}.
 While a variety of graph embeddings, such as multidimensional scaling~\cite{mds}, are available in the literature, they aim to preserve (global) pairwise similarities and are not optimized to networks and the problem of anomaly detection.
 Hence, they cannot be directly used for the detection of structural inconsistencies proposed in this paper.
-Therefore, a novel embedding method will be developed, which is specifically designed to ferret out the anomalous nodes in large networks.
+We propose a novel graph embedding method, specifically designed to ferret out the anomalous nodes in large networks.
 
-The embedding approach is  based on a model,
-in which each dimension of the embedding corresponds to a clustered
-region in the network.
+Our embedding approach is  based on a model, in which each dimension of the embedding corresponds to a clustered region in the network.
 In other words, the similarity of different nodes along a particular dimension, indicates their similarity to a particular clustered region.
-Therefore, this embedding retains
-a very high level of interpretability in  terms of the original
-graph data, which is very useful from an application-specific perspective.
+Therefore, this embedding retains a very high level of interpretability in  terms of the original graph data, which is very useful from an application-specific perspective.
 The nature of  the embedding also  makes it  possible  to detect anomalous nodes, by examining the interaction of each node with the different regions in terms of the embedding.
@@
 
-Such an approach is however rather hard to apply to the case of large networks, because
-the complexity of the approach is in proportion to the square of the number of nodes when optimizing the embedding and
-because the noises in the embedding seriously impair the accuracy of detected anomalous nodes.
-Hence, we incorporate the sampling and  graph partitioning techniques, and, moreover, propose a novel dimension reduction technique to make the approach more scalable and effective for large networks.
+Dimensionality of embedding, each node is represented as a d-dimensional vector, can be large.
+Hence, such an approach is rather hard to apply to the case of large networks, because the complexity of the approach is in proportion to the square of the number of nodes when optimizing the embedding and because the noises in the embedding seriously impair the accuracy of detected anomalous nodes.
+Hence, we incorporate data approximation techniques (sampling, graph partitioning techniques, and, moreover, a novel dimension reduction technique) to make the approach more scalable and effective for large networks.
+
+Essentially, in our graph embedding, $d$ represents the number of communities.
+As the anomalous nodes are only determined by influential communities and nodes typically connect to a limited number of communities, the complete d-dimensions are unnecessary, and a limited number of communities suffice to ascertain anomalies.
+Thus, our dimension reduction technique (referred to as ($k+\beta$ reduction) only maintains ($k + \beta$)-dimensions for embedding of each node, where k is the maximum number of communities to connect, $\beta$ is to tolerate mistakes when determining the $k$ communities and is removed after the computation process.
+Here $k \ll d$ and  $\ll d$, \eg $k = 10$ and $\beta = 2$ and $d=600$ for a network with $10^6$ nodes.
 
@@
 data , we conduct an extensive experimental study.
-We find that our embedding approach to network anomaly detection is both effective and efficient.
-(a) The modularity \cite{newman1} was increased about 2.9\% and 2.4\% for amazon, 4.9\% and 4.2\% for dblp and 6.3\% and 4.2\% for with our approach and oddball~\cite{akoglu14}, respectively; (b) The $F_1$ measure was about $88\%$ and $70\%$ for synthetic with our approach and oddball, respectively; And (c) the running time of our embedding approach increases reasonably with the increase of graph sizes, even with large number of communities, while traditional  multidimensional scaling approach~\cite{mds} ran out of memory.
+ (a) The modularity \cite{newman1} was increased about 4.9\% and 3.6\% with our approach and oddball~\cite{akoglu14}, respectively; (b) The $F_1$ measure was about $88\%$ and $70\%$ for synthetic with our approach and oddball, respectively; (c) The running time of our embedding approach increases reasonably with the increase of graph sizes, even with large number of communities, while traditional  multidimensional scaling approach~\cite{mds} ran out of memory.
 
 \stitle{(3) Ensemble Enabled Link Prediction~\cite{DuanAMHH16,DuanMAMH17}}.
-Link prediction is the task to predict the formation of future links in a dynamic and evolving network, and has been extensively studied due to its numerous applications, such as the recommendation of friends in a social network, images in a multimedia network, or
-collaborators in a scientific network.
+Link prediction is the task to predict the formation of future links in a dynamic and evolving network, and has been extensively studied due to its numerous applications, such as the recommendation of friends in a social network, images in a multimedia network, or collaborators in a scientific network.
 

### 2018-09-20 ApproxComp/TKDE/sec-query.tex

@@
 
-We develop a data-driven approach, instead of filter-and-verification, to  identifying the most possible $k$ time intervals from $T \times (T + 1)/2$ time intervals, in which $T$ is the number of snapshots and k is a small constant, \eg 10.
+We develop a data-driven approach (referred to as \kw{FIDES}), instead of filter-and-verification, to  identifying the most possible $k$ time intervals from $T \times (T + 1)/2$ time intervals, in which $T$ is the number of snapshots and k is a small constant, \eg 10.
 This is achieved by exploring the characteristics of time intervals involved with dense subgraphs based on the observation of {\em evolving convergence phenomenon} in traffic data, inspired by the convergent evolution in nature\footnote{\small \url{https://en.wikipedia.org/wiki/Convergent_evolution}}.

### 2018-09-23 ApproxComp/TKDE/sec-beyond.tex

--- 2018-01-31 ApproxComp/sec-beyond.tex
@@
 
-We have seen that data sampling helps to achieve a balance between efficiency and effectiveness for link prediction,
-and other techniques such as incremental computation, data partitioning, data indexing and distributed computing can
-also be unitized for big data analytics, and even for designing query and data approximation techniques for big data analytics.
-For instance, it is easy to see that incremental algorithms (see~\cite{Reps96} for a survey) can be utilized to achieve query approximation.
+We have seen that sampling helps to achieve a balance between efficiency and effectiveness for approximate query processing~\cite{ChaudhuriDK17,Mozafari17,Kraska17,GarofalakisG01} and link prediction~\cite{DuanAMHH16,DuanMAMH17}},
+and other techniques such as incremental computation~\cite{Reps96,FanLMTWW10,rankicde2018}, distributed computing~\cite{MaCHW12,FanXWYJZZCT17}, and system techniques~\eg caching~\cite{WangLMNT18}, new hard ware~\cite{ArulrajPD15,iccd2018} can also be unitized for big data analytics, and can even be combined for designing query and data approximation techniques for big data analytics.
 
+It is worth pointing out that for all kind of techniques big data analytics, various computing resources should be seriously considered, \eg using bounded resources for approximation~\cite{CaoF17} and for incremental computation~\cite{abs-1801-01012}.
 It is also obvious that techniques beyond query approximation and data approximation, such as theory and systems~\cite{FanGN13,Jordan15,ZahariaXWDADMRV16}, are must things for big data analytics.

### 2018-09-23 ApproxComp/TKDE/sec-conclusion.tex

@@
 theoretical bounds with respect to optimal solutions, it does expect a balance between efficiency and effectiveness.
-Indeed, (a) our query approximation techniques~\cite{tods-MaCFHW14,LinMZWH17,MaHWLH17} show that efficiency can be obtained with high accuracy in practice, and (b) our data approximation techniques for shortest paths/distances and link prediction~\cite{MaFLWCH16,DuanMAMH17} show that efficiency and accuracy can be obtained simultaneously for certain data analytic tasks.
+Indeed, (a) our query approximation techniques~\cite{ShuaiMaVLDB12,tods-MaCFHW14,LinMZWH17,MaHWLH17} show that efficiency can be obtained with high accuracy in practice, and (b) our data approximation techniques for shortest paths/distances and link prediction~\cite{MaFLWCH16,MaFLWCH17,HuAMH16,DuanAMHH16,DuanMAMH17} show that efficiency and accuracy can be obtained simultaneously for certain data analytic tasks.
 That is, the design policy of approximate computation is not to sacrifice effectiveness for efficiency, but to achieve both efficiency and effectiveness in practice.

### 2018-09-23 ApproxComp/TKDE/sec-data.tex

@@
 Thus, our dimension reduction technique (referred to as ($k+\beta$ reduction) only maintains ($k + \beta$)-dimensions for embedding of each node, where k is the maximum number of communities to connect, $\beta$ is to tolerate mistakes when determining the $k$ communities and is removed after the computation process.
-Here $k \ll d$ and  $\ll d$, \eg $k = 10$ and $\beta = 2$ and $d=600$ for a network with $10^6$ nodes.
+Here $k, \beta \ll d$, \eg $k = 10$ and $\beta = 2$ and $d=600$ for a network with $10^6$ nodes.
 
@@
 data , we conduct an extensive experimental study.
- (a) The modularity \cite{newman1} was increased about 4.9\% and 3.6\% with our approach and oddball~\cite{akoglu14}, respectively; (b) The $F_1$ measure was about $88\%$ and $70\%$ for synthetic with our approach and oddball, respectively; (c) The running time of our embedding approach increases reasonably with the increase of graph sizes, even with large number of communities, while traditional  multidimensional scaling approach~\cite{mds} ran out of memory.
+ (a) The modularity \cite{newman1} was increased about 4.9\% and 3.6\% with our approach and OddBall~\cite{akoglu14}, respectively; (c) Our approach scales to graph graphs with large number of communities, while traditional  multidimensional scaling approach~\cite{mds} ran out of memory.
 

### 2018-09-23 ApproxComp/TKDE/sec-introduction.tex

@@
 Over the past two decades, approximate query processing has been successfully studied, among which sampling technique are heavily employed~\cite{ChaudhuriDK17,Mozafari17,Kraska17,GarofalakisG01}.
-There are not only classical DBMS systems such as Oracle that provide approximate functions to support approximate results~\footnote{\small \url{https://oracle-base.com/articles/12c/approximate-query-processing-12cr2}}, but also emerging new systems specially designed for approximate queries, such as BlinkDB~\footnote{\small \url{http://blindb.org/}}, Verdict~\footnote{\small \url{http://verdictdb.org/}}, Simba~~\footnote{\small \url{https://initialdlab.github.io/Simba/index.html}}.
+There are not only classical DBMS systems such as Oracle that provide approximate functions to support approximate results~\footnote{\small \url{https://oracle-base.com/articles/12c/approximate-query} \url{-processing-12cr2}}, but also emerging new systems specially designed for approximate queries, such as BlinkDB~\footnote{\small \url{http://blindb.org/}}, Verdict~\footnote{\small \url{http://verdictdb.org/}}, Simba~~\footnote{\small \url{https://initialdlab.github.io/Simba/index.html}}.
 However, as pointed out in~\cite{ChaudhuriDK17}, `` it seems impossible to have an AQP system that supports the richness of SQL with significant saving of work while providing an accuracy guarantee that is acceptable to a broad set of application workloads.''
@@
 It is involved with multiple layers of the system stack from software to hardware to systems (such as approximate circuits, approximate storage and loop perforation), and can be used for applications where an approximate result is sufficient for its purpose~\cite{AgrawalCGGNOPSS16,Mittal16b}.
-Recently, Workshop on approximate computing across the stack has been usefully held for research on hardware, programming languages and compiler support  for approximate computing  since 2014.
+Recently, workshop on approximate computing across the stack has been usefully held for research on hardware, programming languages and compiler support  for approximate computing  since 2014.
 (2015~\footnote{\small \url{https://sampa.cs.washington.edu/new/wax2015/}},2016~\footnote{\small \url{http://approximate.computer/wax2016/}},2017~\footnote{\small  \url{http://approximate.computer/wax2017/}}, 2018~\footnote{\small  \url{http://approximate.computer/wax2018/}}).
@@
 
-In this article, we present the idea of approximate computation for efficient and effective big data analytics: query approximation and data approximation, based on our recent research experiences.
-Different from existing approximation techniques~\cite{CormenLRS01,approx03,FanH14}, the approximation computation that we are going to introduce is unnecessarily theoretically bounded with respect to optimal solutions, but asks for both efficiency and effectiveness in practice.
-????
-\textbf{clarify differences
-}
- is a computation which returns a possibly inaccurate result rather than a guaranteed accurate result, for a situation where an approximate result is sufficient for a purpose
+In this article, we present the idea of approximate computation for efficient and effective big data analytics: query approximation and data approximation, based on our recent research experiences~\cite{MaCHW12,ShuaiMaVLDB12,tods-MaCFHW14,LinMZWH17,MaHWLH17,MaFLWCH16,MaFLWCH17,HuAMH16,DuanAMHH16,DuanMAMH17,rankicde2018}.
+Approximation algorithms ask for feasible solutions that are theoretically bounded with respect to optimal solutions from an algorithm design aspect.
+Approximate query processing and approximation computing relax the need for accuracy guarantees for aggregate SQL queries and for multiple layers of the system stack, respectively.
+Similarly, our approximate computation is unnecessarily theoretically bounded with respect to optimal solutions, but from an algorithm design point of view.
+That is, we focus on approximate computation for big data analytics for a situation where an approximate result is sufficient for a purpose.
+
+%Different from existing approximation techniques~\cite{CormenLRS01,approx03,FanH14}, the approximation computation that we are going to introduce is unnecessarily theoretically bounded with respect to optimal solutions, but asks for both efficiency and effectiveness in practice.

### 2018-09-23 ApproxComp/TKDE/sec-beyond.tex

@@
-\section{Beyond Query and Data Approximation}
+\section{Beyond Approximation Techniques}
 \label{sec-beyond}
@@
 We have seen that sampling helps to achieve a balance between efficiency and effectiveness for approximate query processing~\cite{ChaudhuriDK17,Mozafari17,Kraska17,GarofalakisG01} and link prediction~\cite{DuanAMHH16,DuanMAMH17}},
-and other techniques such as incremental computation~\cite{Reps96,FanLMTWW10,rankicde2018}, distributed computing~\cite{MaCHW12,FanXWYJZZCT17}, and system techniques~\eg caching~\cite{WangLMNT18}, new hard ware~\cite{ArulrajPD15,iccd2018} can also be unitized for big data analytics, and can even be combined for designing query and data approximation techniques for big data analytics.
+and other techniques such as incremental computation~\cite{Reps96,FanLMTWW10,rankicde2018}, distributed computing~\cite{MaCHW12,FanXWYJZZCT17}, and system techniques~\eg caching~\cite{WangLMNT18}, hardware~\cite{AbergerLTNOR17,Han0Y18} can also be unitized for big data analytics, and can even be combined for designing query and data approximation techniques for big data analytics.
 

### 2018-09-23 ApproxComp/TKDE/sec-data.tex

@@
 As the anomalous nodes are only determined by influential communities and nodes typically connect to a limited number of communities, the complete d-dimensions are unnecessary, and a limited number of communities suffice to ascertain anomalies.
-Thus, our dimension reduction technique (referred to as ($k+\beta$ reduction) only maintains ($k + \beta$)-dimensions for embedding of each node, where k is the maximum number of communities to connect, $\beta$ is to tolerate mistakes when determining the $k$ communities and is removed after the computation process.
+Thus, our dimension reduction technique (referred to as $k+\beta$ reduction) only maintains ($k + \beta$)-dimensions for embedding of each node, where k is the maximum number of communities to connect, $\beta$ is to tolerate mistakes when determining the $k$ communities and is removed after the computation process.
 Here $k, \beta \ll d$, \eg $k = 10$ and $\beta = 2$ and $d=600$ for a network with $10^6$ nodes.

### 2018-09-23 ApproxComp/TKDE/sec-introduction.tex

@@
 A fundamental issue for big data analytics is the efficiency, and various advances towards attacking this issues have been achieved recently, from theory to algorithms to systems~\cite{FanGN13,Jordan15,ZahariaXWDADMRV16}.
-However, if the optimal solution is unable to attain or not required or has a price to high to pay, it is reasonable to sacrifice optimality with a ``good'' feasible solution that can be computed efficiently.
-Hence, various approximation techniques have been developed, and can be classified into three aspects: algorithms, SQL aggregate queries and multiple layers of the system stack.
+However, {\em if the optimal solution is unable to attain or not required or has a price to high to pay, it is reasonable to sacrifice optimality with a ``good'' feasible solution that can be computed efficiently}.
+Hence, various approximation techniques have been developed, and can in general be classified into three aspects: algorithms, SQL aggregate queries and multiple layers of the system stack.
+
 \bi
-\item[(1)] {\em Approximation algorithms} were formalized in the 1970s~\cite{GareyGU72,Johnson74a}, and an approximation algorithm is necessarily polynomial, and is evaluated by the worst case possible relative error over all possible instances of the  NP-hard optimization problem, under the widely believed $P\ne NP$ conjecture.
-This is relatively mature research field algorithm community, many approximation algorithm have been designed for optimization problems~\cite{Dorit96,approx03,Ausiello99}.
+\item[(1)] {\em Approximation algorithms} were formally defined in the 1970s~\cite{GareyGU72,Johnson74a}.
+An approximation algorithm is necessarily polynomial, and is evaluated by the worst case possible relative error over all possible instances of the  NP-hard optimization problem, under the widely believed $P\ne NP$ conjecture.
+This is relatively mature research field algorithm community, many approximation algorithm have been designed for optimization problems (see books~\cite{Dorit96,approx03,Ausiello99}).
 \item[(2)] {\em Approximate query processing} supports a slightly constrained set of SQL-style declarative queries, and it specifically provides approximate results for standard SQL aggregate queries, \eg queries involving COUNT, AVG, SUM and PERCENTILE.
 Over the past two decades, approximate query processing has been successfully studied, among which sampling technique are heavily employed~\cite{ChaudhuriDK17,Mozafari17,Kraska17,GarofalakisG01}.
-There are not only classical DBMS systems such as Oracle that provide approximate functions to support approximate results~\footnote{\small \url{https://oracle-base.com/articles/12c/approximate-query} \url{-processing-12cr2}}, but also emerging new systems specially designed for approximate queries, such as BlinkDB~\footnote{\small \url{http://blindb.org/}}, Verdict~\footnote{\small \url{http://verdictdb.org/}}, Simba~~\footnote{\small \url{https://initialdlab.github.io/Simba/index.html}}.
+Not only traditional DBMS systems, such as Oracle\footnote{\small \url{https://oracle-base.com/articles/12c/approximate-query} \url{-processing-12cr2}},  provide approximate functions to support approximate results, but also emerging new systems specially designed for approximate queries, such as BlinkDB\footnote{\small \url{http://blindb.org/}}, Verdict\footnote{\small \url{http://verdictdb.org/}}, Simba\footnote{\small \url{https://initialdlab.github.io/Simba/index.html}}, have been designed.
 However, as pointed out in~\cite{ChaudhuriDK17}, `` it seems impossible to have an AQP system that supports the richness of SQL with significant saving of work while providing an accuracy guarantee that is acceptable to a broad set of application workloads.''
@@
 \item[(3)] {\em Approximation computing} is a recent computation technique that returns a possibly inaccurate result rather than a guaranteed accurate result from a system point of view.
-It is involved with multiple layers of the system stack from software to hardware to systems (such as approximate circuits, approximate storage and loop perforation), and can be used for applications where an approximate result is sufficient for its purpose~\cite{AgrawalCGGNOPSS16,Mittal16b}.
-Recently, workshop on approximate computing across the stack has been usefully held for research on hardware, programming languages and compiler support  for approximate computing  since 2014.
-(2015~\footnote{\small \url{https://sampa.cs.washington.edu/new/wax2015/}},2016~\footnote{\small \url{http://approximate.computer/wax2016/}},2017~\footnote{\small  \url{http://approximate.computer/wax2017/}}, 2018~\footnote{\small  \url{http://approximate.computer/wax2018/}}).
+It involves with multiple layers of the system stack from software to hardware to systems (such as approximate circuits, approximate storage and loop perforation), and can be used for applications where an approximate result is sufficient for its purpose~\cite{AgrawalCGGNOPSS16,Mittal16b}.
+Recently, a workshop on approximate computing across the stack has been usefully held for research on hardware, programming languages and compiler support  for approximate computing  since 2014.
+(see \eg 2016\footnote{\small \url{http://approximate.computer/wax2016/}}, 2017\footnote{\small  \url{http://approximate.computer/wax2017/}} and 2018\footnote{\small \url{http://approximate.computer/wax2018/}}).
 Besides the various task oriented quality metrics,  the quality-energy trade-off is also  concerned for approximate computing.
-For example, in k-means clustering algorithm, allowing only 5\% loss in classification accuracy can provide 50 times energy saving compared to the fully accurate classification~\cite{Mittal16b}
+For example, in k-means clustering algorithm, allowing only 5\% loss in classification accuracy can provide 50 times energy saving compared with the fully accurate classification~\cite{Mittal16b}
 \ei

### 2018-09-23 ApproxComp/TKDE/sec-beyond.tex

@@
 It is worth pointing out that for all kind of techniques big data analytics, various computing resources should be seriously considered, \eg using bounded resources for approximation~\cite{CaoF17} and for incremental computation~\cite{abs-1801-01012}.
-It is also obvious that techniques beyond query approximation and data approximation, such as theory and systems~\cite{FanGN13,Jordan15,ZahariaXWDADMRV16}, are must things for big data analytics.
+Further, theoretical analyses are also important for developing approximation techniques.
+For instance, our query and data approximation techniques are based serious theoretical results~\cite{ShuaiMaVLDB12,tods-MaCFHW14,LinMZWH17,MaFLWCH16,MaFLWCH17}.

### 2018-09-23 ApproxComp/TKDE/sec-data.tex

@@
 
-The framework for speeding-up shortest path and distance queries with proxies consists of modules preprocessing and query answering as follows.
+The framework for speeding-up shortest path and distance queries with proxies consists of two module, preprocessing and query answering, as follows.
 
@@
   \caption{Data approximation}\label{fig-tech-dataappro}
-  \vspace{-1ex}
+  \vspace{-2ex}
 \end{figure}
@@
 link prediction is due to their complexity. In
-collaborative filtering applications, the item dimension is of the
-order of a few hundred thousand, whereas even the smallest  real-world networks contain more than a million nodes.
-Even worse, we also experientially find that the quality of link prediction for latent factor models decreases with the increase of data sparsity,
+collaborative filtering applications, items have a few hundred thousand dimensions, whereas even the smallest  real-world networks contain more than a million nodes.
+Even worse, we also experientially verify that the quality of link prediction for latent factor models decreases with the increase of data sparsity,
 and networks typically become sparser when their sizes grow larger.

### 2018-09-23 ApproxComp/TKDE/sec-introduction.tex

@@
 Over the past a few years, research and development has made significant progresses on big data analytics with the supports from both governments and industries all over the world, such as Spark\footnote{\small \url{https://spark.apache.org}}, IBM Watson\footnote{\small \url{https://www.ibm.com/watson}} and Google AlphaGo\footnote{\small \url{https://deepmind.com/research/alphago}}.
-A fundamental issue for big data analytics is the efficiency, and various advances towards attacking this issues have been achieved recently, from theory to algorithms to systems~\cite{FanGN13,Jordan15,ZahariaXWDADMRV16}.
+A fundamental issue for big data analytics is the efficiency, and various advances towards attacking this issue have been achieved recently, from theory to algorithms to systems~\cite{FanGN13,Jordan15,ZahariaXWDADMRV16}.
 However, {\em if the optimal solution is unable to attain or not required or has a price to high to pay, it is reasonable to sacrifice optimality with a ``good'' feasible solution that can be computed efficiently}.

### 2018-09-23 ApproxComp/TKDE/sec-query.tex

@@
 On the other hand, when taking noises (very common for big data) into account, it may not always be a good idea to compute exact answers
-for those data analytic tasks whose answers are rare or hard to identify, such as the detection of homegrown violent extremists (HVEs) who seek to commit acts of terrorism in the United States and abroad~\cite{HungJ16}, as exact solutions may have a high chance to miss/ignore possible candidates.
+for those data analytic tasks whose answers are rare or hard to identify, such as the detection of homegrown violent extremists (HVEs) who seek to commit acts of terrorism in the United States and abroad~\cite{HungJ16}, as finding exact solutions may have a high chance to miss/ignore possible candidates.
 
@@
   \end{center}
-  \vspace{-1ex}
+  \vspace{-2ex}
 \end{figure}
@@
 The goodness of subgraph isomorphism is that all matched subgraphs  are exactly the same as the pattern graph, \ie completely preserving the  topology structure between the pattern graph and data graph.
-However, subgraph isomorphism is \NP-complete, and may return exponential many matched subgraphs.
+However, subgraph isomorphism is \NP-complete, and may return exponentially many matched subgraphs.
 Further, subgraph isomorphism is too restrictive to find sensible matches in certain scenarios, as observed in~\cite{FanLMTWW10}.
-Even worse, online data in many cases only represents a partial world (\eg terrorist collaboration networks and homosexual networks often involve with a large amount of off-line data).
-Exact computations on such online data, whose off-line counterpart is extremely hard to gather, typically decreases the chance of identifying candidate answers.
+Even worse, online data in many cases only represents a partial world (\eg terrorist collaboration networks and homosexual networks are often accompanied with a large amount of offline data).
+Exact computations on online data, whose offline counterpart is extremely hard to collect, typically decreases the chance of identifying candidate answers.
 These hinder the usability of graph pattern matching in emerging applications.
@@
 
-Dense subgraphs are a general concept, and their concrete semantics highly depend on the studied problems and applications.
+Dense subgraphs are a general concept, and their concrete semantics highly depends on the studied problems and applications.
 Though  dense subgraphs have been widely studied in static networks, how to properly define their semantics over temporal networks is still in the early stage, not to mention effective and efficient analytic algorithms.

### 2018-09-23 ApproxComp/TKDE/sec-beyond.tex

@@
 
-It is worth pointing out that for all kind of techniques big data analytics, various computing resources should be seriously considered, \eg using bounded resources for approximation~\cite{CaoF17} and for incremental computation~\cite{abs-1801-01012}.
-Further, theoretical analyses are also important for developing approximation techniques.
+It is worth pointing out that (1) for all kind of techniques big data analytics, various computing resources should be seriously considered, \eg using bounded resources for approximation~\cite{CaoF17} and for incremental computation~\cite{abs-1801-01012}, and (2) theoretical analyses are also important for developing approximation techniques.
 For instance, our query and data approximation techniques are based serious theoretical results~\cite{ShuaiMaVLDB12,tods-MaCFHW14,LinMZWH17,MaFLWCH16,MaFLWCH17}.

### 2018-09-23 ApproxComp/TKDE/sec-introduction.tex

@@
 Recently, a workshop on approximate computing across the stack has been usefully held for research on hardware, programming languages and compiler support  for approximate computing  since 2014.
-(see \eg 2016\footnote{\small \url{http://approximate.computer/wax2016/}}, 2017\footnote{\small  \url{http://approximate.computer/wax2017/}} and 2018\footnote{\small \url{http://approximate.computer/wax2018/}}).
+(see \eg 2017\footnote{\small  \url{http://approximate.computer/wax2017/}} and 2018\footnote{\small \url{http://approximate.computer/wax2018/}}).
 Besides the various task oriented quality metrics,  the quality-energy trade-off is also  concerned for approximate computing.

### 2018-09-23 ApproxComp/TKDE/sec-introduction.tex

--- 2018-09-23 ApproxComp/TKDE/sec-introduction.tex
@@
 Not only traditional DBMS systems, such as Oracle\footnote{\small \url{https://oracle-base.com/articles/12c/approximate-query} \url{-processing-12cr2}},  provide approximate functions to support approximate results, but also emerging new systems specially designed for approximate queries, such as BlinkDB\footnote{\small \url{http://blindb.org/}}, Verdict\footnote{\small \url{http://verdictdb.org/}}, Simba\footnote{\small \url{https://initialdlab.github.io/Simba/index.html}}, have been designed.
-However, as pointed out in~\cite{ChaudhuriDK17}, `` it seems impossible to have an AQP system that supports the richness of SQL with significant saving of work while providing an accuracy guarantee that is acceptable to a broad set of application workloads.''
+However, as pointed out in~\cite{ChaudhuriDK17}, `` it seems impossible to have an approximate query processing system that supports the richness of SQL with significant saving of work while providing an accuracy guarantee that is acceptable to a broad set of application workloads.''
 
@@
 Besides the various task oriented quality metrics,  the quality-energy trade-off is also  concerned for approximate computing.
-For example, in k-means clustering algorithm, allowing only 5\% loss in classification accuracy can provide 50 times energy saving compared with the fully accurate classification~\cite{Mittal16b}
+For instance, allowing only 5\% loss of classification accuracy can provide 50 times energy saving for clustering algorithm k-means~\cite{Mittal16b}
 \ei

### 2018-09-24 ApproxComp/TKDE/sec-data.tex

@@
 We next explain data approximation computation in more detail using three different data analytic tasks.
+
+\begin{figure}[tb!]
+  %\vspace{-1ex}
+  \begin{center}
+  \includegraphics[scale=0.45]{./dataApprox.png}
+  \end{center}
+  %\vspace{-1ex}
+  \caption{Data approximation}\label{fig-tech-dataappro}
+  \vspace{-1ex}
+\end{figure}
 
@@
 
-\begin{figure}[tb!]
-  %\vspace{-1ex}
-  \begin{center}
-  \includegraphics[scale=0.45]{./dataApprox.png}
-  \end{center}
-  %\vspace{-1ex}
-  \caption{Data approximation}\label{fig-tech-dataappro}
-  \vspace{-2ex}
-\end{figure}
-
 \stitle{(2) Network Anomaly Detection~\cite{HuAMH16}}
-Anomaly (or outlier) detection aims at identifying those objects in a database that are unusual, i.e., different than the majority of the data and therefore suspicious resulting from a contamination, error, or fraud~\cite{Zimek2017}.
+Anomaly (or outlier) detection aims at identifying those objects in a dataset that are unusual, i.e., different than the majority and therefore suspicious resulting from a contamination, error, or fraud~\cite{Zimek2017}.
 Network anomaly detection has become very popular
@@
 
-Dimensionality of embedding, each node is represented as a d-dimensional vector, can be large.
+For graph embedding, each node is represented as a d-dimensional vector, and the dimensionality $d$ can be large.
 Hence, such an approach is rather hard to apply to the case of large networks, because the complexity of the approach is in proportion to the square of the number of nodes when optimizing the embedding and because the noises in the embedding seriously impair the accuracy of detected anomalous nodes.

### 2018-09-24 ApproxComp/TKDE/sec-conclusion.tex

--- 2018-09-19 ApproxComp/TKDE/sec-conclusion.tex
@@
 theoretical bounds with respect to optimal solutions, it does expect a balance between efficiency and effectiveness.
-Indeed, (a) our query approximation techniques~\cite{tods-MaCFHW14,LinMZWH17,MaHWLH17} show that efficiency can be obtained with high accuracy in practice, and (b) our data approximation techniques for shortest paths/distances and link prediction~\cite{MaFLWCH16,DuanMAMH17} show that efficiency and accuracy can be obtained simultaneously for certain data analytic tasks.
-That is, the design policy of approximate computation is not to sacrifice effectiveness for efficiency, but to achieve both efficiency and effectiveness in practice.
+Indeed, (a) our query approximation techniques~\cite{ShuaiMaVLDB12,tods-MaCFHW14,LinMZWH17,MaHWLH17} show that efficiency can be obtained with high accuracy in practice, and (b) our data approximation techniques~\cite{MaFLWCH16,MaFLWCH17,HuAMH16,DuanAMHH16,DuanMAMH17} show that efficiency and accuracy can be obtained simultaneously for certain data analytic tasks.
+That is, though approximate computation is for a situation where an approximate result is sufficient for a purpose, its design policy is not always to sacrifice effectiveness for efficiency.
+
+%policy is not always to sacrifice effectiveness for efficiency.
+
+%approximate computation  the design policy of is not always to sacrifice effectiveness for efficiency, but to achieve both efficiency and effectiveness in practice for a situation where an approximate result is sufficient for a purpose.

### 2018-09-24 ApproxComp/TKDE/sec-data.tex

@@
 
-For graph embedding, each node is represented as a d-dimensional vector, and the dimensionality $d$ can be large.
+Each node in graph embedding is represented as a d-dimensional vector, and the dimensionality $d$ can be large.
 Hence, such an approach is rather hard to apply to the case of large networks, because the complexity of the approach is in proportion to the square of the number of nodes when optimizing the embedding and because the noises in the embedding seriously impair the accuracy of detected anomalous nodes.
-Hence, we incorporate data approximation techniques (sampling, graph partitioning techniques, and, moreover, a novel dimension reduction technique) to make the approach more scalable and effective for large networks.
+Hence, we incorporate data approximation techniques (sampling, graph partitioning, and, moreover, a novel dimension reduction technique) to make the approach more scalable and effective for large networks.
 

### 2018-09-24 ApproxComp/TKDE/coverletter.tex

--- 2018-01-27 ApproxComp/coverletter.tex
@@
 
-I would like to request you to consider the attached manuscript entitled ``Approximate Computation for Big Data Analytics'' for publication in Communications of the ACM  as a contributed article.
+I would like to request you to consider the attached manuscript entitled ``Approximate Computation for Big Data Analytics'' for publication in IEEE Transactions on Knowledge and Data Engineering a concise article.
 
@@
 No conflicts of interest exits in the submission of this manuscript, and this manuscript is approved by all authors for publication, and  all the authors listed have approved the manuscript that is enclosed.
-
-Below please find the names and email addresses of possessible appropriate reviewers:
-
-\bi
-\item[(1)] Prof. Sihem Amer-Yahia: Sihem.Amer-Yahia@imag.fr
-
-\item[(2)]  Prof. Evaggelia Pitoura: pitoura@cs.uoi.gr
-
-\item[(3)]  Prof. Lei Chen: leichen@cse.ust.hk
-
-\item[(4)]  Prof. Feifei Li: lifeifei@cs.utah.edu
-\ei
 
